### 2021-12-10 paper.tex
First commit; interim results from simulation

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Estimating survival in left filtered data: simulation and application},
  pdfauthor={Kevin Chen},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=2.54cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\PassOptionsToPackage{no-math}{fontspec}

%---------------------------------------------------------------------------
% Kevin's style file
%---------------------------------------------------------------------------
\usepackage{ifxetex,ifluatex}

%---------------------------------------------------------------------------
% General
%---------------------------------------------------------------------------

% When testing
% \usepackage{lipsum}

% Line numbering
\usepackage{lineno}

% Usage
	% \linenumbers
	% \modulolinenumbers[2]
	% \renewcommand\thelinenumber{\color{red}\Roman{linenumber}}
	% \begin{linenumbers}  \end{linenumbers}

\usepackage{setspace}
%\doublespacing

\usepackage{outlines}
% \usepackage{enumerate}
\usepackage{enumitem} % more powerful than enumerate
% \setenumerate[4]{label=\alph*).}

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\usepackage{sectsty} % Allows customizing section commands
% \renewcommand{\thesection}{\Alph{section}} % Lettered, not numbered sections
% \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
%\numberwithin{equation}{section} % Number equations within sections
%\numberwithin{figure}{section} % Number figures within sections
%\numberwithin{table}{section} % Number tables within sections

\usepackage{multicol}
\setlength{\columnsep}{15pt}
\newlength\Colsep

%---------------------------------------------------------------------------
% Tables, figures, images
%---------------------------------------------------------------------------
\usepackage{color}
% \usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xparse}
\usepackage{xhfill}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0
% Requires pdfTeX
\usepackage{linegoal}
\fi

\usepackage{longtable}
\setlength{\LTcapwidth}{\textwidth}
\usepackage{xtab, booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable} % Suzanne's

\usepackage{float} % Check code chunks section for floatrow

\usepackage{graphicx}
% \usepackage{grffile}
% \usepackage{subcaption}
% For tables and figures in parts %%%%
\usepackage{caption}
% \DeclareCaptionLabelFormat{cont}{#1~#2\alph{ContinuedFloat}}
% \captionsetup[ContinuedFloat]{labelformat=cont}
%\graphicspath{ {file.path.here} }

% Set column widths in tabular environment!
\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

% STATA output for `estout` package
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

%---------------------------------------------------------------------------
% Header/footer
%---------------------------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead[L]{}
\fancyhead[C]{}
\fancyhead[R]{}
% \fancyfoot[L]{}
% \fancyfoot[C]{}
% \fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{14.5pt}

%---------------------------------------------------------------------------
% Supplement (compatible for Beamer and Article)
%---------------------------------------------------------------------------
\input{\string~/HeadRs/common_supplement.tex}

%---------------------------------------------------------------------------
% Bibliography
%---------------------------------------------------------------------------
% \usepackage[backend=bibtex]{biblatex}

%---------------------------------------------------------------------------
% Usage
%---------------------------------------------------------------------------

% For use in LaTex or Sweave:
% \input{/Users/kevinchen/Documents/computing/HeadRs/StatHead.tex}

% An example YAML header for Rmd
% ---
% title: "Stat 2"
% author: "Kevin Chen"
% date: \today
% output:
%   pdf_document:
%      # keep_tex: true
%     #  pandoc_args: [
%     #   "-V", "classoption=twocolumn"
%     # ]
%      includes:
%         in_header: /Users/kevinchen/Documents/computing/HeadRs/StatHead.tex
% bibliography: /Users/kevinchen/Documents/2017 Fa/245/MV_FinalProj/mv_final.bib
% csl: /Users/kevinchen/Documents/computing/HeadRs/AMA.csl
% geometry: margin=2cm, bottom=2.5cm
% ---

%---------------------------------------------------------------------------
% Fonts
%---------------------------------------------------------------------------

%\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
%\usepackage[utf8]{inputenc}
% Latin Modern Roman
% \usepackage{lmodern}
%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default

\ifluatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For Arial (with lualatex)
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[no-math]{fontspec}
% \setmainfont{Arial}[
% % Options below necessary for Windows
% 	% Extension = .ttf,
% 	% UprightFont = *,
% 	% BoldFont = *bd,
% 	% ItalicFont = *i,
% 	% BoldItalicFont = *bi
% 	]
% In YAML
% ---
% mainfont: Arial
% ---
% \usepackage{lualatex-math}

% Math as text, but numerals do not mpa well becuase
% mathastext clahes with unicode-math
% \usepackage[italic]{mathastext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Estimating survival in left filtered data: simulation and
application}
\author{Kevin Chen}
\date{Stat 256: Causal Inference (Fall 2021)}

\begin{document}
\maketitle

\fancyhead[R]{Kevin Chen}
\fancyhead[L]{}
\renewcommand{\headrulewidth}{0pt}

\onehalfspacing
\renewcommand{\arraystretch}{1.1}

\thispagestyle{empty}

\setlength{\columnseprule}{0pt}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The United Auto Workers-General Motors (UAW-GM) Cohort Study is a
longitudinal occupational cohort study established in the early 1980s to
study the health effects of metalworking fluids (Eisen et al. 1992,
2001). Metalworking fluids (MWF) are complex mixtures of fluids used in
industrial metalworking operations to lubricate and cool machinery and
parts. The three major classes of MWF are straight, soluble, and
synthetic metalworking fluids (Byers 2006). Possible routes of human
exposure include absorption through skin, inhalation or aerosols, and
ingestion of droplets.

A central concern in the analysis of occupational cohorts is the
potential for the healthy worker survivor effect (HWSE), the phenomenon
by which healthy individuals remain at work, while less healthy
individuals leave work -- possibly in response to exposure-related
health decline. In the presence of the HWSE, those with the highest
cumulative occupational exposures are also those who are less at risk of
disease. Thus, standard measures of association would show an inverse
relationship between occupational exposure and poor health outcomes
(Arrighi and Hertz-Picciotto 1994). The HWSE is an example of
time-varying confounding affected by past exposure. Previous studies
have attempted to assess the presence of the HWSE in observed data by
assessing so-called path-specific associations using Cox proportional
hazards modeling (Naimi et al. 2013; Garcia et al. 2017). However, these
measures of associations are themselves subject to the confounding they
seek to quantify.

If sequential ignorability of exposure status at each point in follow-up
and positivity can be attained conditional on covariates, then causal
methods can be applied to account for the HWSE. Past studies have
applied causal methods capable of accounting for time-varying
confounding affected by past exposure to the study of MWF exposures and
cancer mortality outcomes in the UAW-GM Cohort Study (Garcia et al.
2018; Izano et al. 2019), but the study of cancer incidence outcomes is
further problematized by incomplete observation of cancer incidence
outcomes over the study period. We wish to make inferences about the
carcinogenicity of MWF exposure over an individual's lifetime starting
three years after they enter the workforce. The UAW-GM cohort includes
those hired roughly between 1938 and 1982. However, cancer incidence
reporting at the Michigan Cancer Registry did not begin until 1985. In
particular, we have the presence of \emph{left filtering} in the UAW-GM
Cohort Study when cancer incidence is the outcome of interest: before
1985, both cancer incidence status and time of cancer incidence are
unknown. Observation of the complete cancer incidence outcome vector
over the study period is conditional on an individual surviving to 1985
cancer-free.

In the presence of the HWSE, left filtering implies outcome
misclassification that is informative of true cancer status. As part of
her dissertation research, Izano (2017) conducted a quantitative bias
analysis for the estimation of survival curves in the presence of left
filtering and the HWSE. She simulated data compatible with the HWSE and
estimated cancer-free survival curves using an inverse probability of
treatment and censoring weighted Kaplan-Meier (WKM) estimator and the
WKM with an Aalen filter for left-filtering (AWKM) (Andersen et al.
1993; Xie and Liu 2005). Data were simulated under five different
scenarios. The causal estimands of interest were the survival curves
under interventions: (1) always exposed at work with no censoring due to
death and (2) never exposed at work with no censoring due to death. For
each intervention, three survival curves were produced: (1) the true
survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
The bias in mean survival difference calculated by AWKM was negligible
when the true 20-year risk of cancer was under 0.25.

Here, we replicate the simulation and bias analysis presented in Chapter
3 of Izano (2017), embed the problem in the non-parametric structural
causal approach of Pearl (1995), comment on the results, and apply the
WKM and AWKM estimators to the UAW-GM Cohort.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{causal-model}{%
\subsection{Causal model}\label{causal-model}}

The UAW-GM Cohort data includes person-year level exposure, outcome, and
covariate data starting three years after hire. To emulate the shape of
the data for this longitudinal cohort, we consider 20 years of data over
time indexed by years since hire. Notation representing the variables of
interest are presented in Table \ref{tab:variables}.

\begin{table}
\caption{Descriptions of variables.}\label{tab:variables}
\begin{center}
\begin{tabular}{lp{0.5\linewidth}}
\toprule
 Variable  &  Description                                 \\ \midrule
 $R$       & Time until start of registry \\
 $W$       & Baseline covariates \\
 $S$       & Susceptibility to effects of metalworking fluid exposure \\
 $H(t)$    & Adverse health status at time $t$ \\
 $N(t)$    & Employment status at time $t$ \\
 $A(t)$    & Metalworking fluid exposure at time $t$ \\
 $D(t)$    & Mortality status at time $t$ \\
 $Y^*(t)$  & Cancer status at time $t$ \\
 $Y(t)$    & Observed Cancer status at time $t$ \\
 $t = \{1, 2, \ldots, 20\}$ & Time, indexed in years after hire \\
 \bottomrule
\end{tabular}
\end{center}\end{table}

Assume we have \(n = 50\,000\) iid units in \(X\) with
\[X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).\]
The bar notation to indicates variable history where
\(\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t\). In the case of
exposure, \(\bar A_i(t)\) is the indicator of whether unit \(i\) was
ever exposed through time \(t\). Note that true cancer status \(Y^*(t)\)
not observed until \(t \ge R\), after the start of the registry. Call
\(X\) the full data, where we have \(R = 0\) for all. In the observed
data \(X^\text{obs}\), we cannot assume \(R = 0\) for all, and
susceptibility \(S\) is not known:
\[X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).\]
Under the causal model, we assume the following non-parametric
structural equations: \[\begin{aligned}
R     & = f_R \left( U_R \right) \\
W     & = f_W \left( U_W \right) \\
S     & = f_S \left( U_S \right) \\
H(t)  & = f_{H(t)} \left( H(t - 1), U_{H(t)} \right) \\
N(t)  & = f_{N(t)} \left( W, N(t - 1), H(t), A(t - 1), U_{N(t)} \right) \\
A(t)  & = f_{A(t)} \left( W, \bar A(t - 1), N(t), U_{A(t)} \right) \\
D(t)  & = f_{D(t)} \left( W, \bar A(t - 1), D(t - 1), Y^*(t - 1), U_{D(t)} \right) \\
Y^*(t)& = f_{Y^*(t)} \left(W, S, H(t), \bar A (t), D(t), Y^*(t - 1), U_{Y^*(t)} \right) \\
Y(t) & = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0} \ .
\end{aligned}\] The exogenous variables (errors)
\(U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}\)
are mutually independent. Exposure status is a time-varying indicator;
let exposure history \(\bar A(t)\) be summarized as being ever-exposed
or not with \(\bar A(t) = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}\). The
outcome of interest is a survival outcome, so
\(Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1\). The observed outcome \(Y(t)\)
at time \(t\) is a function of true outcome status and the time points
delimiting left and right censoring. An abbreviated directed acyclic
graph (DAG) representing the causal relationships encoded in the
equations above is presented in Figure \ref{fig:dag}.

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$.}
\label{fig:dag}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
\path[->] (W) edge [bend right=10] (N);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
\path[->] (A0) edge (N);
\path[->] (W) edge [bend right=15] (A);
\path[->] (A0) edge (A);
\path[->] (N) edge (A);
\path[->] (W) edge (D);
\path[->] (A0) edge [bend left=15] (D);
\path[->] (D0) edge [bend right=15] (D);
\path[->] (Y0) edge [bend right=10] (D);
\path[->] (W) edge [bend left=5] (Y);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

\hypertarget{simulation}{%
\subsection{Simulation}\label{simulation}}

Parametric relationships between the variables were imposed in
simulations. For the \(n = 50\,000\) units over \(T = 20\) years, we
have:

\begin{itemize}
\tightlist
\item
  \(U_j \overset{\text{iid}}{\sim} \text{uniform}\,[0,1]\) for all \(j\)
\item
  In full data \(R = 0\) otherwise \(R \sim \text{uniform}\,[0, 30]\)
\item
  \(W = \Ind{U_W \le p_W} \sim \text{Bernoulli}\left( p_W \right)\)
\item
  \(S = \Ind{U_S \le p_S} \sim \text{Bernoulli}\,(p_S)\)
\item
  If \(H(t - 1) = 1\), then \(H(t) = 1\) otherwise
  \(H(t) = \Ind{U_{H(t)} \le p_H} \sim \text{Bernoulli}\,(p_H)\)
\item
  if \(N(t - 1) = 0\) then \(N(t) = 0\) otherwise
  \[N(t) \sim \text{Bernoulli}\left\{
    \text{logit}\,\left(
        \beta_0^N
        + \beta_W^N W
        + \beta_H^N H(t)
        + \beta_A^N A(t - 1) \times \Ind{t > 1}
        + U_{N(t)}
    \right)
    \right\}\]
\item
  If \(N(t) = 0\) then \(A(t) = 0\) otherwise
  \[A(t) \sim \text{Bernoulli}\left\{
    \text{logit}\,\left(
        \left( \beta_0^A + \beta_W^A W\right) \times \Ind{t = 1}
        + \beta_A^A A(t - 1) \times \Ind{t > 1}
        + U_{A(t)}
    \right)
    \right\}\]
\item
  If \(D(t - 1) = 1\) then \(D(t) = 1\) otherwise
  \[D(t) \sim \text{Bernoulli}\left\{
    \text{logit}\,\left(\begin{aligned}
        \beta_0^D
        + \beta_W^D W
        + \beta_{\bar A}^D \bar A(t - 1) \times \Ind{t > 1} \\
        + \beta_{\bar Y}^D \sum_{k = 1}^{t - 1} Y^*(k) \times \Ind{t > 1}
        + U_{D(t)}
    \end{aligned}\right)
    \right\}\]
\item
  If \(Y^*(t - 1) = 1\) then \(Y^*(t) = 1\) otherwise
  \[Y^*(t) \sim \text{Bernoulli}\left\{
    \text{logit}\,\left(\begin{aligned}
        \beta_0^Y
        + \beta_W^Y W
        + \beta_{A}^Y A(t)
        + \beta_{\bar A}^Y \bar A(t - 1) \times \Ind{t > 1} \\
        + \beta_{S}^Y S \times \bar A(t)
        + \beta_{H}^Y H(t)
        + U_{Y^*(t)}
    \end{aligned}\right)
    \right\}\]
\item
  If \(t < R\) then \(Y(t) = 0\)
\item
  If \(t \ge R\) then
  \(Y(t) = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0}\).
\end{itemize}

Five sets of data were generated using these equations to represent five
scenarios. Scenario 1 represents the base case where 10\% of workers are
susceptible to exposure-related effects, the odds ratio of mortality
each additional year following cancer diagnosis is about 1.6, and there
is moderate time-varying confounding by health status. In scenario 2, we
have greater cancer-related mortality by increasing
\(\beta_{\bar Y}^D\). In scenario 3, we increase \(p_S\), the proportion
of the study population susceptible to the carcinogenic effects of MWF
exposure. In scenario 4, we consider greater time-varying confounding by
health status by increasing \(\beta_H^N\) and \(\beta_H^Y\). In the last
scenario, we have greater background cancer incidence by increasing
\(\beta_0^Y\). The sets of parameters used in the five scenarios are
presented in Table \ref{tab:params}.

\begin{table}
\caption{Simulation parameters.}
\label{tab:params}
\begin{center}
\begin{tabular}{rrrrrr}
  \toprule
Parameter & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
  \midrule
$p_S$ & 0.10 & 0.10 & \textbf{0.20} & 0.10 & 0.10 \\ 
  $p_W$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
  $p_H$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
  $\beta_0^N$ & 3.00 & 3.00 & 3.00 & 3.00 & 3.00 \\ 
  $\beta_W^N$ & -0.10 & -0.10 & -0.10 & -0.10 & -0.10 \\ 
  $\beta_H^N$ & -0.50 & -0.50 & -0.50 & \textbf{-1.50} & -0.50 \\ 
  $\beta_A^N$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
  $\beta_0^A$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
  $\beta_W^A$ & -0.50 & -0.50 & -0.50 & -0.50 & -0.50 \\ 
  $\beta_A^A$ & 2.50 & 2.50 & 2.50 & 2.50 & 2.50 \\ 
  $\beta_0^D$ & -5.50 & -5.50 & -5.50 & -5.50 & -5.50 \\ 
  $\beta_W^D$ & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
  $\beta_{\bar A}^D$ & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\ 
  $\beta_{\bar Y}^D$ & 0.50 & \textbf{2.00} & 0.50 & 0.50 & 0.50 \\ 
  $\beta_0^Y$ & -7.00 & -7.00 & -7.00 & -7.00 & \textbf{-6.00} \\ 
  $\beta_W^Y$ & 2.00 & 2.00 & 2.00 & 2.00 & 2.00 \\ 
  $\beta_A^Y$ & 0.25 & 0.25 & 0.25 & 0.25 & 0.25 \\ 
  $\beta_{\bar A}^Y$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
  $\beta_H^Y$ & 0.70 & 0.70 & 0.70 & \textbf{1.70} & 0.70 \\ 
  $\beta_S^Y$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
   \bottomrule
\end{tabular}
\end{center}
\end{table}

\hypertarget{interventions-potential-outcomes-target-parameters-and-estimation}{%
\subsection{Interventions, potential outcomes, target parameters, and
estimation}\label{interventions-potential-outcomes-target-parameters-and-estimation}}

The substantive question of interest is the causal effect of
occupational exposure to MWF on cancer incidence risk. Since
occupational MWF exposure occurs only when individuals are at work, we
define dynamic exposure regimes that depend on employment status. Under
rule \(a_0\), set \(D(t) = 0\), and set \(A(t) = 0\) while \(N(t) = 1\).
Under rule \(a_1\), set \(D(t) = 0\), and set \(A(t) = 1\) while
\(N(t) = 1\). Under both rules, we prevent censoring by death as if it
were intervenable. The causal effect is defined by contrasting the
survival function \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule \(a_1\)
to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\). Note
that this causal estimand is defined over \emph{a priori
counterfactuals} not observable in the real world (Frangakis and Rubin
2002). This approach is standard in epidemiologic studies, however.

The survival function expresses the probability that a person following
rule \(a\) is cancer-free at the end of time point \(t\). The expected
time until cancer under rule \(a\) is
\(\mu_{a} = \sum_0^K S_{a}(t) \, dt\). Our causal estimand is summary
measure \(\psi = \mu_{a_1} - \mu_{a_0}\), the difference in expected
time until event under two different interventions over 20 years of
follow-up under five different data generating scenarios. Bias will be
evaluated by comparing estimates of \(\psi\) to its true value in 250
simulations per scenario (the original analysis performed 500). The true
value will be calculated by simulating the full data for five hundred
thousand individuals (the original analysis used one million) with rules
\(a_0\) and \(a_1\) applied deterministically. Estimates of \(\psi\)
will be obtained by first estimating the survival curves \(S_a(t)\)
using two estimators: the inverse probability weighted Kaplan-Meier
estimator (WKM) and the Aalen-filtered WKM (AWKM). These survival
estimators are detailed in the following section.

\hypertarget{kaplan-meier-estimator-and-extensions}{%
\subsection{Kaplan-Meier estimator and
extensions}\label{kaplan-meier-estimator-and-extensions}}

To estimate survival, we applied extensions of the widely-known
Kaplan-Meier (KM) estimator for survival (Kaplan and Meier 1958). First,
we review the estimator of Xie and Liu (2005), an extension of the KM
estimator where units are weighted by the inverse probability of
treatment. The standard KM estimator requires counting up the number of
cases \(c^0_{a}(t)\) that occurred in interval \((t - 1, t]\) and the
number of units at risk \(R^0_{a}(t)\) in that interval at all event
times \(t\). Assuming cancer status was assessed at the end of regular
intervals \(t = 1, \ldots, K\), we have: \[\begin{aligned}
c^0_{a} (t)
& = \sum_i^n \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \\
R^0_{a} (t)
& = \sum_i^n \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}.
\end{aligned}\] The standard survival estimator is \[\hat S^0_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}\] where \(t_1\) is the first event time.

In observational studies, survival contrasts estimated using the
standard KM estimator are biased for the true causal survival contrast.
However, if conditional ignorability and positivity are attained, the
inverse probability weighted KM (WKM) estimator of Xie and Liu (2005)
yields unbiased estimates of the true causal survival curve. The WKM
estimator augments the standard KM estimator by weighting units at time
\(t\) by \(w_{i, a}(t)\) the inverse probability of treatment:
\[\begin{aligned}
c^w_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}\\
R^w_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}
\end{aligned}\] The WKM survival estimator for rule \(a\) is
\[\hat S^w_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c^w_{a}(j)}{R^w_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}\] where \(t_1\) is the first event time.

Finally, to account for (uninformative) left filtering, we applied the
Aalen filter, which considers only the units at time \(t\) for which the
outcome is observed: \[\begin{aligned}
c_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
R_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
\end{aligned}\] The Aalen-filtered WKM (AWKM) estimator for rule \(a\)
is \[\hat S_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}\] where \(t_1\) is the first event time.

In the full data, the WKM and AWKM estimators are equivalent, and
identification is achieved under overlap (positivity) and sequential
ignorability (randomization) assumptions: \[\begin{aligned}
Y^*_{a, \bar d = 0} (t')   & \indep A(t) \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1\\
Y^*_{a, \bar d = 0} (t') & \indep D(t) \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)
\end{aligned}\] for all times \(t'\ge t\), and
\[0 < \Prob{ A(t) = 1 \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1} < 1\]
\[0 < \Prob{D(t) = 0 \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)} < 1.\]

Graphical representations of the first and second components of the
ignorability assumption are presented in Figures
\ref{fig:ignorability_a} and \ref{fig:ignorability_d} where conditioning
on boxed variables are represented by the removal of edges pointing away
from those variables. The resulting graphs show the fulfillment of
Pearl's backdoor criterion for the estimation of the causal effects of
\(\bar A(t)\) on \(Y^*(t)\) and \(D(t)\) on \(Y^*(t)\), respectively.
Thus, the causal effect of the joint intervention on
\(\big(\bar A(t), D(t)\big)\) at each time \(t\) is identified. Causal
identification is not attained when true cancer status \(Y^*(t)\) is not
known.

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ N(t)\}$.}
\label{fig:ignorability_a}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [shape=rectangle, draw=black, inner sep=2.5pt, above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
\path[->] (Y0) edge [bend right=10] (D);
\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ Y^*(t - 1)\}$.}
\label{fig:ignorability_d}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [shape=rectangle, draw=black, inner sep=2pt, below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [shape=rectangle, draw=black, inner sep=2pt, below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [shape=rectangle, draw=black, inner sep=2pt, below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [shape=rectangle, draw=black, inner sep=2pt, above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
%\path[->] (W) edge [bend right=10] (N);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
%\path[->] (A0) edge (N);
%\path[->] (W) edge [bend right=15] (A);
%\path[->] (A0) edge (A);
\path[->] (N) edge (A);
%\path[->] (W) edge (D);
%\path[->] (A0) edge [bend left=15] (D);
%\path[->] (D0) edge [bend right=15] (D);
%\path[->] (Y0) edge [bend right=10] (D);
%\path[->] (W) edge [bend left=5] (Y);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
%\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

\hypertarget{estimation-of-weights}{%
\subsection{Estimation of weights}\label{estimation-of-weights}}

To estimate the weights for the WKM and AWKM estimators, we fit two
logistic regressions at each time point \(t = 1, \ldots 20\):
\[\begin{aligned}
\text{logit} \left(\Prob{
    A(t) = 1
    \mid W,\ \bar A(t - 1),\ D(t - 1) = 0,\ N(t) = 1
    }\right)
& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
\text{logit} \left(\Prob{
    D(t) = 1
    \mid W,\ D(t - 1) = 0,\ Y(t - 1) = 0,\ \bar A(t - 1)}\right)
    & = \beta_0 + W \beta_1 + \bar A(t - 1) \beta_2
\end{aligned}\] The first will be fitted on data for those alive and at
work at time \(t\). The second will be among those alive and (observed
to be) cancer-free. For each unit at time \(t\), the weight will be
calculated by taking the inverse of the cumulative probability of
following the exposure rule and remaining uncensored: \[\hat w_{a} (t) =
    \left[
    \prod^t_{j = 1}
    \begin{aligned}
    \widehat {\mathbb P} \left\{
    A(j) = a(j) \mid W,\ \bar A(j - 1) = \bar a (j - 1),\ D(j - 1) = 0,\ N(j) = 1
    \right\} \times \\
    \widehat {\mathbb P} \left\{D(j) = 0
    \mid W,\ D(j - 1) = 0,\ Y(j - 1) = 0,\ \bar A(j) = \bar a (j) \right\}
    \end{aligned}\right]^{-1}.\]

\hypertarget{results}{%
\section{Results}\label{results}}

Figure \ref{fig:survival} presents the true survival curves as well as
the WKM and AWKM survival curves averaged over 250 replications for each
intervention rule and scenario. Qualitatively, the WKM estimator
consistently over-estimates survival whereas the the AWKM survival curve
is much closer to the truth. The bias of the AWKM survival estimate
appears to be larger earlier in follow-up and smaller as follow-up
extends forward. The bias of both the the WKM and the AWKM survival
curves appears largest in Scenario 5.

\begin{figure}
\caption{Cancer-free survival over time since hire in five simulation scenarios. The true (discrete) survival curve is represented by the solid lines. The average inverse probability weighted Kaplan-Meier (WKM) survival curve is represented by the dashed-line with short dashes. The average Aalen-filtered inverse probability weighted Kaplan-Meier (AWKM) survival curve is represented by the dashed-line with long dashes. Estimated survival curves were averaged over 250 replicates. Salmon color indicates survival and survival estimates under rule $a_0$ when workers are always unexposed. Cyan color indicates those under rule $a_1$ when workers are always exposed while employed.}
\label{fig:survival}
\begin{center}
\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/results.pdf}
\end{center}
\end{figure}

Table \ref{tab:survival} presents true and estimated average cancer-free
survival times under each intervention rule and scenario. Table
\ref{tab:differences} presents differences in survival time contrasting
rule \(a_1\) to rule \(a_0\). Table \ref{tab:bias} presents estimates of
the bias of the WKM and AWKM estimators for \(\psi\), the difference in
average cancer-free survival time over 20 years of follow-up. These
numeric results are consistent with the qualitative interpretations of
Figure \ref{fig:survival}. The WKM estimator over-estimates the
difference in cancer-free survival time, resulting in bias toward the
null, whereas the AWKM estimator under-estimates the cancer-free
survival, resulting in bias away from the null. In every scenario, the
bias of the WKM-derived contrast is several times larger in magnitude
than that of the AWKM-derived contrast. The bias of both estimators is
greatest for Scenario 5.

The qualitative results here are consistent with those of Izano (2017).
However, true and estimated survival in the present analysis is larger
than those found previously. Furthermore, the true and estimator average
mean differences in survival are smaller in magnitude in the present
case. The magnitudes of the bias estimates are also smaller.

\begin{table}[H]
\centering
\caption{True cancer-free survival time $\mu_{a}$ over 20-year follow-up and estimator averages over 250 replicates.} 
\label{tab:survival}
\begin{tabular}{llrrrrr}
  \toprule
Rule & Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
  \midrule
$a_0$ & Truth & 19.08 & 19.10 & 19.10 & 18.02 & 17.83 \\ 
   & WKM & 19.52 & 19.51 & 19.53 & 18.92 & 18.90 \\ 
   & AWKM & 19.02 & 19.00 & 19.02 & 17.79 & 17.72 \\ 
   \midrule
$a_1$ & Truth & 18.80 & 18.79 & 18.76 & 17.54 & 17.29 \\ 
   & WKM & 19.39 & 19.37 & 19.37 & 18.68 & 18.62 \\ 
   & AWKM & 18.70 & 18.67 & 18.67 & 17.30 & 17.07 \\ 
   \bottomrule
\end{tabular}
\end{table}
\begin{table}[H]
\centering
\caption{Difference in average cancer-free survival time over 20-year follow-up comparing rule $a_1$ always exposed to rule $a_0$ never exposed at work: true value $\psi$ and estimator averages over 250 replicates.} 
\label{tab:differences}
\begin{tabular}{lrrrrr}
  \toprule
Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
  \midrule
Truth & -0.28 & -0.31 & -0.34 & -0.48 & -0.54 \\ 
  WKM & -0.14 & -0.15 & -0.15 & -0.23 & -0.28 \\ 
  AWKM & -0.31 & -0.33 & -0.35 & -0.50 & -0.64 \\ 
   \bottomrule
\end{tabular}
\end{table}
\begin{table}[H]
\centering
\caption{Bias estimates of estimators for $\psi$, the difference in average cancer-free survival time over 20 years of follow-up.} 
\label{tab:bias}
\begin{tabular}{lrrrrr}
  \toprule
Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
  \midrule
WKM & 0.14 & 0.16 & 0.19 & 0.25 & 0.26 \\ 
  AWKM & -0.03 & -0.02 & -0.01 & -0.02 & -0.10 \\ 
   \bottomrule
\end{tabular}
\end{table}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Andersen_1993}{}%
Andersen, P. K., Ø. Borgan, R. D. Gill, and N. Keiding. 1993.
\emph{Statistical Models Based on Counting Processes}. Springer Series
in Statistics. Springer, New York, NY.
\url{https://books.google.com/books?id=kBnvAAAAMAAJ}.

\leavevmode\hypertarget{ref-Arrighi_1994}{}%
Arrighi, H. Michael, and Irva Hertz-Picciotto. 1994. {``The Evolving
Concept of the Healthy Worker Survivor Effect.''} \emph{Epidemiology} 5
(2): 189--96. \url{http://www.jstor.org/stable/3702361}.

\leavevmode\hypertarget{ref-Byers_2006}{}%
Byers, Jerry P. 2006. \emph{Metalworking Fluids}. CRC Press.

\leavevmode\hypertarget{ref-Eisen_2001}{}%
Eisen, Ellen A, Judith Bardin, Rebecca Gore, Susan R Woskie, Marilyn F
Hallock, and Richard R Monson. 2001. {``Exposure-Response Models Based
on Extended Follow-up of a Cohort Mortality Study in the Automobile
Industry.''} \emph{Scandinavian Journal of Work, Environment \& Health}
27 (4): 240--49.

\leavevmode\hypertarget{ref-Eisen_1992}{}%
Eisen, Ellen A, Paige E Tolbert, Richard R Monson, and Thomas J Smith.
1992. {``Mortality Studies of Machining Fluid Exposure in the Automobile
Industry {I}: A Standardized Mortality Ratio Analysis.''} \emph{American
Journal of Industrial Medicine} 22 (6): 809--24.

\leavevmode\hypertarget{ref-Frangakis_2002}{}%
Frangakis, Constantine E, and Donald B Rubin. 2002. {``Principal
Stratification in Causal Inference.''} \emph{Biometrics} 58 (1): 21--29.

\leavevmode\hypertarget{ref-Garcia_2017}{}%
Garcia, Erika, Sally Picciotto, Sadie Costello, Patrick T Bradshaw, and
Ellen A Eisen. 2017. {``Assessment of the Healthy Worker Survivor Effect
in Cancer Studies of the United Autoworkers-General Motors Cohort.''}
\emph{Occupational and Environmental Medicine} 74 (4): 294--300.

\leavevmode\hypertarget{ref-Garcia_2018}{}%
Garcia, Erika, Sally Picciotto, Andreas M Neophytou, Patrick T Bradshaw,
John R Balmes, and Ellen A Eisen. 2018. {``Lung Cancer Mortality and
Exposure to Synthetic Metalworking Fluid and Biocides: Controlling for
the Healthy Worker Survivor Effect.''} \emph{Occupational and
Environmental Medicine} 75 (10): 730--35.

\leavevmode\hypertarget{ref-Izano_2017_thesis}{}%
Izano, Monika A. 2017. {``Estimating Causal Effects of Occupational
Exposures.''} PhD thesis, University of California, Berkeley; University
of California, Berkeley.

\leavevmode\hypertarget{ref-Izano_2019}{}%
Izano, Monika A, Oleg A Sofrygin, Sally Picciotto, Patrick T Bradshaw,
and Ellen A Eisen. 2019. {``Metalworking Fluids and Colon Cancer Risk:
Longitudinal Targeted Minimum Loss-Based Estimation.''}
\emph{Environmental Epidemiology} 3 (1): e035.

\leavevmode\hypertarget{ref-Kaplan_1958}{}%
Kaplan, Edward L, and Paul Meier. 1958. {``Nonparametric Estimation from
Incomplete Observations.''} \emph{Journal of the American Statistical
Association} 53 (282): 457--81.

\leavevmode\hypertarget{ref-Naimi_2013}{}%
Naimi, Ashley I, Stephen R Cole, Michael G Hudgens, M Alan Brookhart,
and David B Richardson. 2013. {``Assessing the Component Associations of
the Healthy Worker Survivor Bias: Occupational Asbestos Exposure and
Lung Cancer Mortality.''} \emph{Annals of Epidemiology} 23 (6): 334--41.

\leavevmode\hypertarget{ref-Pearl_1995}{}%
Pearl, Judea. 1995. {``Causal Diagrams for Empirical Research.''}
\emph{Biometrika} 82 (4): 669--88.

\leavevmode\hypertarget{ref-Xie_2005}{}%
Xie, Jun, and Chaofeng Liu. 2005. {``Adjusted Kaplan--Meier Estimator
and Log-Rank Test with Inverse Probability of Treatment Weighting for
Survival Data.''} \emph{Statistics in Medicine} 24 (20): 3089--3110.

\end{CSLReferences}

\end{document}

### 2021-12-10 reports/01-introduction.Rmd
First commit; interim results from simulation

--- 2021-12-10 paper.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  11pt,
-]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Estimating survival in left filtered data: simulation and application},
-  pdfauthor={Kevin Chen},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=2.54cm]{geometry}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\PassOptionsToPackage{no-math}{fontspec}
+---
+output:
+  pdf_document:
+    includes:
+      in_header: "~/headRs/StatHead.sty"
+fontsize: 11pt
+bibliography: "../../causal.bib"
+# csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
+---
 
-%---------------------------------------------------------------------------
-% Kevin's style file
-%---------------------------------------------------------------------------
-\usepackage{ifxetex,ifluatex}
+# Introduction
 
-%---------------------------------------------------------------------------
-% General
-%---------------------------------------------------------------------------
+The United Auto Workers-General Motors (UAW-GM) Cohort Study is a longitudinal occupational cohort study established in the early 1980s to study the health effects of metalworking fluids [@Eisen_1992;@Eisen_2001].
+Metalworking fluids (MWF) are complex mixtures of fluids used in industrial metalworking operations to lubricate and cool machinery and parts.
+The three major classes of MWF are straight, soluble, and synthetic metalworking fluids [@Byers_2006].
+Possible routes of human exposure include absorption through skin, inhalation or aerosols, and ingestion of droplets.
 
-% When testing
-% \usepackage{lipsum}
+A central concern in the analysis of occupational cohorts is the potential for the healthy worker survivor effect (HWSE), the phenomenon by which healthy individuals remain at work, while less healthy individuals leave work -- possibly in response to exposure-related health decline.
+In the presence of the HWSE, those with the highest cumulative occupational exposures are also those who are less at risk of disease.
+Thus, standard measures of association would show an inverse relationship between occupational exposure and poor health outcomes [@Arrighi_1994].
+The HWSE is an example of time-varying confounding affected by past exposure.
+Previous studies have attempted to assess the presence of the HWSE in observed data by assessing so-called path-specific associations using Cox proportional hazards modeling [@Naimi_2013;@Garcia_2017].
+However, these measures of associations are themselves subject to the confounding they seek to quantify.
 
-% Line numbering
-\usepackage{lineno}
+If sequential ignorability of exposure status at each point in follow-up and positivity can be attained conditional on covariates, then causal methods can be applied to account for the HWSE.
+Past studies have applied causal methods capable of accounting for time-varying confounding affected by past exposure to the study of MWF exposures and cancer mortality outcomes in the UAW-GM Cohort Study [@Garcia_2018;@Izano_2019], but the study of cancer incidence outcomes is further problematized by incomplete observation of cancer incidence outcomes over the study period.
+We wish to make inferences about the carcinogenicity of MWF exposure over an individual's lifetime starting three years after they enter the workforce.
+The UAW-GM Cohort includes those hired roughly between 1938 and 1982.
+However, cancer incidence reporting at the Michigan Cancer Registry did not begin until 1985.
+In particular, we have the presence of _left filtering_ in the UAW-GM Cohort Study when cancer incidence is the outcome of interest: before 1985, both cancer incidence status and time of cancer incidence are unknown.
+Observation of the complete cancer incidence outcome vector over the study period is conditional on an individual surviving to 1985 cancer-free.
 
-% Usage
-	% \linenumbers
-	% \modulolinenumbers[2]
-	% \renewcommand\thelinenumber{\color{red}\Roman{linenumber}}
-	% \begin{linenumbers}  \end{linenumbers}
+In the presence of the HWSE, left filtering implies outcome misclassification that is informative of true cancer status.
+As part of her dissertation research, @Izano_2017_thesis conducted a quantitative bias analysis for the estimation of survival curves in the presence of left filtering and the HWSE.
+She simulated data compatible with the HWSE and estimated cancer-free survival curves using an inverse probability of treatment and censoring weighted Kaplan-Meier (WKM) estimator and the WKM with an Aalen filter for left-filtering (AWKM) [@Andersen_1993;@Xie_2005].
+Data were simulated under five different scenarios.
+The causal estimands of interest were the survival curves under interventions: (1) always exposed at work with no censoring due to death and (2) never exposed at work with no censoring due to death.
+For each intervention, three survival curves were produced: (1) the true survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
+The bias in mean survival difference calculated by AWKM was negligible when the true 20-year risk of cancer was under 0.25.
 
-\usepackage{setspace}
-%\doublespacing
-
-\usepackage{outlines}
-% \usepackage{enumerate}
-\usepackage{enumitem} % more powerful than enumerate
-% \setenumerate[4]{label=\alph*).}
-
-\setlength\parindent{0pt} % Removes all indentation from paragraphs
-
-\usepackage{sectsty} % Allows customizing section commands
-% \renewcommand{\thesection}{\Alph{section}} % Lettered, not numbered sections
-% \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
-%\numberwithin{equation}{section} % Number equations within sections
-%\numberwithin{figure}{section} % Number figures within sections
-%\numberwithin{table}{section} % Number tables within sections
-
-\usepackage{multicol}
-\setlength{\columnsep}{15pt}
-\newlength\Colsep
-
-%---------------------------------------------------------------------------
-% Tables, figures, images
-%---------------------------------------------------------------------------
-\usepackage{color}
-% \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{xparse}
-\usepackage{xhfill}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0
-% Requires pdfTeX
-\usepackage{linegoal}
-\fi
-
-\usepackage{longtable}
-\setlength{\LTcapwidth}{\textwidth}
-\usepackage{xtab, booktabs}
-\usepackage{multirow}
-\usepackage[flushleft]{threeparttable} % Suzanne's
-
-\usepackage{float} % Check code chunks section for floatrow
-
-\usepackage{graphicx}
-% \usepackage{grffile}
-% \usepackage{subcaption}
-% For tables and figures in parts %%%%
-\usepackage{caption}
-% \DeclareCaptionLabelFormat{cont}{#1~#2\alph{ContinuedFloat}}
-% \captionsetup[ContinuedFloat]{labelformat=cont}
-%\graphicspath{ {file.path.here} }
-
-% Set column widths in tabular environment!
-\usepackage{array}
-\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
-\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
-\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
-\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
-
-% STATA output for `estout` package
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-
-%---------------------------------------------------------------------------
-% Header/footer
-%---------------------------------------------------------------------------
-\usepackage{fancyhdr}
-\pagestyle{fancyplain}
-\fancyhead[L]{}
-\fancyhead[C]{}
-\fancyhead[R]{}
-% \fancyfoot[L]{}
-% \fancyfoot[C]{}
-% \fancyfoot[R]{\thepage}
-\renewcommand{\headrulewidth}{0pt}
-% \renewcommand{\footrulewidth}{0pt}
-\setlength{\headheight}{14.5pt}
-
-%---------------------------------------------------------------------------
-% Supplement (compatible for Beamer and Article)
-%---------------------------------------------------------------------------
-\input{\string~/HeadRs/common_supplement.tex}
-
-%---------------------------------------------------------------------------
-% Bibliography
-%---------------------------------------------------------------------------
-% \usepackage[backend=bibtex]{biblatex}
-
-%---------------------------------------------------------------------------
-% Usage
-%---------------------------------------------------------------------------
-
-% For use in LaTex or Sweave:
-% \input{/Users/kevinchen/Documents/computing/HeadRs/StatHead.tex}
-
-% An example YAML header for Rmd
-% ---
-% title: "Stat 2"
-% author: "Kevin Chen"
-% date: \today
-% output:
-%   pdf_document:
-%      # keep_tex: true
-%     #  pandoc_args: [
-%     #   "-V", "classoption=twocolumn"
-%     # ]
-%      includes:
-%         in_header: /Users/kevinchen/Documents/computing/HeadRs/StatHead.tex
-% bibliography: /Users/kevinchen/Documents/2017 Fa/245/MV_FinalProj/mv_final.bib
-% csl: /Users/kevinchen/Documents/computing/HeadRs/AMA.csl
-% geometry: margin=2cm, bottom=2.5cm
-% ---
-
-%---------------------------------------------------------------------------
-% Fonts
-%---------------------------------------------------------------------------
-
-%\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-%\usepackage[utf8]{inputenc}
-% Latin Modern Roman
-% \usepackage{lmodern}
-%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
-
-\ifluatex
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% For Arial (with lualatex)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[no-math]{fontspec}
-% \setmainfont{Arial}[
-% % Options below necessary for Windows
-% 	% Extension = .ttf,
-% 	% UprightFont = *,
-% 	% BoldFont = *bd,
-% 	% ItalicFont = *i,
-% 	% BoldItalicFont = *bi
-% 	]
-% In YAML
-% ---
-% mainfont: Arial
-% ---
-% \usepackage{lualatex-math}
-
-% Math as text, but numerals do not mpa well becuase
-% mathastext clahes with unicode-math
-% \usepackage[italic]{mathastext}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Estimating survival in left filtered data: simulation and
-application}
-\author{Kevin Chen}
-\date{Stat 256: Causal Inference (Fall 2021)}
-
-\begin{document}
-\maketitle
-
-\fancyhead[R]{Kevin Chen}
-\fancyhead[L]{}
-\renewcommand{\headrulewidth}{0pt}
-
-\onehalfspacing
-\renewcommand{\arraystretch}{1.1}
-
-\thispagestyle{empty}
-
-\setlength{\columnseprule}{0pt}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The United Auto Workers-General Motors (UAW-GM) Cohort Study is a
-longitudinal occupational cohort study established in the early 1980s to
-study the health effects of metalworking fluids (Eisen et al. 1992,
-2001). Metalworking fluids (MWF) are complex mixtures of fluids used in
-industrial metalworking operations to lubricate and cool machinery and
-parts. The three major classes of MWF are straight, soluble, and
-synthetic metalworking fluids (Byers 2006). Possible routes of human
-exposure include absorption through skin, inhalation or aerosols, and
-ingestion of droplets.
-
-A central concern in the analysis of occupational cohorts is the
-potential for the healthy worker survivor effect (HWSE), the phenomenon
-by which healthy individuals remain at work, while less healthy
-individuals leave work -- possibly in response to exposure-related
-health decline. In the presence of the HWSE, those with the highest
-cumulative occupational exposures are also those who are less at risk of
-disease. Thus, standard measures of association would show an inverse
-relationship between occupational exposure and poor health outcomes
-(Arrighi and Hertz-Picciotto 1994). The HWSE is an example of
-time-varying confounding affected by past exposure. Previous studies
-have attempted to assess the presence of the HWSE in observed data by
-assessing so-called path-specific associations using Cox proportional
-hazards modeling (Naimi et al. 2013; Garcia et al. 2017). However, these
-measures of associations are themselves subject to the confounding they
-seek to quantify.
-
-If sequential ignorability of exposure status at each point in follow-up
-and positivity can be attained conditional on covariates, then causal
-methods can be applied to account for the HWSE. Past studies have
-applied causal methods capable of accounting for time-varying
-confounding affected by past exposure to the study of MWF exposures and
-cancer mortality outcomes in the UAW-GM Cohort Study (Garcia et al.
-2018; Izano et al. 2019), but the study of cancer incidence outcomes is
-further problematized by incomplete observation of cancer incidence
-outcomes over the study period. We wish to make inferences about the
-carcinogenicity of MWF exposure over an individual's lifetime starting
-three years after they enter the workforce. The UAW-GM cohort includes
-those hired roughly between 1938 and 1982. However, cancer incidence
-reporting at the Michigan Cancer Registry did not begin until 1985. In
-particular, we have the presence of \emph{left filtering} in the UAW-GM
-Cohort Study when cancer incidence is the outcome of interest: before
-1985, both cancer incidence status and time of cancer incidence are
-unknown. Observation of the complete cancer incidence outcome vector
-over the study period is conditional on an individual surviving to 1985
-cancer-free.
-
-In the presence of the HWSE, left filtering implies outcome
-misclassification that is informative of true cancer status. As part of
-her dissertation research, Izano (2017) conducted a quantitative bias
-analysis for the estimation of survival curves in the presence of left
-filtering and the HWSE. She simulated data compatible with the HWSE and
-estimated cancer-free survival curves using an inverse probability of
-treatment and censoring weighted Kaplan-Meier (WKM) estimator and the
-WKM with an Aalen filter for left-filtering (AWKM) (Andersen et al.
-1993; Xie and Liu 2005). Data were simulated under five different
-scenarios. The causal estimands of interest were the survival curves
-under interventions: (1) always exposed at work with no censoring due to
-death and (2) never exposed at work with no censoring due to death. For
-each intervention, three survival curves were produced: (1) the true
-survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
-The bias in mean survival difference calculated by AWKM was negligible
-when the true 20-year risk of cancer was under 0.25.
-
-Here, we replicate the simulation and bias analysis presented in Chapter
-3 of Izano (2017), embed the problem in the non-parametric structural
-causal approach of Pearl (1995), comment on the results, and apply the
-WKM and AWKM estimators to the UAW-GM Cohort.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{causal-model}{%
-\subsection{Causal model}\label{causal-model}}
-
-The UAW-GM Cohort data includes person-year level exposure, outcome, and
-covariate data starting three years after hire. To emulate the shape of
-the data for this longitudinal cohort, we consider 20 years of data over
-time indexed by years since hire. Notation representing the variables of
-interest are presented in Table \ref{tab:variables}.
-
-\begin{table}
-\caption{Descriptions of variables.}\label{tab:variables}
-\begin{center}
-\begin{tabular}{lp{0.5\linewidth}}
-\toprule
- Variable  &  Description                                 \\ \midrule
- $R$       & Time until start of registry \\
- $W$       & Baseline covariates \\
- $S$       & Susceptibility to effects of metalworking fluid exposure \\
- $H(t)$    & Adverse health status at time $t$ \\
- $N(t)$    & Employment status at time $t$ \\
- $A(t)$    & Metalworking fluid exposure at time $t$ \\
- $D(t)$    & Mortality status at time $t$ \\
- $Y^*(t)$  & Cancer status at time $t$ \\
- $Y(t)$    & Observed Cancer status at time $t$ \\
- $t = \{1, 2, \ldots, 20\}$ & Time, indexed in years after hire \\
- \bottomrule
-\end{tabular}
-\end{center}\end{table}
-
-Assume we have \(n = 50\,000\) iid units in \(X\) with
-\[X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).\]
-The bar notation to indicates variable history where
-\(\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t\). In the case of
-exposure, \(\bar A_i(t)\) is the indicator of whether unit \(i\) was
-ever exposed through time \(t\). Note that true cancer status \(Y^*(t)\)
-not observed until \(t \ge R\), after the start of the registry. Call
-\(X\) the full data, where we have \(R = 0\) for all. In the observed
-data \(X^\text{obs}\), we cannot assume \(R = 0\) for all, and
-susceptibility \(S\) is not known:
-\[X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).\]
-Under the causal model, we assume the following non-parametric
-structural equations: \[\begin{aligned}
-R     & = f_R \left( U_R \right) \\
-W     & = f_W \left( U_W \right) \\
-S     & = f_S \left( U_S \right) \\
-H(t)  & = f_{H(t)} \left( H(t - 1), U_{H(t)} \right) \\
-N(t)  & = f_{N(t)} \left( W, N(t - 1), H(t), A(t - 1), U_{N(t)} \right) \\
-A(t)  & = f_{A(t)} \left( W, \bar A(t - 1), N(t), U_{A(t)} \right) \\
-D(t)  & = f_{D(t)} \left( W, \bar A(t - 1), D(t - 1), Y^*(t - 1), U_{D(t)} \right) \\
-Y^*(t)& = f_{Y^*(t)} \left(W, S, H(t), \bar A (t), D(t), Y^*(t - 1), U_{Y^*(t)} \right) \\
-Y(t) & = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0} \ .
-\end{aligned}\] The exogenous variables (errors)
-\(U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}\)
-are mutually independent. Exposure status is a time-varying indicator;
-let exposure history \(\bar A(t)\) be summarized as being ever-exposed
-or not with \(\bar A(t) = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}\). The
-outcome of interest is a survival outcome, so
-\(Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1\). The observed outcome \(Y(t)\)
-at time \(t\) is a function of true outcome status and the time points
-delimiting left and right censoring. An abbreviated directed acyclic
-graph (DAG) representing the causal relationships encoded in the
-equations above is presented in Figure \ref{fig:dag}.
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$.}
-\label{fig:dag}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-\path[->] (W) edge [bend right=10] (N);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-\path[->] (A0) edge (N);
-\path[->] (W) edge [bend right=15] (A);
-\path[->] (A0) edge (A);
-\path[->] (N) edge (A);
-\path[->] (W) edge (D);
-\path[->] (A0) edge [bend left=15] (D);
-\path[->] (D0) edge [bend right=15] (D);
-\path[->] (Y0) edge [bend right=10] (D);
-\path[->] (W) edge [bend left=5] (Y);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\hypertarget{simulation}{%
-\subsection{Simulation}\label{simulation}}
-
-Parametric relationships between the variables were imposed in
-simulations. For the \(n = 50\,000\) units over \(T = 20\) years, we
-have:
-
-\begin{itemize}
-\tightlist
-\item
-  \(U_j \overset{\text{iid}}{\sim} \text{uniform}\,[0,1]\) for all \(j\)
-\item
-  In full data \(R = 0\) otherwise \(R \sim \text{uniform}\,[0, 30]\)
-\item
-  \(W = \Ind{U_W \le p_W} \sim \text{Bernoulli}\left( p_W \right)\)
-\item
-  \(S = \Ind{U_S \le p_S} \sim \text{Bernoulli}\,(p_S)\)
-\item
-  If \(H(t - 1) = 1\), then \(H(t) = 1\) otherwise
-  \(H(t) = \Ind{U_{H(t)} \le p_H} \sim \text{Bernoulli}\,(p_H)\)
-\item
-  if \(N(t - 1) = 0\) then \(N(t) = 0\) otherwise
-  \[N(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(
-        \beta_0^N
-        + \beta_W^N W
-        + \beta_H^N H(t)
-        + \beta_A^N A(t - 1) \times \Ind{t > 1}
-        + U_{N(t)}
-    \right)
-    \right\}\]
-\item
-  If \(N(t) = 0\) then \(A(t) = 0\) otherwise
-  \[A(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(
-        \left( \beta_0^A + \beta_W^A W\right) \times \Ind{t = 1}
-        + \beta_A^A A(t - 1) \times \Ind{t > 1}
-        + U_{A(t)}
-    \right)
-    \right\}\]
-\item
-  If \(D(t - 1) = 1\) then \(D(t) = 1\) otherwise
-  \[D(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(\begin{aligned}
-        \beta_0^D
-        + \beta_W^D W
-        + \beta_{\bar A}^D \bar A(t - 1) \times \Ind{t > 1} \\
-        + \beta_{\bar Y}^D \sum_{k = 1}^{t - 1} Y^*(k) \times \Ind{t > 1}
-        + U_{D(t)}
-    \end{aligned}\right)
-    \right\}\]
-\item
-  If \(Y^*(t - 1) = 1\) then \(Y^*(t) = 1\) otherwise
-  \[Y^*(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(\begin{aligned}
-        \beta_0^Y
-        + \beta_W^Y W
-        + \beta_{A}^Y A(t)
-        + \beta_{\bar A}^Y \bar A(t - 1) \times \Ind{t > 1} \\
-        + \beta_{S}^Y S \times \bar A(t)
-        + \beta_{H}^Y H(t)
-        + U_{Y^*(t)}
-    \end{aligned}\right)
-    \right\}\]
-\item
-  If \(t < R\) then \(Y(t) = 0\)
-\item
-  If \(t \ge R\) then
-  \(Y(t) = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0}\).
-\end{itemize}
-
-Five sets of data were generated using these equations to represent five
-scenarios. Scenario 1 represents the base case where 10\% of workers are
-susceptible to exposure-related effects, the odds ratio of mortality
-each additional year following cancer diagnosis is about 1.6, and there
-is moderate time-varying confounding by health status. In scenario 2, we
-have greater cancer-related mortality by increasing
-\(\beta_{\bar Y}^D\). In scenario 3, we increase \(p_S\), the proportion
-of the study population susceptible to the carcinogenic effects of MWF
-exposure. In scenario 4, we consider greater time-varying confounding by
-health status by increasing \(\beta_H^N\) and \(\beta_H^Y\). In the last
-scenario, we have greater background cancer incidence by increasing
-\(\beta_0^Y\). The sets of parameters used in the five scenarios are
-presented in Table \ref{tab:params}.
-
-\begin{table}
-\caption{Simulation parameters.}
-\label{tab:params}
-\begin{center}
-\begin{tabular}{rrrrrr}
-  \toprule
-Parameter & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-$p_S$ & 0.10 & 0.10 & \textbf{0.20} & 0.10 & 0.10 \\ 
-  $p_W$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
-  $p_H$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
-  $\beta_0^N$ & 3.00 & 3.00 & 3.00 & 3.00 & 3.00 \\ 
-  $\beta_W^N$ & -0.10 & -0.10 & -0.10 & -0.10 & -0.10 \\ 
-  $\beta_H^N$ & -0.50 & -0.50 & -0.50 & \textbf{-1.50} & -0.50 \\ 
-  $\beta_A^N$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
-  $\beta_0^A$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
-  $\beta_W^A$ & -0.50 & -0.50 & -0.50 & -0.50 & -0.50 \\ 
-  $\beta_A^A$ & 2.50 & 2.50 & 2.50 & 2.50 & 2.50 \\ 
-  $\beta_0^D$ & -5.50 & -5.50 & -5.50 & -5.50 & -5.50 \\ 
-  $\beta_W^D$ & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
-  $\beta_{\bar A}^D$ & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\ 
-  $\beta_{\bar Y}^D$ & 0.50 & \textbf{2.00} & 0.50 & 0.50 & 0.50 \\ 
-  $\beta_0^Y$ & -7.00 & -7.00 & -7.00 & -7.00 & \textbf{-6.00} \\ 
-  $\beta_W^Y$ & 2.00 & 2.00 & 2.00 & 2.00 & 2.00 \\ 
-  $\beta_A^Y$ & 0.25 & 0.25 & 0.25 & 0.25 & 0.25 \\ 
-  $\beta_{\bar A}^Y$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
-  $\beta_H^Y$ & 0.70 & 0.70 & 0.70 & \textbf{1.70} & 0.70 \\ 
-  $\beta_S^Y$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
-   \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\hypertarget{interventions-potential-outcomes-target-parameters-and-estimation}{%
-\subsection{Interventions, potential outcomes, target parameters, and
-estimation}\label{interventions-potential-outcomes-target-parameters-and-estimation}}
-
-The substantive question of interest is the causal effect of
-occupational exposure to MWF on cancer incidence risk. Since
-occupational MWF exposure occurs only when individuals are at work, we
-define dynamic exposure regimes that depend on employment status. Under
-rule \(a_0\), set \(D(t) = 0\), and set \(A(t) = 0\) while \(N(t) = 1\).
-Under rule \(a_1\), set \(D(t) = 0\), and set \(A(t) = 1\) while
-\(N(t) = 1\). Under both rules, we prevent censoring by death as if it
-were intervenable. The causal effect is defined by contrasting the
-survival function \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule \(a_1\)
-to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\). Note
-that this causal estimand is defined over \emph{a priori
-counterfactuals} not observable in the real world (Frangakis and Rubin
-2002). This approach is standard in epidemiologic studies, however.
-
-The survival function expresses the probability that a person following
-rule \(a\) is cancer-free at the end of time point \(t\). The expected
-time until cancer under rule \(a\) is
-\(\mu_{a} = \sum_0^K S_{a}(t) \, dt\). Our causal estimand is summary
-measure \(\psi = \mu_{a_1} - \mu_{a_0}\), the difference in expected
-time until event under two different interventions over 20 years of
-follow-up under five different data generating scenarios. Bias will be
-evaluated by comparing estimates of \(\psi\) to its true value in 250
-simulations per scenario (the original analysis performed 500). The true
-value will be calculated by simulating the full data for five hundred
-thousand individuals (the original analysis used one million) with rules
-\(a_0\) and \(a_1\) applied deterministically. Estimates of \(\psi\)
-will be obtained by first estimating the survival curves \(S_a(t)\)
-using two estimators: the inverse probability weighted Kaplan-Meier
-estimator (WKM) and the Aalen-filtered WKM (AWKM). These survival
-estimators are detailed in the following section.
-
-\hypertarget{kaplan-meier-estimator-and-extensions}{%
-\subsection{Kaplan-Meier estimator and
-extensions}\label{kaplan-meier-estimator-and-extensions}}
-
-To estimate survival, we applied extensions of the widely-known
-Kaplan-Meier (KM) estimator for survival (Kaplan and Meier 1958). First,
-we review the estimator of Xie and Liu (2005), an extension of the KM
-estimator where units are weighted by the inverse probability of
-treatment. The standard KM estimator requires counting up the number of
-cases \(c^0_{a}(t)\) that occurred in interval \((t - 1, t]\) and the
-number of units at risk \(R^0_{a}(t)\) in that interval at all event
-times \(t\). Assuming cancer status was assessed at the end of regular
-intervals \(t = 1, \ldots, K\), we have: \[\begin{aligned}
-c^0_{a} (t)
-& = \sum_i^n \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \\
-R^0_{a} (t)
-& = \sum_i^n \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}.
-\end{aligned}\] The standard survival estimator is \[\hat S^0_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-In observational studies, survival contrasts estimated using the
-standard KM estimator are biased for the true causal survival contrast.
-However, if conditional ignorability and positivity are attained, the
-inverse probability weighted KM (WKM) estimator of Xie and Liu (2005)
-yields unbiased estimates of the true causal survival curve. The WKM
-estimator augments the standard KM estimator by weighting units at time
-\(t\) by \(w_{i, a}(t)\) the inverse probability of treatment:
-\[\begin{aligned}
-c^w_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}\\
-R^w_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}
-\end{aligned}\] The WKM survival estimator for rule \(a\) is
-\[\hat S^w_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^w_{a}(j)}{R^w_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-Finally, to account for (uninformative) left filtering, we applied the
-Aalen filter, which considers only the units at time \(t\) for which the
-outcome is observed: \[\begin{aligned}
-c_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
-R_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
-\end{aligned}\] The Aalen-filtered WKM (AWKM) estimator for rule \(a\)
-is \[\hat S_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-In the full data, the WKM and AWKM estimators are equivalent, and
-identification is achieved under overlap (positivity) and sequential
-ignorability (randomization) assumptions: \[\begin{aligned}
-Y^*_{a, \bar d = 0} (t')   & \indep A(t) \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1\\
-Y^*_{a, \bar d = 0} (t') & \indep D(t) \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)
-\end{aligned}\] for all times \(t'\ge t\), and
-\[0 < \Prob{ A(t) = 1 \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1} < 1\]
-\[0 < \Prob{D(t) = 0 \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)} < 1.\]
-
-Graphical representations of the first and second components of the
-ignorability assumption are presented in Figures
-\ref{fig:ignorability_a} and \ref{fig:ignorability_d} where conditioning
-on boxed variables are represented by the removal of edges pointing away
-from those variables. The resulting graphs show the fulfillment of
-Pearl's backdoor criterion for the estimation of the causal effects of
-\(\bar A(t)\) on \(Y^*(t)\) and \(D(t)\) on \(Y^*(t)\), respectively.
-Thus, the causal effect of the joint intervention on
-\(\big(\bar A(t), D(t)\big)\) at each time \(t\) is identified. Causal
-identification is not attained when true cancer status \(Y^*(t)\) is not
-known.
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ N(t)\}$.}
-\label{fig:ignorability_a}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [shape=rectangle, draw=black, inner sep=2.5pt, above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-\path[->] (Y0) edge [bend right=10] (D);
-\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ Y^*(t - 1)\}$.}
-\label{fig:ignorability_d}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [shape=rectangle, draw=black, inner sep=2pt, below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [shape=rectangle, draw=black, inner sep=2pt, below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [shape=rectangle, draw=black, inner sep=2pt, below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [shape=rectangle, draw=black, inner sep=2pt, above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-%\path[->] (W) edge [bend right=10] (N);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-%\path[->] (A0) edge (N);
-%\path[->] (W) edge [bend right=15] (A);
-%\path[->] (A0) edge (A);
-\path[->] (N) edge (A);
-%\path[->] (W) edge (D);
-%\path[->] (A0) edge [bend left=15] (D);
-%\path[->] (D0) edge [bend right=15] (D);
-%\path[->] (Y0) edge [bend right=10] (D);
-%\path[->] (W) edge [bend left=5] (Y);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-%\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\hypertarget{estimation-of-weights}{%
-\subsection{Estimation of weights}\label{estimation-of-weights}}
-
-To estimate the weights for the WKM and AWKM estimators, we fit two
-logistic regressions at each time point \(t = 1, \ldots 20\):
-\[\begin{aligned}
-\text{logit} \left(\Prob{
-    A(t) = 1
-    \mid W,\ \bar A(t - 1),\ D(t - 1) = 0,\ N(t) = 1
-    }\right)
-& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
-\text{logit} \left(\Prob{
-    D(t) = 1
-    \mid W,\ D(t - 1) = 0,\ Y(t - 1) = 0,\ \bar A(t - 1)}\right)
-    & = \beta_0 + W \beta_1 + \bar A(t - 1) \beta_2
-\end{aligned}\] The first will be fitted on data for those alive and at
-work at time \(t\). The second will be among those alive and (observed
-to be) cancer-free. For each unit at time \(t\), the weight will be
-calculated by taking the inverse of the cumulative probability of
-following the exposure rule and remaining uncensored: \[\hat w_{a} (t) =
-    \left[
-    \prod^t_{j = 1}
-    \begin{aligned}
-    \widehat {\mathbb P} \left\{
-    A(j) = a(j) \mid W,\ \bar A(j - 1) = \bar a (j - 1),\ D(j - 1) = 0,\ N(j) = 1
-    \right\} \times \\
-    \widehat {\mathbb P} \left\{D(j) = 0
-    \mid W,\ D(j - 1) = 0,\ Y(j - 1) = 0,\ \bar A(j) = \bar a (j) \right\}
-    \end{aligned}\right]^{-1}.\]
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Figure \ref{fig:survival} presents the true survival curves as well as
-the WKM and AWKM survival curves averaged over 250 replications for each
-intervention rule and scenario. Qualitatively, the WKM estimator
-consistently over-estimates survival whereas the the AWKM survival curve
-is much closer to the truth. The bias of the AWKM survival estimate
-appears to be larger earlier in follow-up and smaller as follow-up
-extends forward. The bias of both the the WKM and the AWKM survival
-curves appears largest in Scenario 5.
-
-\begin{figure}
-\caption{Cancer-free survival over time since hire in five simulation scenarios.
-The true (discrete) survival curve is represented by the solid lines.
-The average inverse probability weighted Kaplan-Meier (WKM) survival curve is represented by the dashed-line with short dashes.
-The average Aalen-filtered inverse probability weighted Kaplan-Meier (AWKM) survival curve is represented by the dashed-line with long dashes.
-Estimated survival curves were averaged over 250 replicates.
-Salmon color indicates survival and survival estimates under rule $a_0$ when workers are always unexposed.
-Cyan color indicates those under rule $a_1$ when workers are always exposed while employed.}
-\label{fig:survival}
-\begin{center}
-\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/results.pdf}
-\end{center}
-\end{figure}
-
-Table \ref{tab:survival} presents true and estimated average cancer-free
-survival times under each intervention rule and scenario. Table
-\ref{tab:differences} presents differences in survival time contrasting
-rule \(a_1\) to rule \(a_0\). Table \ref{tab:bias} presents estimates of
-the bias of the WKM and AWKM estimators for \(\psi\), the difference in
-average cancer-free survival time over 20 years of follow-up. These
-numeric results are consistent with the qualitative interpretations of
-Figure \ref{fig:survival}. The WKM estimator over-estimates the
-difference in cancer-free survival time, resulting in bias toward the
-null, whereas the AWKM estimator under-estimates the cancer-free
-survival, resulting in bias away from the null. In every scenario, the
-bias of the WKM-derived contrast is several times larger in magnitude
-than that of the AWKM-derived contrast. The bias of both estimators is
-greatest for Scenario 5.
-
-The qualitative results here are consistent with those of Izano (2017).
-However, true and estimated survival in the present analysis is larger
-than those found previously. Furthermore, the true and estimator average
-mean differences in survival are smaller in magnitude in the present
-case. The magnitudes of the bias estimates are also smaller.
-
-\begin{table}[H]
-\centering
-\caption{True cancer-free survival time $\mu_{a}$ over 20-year follow-up and estimator averages over 250 replicates.} 
-\label{tab:survival}
-\begin{tabular}{llrrrrr}
-  \toprule
-Rule & Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-$a_0$ & Truth & 19.08 & 19.10 & 19.10 & 18.02 & 17.83 \\ 
-   & WKM & 19.52 & 19.51 & 19.53 & 18.92 & 18.90 \\ 
-   & AWKM & 19.02 & 19.00 & 19.02 & 17.79 & 17.72 \\ 
-   \midrule
-$a_1$ & Truth & 18.80 & 18.79 & 18.76 & 17.54 & 17.29 \\ 
-   & WKM & 19.39 & 19.37 & 19.37 & 18.68 & 18.62 \\ 
-   & AWKM & 18.70 & 18.67 & 18.67 & 17.30 & 17.07 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
-\begin{table}[H]
-\centering
-\caption{Difference in average cancer-free survival time over 20-year follow-up comparing rule $a_1$ always exposed to rule $a_0$ never exposed at work: true value $\psi$ and estimator averages over 250 replicates.}
-\label{tab:differences}
-\begin{tabular}{lrrrrr}
-  \toprule
-Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-Truth & -0.28 & -0.31 & -0.34 & -0.48 & -0.54 \\ 
-  WKM & -0.14 & -0.15 & -0.15 & -0.23 & -0.28 \\ 
-  AWKM & -0.31 & -0.33 & -0.35 & -0.50 & -0.64 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
-\begin{table}[H]
-\centering
-\caption{Bias estimates of estimators for $\psi$, the difference in average cancer-free survival time over 20 years of follow-up.} 
-\label{tab:bias}
-\begin{tabular}{lrrrrr}
-  \toprule
-Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-WKM & 0.14 & 0.16 & 0.19 & 0.25 & 0.26 \\ 
-  AWKM & -0.03 & -0.02 & -0.01 & -0.02 & -0.10 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
-
-\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Andersen_1993}{}%
-Andersen, P. K., Ø. Borgan, R. D. Gill, and N. Keiding. 1993.
-\emph{Statistical Models Based on Counting Processes}. Springer Series
-in Statistics. Springer, New York, NY.
-\url{https://books.google.com/books?id=kBnvAAAAMAAJ}.
-
-\leavevmode\hypertarget{ref-Arrighi_1994}{}%
-Arrighi, H. Michael, and Irva Hertz-Picciotto. 1994. {``The Evolving
-Concept of the Healthy Worker Survivor Effect.''} \emph{Epidemiology} 5
-(2): 189--96. \url{http://www.jstor.org/stable/3702361}.
-
-\leavevmode\hypertarget{ref-Byers_2006}{}%
-Byers, Jerry P. 2006. \emph{Metalworking Fluids}. CRC Press.
-
-\leavevmode\hypertarget{ref-Eisen_2001}{}%
-Eisen, Ellen A, Judith Bardin, Rebecca Gore, Susan R Woskie, Marilyn F
-Hallock, and Richard R Monson. 2001. {``Exposure-Response Models Based
-on Extended Follow-up of a Cohort Mortality Study in the Automobile
-Industry.''} \emph{Scandinavian Journal of Work, Environment \& Health}
-27 (4): 240--49.
-
-\leavevmode\hypertarget{ref-Eisen_1992}{}%
-Eisen, Ellen A, Paige E Tolbert, Richard R Monson, and Thomas J Smith.
-1992. {``Mortality Studies of Machining Fluid Exposure in the Automobile
-Industry {I}: A Standardized Mortality Ratio Analysis.''} \emph{American
-Journal of Industrial Medicine} 22 (6): 809--24.
-
-\leavevmode\hypertarget{ref-Frangakis_2002}{}%
-Frangakis, Constantine E, and Donald B Rubin. 2002. {``Principal
-Stratification in Causal Inference.''} \emph{Biometrics} 58 (1): 21--29.
-
-\leavevmode\hypertarget{ref-Garcia_2017}{}%
-Garcia, Erika, Sally Picciotto, Sadie Costello, Patrick T Bradshaw, and
-Ellen A Eisen. 2017. {``Assessment of the Healthy Worker Survivor Effect
-in Cancer Studies of the United Autoworkers-General Motors Cohort.''}
-\emph{Occupational and Environmental Medicine} 74 (4): 294--300.
-
-\leavevmode\hypertarget{ref-Garcia_2018}{}%
-Garcia, Erika, Sally Picciotto, Andreas M Neophytou, Patrick T Bradshaw,
-John R Balmes, and Ellen A Eisen. 2018. {``Lung Cancer Mortality and
-Exposure to Synthetic Metalworking Fluid and Biocides: Controlling for
-the Healthy Worker Survivor Effect.''} \emph{Occupational and
-Environmental Medicine} 75 (10): 730--35.
-
-\leavevmode\hypertarget{ref-Izano_2017_thesis}{}%
-Izano, Monika A. 2017. {``Estimating Causal Effects of Occupational
-Exposures.''} PhD thesis, University of California, Berkeley; University
-of California, Berkeley.
-
-\leavevmode\hypertarget{ref-Izano_2019}{}%
-Izano, Monika A, Oleg A Sofrygin, Sally Picciotto, Patrick T Bradshaw,
-and Ellen A Eisen. 2019. {``Metalworking Fluids and Colon Cancer Risk:
-Longitudinal Targeted Minimum Loss-Based Estimation.''}
-\emph{Environmental Epidemiology} 3 (1): e035.
-
-\leavevmode\hypertarget{ref-Kaplan_1958}{}%
-Kaplan, Edward L, and Paul Meier. 1958. {``Nonparametric Estimation from
-Incomplete Observations.''} \emph{Journal of the American Statistical
-Association} 53 (282): 457--81.
-
-\leavevmode\hypertarget{ref-Naimi_2013}{}%
-Naimi, Ashley I, Stephen R Cole, Michael G Hudgens, M Alan Brookhart,
-and David B Richardson. 2013. {``Assessing the Component Associations of
-the Healthy Worker Survivor Bias: Occupational Asbestos Exposure and
-Lung Cancer Mortality.''} \emph{Annals of Epidemiology} 23 (6): 334--41.
-
-\leavevmode\hypertarget{ref-Pearl_1995}{}%
-Pearl, Judea. 1995. {``Causal Diagrams for Empirical Research.''}
-\emph{Biometrika} 82 (4): 669--88.
-
-\leavevmode\hypertarget{ref-Xie_2005}{}%
-Xie, Jun, and Chaofeng Liu. 2005. {``Adjusted Kaplan--Meier Estimator
-and Log-Rank Test with Inverse Probability of Treatment Weighting for
-Survival Data.''} \emph{Statistics in Medicine} 24 (20): 3089--3110.
-
-\end{CSLReferences}
-
-\end{document}
+Here, we replicate the simulation and bias analysis presented in Chapter 3 of @Izano_2017_thesis, embed the problem in the non-parametric structural causal approach of @Pearl_1995, comment on the results, and apply the WKM and AWKM estimators to the UAW-GM Cohort.

### 2021-12-10 reports/02-methods.Rmd
First commit; interim results from simulation

---
output:
  pdf_document:
    includes:
      in_header: "~/headRs/StatHead.sty"
fontsize: 11pt
bibliography: "../../causal.bib"
# csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

```{r, include=F}
knitr::opts_chunk$set(echo = F, results = "asis", fig.align = "center")
if (!"mytheme" %in% ls()) {
  source("~/headRs/00-my-theme.R")
  library(data.table)
  options(tikzDefaultEngine = 'pdftex')
}
```

# Methods

## Causal model

The UAW-GM Cohort data includes person-year level exposure, outcome, and covariate data starting three years after hire. To emulate the shape of the data for this longitudinal cohort, we consider 20 years of data over time indexed by years since hire. Notation representing the variables of interest are presented in Table \ref{tab:variables}.

\begin{table}
\caption{Descriptions of variables.}\label{tab:variables}
\begin{center}
\begin{tabular}{lp{0.5\linewidth}}
\toprule
 Variable  &  Description                                 \\ \midrule
 $R$       & Time until start of registry \\
 $W$       & Baseline covariates \\
 $S$       & Susceptibility to effects of metalworking fluid exposure \\
 $H(t)$    & Adverse health status at time $t$ \\
 $N(t)$    & Employment status at time $t$ \\
 $A(t)$    & Metalworking fluid exposure at time $t$ \\
 $D(t)$    & Mortality status at time $t$ \\
 $Y^*(t)$  & Cancer status at time $t$ \\
 $Y(t)$    & Observed Cancer status at time $t$ \\
 $t = \{1, 2, \ldots, 20\}$ & Time, indexed in years after hire \\
 \bottomrule
\end{tabular}
\end{center}\end{table}

Assume we have $n = 50\,000$ iid units in $X$ with
$$X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).$$
The bar notation to indicates variable history where $\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t$. In the case of exposure, $\bar A_i(t)$ is the indicator of whether unit $i$ was ever exposed through time $t$. Note that true cancer status $Y^*(t)$ not observed until $t \ge R$, after the start of the registry. Call $X$ the full data, where we have $R = 0$ for all. In the observed data $X^\text{obs}$, we cannot assume $R = 0$ for all, and susceptibility $S$ is not known:
$$X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).$$
Under the causal model, we assume the following non-parametric structural equations:
$$\begin{aligned}
R     & = f_R \left( U_R \right) \\
W     & = f_W \left( U_W \right) \\
S     & = f_S \left( U_S \right) \\
H(t)  & = f_{H(t)} \left( H(t - 1), U_{H(t)} \right) \\
N(t)  & = f_{N(t)} \left( W, N(t - 1), H(t), A(t - 1), U_{N(t)} \right) \\
A(t)  & = f_{A(t)} \left( W, \bar A(t - 1), N(t), U_{A(t)} \right) \\
D(t)  & = f_{D(t)} \left( W, \bar A(t - 1), D(t - 1), Y^*(t - 1), U_{D(t)} \right) \\
Y^*(t)& = f_{Y^*(t)} \left(W, S, H(t), \bar A (t), D(t), Y^*(t - 1), U_{Y^*(t)} \right) \\
Y(t) & = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0} \ .
\end{aligned}$$
The exogenous variables (errors) $U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}$ are mutually independent. Exposure status is a time-varying indicator; let exposure history $\bar A(t)$ be summarized as being ever-exposed or not with $\bar A(t)  = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}$. The outcome of interest is a survival outcome, so $Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1$. The observed outcome $Y(t)$ at time $t$ is a function of true outcome status and the time points delimiting left and right censoring. An abbreviated directed acyclic graph (DAG) representing the causal relationships encoded in the equations above is presented in Figure \ref{fig:dag}.

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$.}
\label{fig:dag}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
\path[->] (W) edge [bend right=10] (N);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
\path[->] (A0) edge (N);
\path[->] (W) edge [bend right=15] (A);
\path[->] (A0) edge (A);
\path[->] (N) edge (A);
\path[->] (W) edge (D);
\path[->] (A0) edge [bend left=15] (D);
\path[->] (D0) edge [bend right=15] (D);
\path[->] (Y0) edge [bend right=10] (D);
\path[->] (W) edge [bend left=5] (Y);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

## Simulation

Parametric relationships between the variables were imposed in simulations. For the $n = 50\,000$ units over $T = 20$ years, we have:

- $U_j \overset{\text{iid}}{\sim} \text{uniform}\,[0,1]$ for all $j$
- In full data $R = 0$ otherwise $R \sim \text{uniform}\,[0, 30]$
- $W = \Ind{U_W \le p_W} \sim \text{Bernoulli}\left( p_W \right)$
- $S = \Ind{U_S \le p_S} \sim \text{Bernoulli}\,(p_S)$
- If $H(t - 1) = 1$, then $H(t) = 1$ otherwise $H(t) = \Ind{U_{H(t)} \le p_H} \sim \text{Bernoulli}\,(p_H)$
- if $N(t - 1) = 0$ then $N(t) = 0$ otherwise
	$$N(t) \sim \text{Bernoulli}\left\{
	\text{logit}\,\left(
		\beta_0^N
		+ \beta_W^N W
		+ \beta_H^N H(t)
		+ \beta_A^N A(t - 1) \times \Ind{t > 1}
		+ U_{N(t)}
	\right)
	\right\}$$
- If $N(t) = 0$ then $A(t) = 0$ otherwise
	$$A(t) \sim \text{Bernoulli}\left\{
	\text{logit}\,\left(
		\left( \beta_0^A + \beta_W^A W\right) \times \Ind{t = 1}
		+ \beta_A^A A(t - 1) \times \Ind{t > 1}
		+ U_{A(t)}
	\right)
	\right\}$$
- If $D(t - 1) = 1$ then $D(t) = 1$ otherwise
	$$D(t) \sim \text{Bernoulli}\left\{
	\text{logit}\,\left(\begin{aligned}
		\beta_0^D
		+ \beta_W^D W
		+ \beta_{\bar A}^D \bar A(t - 1) \times \Ind{t > 1} \\
		+ \beta_{\bar Y}^D \sum_{k = 1}^{t - 1} Y^*(k) \times \Ind{t > 1}
		+ U_{D(t)}
	\end{aligned}\right)
	\right\}$$
- If $Y^*(t - 1) = 1$ then $Y^*(t) = 1$ otherwise
	$$Y^*(t) \sim \text{Bernoulli}\left\{
	\text{logit}\,\left(\begin{aligned}
		\beta_0^Y
		+ \beta_W^Y W
		+ \beta_{A}^Y A(t)
		+ \beta_{\bar A}^Y \bar A(t - 1) \times \Ind{t > 1} \\
		+ \beta_{S}^Y S \times \bar A(t)
		+ \beta_{H}^Y H(t)
		+ U_{Y^*(t)}
	\end{aligned}\right)
	\right\}$$
- If $t < R$ then $Y(t) = 0$
- If $t \ge R$ then $Y(t) = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0}$.

Five sets of data were generated using these equations to represent five scenarios. Scenario 1 represents the base case where 10% of workers are susceptible to exposure-related effects, the odds ratio of mortality each additional year following cancer diagnosis is about 1.6, and there is moderate time-varying confounding by health status. In scenario 2, we have greater cancer-related mortality by increasing $\beta_{\bar Y}^D$. In scenario 3, we increase $p_S$, the proportion of the study population susceptible to the carcinogenic effects of MWF exposure. In scenario 4, we consider greater time-varying confounding by health status by increasing $\beta_H^N$ and $\beta_H^Y$. In the last scenario, we have greater background cancer incidence by increasing $\beta_0^Y$. The sets of parameters used in the five scenarios are presented in Table \ref{tab:params}.

\begin{table}
\caption{Simulation parameters.}
\label{tab:params}
\begin{center}
```{r}
sim_param.tab <- sim_param <- data.frame(
	check.names = F,
	Parameter =  c(
		"p_S", "p_W", "p_H", "\\beta_0^N", "\\beta_W^N", "\\beta_H^N",
		"\\beta_A^N", "\\beta_0^A", "\\beta_W^A", "\\beta_A^A", "\\beta_0^D",
		"\\beta_W^D", "\\beta_{\\bar A}^D", "\\beta_{\\bar Y}^D", "\\beta_0^Y",
		"\\beta_W^Y", "\\beta_A^Y", "\\beta_{\\bar A}^Y", "\\beta_H^Y",
		"\\beta_S^Y"),
	"Scenario 1" = c(
		0.1, 0.2, 0.3, 3, -0.1, -0.5, -1.5, -1.5, -0.5, 2.5, -5.5, 1, 0.5, 0.5, -7, 2, 0.25, 0.2, 0.7, 0.3
	),
	"Scenario 2" = c(
		0.1, 0.2, 0.3, 3, -0.1, -0.5, -1.5, -1.5, -0.5, 2.5, -5.5, 1, 0.5, 2.0, -7, 2, 0.25, 0.2, 0.7, 0.3
	),
	"Scenario 3" = c(
		0.2, 0.2, 0.3, 3, -0.1, -0.5, -1.5, -1.5, -0.5, 2.5, -5.5, 1, 0.5, 0.5, -7, 2, 0.25, 0.2, 0.7, 0.3
	),
	"Scenario 4" = c(
		0.1, 0.2, 0.3, 3, -0.1, -1.5, -1.5, -1.5, -0.5, 2.5, -5.5, 1, 0.5, 0.5, -7, 2, 0.25, 0.2, 1.7, 0.3
	),
	"Scenario 5" = c(
		0.1, 0.2, 0.3, 3, -0.1, -0.5, -1.5, -1.5, -0.5, 2.5, -5.5, 1, 0.5, 0.5, -6, 2, 0.25, 0.2, 0.7, 0.3
	)
)

sim_param$Parameter <- c(
		"p_S", "p_W", "p_H", "beta_0N", "beta_WN", "beta_HN",
		"beta_AN", "beta_0A", "beta_WA", "beta_AA", "beta_0D",
		"beta_WD", "beta_barAD", "beta_barYD", "beta_0Y",
		"beta_WY", "beta_AY", "beta_barAY", "beta_HY",
		"beta_SY")
saveRDS(sim_param, here::here("resources", "sim_param.rds"))

sim_param.tab[,1] <- paste0("$", sim_param.tab[,1], "$")
sim_param.tab[,2:ncol(sim_param.tab)] <- sapply(
	sim_param.tab[,2:ncol(sim_param.tab)], function(x) {
		formatC(x, digits = 2, format = "f")
	})

for (x in list(
	c(1, 4),
	c(6, 5),
	c(14, 3),
	c(15, 6),
	c(19, 5)
)) {
	sim_param.tab[x[[1]], x[[2]]] <- paste0(
		"\\textbf{", sim_param.tab[x[[1]], x[[2]]], "}")
}

sim_param.tab <- sim_param.tab[,c(
	"Parameter", paste("Scenario", 1:5))]
names(sim_param.tab)[-1] <- paste("Scenario", 1:(ncol(sim_param.tab) - 1))

xtable(sim_param.tab, align = c("c", rep("r", ncol(sim_param.tab))))
```
\end{center}
\end{table}

## Interventions, potential outcomes, target parameters, and estimation

The substantive question of interest is the causal effect of occupational exposure to MWF on cancer incidence risk. Since occupational MWF exposure occurs only when individuals are at work, we define dynamic exposure regimes that depend on employment status. Under rule $a_0$, set $D(t) = 0$, and set $A(t) = 0$ while $N(t) = 1$. Under rule $a_1$, set $D(t) = 0$, and set $A(t) = 1$ while $N(t) = 1$. Under both rules, we prevent censoring by death as if it were intervenable. The causal effect is defined by contrasting the survival function $S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}$ under rule $a_1$ to $S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}$ that under rule $a_0$. Note that this causal estimand is defined over _a priori counterfactuals_ not observable in the real world [@Frangakis_2002]. This approach is standard in epidemiologic studies, however.

The survival function  expresses the probability that a person following rule $a$ is cancer-free at the end of time point $t$. The expected time until cancer under rule $a$ is $\mu_{a} = \sum_0^K S_{a}(t) \, dt$. Our causal estimand is summary measure $\psi = \mu_{a_1} - \mu_{a_0}$, the difference in expected time until event under two different interventions over 20 years of follow-up under five different data generating scenarios. Bias will be evaluated by comparing estimates of $\psi$ to its true value in 250 simulations per scenario (the original analysis performed 500). The true value will be calculated by simulating the full data for five hundred thousand individuals (the original analysis used one million) with rules $a_0$ and $a_1$ applied deterministically. Estimates of $\psi$ will be obtained by first estimating the survival curves $S_a(t)$ using two estimators: the inverse probability weighted Kaplan-Meier estimator (WKM) and the Aalen-filtered WKM (AWKM). These survival estimators are detailed in the following section.

## Kaplan-Meier estimator and extensions

To estimate survival, we applied extensions of the widely-known Kaplan-Meier (KM) estimator for survival [@Kaplan_1958]. First, we review the estimator of @Xie_2005, an extension of the KM estimator where units are weighted by the inverse probability of treatment. The standard KM estimator requires counting up the number of cases $c^0_{a}(t)$ that occurred in interval $(t - 1, t]$ and the number of units at risk $R^0_{a}(t)$ in that interval at all event times $t$. Assuming cancer status was assessed at the end of regular intervals $t = 1, \ldots, K$, we have:
$$\begin{aligned}
c^0_{a} (t)
& = \sum_i^n \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \\
R^0_{a} (t)
& = \sum_i^n \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}.
\end{aligned}$$
The standard survival estimator is
$$\hat S^0_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}$$
where $t_1$ is the first event time.

In observational studies, survival contrasts estimated using the standard KM estimator are biased for the true causal survival contrast. However, if conditional ignorability and positivity are attained, the inverse probability weighted KM (WKM) estimator of @Xie_2005 yields unbiased estimates of the true causal survival curve. The WKM estimator augments the standard KM estimator by weighting units at time $t$ by $w_{i, a}(t)$ the inverse probability of treatment:
$$\begin{aligned}
c^w_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}\\
R^w_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}
\end{aligned}$$
The WKM survival estimator for rule $a$ is
$$\hat S^w_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c^w_{a}(j)}{R^w_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}$$
where $t_1$ is the first event time.

Finally, to account for (uninformative) left filtering, we applied the Aalen filter, which considers only the units at time $t$ for which the outcome is observed:
$$\begin{aligned}
c_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
R_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
\end{aligned}$$
The Aalen-filtered WKM (AWKM) estimator for rule $a$ is
$$\hat S_{a}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}$$
where $t_1$ is the first event time.

In the full data, the WKM and AWKM estimators are equivalent, and identification is achieved under overlap (positivity) and sequential ignorability (randomization) assumptions:
$$\begin{aligned}
Y^*_{a, \bar d = 0} (t')   & \indep A(t) \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1\\
Y^*_{a, \bar d = 0} (t') & \indep D(t) \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)
\end{aligned}$$
for all times $t'\ge t$, and
<!-- Note that @Izano_2017_thesis did not condition on cancer status $Y^*(t - 1)$ in their estimation of weights. -->
$$0 < \Prob{ A(t) = 1 \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1} < 1$$
$$0 < \Prob{D(t) = 0 \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)} < 1.$$

Graphical representations of the first and second components of the ignorability assumption are presented in Figures \ref{fig:ignorability_a} and \ref{fig:ignorability_d} where conditioning on boxed variables are represented by the removal of edges pointing away from those variables. The resulting graphs show the fulfillment of Pearl's backdoor criterion for the estimation of the causal effects of $\bar A(t)$ on $Y^*(t)$ and $D(t)$ on $Y^*(t)$, respectively. Thus, the causal effect of the joint intervention on $\big(\bar A(t), D(t)\big)$ at each time $t$ is identified. Causal identification is not attained when true cancer status $Y^*(t)$ is not known.

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ N(t)\}$.}
\label{fig:ignorability_a}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [shape=rectangle, draw=black, inner sep=2.5pt, above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
\path[->] (Y0) edge [bend right=10] (D);
\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

\begin{figure}
\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ Y^*(t - 1)\}$.}
\label{fig:ignorability_d}
\begin{center}
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [shape=rectangle, draw=black, inner sep=2pt, below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [shape=rectangle, draw=black, inner sep=2pt, below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [shape=rectangle, draw=black, inner sep=2pt, below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [shape=rectangle, draw=black, inner sep=2pt, above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (H);
%\path[->] (W) edge [bend right=10] (N);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
%\path[->] (A0) edge (N);
%\path[->] (W) edge [bend right=15] (A);
%\path[->] (A0) edge (A);
\path[->] (N) edge (A);
%\path[->] (W) edge (D);
%\path[->] (A0) edge [bend left=15] (D);
%\path[->] (D0) edge [bend right=15] (D);
%\path[->] (Y0) edge [bend right=10] (D);
%\path[->] (W) edge [bend left=5] (Y);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
%\path[->] (Y0) edge (Y);
\end{tikzpicture}
\end{center}
\end{figure}

## Estimation of weights

To estimate the weights for the WKM and AWKM estimators, we fit two logistic regressions at each time point $t = 1, \ldots 20$:
$$\begin{aligned}
\text{logit} \left(\Prob{
	A(t) = 1
	\mid W,\ \bar A(t - 1),\ D(t - 1) = 0,\ N(t) = 1
	}\right)
& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
\text{logit} \left(\Prob{
	D(t) = 1
	\mid W,\ D(t - 1) = 0,\ Y(t - 1) = 0,\ \bar A(t - 1)}\right)
	& = \beta_0 + W \beta_1 + \bar A(t - 1) \beta_2
\end{aligned}$$
The first will be fitted on data for those alive and at work at time $t$. The second will be among those alive and (observed to be) cancer-free. For each unit at time $t$, the weight will be calculated by taking the inverse of the cumulative probability of following the exposure rule and remaining uncensored:
$$\hat w_{a} (t) =
	\left[
	\prod^t_{j = 1}
	\begin{aligned}
	\widehat {\mathbb P} \left\{
	A(j) = a(j) \mid W,\ \bar A(j - 1) = \bar a (j - 1),\ D(j - 1) = 0,\ N(j) = 1
	\right\} \times \\
	\widehat {\mathbb P} \left\{D(j) = 0
	\mid W,\ D(j - 1) = 0,\ Y(j - 1) = 0,\ \bar A(j) = \bar a (j) \right\}
	\end{aligned}\right]^{-1}.$$

### 2021-12-10 reports/03-results.Rmd
First commit; interim results from simulation

--- 2021-12-10 paper.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  11pt,
-]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Estimating survival in left filtered data: simulation and application},
-  pdfauthor={Kevin Chen},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=2.54cm]{geometry}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\PassOptionsToPackage{no-math}{fontspec}
+---
+output:
+  pdf_document:
+    includes:
+      in_header: "~/headRs/StatHead.sty"
+fontsize: 11pt
+bibliography: "../../causal.bib"
+# csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
+---
 
-%---------------------------------------------------------------------------
-% Kevin's style file
-%---------------------------------------------------------------------------
-\usepackage{ifxetex,ifluatex}
+```{r, include=F}
+knitr::opts_chunk$set(echo = F, results = "asis", fig.align = "center")
+if (!"mytheme" %in% ls()) {
+  source("~/headRs/00-my-theme.R")
+  library(data.table)
+  options(tikzDefaultEngine = 'pdftex')
+}
+library(tidyverse); library(data.table)
+library(here)
+```
 
-%---------------------------------------------------------------------------
-% General
-%---------------------------------------------------------------------------
+```{r}
+sim_results <- readRDS(here("reports/resources", "sim_results.rds"))
+survival.tab <- dcast(
+	sim_results[,.(
+		Survival = sum(Survival)
+	), .(Rule = rule, scenario, Estimator)],
+	... ~ scenario,
+	value.var = "Survival"
+)
 
-% When testing
-% \usepackage{lipsum}
+setorder(survival.tab, Rule, Estimator)
 
-% Line numbering
-\usepackage{lineno}
+differences.tab <- survival.tab[,.(
+		`Scenario 1` = `Scenario 1`[2] - `Scenario 1`[1],
+		`Scenario 2` = `Scenario 2`[2] - `Scenario 2`[1],
+		`Scenario 3` = `Scenario 3`[2] - `Scenario 3`[1],
+		`Scenario 4` = `Scenario 4`[2] - `Scenario 4`[1],
+		`Scenario 5` = `Scenario 5`[2] - `Scenario 5`[1]
+	), .(Estimator)]
 
-% Usage
-	% \linenumbers
-	% \modulolinenumbers[2]
-	% \renewcommand\thelinenumber{\color{red}\Roman{linenumber}}
-	% \begin{linenumbers}  \end{linenumbers}
+bias.tab <- data.table(
+	Estimator = c("WKM", "AWKM"),
+	sapply(differences.tab[,-1], function(x) {
+		c(x[2] - x[1], x[3] - x[1])
+	}))
 
-\usepackage{setspace}
-%\doublespacing
+survival.tab[,`:=`(
+	Rule = {Rule <- gsub("Rule ", "", Rule)
+	Rule[duplicated(Rule)] <- ""
+	Rule}
+)]
+```
 
-\usepackage{outlines}
-% \usepackage{enumerate}
-\usepackage{enumitem} % more powerful than enumerate
-% \setenumerate[4]{label=\alph*).}
+# Results
 
-\setlength\parindent{0pt} % Removes all indentation from paragraphs
-
-\usepackage{sectsty} % Allows customizing section commands
-% \renewcommand{\thesection}{\Alph{section}} % Lettered, not numbered sections
-% \allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
-%\numberwithin{equation}{section} % Number equations within sections
-%\numberwithin{figure}{section} % Number figures within sections
-%\numberwithin{table}{section} % Number tables within sections
-
-\usepackage{multicol}
-\setlength{\columnsep}{15pt}
-\newlength\Colsep
-
-%---------------------------------------------------------------------------
-% Tables, figures, images
-%---------------------------------------------------------------------------
-\usepackage{color}
-% \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{xparse}
-\usepackage{xhfill}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0
-% Requires pdfTeX
-\usepackage{linegoal}
-\fi
-
-\usepackage{longtable}
-\setlength{\LTcapwidth}{\textwidth}
-\usepackage{xtab, booktabs}
-\usepackage{multirow}
-\usepackage[flushleft]{threeparttable} % Suzanne's
-
-\usepackage{float} % Check code chunks section for floatrow
-
-\usepackage{graphicx}
-% \usepackage{grffile}
-% \usepackage{subcaption}
-% For tables and figures in parts %%%%
-\usepackage{caption}
-% \DeclareCaptionLabelFormat{cont}{#1~#2\alph{ContinuedFloat}}
-% \captionsetup[ContinuedFloat]{labelformat=cont}
-%\graphicspath{ {file.path.here} }
-
-% Set column widths in tabular environment!
-\usepackage{array}
-\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
-\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
-\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
-\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
-
-% STATA output for `estout` package
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-
-%---------------------------------------------------------------------------
-% Header/footer
-%---------------------------------------------------------------------------
-\usepackage{fancyhdr}
-\pagestyle{fancyplain}
-\fancyhead[L]{}
-\fancyhead[C]{}
-\fancyhead[R]{}
-% \fancyfoot[L]{}
-% \fancyfoot[C]{}
-% \fancyfoot[R]{\thepage}
-\renewcommand{\headrulewidth}{0pt}
-% \renewcommand{\footrulewidth}{0pt}
-\setlength{\headheight}{14.5pt}
-
-%---------------------------------------------------------------------------
-% Supplement (compatible for Beamer and Article)
-%---------------------------------------------------------------------------
-\input{\string~/HeadRs/common_supplement.tex}
-
-%---------------------------------------------------------------------------
-% Bibliography
-%---------------------------------------------------------------------------
-% \usepackage[backend=bibtex]{biblatex}
-
-%---------------------------------------------------------------------------
-% Usage
-%---------------------------------------------------------------------------
-
-% For use in LaTex or Sweave:
-% \input{/Users/kevinchen/Documents/computing/HeadRs/StatHead.tex}
-
-% An example YAML header for Rmd
-% ---
-% title: "Stat 2"
-% author: "Kevin Chen"
-% date: \today
-% output:
-%   pdf_document:
-%      # keep_tex: true
-%     #  pandoc_args: [
-%     #   "-V", "classoption=twocolumn"
-%     # ]
-%      includes:
-%         in_header: /Users/kevinchen/Documents/computing/HeadRs/StatHead.tex
-% bibliography: /Users/kevinchen/Documents/2017 Fa/245/MV_FinalProj/mv_final.bib
-% csl: /Users/kevinchen/Documents/computing/HeadRs/AMA.csl
-% geometry: margin=2cm, bottom=2.5cm
-% ---
-
-%---------------------------------------------------------------------------
-% Fonts
-%---------------------------------------------------------------------------
-
-%\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-%\usepackage[utf8]{inputenc}
-% Latin Modern Roman
-% \usepackage{lmodern}
-%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
-
-\ifluatex
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% For Arial (with lualatex)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[no-math]{fontspec}
-% \setmainfont{Arial}[
-% % Options below necessary for Windows
-% 	% Extension = .ttf,
-% 	% UprightFont = *,
-% 	% BoldFont = *bd,
-% 	% ItalicFont = *i,
-% 	% BoldItalicFont = *bi
-% 	]
-% In YAML
-% ---
-% mainfont: Arial
-% ---
-% \usepackage{lualatex-math}
-
-% Math as text, but numerals do not mpa well becuase
-% mathastext clahes with unicode-math
-% \usepackage[italic]{mathastext}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Estimating survival in left filtered data: simulation and
-application}
-\author{Kevin Chen}
-\date{Stat 256: Causal Inference (Fall 2021)}
-
-\begin{document}
-\maketitle
-
-\fancyhead[R]{Kevin Chen}
-\fancyhead[L]{}
-\renewcommand{\headrulewidth}{0pt}
-
-\onehalfspacing
-\renewcommand{\arraystretch}{1.1}
-
-\thispagestyle{empty}
-
-\setlength{\columnseprule}{0pt}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The United Auto Workers-General Motors (UAW-GM) Cohort Study is a
-longitudinal occupational cohort study established in the early 1980s to
-study the health effects of metalworking fluids (Eisen et al. 1992,
-2001). Metalworking fluids (MWF) are complex mixtures of fluids used in
-industrial metalworking operations to lubricate and cool machinery and
-parts. The three major classes of MWF are straight, soluble, and
-synthetic metalworking fluids (Byers 2006). Possible routes of human
-exposure include absorption through skin, inhalation or aerosols, and
-ingestion of droplets.
-
-A central concern in the analysis of occupational cohorts is the
-potential for the healthy worker survivor effect (HWSE), the phenomenon
-by which healthy individuals remain at work, while less healthy
-individuals leave work -- possibly in response to exposure-related
-health decline. In the presence of the HWSE, those with the highest
-cumulative occupational exposures are also those who are less at risk of
-disease. Thus, standard measures of association would show an inverse
-relationship between occupational exposure and poor health outcomes
-(Arrighi and Hertz-Picciotto 1994). The HWSE is an example of
-time-varying confounding affected by past exposure. Previous studies
-have attempted to assess the presence of the HWSE in observed data by
-assessing so-called path-specific associations using Cox proportional
-hazards modeling (Naimi et al. 2013; Garcia et al. 2017). However, these
-measures of associations are themselves subject to the confounding they
-seek to quantify.
-
-If sequential ignorability of exposure status at each point in follow-up
-and positivity can be attained conditional on covariates, then causal
-methods can be applied to account for the HWSE. Past studies have
-applied causal methods capable of accounting for time-varying
-confounding affected by past exposure to the study of MWF exposures and
-cancer mortality outcomes in the UAW-GM Cohort Study (Garcia et al.
-2018; Izano et al. 2019), but the study of cancer incidence outcomes is
-further problematized by incomplete observation of cancer incidence
-outcomes over the study period. We wish to make inferences about the
-carcinogenicity of MWF exposure over an individual's lifetime starting
-three years after they enter the workforce. The UAW-GM cohort includes
-those hired roughly between 1938 and 1982. However, cancer incidence
-reporting at the Michigan Cancer Registry did not begin until 1985. In
-particular, we have the presence of \emph{left filtering} in the UAW-GM
-Cohort Study when cancer incidence is the outcome of interest: before
-1985, both cancer incidence status and time of cancer incidence are
-unknown. Observation of the complete cancer incidence outcome vector
-over the study period is conditional on an individual surviving to 1985
-cancer-free.
-
-In the presence of the HWSE, left filtering implies outcome
-misclassification that is informative of true cancer status. As part of
-her dissertation research, Izano (2017) conducted a quantitative bias
-analysis for the estimation of survival curves in the presence of left
-filtering and the HWSE. She simulated data compatible with the HWSE and
-estimated cancer-free survival curves using an inverse probability of
-treatment and censoring weighted Kaplan-Meier (WKM) estimator and the
-WKM with an Aalen filter for left-filtering (AWKM) (Andersen et al.
-1993; Xie and Liu 2005). Data were simulated under five different
-scenarios. The causal estimands of interest were the survival curves
-under interventions: (1) always exposed at work with no censoring due to
-death and (2) never exposed at work with no censoring due to death. For
-each intervention, three survival curves were produced: (1) the true
-survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
-The bias in mean survival difference calculated by AWKM was negligible
-when the true 20-year risk of cancer was under 0.25.
-
-Here, we replicate the simulation and bias analysis presented in Chapter
-3 of Izano (2017), embed the problem in the non-parametric structural
-causal approach of Pearl (1995), comment on the results, and apply the
-WKM and AWKM estimators to the UAW-GM Cohort.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{causal-model}{%
-\subsection{Causal model}\label{causal-model}}
-
-The UAW-GM Cohort data includes person-year level exposure, outcome, and
-covariate data starting three years after hire. To emulate the shape of
-the data for this longitudinal cohort, we consider 20 years of data over
-time indexed by years since hire. Notation representing the variables of
-interest are presented in Table \ref{tab:variables}.
-
-\begin{table}
-\caption{Descriptions of variables.}\label{tab:variables}
-\begin{center}
-\begin{tabular}{lp{0.5\linewidth}}
-\toprule
- Variable  &  Description                                 \\ \midrule
- $R$       & Time until start of registry \\
- $W$       & Baseline covariates \\
- $S$       & Susceptibility to effects of metalworking fluid exposure \\
- $H(t)$    & Adverse health status at time $t$ \\
- $N(t)$    & Employment status at time $t$ \\
- $A(t)$    & Metalworking fluid exposure at time $t$ \\
- $D(t)$    & Mortality status at time $t$ \\
- $Y^*(t)$  & Cancer status at time $t$ \\
- $Y(t)$    & Observed Cancer status at time $t$ \\
- $t = \{1, 2, \ldots, 20\}$ & Time, indexed in years after hire \\
- \bottomrule
-\end{tabular}
-\end{center}\end{table}
-
-Assume we have \(n = 50\,000\) iid units in \(X\) with
-\[X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).\]
-The bar notation to indicates variable history where
-\(\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t\). In the case of
-exposure, \(\bar A_i(t)\) is the indicator of whether unit \(i\) was
-ever exposed through time \(t\). Note that true cancer status \(Y^*(t)\)
-not observed until \(t \ge R\), after the start of the registry. Call
-\(X\) the full data, where we have \(R = 0\) for all. In the observed
-data \(X^\text{obs}\), we cannot assume \(R = 0\) for all, and
-susceptibility \(S\) is not known:
-\[X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).\]
-Under the causal model, we assume the following non-parametric
-structural equations: \[\begin{aligned}
-R     & = f_R \left( U_R \right) \\
-W     & = f_W \left( U_W \right) \\
-S     & = f_S \left( U_S \right) \\
-H(t)  & = f_{H(t)} \left( H(t - 1), U_{H(t)} \right) \\
-N(t)  & = f_{N(t)} \left( W, N(t - 1), H(t), A(t - 1), U_{N(t)} \right) \\
-A(t)  & = f_{A(t)} \left( W, \bar A(t - 1), N(t), U_{A(t)} \right) \\
-D(t)  & = f_{D(t)} \left( W, \bar A(t - 1), D(t - 1), Y^*(t - 1), U_{D(t)} \right) \\
-Y^*(t)& = f_{Y^*(t)} \left(W, S, H(t), \bar A (t), D(t), Y^*(t - 1), U_{Y^*(t)} \right) \\
-Y(t) & = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0} \ .
-\end{aligned}\] The exogenous variables (errors)
-\(U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}\)
-are mutually independent. Exposure status is a time-varying indicator;
-let exposure history \(\bar A(t)\) be summarized as being ever-exposed
-or not with \(\bar A(t) = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}\). The
-outcome of interest is a survival outcome, so
-\(Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1\). The observed outcome \(Y(t)\)
-at time \(t\) is a function of true outcome status and the time points
-delimiting left and right censoring. An abbreviated directed acyclic
-graph (DAG) representing the causal relationships encoded in the
-equations above is presented in Figure \ref{fig:dag}.
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$.}
-\label{fig:dag}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-\path[->] (W) edge [bend right=10] (N);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-\path[->] (A0) edge (N);
-\path[->] (W) edge [bend right=15] (A);
-\path[->] (A0) edge (A);
-\path[->] (N) edge (A);
-\path[->] (W) edge (D);
-\path[->] (A0) edge [bend left=15] (D);
-\path[->] (D0) edge [bend right=15] (D);
-\path[->] (Y0) edge [bend right=10] (D);
-\path[->] (W) edge [bend left=5] (Y);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\hypertarget{simulation}{%
-\subsection{Simulation}\label{simulation}}
-
-Parametric relationships between the variables were imposed in
-simulations. For the \(n = 50\,000\) units over \(T = 20\) years, we
-have:
-
-\begin{itemize}
-\tightlist
-\item
-  \(U_j \overset{\text{iid}}{\sim} \text{uniform}\,[0,1]\) for all \(j\)
-\item
-  In full data \(R = 0\) otherwise \(R \sim \text{uniform}\,[0, 30]\)
-\item
-  \(W = \Ind{U_W \le p_W} \sim \text{Bernoulli}\left( p_W \right)\)
-\item
-  \(S = \Ind{U_S \le p_S} \sim \text{Bernoulli}\,(p_S)\)
-\item
-  If \(H(t - 1) = 1\), then \(H(t) = 1\) otherwise
-  \(H(t) = \Ind{U_{H(t)} \le p_H} \sim \text{Bernoulli}\,(p_H)\)
-\item
-  if \(N(t - 1) = 0\) then \(N(t) = 0\) otherwise
-  \[N(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(
-        \beta_0^N
-        + \beta_W^N W
-        + \beta_H^N H(t)
-        + \beta_A^N A(t - 1) \times \Ind{t > 1}
-        + U_{N(t)}
-    \right)
-    \right\}\]
-\item
-  If \(N(t) = 0\) then \(A(t) = 0\) otherwise
-  \[A(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(
-        \left( \beta_0^A + \beta_W^A W\right) \times \Ind{t = 1}
-        + \beta_A^A A(t - 1) \times \Ind{t > 1}
-        + U_{A(t)}
-    \right)
-    \right\}\]
-\item
-  If \(D(t - 1) = 1\) then \(D(t) = 1\) otherwise
-  \[D(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(\begin{aligned}
-        \beta_0^D
-        + \beta_W^D W
-        + \beta_{\bar A}^D \bar A(t - 1) \times \Ind{t > 1} \\
-        + \beta_{\bar Y}^D \sum_{k = 1}^{t - 1} Y^*(k) \times \Ind{t > 1}
-        + U_{D(t)}
-    \end{aligned}\right)
-    \right\}\]
-\item
-  If \(Y^*(t - 1) = 1\) then \(Y^*(t) = 1\) otherwise
-  \[Y^*(t) \sim \text{Bernoulli}\left\{
-    \text{logit}\,\left(\begin{aligned}
-        \beta_0^Y
-        + \beta_W^Y W
-        + \beta_{A}^Y A(t)
-        + \beta_{\bar A}^Y \bar A(t - 1) \times \Ind{t > 1} \\
-        + \beta_{S}^Y S \times \bar A(t)
-        + \beta_{H}^Y H(t)
-        + U_{Y^*(t)}
-    \end{aligned}\right)
-    \right\}\]
-\item
-  If \(t < R\) then \(Y(t) = 0\)
-\item
-  If \(t \ge R\) then
-  \(Y(t) = Y^*(t) \times \Ind{Y^*(\lfloor R \rfloor) = 0} \times \Ind{D(t) = 0}\).
-\end{itemize}
-
-Five sets of data were generated using these equations to represent five
-scenarios. Scenario 1 represents the base case where 10\% of workers are
-susceptible to exposure-related effects, the odds ratio of mortality
-each additional year following cancer diagnosis is about 1.6, and there
-is moderate time-varying confounding by health status. In scenario 2, we
-have greater cancer-related mortality by increasing
-\(\beta_{\bar Y}^D\). In scenario 3, we increase \(p_S\), the proportion
-of the study population susceptible to the carcinogenic effects of MWF
-exposure. In scenario 4, we consider greater time-varying confounding by
-health status by increasing \(\beta_H^N\) and \(\beta_H^Y\). In the last
-scenario, we have greater background cancer incidence by increasing
-\(\beta_0^Y\). The sets of parameters used in the five scenarios are
-presented in Table \ref{tab:params}.
-
-\begin{table}
-\caption{Simulation parameters.}
-\label{tab:params}
-\begin{center}
-\begin{tabular}{rrrrrr}
-  \toprule
-Parameter & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-$p_S$ & 0.10 & 0.10 & \textbf{0.20} & 0.10 & 0.10 \\ 
-  $p_W$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
-  $p_H$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
-  $\beta_0^N$ & 3.00 & 3.00 & 3.00 & 3.00 & 3.00 \\ 
-  $\beta_W^N$ & -0.10 & -0.10 & -0.10 & -0.10 & -0.10 \\ 
-  $\beta_H^N$ & -0.50 & -0.50 & -0.50 & \textbf{-1.50} & -0.50 \\ 
-  $\beta_A^N$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
-  $\beta_0^A$ & -1.50 & -1.50 & -1.50 & -1.50 & -1.50 \\ 
-  $\beta_W^A$ & -0.50 & -0.50 & -0.50 & -0.50 & -0.50 \\ 
-  $\beta_A^A$ & 2.50 & 2.50 & 2.50 & 2.50 & 2.50 \\ 
-  $\beta_0^D$ & -5.50 & -5.50 & -5.50 & -5.50 & -5.50 \\ 
-  $\beta_W^D$ & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
-  $\beta_{\bar A}^D$ & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\ 
-  $\beta_{\bar Y}^D$ & 0.50 & \textbf{2.00} & 0.50 & 0.50 & 0.50 \\ 
-  $\beta_0^Y$ & -7.00 & -7.00 & -7.00 & -7.00 & \textbf{-6.00} \\ 
-  $\beta_W^Y$ & 2.00 & 2.00 & 2.00 & 2.00 & 2.00 \\ 
-  $\beta_A^Y$ & 0.25 & 0.25 & 0.25 & 0.25 & 0.25 \\ 
-  $\beta_{\bar A}^Y$ & 0.20 & 0.20 & 0.20 & 0.20 & 0.20 \\ 
-  $\beta_H^Y$ & 0.70 & 0.70 & 0.70 & \textbf{1.70} & 0.70 \\ 
-  $\beta_S^Y$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 \\ 
-   \bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\hypertarget{interventions-potential-outcomes-target-parameters-and-estimation}{%
-\subsection{Interventions, potential outcomes, target parameters, and
-estimation}\label{interventions-potential-outcomes-target-parameters-and-estimation}}
-
-The substantive question of interest is the causal effect of
-occupational exposure to MWF on cancer incidence risk. Since
-occupational MWF exposure occurs only when individuals are at work, we
-define dynamic exposure regimes that depend on employment status. Under
-rule \(a_0\), set \(D(t) = 0\), and set \(A(t) = 0\) while \(N(t) = 1\).
-Under rule \(a_1\), set \(D(t) = 0\), and set \(A(t) = 1\) while
-\(N(t) = 1\). Under both rules, we prevent censoring by death as if it
-were intervenable. The causal effect is defined by contrasting the
-survival function \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule \(a_1\)
-to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\). Note
-that this causal estimand is defined over \emph{a priori
-counterfactuals} not observable in the real world (Frangakis and Rubin
-2002). This approach is standard in epidemiologic studies, however.
-
-The survival function expresses the probability that a person following
-rule \(a\) is cancer-free at the end of time point \(t\). The expected
-time until cancer under rule \(a\) is
-\(\mu_{a} = \sum_0^K S_{a}(t) \, dt\). Our causal estimand is summary
-measure \(\psi = \mu_{a_1} - \mu_{a_0}\), the difference in expected
-time until event under two different interventions over 20 years of
-follow-up under five different data generating scenarios. Bias will be
-evaluated by comparing estimates of \(\psi\) to its true value in 250
-simulations per scenario (the original analysis performed 500). The true
-value will be calculated by simulating the full data for five hundred
-thousand individuals (the original analysis used one million) with rules
-\(a_0\) and \(a_1\) applied deterministically. Estimates of \(\psi\)
-will be obtained by first estimating the survival curves \(S_a(t)\)
-using two estimators: the inverse probability weighted Kaplan-Meier
-estimator (WKM) and the Aalen-filtered WKM (AWKM). These survival
-estimators are detailed in the following section.
-
-\hypertarget{kaplan-meier-estimator-and-extensions}{%
-\subsection{Kaplan-Meier estimator and
-extensions}\label{kaplan-meier-estimator-and-extensions}}
-
-To estimate survival, we applied extensions of the widely-known
-Kaplan-Meier (KM) estimator for survival (Kaplan and Meier 1958). First,
-we review the estimator of Xie and Liu (2005), an extension of the KM
-estimator where units are weighted by the inverse probability of
-treatment. The standard KM estimator requires counting up the number of
-cases \(c^0_{a}(t)\) that occurred in interval \((t - 1, t]\) and the
-number of units at risk \(R^0_{a}(t)\) in that interval at all event
-times \(t\). Assuming cancer status was assessed at the end of regular
-intervals \(t = 1, \ldots, K\), we have: \[\begin{aligned}
-c^0_{a} (t)
-& = \sum_i^n \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \\
-R^0_{a} (t)
-& = \sum_i^n \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}.
-\end{aligned}\] The standard survival estimator is \[\hat S^0_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-In observational studies, survival contrasts estimated using the
-standard KM estimator are biased for the true causal survival contrast.
-However, if conditional ignorability and positivity are attained, the
-inverse probability weighted KM (WKM) estimator of Xie and Liu (2005)
-yields unbiased estimates of the true causal survival curve. The WKM
-estimator augments the standard KM estimator by weighting units at time
-\(t\) by \(w_{i, a}(t)\) the inverse probability of treatment:
-\[\begin{aligned}
-c^w_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}\\
-R^w_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}
-\end{aligned}\] The WKM survival estimator for rule \(a\) is
-\[\hat S^w_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^w_{a}(j)}{R^w_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-Finally, to account for (uninformative) left filtering, we applied the
-Aalen filter, which considers only the units at time \(t\) for which the
-outcome is observed: \[\begin{aligned}
-c_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
-R_{a} (t)
-& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
-\end{aligned}\] The Aalen-filtered WKM (AWKM) estimator for rule \(a\)
-is \[\hat S_{a}(t) =
-\begin{cases}
-1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
-\end{cases}\] where \(t_1\) is the first event time.
-
-In the full data, the WKM and AWKM estimators are equivalent, and
-identification is achieved under overlap (positivity) and sequential
-ignorability (randomization) assumptions: \[\begin{aligned}
-Y^*_{a, \bar d = 0} (t')   & \indep A(t) \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1\\
-Y^*_{a, \bar d = 0} (t') & \indep D(t) \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)
-\end{aligned}\] for all times \(t'\ge t\), and
-\[0 < \Prob{ A(t) = 1 \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1} < 1\]
-\[0 < \Prob{D(t) = 0 \mid W,\ D(t - 1) = 0,\ Y^*(t - 1) = 0,\ \bar A(t - 1) = \bar a(t - 1)} < 1.\]
-
-Graphical representations of the first and second components of the
-ignorability assumption are presented in Figures
-\ref{fig:ignorability_a} and \ref{fig:ignorability_d} where conditioning
-on boxed variables are represented by the removal of edges pointing away
-from those variables. The resulting graphs show the fulfillment of
-Pearl's backdoor criterion for the estimation of the causal effects of
-\(\bar A(t)\) on \(Y^*(t)\) and \(D(t)\) on \(Y^*(t)\), respectively.
-Thus, the causal effect of the joint intervention on
-\(\big(\bar A(t), D(t)\big)\) at each time \(t\) is identified. Causal
-identification is not attained when true cancer status \(Y^*(t)\) is not
-known.
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ N(t)\}$.}
-\label{fig:ignorability_a}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [shape=rectangle, draw=black, inner sep=2.5pt, above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [shape=rectangle, draw=black, inner sep=2.5pt, below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-\path[->] (Y0) edge [bend right=10] (D);
-\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\caption{Directed acyclic graph representing the causal relationships encoded in the non-parametric structural equation model at time $t$ after conditioning on $\{W,\ \bar A(t - 1),\ D(t - 1),\ Y^*(t - 1)\}$.}
-\label{fig:ignorability_d}
-\begin{center}
-\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
-\tikzstyle{every state}=[shape = circle, align = center, draw = none]
-\node[state] (H0) {$H(t - 1)$};
-\node[state] (N0) [below right of=H0] {$N(t - 1)$};
-\node[state] (A0) [shape=rectangle, draw=black, inner sep=2pt, below right of=N0] {$\bar A(t - 1)$};
-\node[state] (D0) [shape=rectangle, draw=black, inner sep=2pt, below right of=A0] {$D(t - 1)$};
-\node[state] (Y0) [shape=rectangle, draw=black, inner sep=2pt, below right of=D0] {$Y^*(t - 1)$};
-\node[state] (W) [shape=rectangle, draw=black, inner sep=2pt, above right of=H0] {$W$};
-\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
-\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
-\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
-\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
-\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
-\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
-%
-\path[->] (H0) edge (H);
-%\path[->] (W) edge [bend right=10] (N);
-\path[->] (N0) edge (N);
-\path[->] (H) edge (N);
-%\path[->] (A0) edge (N);
-%\path[->] (W) edge [bend right=15] (A);
-%\path[->] (A0) edge (A);
-\path[->] (N) edge (A);
-%\path[->] (W) edge (D);
-%\path[->] (A0) edge [bend left=15] (D);
-%\path[->] (D0) edge [bend right=15] (D);
-%\path[->] (Y0) edge [bend right=10] (D);
-%\path[->] (W) edge [bend left=5] (Y);
-\path[->] (S) edge [bend left=30] (Y);
-\path[->] (S) edge [bend left=15] (Y0);
-\path[->] (H) edge (Y);
-\path[->] (A) edge (Y);
-\path[->] (D) edge (Y);
-%\path[->] (Y0) edge (Y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
-
-\hypertarget{estimation-of-weights}{%
-\subsection{Estimation of weights}\label{estimation-of-weights}}
-
-To estimate the weights for the WKM and AWKM estimators, we fit two
-logistic regressions at each time point \(t = 1, \ldots 20\):
-\[\begin{aligned}
-\text{logit} \left(\Prob{
-    A(t) = 1
-    \mid W,\ \bar A(t - 1),\ D(t - 1) = 0,\ N(t) = 1
-    }\right)
-& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
-\text{logit} \left(\Prob{
-    D(t) = 1
-    \mid W,\ D(t - 1) = 0,\ Y(t - 1) = 0,\ \bar A(t - 1)}\right)
-    & = \beta_0 + W \beta_1 + \bar A(t - 1) \beta_2
-\end{aligned}\] The first will be fitted on data for those alive and at
-work at time \(t\). The second will be among those alive and (observed
-to be) cancer-free. For each unit at time \(t\), the weight will be
-calculated by taking the inverse of the cumulative probability of
-following the exposure rule and remaining uncensored: \[\hat w_{a} (t) =
-    \left[
-    \prod^t_{j = 1}
-    \begin{aligned}
-    \widehat {\mathbb P} \left\{
-    A(j) = a(j) \mid W,\ \bar A(j - 1) = \bar a (j - 1),\ D(j - 1) = 0,\ N(j) = 1
-    \right\} \times \\
-    \widehat {\mathbb P} \left\{D(j) = 0
-    \mid W,\ D(j - 1) = 0,\ Y(j - 1) = 0,\ \bar A(j) = \bar a (j) \right\}
-    \end{aligned}\right]^{-1}.\]
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Figure \ref{fig:survival} presents the true survival curves as well as
-the WKM and AWKM survival curves averaged over 250 replications for each
-intervention rule and scenario. Qualitatively, the WKM estimator
-consistently over-estimates survival whereas the the AWKM survival curve
-is much closer to the truth. The bias of the AWKM survival estimate
-appears to be larger earlier in follow-up and smaller as follow-up
-extends forward. The bias of both the the WKM and the AWKM survival
-curves appears largest in Scenario 5.
+Figure \ref{fig:survival} presents the true survival curves as well as the WKM and AWKM survival curves averaged over 250 replications for each intervention rule and scenario.
+Qualitatively, the WKM estimator consistently over-estimates survival whereas the the AWKM survival curve is much closer to the truth.
+The bias of the AWKM survival estimate appears to be larger earlier in follow-up and smaller as follow-up extends forward.
+The bias of both the the WKM and the AWKM survival curves appears largest in Scenario 5.
 
@@
 \begin{center}
-\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/results.pdf}
+\includegraphics{`r here::here("reports/resources", "results.pdf")`}
 \end{center}
@@
 
-Table \ref{tab:survival} presents true and estimated average cancer-free
-survival times under each intervention rule and scenario. Table
-\ref{tab:differences} presents differences in survival time contrasting
-rule \(a_1\) to rule \(a_0\). Table \ref{tab:bias} presents estimates of
-the bias of the WKM and AWKM estimators for \(\psi\), the difference in
-average cancer-free survival time over 20 years of follow-up. These
-numeric results are consistent with the qualitative interpretations of
-Figure \ref{fig:survival}. The WKM estimator over-estimates the
-difference in cancer-free survival time, resulting in bias toward the
-null, whereas the AWKM estimator under-estimates the cancer-free
-survival, resulting in bias away from the null. In every scenario, the
-bias of the WKM-derived contrast is several times larger in magnitude
-than that of the AWKM-derived contrast. The bias of both estimators is
-greatest for Scenario 5.
+Table \ref{tab:survival} presents true and estimated average cancer-free survival times under each intervention rule and scenario.
+Table \ref{tab:differences} presents differences in survival time contrasting rule $a_1$ to rule $a_0$.
+Table \ref{tab:bias} presents estimates of the bias of the WKM and AWKM estimators for $\psi$, the difference in average cancer-free survival time over 20 years of follow-up.
+These numeric results are consistent with the qualitative interpretations of Figure \ref{fig:survival}.
+The WKM estimator over-estimates the difference in cancer-free survival time, resulting in bias toward the null, whereas the AWKM estimator under-estimates the cancer-free survival, resulting in bias away from the null.
+In every scenario, the bias of the WKM-derived contrast is several times larger in magnitude than that of the AWKM-derived contrast.
+The bias of both estimators is greatest for Scenario 5.
 
-The qualitative results here are consistent with those of Izano (2017).
-However, true and estimated survival in the present analysis is larger
-than those found previously. Furthermore, the true and estimator average
-mean differences in survival are smaller in magnitude in the present
-case. The magnitudes of the bias estimates are also smaller.
+The qualitative results here are consistent with those of @Izano_2017_thesis.
+However, true and estimated survival in the present analysis is larger than those found previously.
+Furthermore, the true and estimator average mean differences in survival are smaller in magnitude in the present case.
+The magnitudes of the bias estimates are also smaller.
 
-\begin{table}[H]
-\centering
-\caption{True cancer-free survival time $\mu_{a}$ over 20-year follow-up and estimator averages over 250 replicates.} 
-\label{tab:survival}
-\begin{tabular}{llrrrrr}
-  \toprule
-Rule & Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-$a_0$ & Truth & 19.08 & 19.10 & 19.10 & 18.02 & 17.83 \\ 
-   & WKM & 19.52 & 19.51 & 19.53 & 18.92 & 18.90 \\ 
-   & AWKM & 19.02 & 19.00 & 19.02 & 17.79 & 17.72 \\ 
-   \midrule
-$a_1$ & Truth & 18.80 & 18.79 & 18.76 & 17.54 & 17.29 \\ 
-   & WKM & 19.39 & 19.37 & 19.37 & 18.68 & 18.62 \\ 
-   & AWKM & 18.70 & 18.67 & 18.67 & 17.30 & 17.07 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
-\begin{table}[H]
-\centering
-\caption{Difference in average cancer-free survival time over 20-year follow-up comparing rule $a_1$ always exposed to rule $a_0$ never exposed at work: true value $\psi$ and estimator averages over 250 replicates.}
-\label{tab:differences}
-\begin{tabular}{lrrrrr}
-  \toprule
-Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-Truth & -0.28 & -0.31 & -0.34 & -0.48 & -0.54 \\ 
-  WKM & -0.14 & -0.15 & -0.15 & -0.23 & -0.28 \\ 
-  AWKM & -0.31 & -0.33 & -0.35 & -0.50 & -0.64 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
-\begin{table}[H]
-\centering
-\caption{Bias estimates of estimators for $\psi$, the difference in average cancer-free survival time over 20 years of follow-up.} 
-\label{tab:bias}
-\begin{tabular}{lrrrrr}
-  \toprule
-Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
-  \midrule
-WKM & 0.14 & 0.16 & 0.19 & 0.25 & 0.26 \\ 
-  AWKM & -0.03 & -0.02 & -0.01 & -0.02 & -0.10 \\ 
-   \bottomrule
-\end{tabular}
-\end{table}
+```{r}
+print(xtable(survival.tab,
+			 caption = "True cancer-free survival time $\\mu_{a}$ over 20-year follow-up and estimator averages over 250 replicates.",
+			 label = "tab:survival"),
+			hline.after = c(-1,0,3, nrow(survival.tab)),
+			floating = T)
 
-\newpage
+print(xtable(
+	differences.tab,
+	caption = "Difference in average cancer-free survival time over 20-year follow-up comparing rule $a_1$ always exposed to rule $a_0$ never exposed at work: true value $\\psi$ and estimator averages over 250 replicates.",
+	label = "tab:differences"),
+	floating = T)
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Andersen_1993}{}%
-Andersen, P. K., Ø. Borgan, R. D. Gill, and N. Keiding. 1993.
-\emph{Statistical Models Based on Counting Processes}. Springer Series
-in Statistics. Springer, New York, NY.
-\url{https://books.google.com/books?id=kBnvAAAAMAAJ}.
-
-\leavevmode\hypertarget{ref-Arrighi_1994}{}%
-Arrighi, H. Michael, and Irva Hertz-Picciotto. 1994. {``The Evolving
-Concept of the Healthy Worker Survivor Effect.''} \emph{Epidemiology} 5
-(2): 189--96. \url{http://www.jstor.org/stable/3702361}.
-
-\leavevmode\hypertarget{ref-Byers_2006}{}%
-Byers, Jerry P. 2006. \emph{Metalworking Fluids}. CRC Press.
-
-\leavevmode\hypertarget{ref-Eisen_2001}{}%
-Eisen, Ellen A, Judith Bardin, Rebecca Gore, Susan R Woskie, Marilyn F
-Hallock, and Richard R Monson. 2001. {``Exposure-Response Models Based
-on Extended Follow-up of a Cohort Mortality Study in the Automobile
-Industry.''} \emph{Scandinavian Journal of Work, Environment \& Health}
-27 (4): 240--49.
-
-\leavevmode\hypertarget{ref-Eisen_1992}{}%
-Eisen, Ellen A, Paige E Tolbert, Richard R Monson, and Thomas J Smith.
-1992. {``Mortality Studies of Machining Fluid Exposure in the Automobile
-Industry {I}: A Standardized Mortality Ratio Analysis.''} \emph{American
-Journal of Industrial Medicine} 22 (6): 809--24.
-
-\leavevmode\hypertarget{ref-Frangakis_2002}{}%
-Frangakis, Constantine E, and Donald B Rubin. 2002. {``Principal
-Stratification in Causal Inference.''} \emph{Biometrics} 58 (1): 21--29.
-
-\leavevmode\hypertarget{ref-Garcia_2017}{}%
-Garcia, Erika, Sally Picciotto, Sadie Costello, Patrick T Bradshaw, and
-Ellen A Eisen. 2017. {``Assessment of the Healthy Worker Survivor Effect
-in Cancer Studies of the United Autoworkers-General Motors Cohort.''}
-\emph{Occupational and Environmental Medicine} 74 (4): 294--300.
-
-\leavevmode\hypertarget{ref-Garcia_2018}{}%
-Garcia, Erika, Sally Picciotto, Andreas M Neophytou, Patrick T Bradshaw,
-John R Balmes, and Ellen A Eisen. 2018. {``Lung Cancer Mortality and
-Exposure to Synthetic Metalworking Fluid and Biocides: Controlling for
-the Healthy Worker Survivor Effect.''} \emph{Occupational and
-Environmental Medicine} 75 (10): 730--35.
-
-\leavevmode\hypertarget{ref-Izano_2017_thesis}{}%
-Izano, Monika A. 2017. {``Estimating Causal Effects of Occupational
-Exposures.''} PhD thesis, University of California, Berkeley; University
-of California, Berkeley.
-
-\leavevmode\hypertarget{ref-Izano_2019}{}%
-Izano, Monika A, Oleg A Sofrygin, Sally Picciotto, Patrick T Bradshaw,
-and Ellen A Eisen. 2019. {``Metalworking Fluids and Colon Cancer Risk:
-Longitudinal Targeted Minimum Loss-Based Estimation.''}
-\emph{Environmental Epidemiology} 3 (1): e035.
-
-\leavevmode\hypertarget{ref-Kaplan_1958}{}%
-Kaplan, Edward L, and Paul Meier. 1958. {``Nonparametric Estimation from
-Incomplete Observations.''} \emph{Journal of the American Statistical
-Association} 53 (282): 457--81.
-
-\leavevmode\hypertarget{ref-Naimi_2013}{}%
-Naimi, Ashley I, Stephen R Cole, Michael G Hudgens, M Alan Brookhart,
-and David B Richardson. 2013. {``Assessing the Component Associations of
-the Healthy Worker Survivor Bias: Occupational Asbestos Exposure and
-Lung Cancer Mortality.''} \emph{Annals of Epidemiology} 23 (6): 334--41.
-
-\leavevmode\hypertarget{ref-Pearl_1995}{}%
-Pearl, Judea. 1995. {``Causal Diagrams for Empirical Research.''}
-\emph{Biometrika} 82 (4): 669--88.
-
-\leavevmode\hypertarget{ref-Xie_2005}{}%
-Xie, Jun, and Chaofeng Liu. 2005. {``Adjusted Kaplan--Meier Estimator
-and Log-Rank Test with Inverse Probability of Treatment Weighting for
-Survival Data.''} \emph{Statistics in Medicine} 24 (20): 3089--3110.
-
-\end{CSLReferences}
-
-\end{document}
+print(xtable(
+	bias.tab,
+	caption = "Bias estimates of estimators for $\\psi$, the difference in average cancer-free survival time over 20 years of follow-up.",
+	label = "tab:bias"),
+	floating = T)
+```

### 2021-12-10 reports/04-gm.Rmd
First commit; interim results from simulation

---
output:
  pdf_document:
    includes:
      in_header: "~/headRs/StatHead.sty"
fontsize: 11pt
bibliography: "../../causal.bib"
# csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

# Application to the UAW-GM Cohort

In the simulation study, we showed that under several scenarios compatible with our hypothetical causal structure, the AWKM survival estimator had small bias compared to the WKM estimator. The bias was smaller when the cumulative incidence of the outcome was low and at later follow-up time points. Now, we estimate cancer-free survival in a real-world context. Using data from the UAW-GM Cohort study, we follow individuals starting from hire to 40 years after hire for incidence of colon cancer. This duration of follow-up spans the vast majority of individuals' working lifetimes.

Colon cancer incidence was obtained via linkage to the Michigan Cancer Registry, which recorded cancer incidence cases starting on January 1, 1985.
<!-- and linkage to Surveillance, Epidemiology, and End Results (SEER), which recorded cancer incidence cases starting on January 1, 1973. -->
The cohort is comprised of individuals hired between 1938 and 1985. Cancer-free survival to the start of the registry is a left-filtering process possibly in the presence of the HWSE as investigated in the simulations. Over the 40 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW. Baseline confounders included race, sex, plant, and year of hire. Time-varying confounders included age, cumulative time off, and exposure to the metalworking fluids not under study. Representations of these terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every year of follow-up. The exposure rules of interest were identical to those in the simulation study: $a_0$ never exposed and $a_1$ always exposed while at work. We assume that the effect of exposure on health status, mortality, cancer incidence, etc occurs after a lag of 15 years. Similarly, we assume that the effects of cumulative time off occur after a 15 year lag. Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.

```{r, eval=F}
mwf <- NULL
source(here("scripts", "04-application.R"))
```

### 2021-12-10 reports/05-discussion.Rmd
First commit; interim results from simulation

---
output:
  pdf_document:
    includes:
      in_header: "~/headRs/StatHead.sty"
fontsize: 11pt
bibliography: "../../causal.bib"
# csl: "`r path.expand('~/HeadRs/csl/ama.csl')`"
---

- FU in GM is much longer than 20 years
- Exclusion restriction on $H$ so that its parents do not include $A$ is not necessary for identification in full data
- Exclusion restriction on $D$ so that its parents do not include $H$ not needed if $H$ is observed and conditioned upon
- Not clear if these were for convenience or what
- What if we increase FU? Lags?
- No way to verify to what extent the simulation informs the real data generating system

### 2021-12-10 reports/resources/results.tex
First commit; interim results from simulation

% Created by tikzDevice version 0.12.3.1 on 2021-12-09 11:35:50
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,542.02);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,542.02);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,465.69) --
	(306.77,465.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,492.39) --
	(306.77,492.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,519.09) --
	(306.77,519.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,446.55) --
	( 63.65,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,446.55) --
	(129.54,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,446.55) --
	(195.42,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,446.55) --
	(261.31,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,452.35) --
	(306.77,452.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,479.04) --
	(306.77,479.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,505.74) --
	(306.77,505.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,532.44) --
	(306.77,532.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,446.55) --
	( 96.59,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,446.55) --
	(162.48,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,446.55) --
	(228.36,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,446.55) --
	(294.25,536.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,531.30) --
	( 96.59,531.30) --
	( 96.59,529.92) --
	(109.77,529.92) --
	(109.77,528.40) --
	(122.95,528.40) --
	(122.95,526.64) --
	(136.12,526.64) --
	(136.12,525.13) --
	(149.30,525.13) --
	(149.30,523.36) --
	(162.48,523.36) --
	(162.48,521.51) --
	(175.66,521.51) --
	(175.66,519.69) --
	(188.83,519.69) --
	(188.83,518.12) --
	(202.01,518.12) --
	(202.01,516.55) --
	(215.19,516.55) --
	(215.19,514.77) --
	(228.36,514.77) --
	(228.36,513.09) --
	(241.54,513.09) --
	(241.54,511.55) --
	(254.72,511.55) --
	(254.72,509.95) --
	(267.89,509.95) --
	(267.89,508.39) --
	(281.07,508.39) --
	(281.07,506.83) --
	(294.25,506.83) --
	(294.25,501.31);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,530.68) --
	( 96.59,530.68) --
	( 96.59,528.65) --
	(109.77,528.65) --
	(109.77,526.44) --
	(122.95,526.44) --
	(122.95,524.39) --
	(136.12,524.39) --
	(136.12,522.13) --
	(149.30,522.13) --
	(149.30,519.74) --
	(162.48,519.74) --
	(162.48,517.64) --
	(175.66,517.64) --
	(175.66,515.55) --
	(188.83,515.55) --
	(188.83,513.42) --
	(202.01,513.42) --
	(202.01,511.30) --
	(215.19,511.30) --
	(215.19,509.43) --
	(228.36,509.43) --
	(228.36,507.50) --
	(241.54,507.50) --
	(241.54,505.67) --
	(254.72,505.67) --
	(254.72,503.67) --
	(267.89,503.67) --
	(267.89,501.87) --
	(281.07,501.87) --
	(281.07,500.13) --
	(294.25,500.13) --
	(294.25,493.53);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.29) --
	( 70.24,532.29) --
	( 70.24,532.07) --
	( 83.42,532.07) --
	( 83.42,531.75) --
	( 96.59,531.75) --
	( 96.59,531.34) --
	(109.77,531.34) --
	(109.77,530.83) --
	(122.95,530.83) --
	(122.95,530.24) --
	(136.12,530.24) --
	(136.12,529.56) --
	(149.30,529.56) --
	(149.30,528.80) --
	(162.48,528.80) --
	(162.48,527.94) --
	(175.66,527.94) --
	(175.66,526.99) --
	(188.83,526.99) --
	(188.83,525.97) --
	(202.01,525.97) --
	(202.01,524.86) --
	(215.19,524.86) --
	(215.19,523.67) --
	(228.36,523.67) --
	(228.36,522.42) --
	(241.54,522.42) --
	(241.54,521.08) --
	(254.72,521.08) --
	(254.72,519.67) --
	(267.89,519.67) --
	(267.89,518.18) --
	(281.07,518.18) --
	(281.07,516.64) --
	(294.25,516.64) --
	(294.25,515.02);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.22) --
	( 70.24,532.22) --
	( 70.24,531.89) --
	( 83.42,531.89) --
	( 83.42,531.43) --
	( 96.59,531.43) --
	( 96.59,530.86) --
	(109.77,530.86) --
	(109.77,530.19) --
	(122.95,530.19) --
	(122.95,529.41) --
	(136.12,529.41) --
	(136.12,528.53) --
	(149.30,528.53) --
	(149.30,527.54) --
	(162.48,527.54) --
	(162.48,526.46) --
	(175.66,526.46) --
	(175.66,525.27) --
	(188.83,525.27) --
	(188.83,523.99) --
	(202.01,523.99) --
	(202.01,522.62) --
	(215.19,522.62) --
	(215.19,521.16) --
	(228.36,521.16) --
	(228.36,519.61) --
	(241.54,519.61) --
	(241.54,517.96) --
	(254.72,517.96) --
	(254.72,516.23) --
	(267.89,516.23) --
	(267.89,514.43) --
	(281.07,514.43) --
	(281.07,512.53) --
	(294.25,512.53) --
	(294.25,510.60);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.49) --
	( 70.24,531.49) --
	( 70.24,530.36) --
	( 83.42,530.36) --
	( 83.42,529.08) --
	( 96.59,529.08) --
	( 96.59,527.72) --
	(109.77,527.72) --
	(109.77,526.29) --
	(122.95,526.29) --
	(122.95,524.82) --
	(136.12,524.82) --
	(136.12,523.34) --
	(149.30,523.34) --
	(149.30,521.83) --
	(162.48,521.83) --
	(162.48,520.30) --
	(175.66,520.30) --
	(175.66,518.75) --
	(188.83,518.75) --
	(188.83,517.21) --
	(202.01,517.21) --
	(202.01,515.66) --
	(215.19,515.66) --
	(215.19,514.12) --
	(228.36,514.12) --
	(228.36,512.61) --
	(241.54,512.61) --
	(241.54,511.09) --
	(254.72,511.09) --
	(254.72,509.58) --
	(267.89,509.58) --
	(267.89,508.07) --
	(281.07,508.07) --
	(281.07,506.59) --
	(294.25,506.59) --
	(294.25,505.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,530.98) --
	( 70.24,530.98) --
	( 70.24,529.33) --
	( 83.42,529.33) --
	( 83.42,527.51) --
	( 96.59,527.51) --
	( 96.59,525.64) --
	(109.77,525.64) --
	(109.77,523.73) --
	(122.95,523.73) --
	(122.95,521.81) --
	(136.12,521.81) --
	(136.12,519.88) --
	(149.30,519.88) --
	(149.30,517.95) --
	(162.48,517.95) --
	(162.48,516.03) --
	(175.66,516.03) --
	(175.66,514.10) --
	(188.83,514.10) --
	(188.83,512.19) --
	(202.01,512.19) --
	(202.01,510.32) --
	(215.19,510.32) --
	(215.19,508.45) --
	(228.36,508.45) --
	(228.36,506.59) --
	(241.54,506.59) --
	(241.54,504.74) --
	(254.72,504.74) --
	(254.72,502.91) --
	(267.89,502.91) --
	(267.89,501.12) --
	(281.07,501.12) --
	(281.07,499.32) --
	(294.25,499.32) --
	(294.25,497.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,446.55) rectangle (306.77,536.52);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,370.22) --
	(306.77,370.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,396.92) --
	(306.77,396.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,423.62) --
	(306.77,423.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,351.08) --
	( 63.65,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,351.08) --
	(129.54,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,351.08) --
	(195.42,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,351.08) --
	(261.31,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,356.87) --
	(306.77,356.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,383.57) --
	(306.77,383.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,410.27) --
	(306.77,410.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,436.96) --
	(306.77,436.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,351.08) --
	( 96.59,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,351.08) --
	(162.48,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,351.08) --
	(228.36,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,351.08) --
	(294.25,441.05);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.74) --
	( 96.59,435.74) --
	( 96.59,434.43) --
	(109.77,434.43) --
	(109.77,432.98) --
	(122.95,432.98) --
	(122.95,431.41) --
	(136.12,431.41) --
	(136.12,429.75) --
	(149.30,429.75) --
	(149.30,427.98) --
	(162.48,427.98) --
	(162.48,426.30) --
	(175.66,426.30) --
	(175.66,424.60) --
	(188.83,424.60) --
	(188.83,422.98) --
	(202.01,422.98) --
	(202.01,421.24) --
	(215.19,421.24) --
	(215.19,419.76) --
	(228.36,419.76) --
	(228.36,418.14) --
	(241.54,418.14) --
	(241.54,416.55) --
	(254.72,416.55) --
	(254.72,414.90) --
	(267.89,414.90) --
	(267.89,413.35) --
	(281.07,413.35) --
	(281.07,411.82) --
	(294.25,411.82) --
	(294.25,406.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.30) --
	( 96.59,435.30) --
	( 96.59,433.15) --
	(109.77,433.15) --
	(109.77,430.80) --
	(122.95,430.80) --
	(122.95,428.76) --
	(136.12,428.76) --
	(136.12,426.39) --
	(149.30,426.39) --
	(149.30,424.20) --
	(162.48,424.20) --
	(162.48,422.13) --
	(175.66,422.13) --
	(175.66,420.01) --
	(188.83,420.01) --
	(188.83,417.89) --
	(202.01,417.89) --
	(202.01,415.73) --
	(215.19,415.73) --
	(215.19,413.87) --
	(228.36,413.87) --
	(228.36,412.02) --
	(241.54,412.02) --
	(241.54,410.11) --
	(254.72,410.11) --
	(254.72,408.09) --
	(267.89,408.09) --
	(267.89,406.26) --
	(281.07,406.26) --
	(281.07,404.36) --
	(294.25,404.36) --
	(294.25,397.39);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.82) --
	( 70.24,436.82) --
	( 70.24,436.59) --
	( 83.42,436.59) --
	( 83.42,436.27) --
	( 96.59,436.27) --
	( 96.59,435.85) --
	(109.77,435.85) --
	(109.77,435.33) --
	(122.95,435.33) --
	(122.95,434.71) --
	(136.12,434.71) --
	(136.12,434.01) --
	(149.30,434.01) --
	(149.30,433.22) --
	(162.48,433.22) --
	(162.48,432.34) --
	(175.66,432.34) --
	(175.66,431.35) --
	(188.83,431.35) --
	(188.83,430.30) --
	(202.01,430.30) --
	(202.01,429.17) --
	(215.19,429.17) --
	(215.19,427.94) --
	(228.36,427.94) --
	(228.36,426.65) --
	(241.54,426.65) --
	(241.54,425.29) --
	(254.72,425.29) --
	(254.72,423.84) --
	(267.89,423.84) --
	(267.89,422.32) --
	(281.07,422.32) --
	(281.07,420.74) --
	(294.25,420.74) --
	(294.25,419.11);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.75) --
	( 70.24,436.75) --
	( 70.24,436.42) --
	( 83.42,436.42) --
	( 83.42,435.95) --
	( 96.59,435.95) --
	( 96.59,435.37) --
	(109.77,435.37) --
	(109.77,434.66) --
	(122.95,434.66) --
	(122.95,433.84) --
	(136.12,433.84) --
	(136.12,432.91) --
	(149.30,432.91) --
	(149.30,431.87) --
	(162.48,431.87) --
	(162.48,430.71) --
	(175.66,430.71) --
	(175.66,429.46) --
	(188.83,429.46) --
	(188.83,428.14) --
	(202.01,428.14) --
	(202.01,426.71) --
	(215.19,426.71) --
	(215.19,425.22) --
	(228.36,425.22) --
	(228.36,423.62) --
	(241.54,423.62) --
	(241.54,421.93) --
	(254.72,421.93) --
	(254.72,420.17) --
	(267.89,420.17) --
	(267.89,418.34) --
	(281.07,418.34) --
	(281.07,416.45) --
	(294.25,416.45) --
	(294.25,414.50);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.03) --
	( 70.24,436.03) --
	( 70.24,434.87) --
	( 83.42,434.87) --
	( 83.42,433.58) --
	( 96.59,433.58) --
	( 96.59,432.19) --
	(109.77,432.19) --
	(109.77,430.73) --
	(122.95,430.73) --
	(122.95,429.20) --
	(136.12,429.20) --
	(136.12,427.66) --
	(149.30,427.66) --
	(149.30,426.11) --
	(162.48,426.11) --
	(162.48,424.55) --
	(175.66,424.55) --
	(175.66,422.95) --
	(188.83,422.95) --
	(188.83,421.38) --
	(202.01,421.38) --
	(202.01,419.81) --
	(215.19,419.81) --
	(215.19,418.23) --
	(228.36,418.23) --
	(228.36,416.67) --
	(241.54,416.67) --
	(241.54,415.13) --
	(254.72,415.13) --
	(254.72,413.59) --
	(267.89,413.59) --
	(267.89,412.05) --
	(281.07,412.05) --
	(281.07,410.53) --
	(294.25,410.53) --
	(294.25,408.97);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,435.55) --
	( 70.24,435.55) --
	( 70.24,433.88) --
	( 83.42,433.88) --
	( 83.42,432.04) --
	( 96.59,432.04) --
	( 96.59,430.10) --
	(109.77,430.10) --
	(109.77,428.11) --
	(122.95,428.11) --
	(122.95,426.11) --
	(136.12,426.11) --
	(136.12,424.08) --
	(149.30,424.08) --
	(149.30,422.06) --
	(162.48,422.06) --
	(162.48,420.03) --
	(175.66,420.03) --
	(175.66,418.03) --
	(188.83,418.03) --
	(188.83,416.08) --
	(202.01,416.08) --
	(202.01,414.13) --
	(215.19,414.13) --
	(215.19,412.24) --
	(228.36,412.24) --
	(228.36,410.33) --
	(241.54,410.33) --
	(241.54,408.44) --
	(254.72,408.44) --
	(254.72,406.60) --
	(267.89,406.60) --
	(267.89,404.77) --
	(281.07,404.77) --
	(281.07,402.99) --
	(294.25,402.99) --
	(294.25,401.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,351.08) rectangle (306.77,441.05);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,255.61) rectangle (306.77,345.58);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,255.61) rectangle (306.77,345.58);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,274.75) --
	(306.77,274.75);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,301.45) --
	(306.77,301.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,328.14) --
	(306.77,328.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,255.61) --
	( 63.65,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,255.61) --
	(129.54,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,255.61) --
	(195.42,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,255.61) --
	(261.31,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,261.40) --
	(306.77,261.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,288.10) --
	(306.77,288.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,314.80) --
	(306.77,314.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,341.49) --
	(306.77,341.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,255.61) --
	( 96.59,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,255.61) --
	(162.48,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,255.61) --
	(228.36,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,255.61) --
	(294.25,345.58);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.49) --
	( 70.24,341.49) --
	( 70.24,341.49) --
	( 83.42,341.49) --
	( 83.42,340.45) --
	( 96.59,340.45) --
	( 96.59,339.00) --
	(109.77,339.00) --
	(109.77,337.47) --
	(122.95,337.47) --
	(122.95,335.92) --
	(136.12,335.92) --
	(136.12,334.17) --
	(149.30,334.17) --
	(149.30,332.43) --
	(162.48,332.43) --
	(162.48,330.88) --
	(175.66,330.88) --
	(175.66,329.12) --
	(188.83,329.12) --
	(188.83,327.55) --
	(202.01,327.55) --
	(202.01,325.87) --
	(215.19,325.87) --
	(215.19,324.26) --
	(228.36,324.26) --
	(228.36,322.63) --
	(241.54,322.63) --
	(241.54,321.13) --
	(254.72,321.13) --
	(254.72,319.53) --
	(267.89,319.53) --
	(267.89,317.83) --
	(281.07,317.83) --
	(281.07,316.18) --
	(294.25,316.18) --
	(294.25,310.63);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.49) --
	( 70.24,341.49) --
	( 70.24,341.49) --
	( 83.42,341.49) --
	( 83.42,339.77) --
	( 96.59,339.77) --
	( 96.59,337.60) --
	(109.77,337.60) --
	(109.77,335.22) --
	(122.95,335.22) --
	(122.95,333.15) --
	(136.12,333.15) --
	(136.12,330.77) --
	(149.30,330.77) --
	(149.30,328.58) --
	(162.48,328.58) --
	(162.48,326.38) --
	(175.66,326.38) --
	(175.66,324.09) --
	(188.83,324.09) --
	(188.83,321.88) --
	(202.01,321.88) --
	(202.01,319.52) --
	(215.19,319.52) --
	(215.19,317.54) --
	(228.36,317.54) --
	(228.36,315.57) --
	(241.54,315.57) --
	(241.54,313.64) --
	(254.72,313.64) --
	(254.72,311.82) --
	(267.89,311.82) --
	(267.89,309.92) --
	(281.07,309.92) --
	(281.07,308.01) --
	(294.25,308.01) --
	(294.25,300.71);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.35) --
	( 70.24,341.35) --
	( 70.24,341.12) --
	( 83.42,341.12) --
	( 83.42,340.81) --
	( 96.59,340.81) --
	( 96.59,340.40) --
	(109.77,340.40) --
	(109.77,339.90) --
	(122.95,339.90) --
	(122.95,339.31) --
	(136.12,339.31) --
	(136.12,338.63) --
	(149.30,338.63) --
	(149.30,337.87) --
	(162.48,337.87) --
	(162.48,337.01) --
	(175.66,337.01) --
	(175.66,336.06) --
	(188.83,336.06) --
	(188.83,335.04) --
	(202.01,335.04) --
	(202.01,333.93) --
	(215.19,333.93) --
	(215.19,332.74) --
	(228.36,332.74) --
	(228.36,331.49) --
	(241.54,331.49) --
	(241.54,330.15) --
	(254.72,330.15) --
	(254.72,328.74) --
	(267.89,328.74) --
	(267.89,327.25) --
	(281.07,327.25) --
	(281.07,325.71) --
	(294.25,325.71) --
	(294.25,324.10);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.27) --
	( 70.24,341.27) --
	( 70.24,340.93) --
	( 83.42,340.93) --
	( 83.42,340.46) --
	( 96.59,340.46) --
	( 96.59,339.87) --
	(109.77,339.87) --
	(109.77,339.17) --
	(122.95,339.17) --
	(122.95,338.37) --
	(136.12,338.37) --
	(136.12,337.47) --
	(149.30,337.47) --
	(149.30,336.45) --
	(162.48,336.45) --
	(162.48,335.35) --
	(175.66,335.35) --
	(175.66,334.13) --
	(188.83,334.13) --
	(188.83,332.82) --
	(202.01,332.82) --
	(202.01,331.40) --
	(215.19,331.40) --
	(215.19,329.89) --
	(228.36,329.89) --
	(228.36,328.30) --
	(241.54,328.30) --
	(241.54,326.62) --
	(254.72,326.62) --
	(254.72,324.85) --
	(267.89,324.85) --
	(267.89,323.00) --
	(281.07,323.00) --
	(281.07,321.08) --
	(294.25,321.08) --
	(294.25,319.07);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.55) --
	( 70.24,340.55) --
	( 70.24,339.41) --
	( 83.42,339.41) --
	( 83.42,338.15) --
	( 96.59,338.15) --
	( 96.59,336.79) --
	(109.77,336.79) --
	(109.77,335.37) --
	(122.95,335.37) --
	(122.95,333.90) --
	(136.12,333.90) --
	(136.12,332.42) --
	(149.30,332.42) --
	(149.30,330.91) --
	(162.48,330.91) --
	(162.48,329.38) --
	(175.66,329.38) --
	(175.66,327.83) --
	(188.83,327.83) --
	(188.83,326.29) --
	(202.01,326.29) --
	(202.01,324.76) --
	(215.19,324.76) --
	(215.19,323.21) --
	(228.36,323.21) --
	(228.36,321.70) --
	(241.54,321.70) --
	(241.54,320.17) --
	(254.72,320.17) --
	(254.72,318.66) --
	(267.89,318.66) --
	(267.89,317.16) --
	(281.07,317.16) --
	(281.07,315.68) --
	(294.25,315.68) --
	(294.25,314.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.03) --
	( 70.24,340.03) --
	( 70.24,338.32) --
	( 83.42,338.32) --
	( 83.42,336.45) --
	( 96.59,336.45) --
	( 96.59,334.51) --
	(109.77,334.51) --
	(109.77,332.52) --
	(122.95,332.52) --
	(122.95,330.54) --
	(136.12,330.54) --
	(136.12,328.59) --
	(149.30,328.59) --
	(149.30,326.59) --
	(162.48,326.59) --
	(162.48,324.64) --
	(175.66,324.64) --
	(175.66,322.66) --
	(188.83,322.66) --
	(188.83,320.72) --
	(202.01,320.72) --
	(202.01,318.76) --
	(215.19,318.76) --
	(215.19,316.84) --
	(228.36,316.84) --
	(228.36,314.94) --
	(241.54,314.94) --
	(241.54,313.05) --
	(254.72,313.05) --
	(254.72,311.18) --
	(267.89,311.18) --
	(267.89,309.34) --
	(281.07,309.34) --
	(281.07,307.52) --
	(294.25,307.52) --
	(294.25,305.63);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,255.61) rectangle (306.77,345.58);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,160.14) rectangle (306.77,250.11);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,160.14) rectangle (306.77,250.11);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,179.28) --
	(306.77,179.28);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,205.98) --
	(306.77,205.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,232.67) --
	(306.77,232.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,160.14) --
	( 63.65,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,160.14) --
	(129.54,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,160.14) --
	(195.42,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,160.14) --
	(261.31,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,165.93) --
	(306.77,165.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,192.63) --
	(306.77,192.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,219.32) --
	(306.77,219.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,246.02) --
	(306.77,246.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,160.14) --
	( 96.59,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,160.14) --
	(162.48,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,160.14) --
	(228.36,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,160.14) --
	(294.25,250.11);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,246.02) --
	( 70.24,246.02) --
	( 70.24,246.02) --
	( 83.42,246.02) --
	( 83.42,243.83) --
	( 96.59,243.83) --
	( 96.59,240.92) --
	(109.77,240.92) --
	(109.77,237.63) --
	(122.95,237.63) --
	(122.95,233.74) --
	(136.12,233.74) --
	(136.12,229.93) --
	(149.30,229.93) --
	(149.30,226.16) --
	(162.48,226.16) --
	(162.48,222.32) --
	(175.66,222.32) --
	(175.66,218.61) --
	(188.83,218.61) --
	(188.83,214.89) --
	(202.01,214.89) --
	(202.01,211.14) --
	(215.19,211.14) --
	(215.19,207.61) --
	(228.36,207.61) --
	(228.36,204.27) --
	(241.54,204.27) --
	(241.54,200.76) --
	(254.72,200.76) --
	(254.72,197.48) --
	(267.89,197.48) --
	(267.89,194.34) --
	(281.07,194.34) --
	(281.07,191.11) --
	(294.25,191.11) --
	(294.25,180.15);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,246.02) --
	( 70.24,246.02) --
	( 70.24,246.02) --
	( 83.42,246.02) --
	( 83.42,243.24) --
	( 96.59,243.24) --
	( 96.59,239.25) --
	(109.77,239.25) --
	(109.77,234.65) --
	(122.95,234.65) --
	(122.95,229.74) --
	(136.12,229.74) --
	(136.12,224.94) --
	(149.30,224.94) --
	(149.30,220.15) --
	(162.48,220.15) --
	(162.48,215.44) --
	(175.66,215.44) --
	(175.66,210.69) --
	(188.83,210.69) --
	(188.83,206.27) --
	(202.01,206.27) --
	(202.01,202.11) --
	(215.19,202.11) --
	(215.19,198.14) --
	(228.36,198.14) --
	(228.36,194.18) --
	(241.54,194.18) --
	(241.54,190.34) --
	(254.72,190.34) --
	(254.72,186.73) --
	(267.89,186.73) --
	(267.89,183.18) --
	(281.07,183.18) --
	(281.07,179.87) --
	(294.25,179.87) --
	(294.25,167.81);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.72) --
	( 70.24,245.72) --
	( 70.24,245.20) --
	( 83.42,245.20) --
	( 83.42,244.44) --
	( 96.59,244.44) --
	( 96.59,243.50) --
	(109.77,243.50) --
	(109.77,242.30) --
	(122.95,242.30) --
	(122.95,240.95) --
	(136.12,240.95) --
	(136.12,239.38) --
	(149.30,239.38) --
	(149.30,237.62) --
	(162.48,237.62) --
	(162.48,235.68) --
	(175.66,235.68) --
	(175.66,233.51) --
	(188.83,233.51) --
	(188.83,231.15) --
	(202.01,231.15) --
	(202.01,228.63) --
	(215.19,228.63) --
	(215.19,225.94) --
	(228.36,225.94) --
	(228.36,223.15) --
	(241.54,223.15) --
	(241.54,220.21) --
	(254.72,220.21) --
	(254.72,217.04) --
	(267.89,217.04) --
	(267.89,213.83) --
	(281.07,213.83) --
	(281.07,210.42) --
	(294.25,210.42) --
	(294.25,206.83);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.60) --
	( 70.24,245.60) --
	( 70.24,244.91) --
	( 83.42,244.91) --
	( 83.42,243.96) --
	( 96.59,243.96) --
	( 96.59,242.75) --
	(109.77,242.75) --
	(109.77,241.30) --
	(122.95,241.30) --
	(122.95,239.59) --
	(136.12,239.59) --
	(136.12,237.68) --
	(149.30,237.68) --
	(149.30,235.54) --
	(162.48,235.54) --
	(162.48,233.19) --
	(175.66,233.19) --
	(175.66,230.59) --
	(188.83,230.59) --
	(188.83,227.77) --
	(202.01,227.77) --
	(202.01,224.78) --
	(215.19,224.78) --
	(215.19,221.62) --
	(228.36,221.62) --
	(228.36,218.26) --
	(241.54,218.26) --
	(241.54,214.74) --
	(254.72,214.74) --
	(254.72,211.07) --
	(267.89,211.07) --
	(267.89,207.27) --
	(281.07,207.27) --
	(281.07,203.34) --
	(294.25,203.34) --
	(294.25,199.32);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,244.02) --
	( 70.24,244.02) --
	( 70.24,241.42) --
	( 83.42,241.42) --
	( 83.42,238.39) --
	( 96.59,238.39) --
	( 96.59,235.27) --
	(109.77,235.27) --
	(109.77,231.91) --
	(122.95,231.91) --
	(122.95,228.58) --
	(136.12,228.58) --
	(136.12,225.17) --
	(149.30,225.17) --
	(149.30,221.77) --
	(162.48,221.77) --
	(162.48,218.37) --
	(175.66,218.37) --
	(175.66,214.93) --
	(188.83,214.93) --
	(188.83,211.48) --
	(202.01,211.48) --
	(202.01,208.09) --
	(215.19,208.09) --
	(215.19,204.75) --
	(228.36,204.75) --
	(228.36,201.51) --
	(241.54,201.51) --
	(241.54,198.32) --
	(254.72,198.32) --
	(254.72,195.10) --
	(267.89,195.10) --
	(267.89,192.02) --
	(281.07,192.02) --
	(281.07,188.93) --
	(294.25,188.93) --
	(294.25,185.68);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,243.21) --
	( 70.24,243.21) --
	( 70.24,239.79) --
	( 83.42,239.79) --
	( 83.42,236.00) --
	( 96.59,236.00) --
	( 96.59,232.02) --
	(109.77,232.02) --
	(109.77,227.97) --
	(122.95,227.97) --
	(122.95,223.83) --
	(136.12,223.83) --
	(136.12,219.72) --
	(149.30,219.72) --
	(149.30,215.62) --
	(162.48,215.62) --
	(162.48,211.58) --
	(175.66,211.58) --
	(175.66,207.50) --
	(188.83,207.50) --
	(188.83,203.47) --
	(202.01,203.47) --
	(202.01,199.53) --
	(215.19,199.53) --
	(215.19,195.67) --
	(228.36,195.67) --
	(228.36,191.86) --
	(241.54,191.86) --
	(241.54,188.13) --
	(254.72,188.13) --
	(254.72,184.48) --
	(267.89,184.48) --
	(267.89,180.92) --
	(281.07,180.92) --
	(281.07,177.44) --
	(294.25,177.44) --
	(294.25,173.89);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,160.14) rectangle (306.77,250.11);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 64.67) rectangle (306.77,154.64);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,154.64);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 83.81) --
	(306.77, 83.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,110.50) --
	(306.77,110.50);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,137.20) --
	(306.77,137.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
	( 63.65,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
	(129.54,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
	(195.42,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
	(261.31,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 70.46) --
	(306.77, 70.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 97.16) --
	(306.77, 97.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,123.85) --
	(306.77,123.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,150.55) --
	(306.77,150.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
	( 96.59,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
	(162.48,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
	(228.36,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
	(294.25,154.64);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,150.55) --
	( 70.24,150.55) --
	( 70.24,150.55) --
	( 83.42,150.55) --
	( 83.42,147.28) --
	( 96.59,147.28) --
	( 96.59,143.70) --
	(109.77,143.70) --
	(109.77,139.54) --
	(122.95,139.54) --
	(122.95,135.49) --
	(136.12,135.49) --
	(136.12,131.43) --
	(149.30,131.43) --
	(149.30,127.27) --
	(162.48,127.27) --
	(162.48,123.40) --
	(175.66,123.40) --
	(175.66,119.60) --
	(188.83,119.60) --
	(188.83,115.97) --
	(202.01,115.97) --
	(202.01,112.27) --
	(215.19,112.27) --
	(215.19,108.52) --
	(228.36,108.52) --
	(228.36,105.14) --
	(241.54,105.14) --
	(241.54,101.84) --
	(254.72,101.84) --
	(254.72, 98.62) --
	(267.89, 98.62) --
	(267.89, 95.61) --
	(281.07, 95.61) --
	(281.07, 92.76) --
	(294.25, 92.76) --
	(294.25, 81.64);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,150.55) --
	( 70.24,150.55) --
	( 70.24,150.55) --
	( 83.42,150.55) --
	( 83.42,146.40) --
	( 96.59,146.40) --
	( 96.59,140.92) --
	(109.77,140.92) --
	(109.77,135.34) --
	(122.95,135.34) --
	(122.95,130.16) --
	(136.12,130.16) --
	(136.12,124.95) --
	(149.30,124.95) --
	(149.30,120.21) --
	(162.48,120.21) --
	(162.48,115.52) --
	(175.66,115.52) --
	(175.66,110.59) --
	(188.83,110.59) --
	(188.83,106.11) --
	(202.01,106.11) --
	(202.01,102.07) --
	(215.19,102.07) --
	(215.19, 98.13) --
	(228.36, 98.13) --
	(228.36, 94.49) --
	(241.54, 94.49) --
	(241.54, 90.89) --
	(254.72, 90.89) --
	(254.72, 87.28) --
	(267.89, 87.28) --
	(267.89, 83.67) --
	(281.07, 83.67) --
	(281.07, 80.56) --
	(294.25, 80.56) --
	(294.25, 68.76);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,150.18) --
	( 70.24,150.18) --
	( 70.24,149.60) --
	( 83.42,149.60) --
	( 83.42,148.80) --
	( 96.59,148.80) --
	( 96.59,147.79) --
	(109.77,147.79) --
	(109.77,146.60) --
	(122.95,146.60) --
	(122.95,145.20) --
	(136.12,145.20) --
	(136.12,143.60) --
	(149.30,143.60) --
	(149.30,141.83) --
	(162.48,141.83) --
	(162.48,139.87) --
	(175.66,139.87) --
	(175.66,137.70) --
	(188.83,137.70) --
	(188.83,135.38) --
	(202.01,135.38) --
	(202.01,132.85) --
	(215.19,132.85) --
	(215.19,130.17) --
	(228.36,130.17) --
	(228.36,127.33) --
	(241.54,127.33) --
	(241.54,124.36) --
	(254.72,124.36) --
	(254.72,121.23) --
	(267.89,121.23) --
	(267.89,117.97) --
	(281.07,117.97) --
	(281.07,114.60) --
	(294.25,114.60) --
	(294.25,111.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,149.98) --
	( 70.24,149.98) --
	( 70.24,149.15) --
	( 83.42,149.15) --
	( 83.42,148.07) --
	( 96.59,148.07) --
	( 96.59,146.72) --
	(109.77,146.72) --
	(109.77,145.12) --
	(122.95,145.12) --
	(122.95,143.34) --
	(136.12,143.34) --
	(136.12,141.33) --
	(149.30,141.33) --
	(149.30,139.13) --
	(162.48,139.13) --
	(162.48,136.72) --
	(175.66,136.72) --
	(175.66,134.08) --
	(188.83,134.08) --
	(188.83,131.21) --
	(202.01,131.21) --
	(202.01,128.21) --
	(215.19,128.21) --
	(215.19,124.95) --
	(228.36,124.95) --
	(228.36,121.55) --
	(241.54,121.55) --
	(241.54,118.03) --
	(254.72,118.03) --
	(254.72,114.36) --
	(267.89,114.36) --
	(267.89,110.52) --
	(281.07,110.52) --
	(281.07,106.54) --
	(294.25,106.54) --
	(294.25,102.60);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,148.10) --
	( 70.24,148.10) --
	( 70.24,145.20) --
	( 83.42,145.20) --
	( 83.42,142.03) --
	( 96.59,142.03) --
	( 96.59,138.69) --
	(109.77,138.69) --
	(109.77,135.34) --
	(122.95,135.34) --
	(122.95,131.92) --
	(136.12,131.92) --
	(136.12,128.47) --
	(149.30,128.47) --
	(149.30,125.06) --
	(162.48,125.06) --
	(162.48,121.64) --
	(175.66,121.64) --
	(175.66,118.21) --
	(188.83,118.21) --
	(188.83,114.83) --
	(202.01,114.83) --
	(202.01,111.45) --
	(215.19,111.45) --
	(215.19,108.12) --
	(228.36,108.12) --
	(228.36,104.84) --
	(241.54,104.84) --
	(241.54,101.63) --
	(254.72,101.63) --
	(254.72, 98.46) --
	(267.89, 98.46) --
	(267.89, 95.35) --
	(281.07, 95.35) --
	(281.07, 92.30) --
	(294.25, 92.30) --
	(294.25, 89.17);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,146.77) --
	( 70.24,146.77) --
	( 70.24,142.62) --
	( 83.42,142.62) --
	( 83.42,138.34) --
	( 96.59,138.34) --
	( 96.59,133.93) --
	(109.77,133.93) --
	(109.77,129.46) --
	(122.95,129.46) --
	(122.95,125.14) --
	(136.12,125.14) --
	(136.12,120.87) --
	(149.30,120.87) --
	(149.30,116.70) --
	(162.48,116.70) --
	(162.48,112.57) --
	(175.66,112.57) --
	(175.66,108.48) --
	(188.83,108.48) --
	(188.83,104.39) --
	(202.01,104.39) --
	(202.01,100.49) --
	(215.19,100.49) --
	(215.19, 96.56) --
	(228.36, 96.56) --
	(228.36, 92.75) --
	(241.54, 92.75) --
	(241.54, 89.06) --
	(254.72, 89.06) --
	(254.72, 85.46) --
	(267.89, 85.46) --
	(267.89, 81.90) --
	(281.07, 81.90) --
	(281.07, 78.43) --
	(294.25, 78.43) --
	(294.25, 74.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,154.64);
\end{scope}
\begin{scope}
\path[clip] (306.77,446.55) rectangle (319.71,536.52);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,446.55) rectangle (319.71,536.52);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,491.54) {Scenario 1};
\end{scope}
\begin{scope}
\path[clip] (306.77,351.08) rectangle (319.71,441.05);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,351.08) rectangle (319.71,441.05);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,396.07) {Scenario 2};
\end{scope}
\begin{scope}
\path[clip] (306.77,255.61) rectangle (319.71,345.58);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,255.61) rectangle (319.71,345.58);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,300.60) {Scenario 3};
\end{scope}
\begin{scope}
\path[clip] (306.77,160.14) rectangle (319.71,250.11);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,160.14) rectangle (319.71,250.11);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,205.12) {Scenario 4};
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,154.64);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,154.64);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,109.65) {Scenario 5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
	( 96.59, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
	(162.48, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
	(228.36, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
	(294.25, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,449.59) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,476.29) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,502.98) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,529.68) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,452.35) --
	( 31.37,452.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,479.04) --
	( 31.37,479.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,505.74) --
	( 31.37,505.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,532.44) --
	( 31.37,532.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,354.12) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,380.82) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,407.51) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,434.21) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,356.87) --
	( 31.37,356.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,383.57) --
	( 31.37,383.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,410.27) --
	( 31.37,410.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,436.96) --
	( 31.37,436.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,258.65) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,285.34) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,312.04) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,338.74) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,261.40) --
	( 31.37,261.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,288.10) --
	( 31.37,288.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,314.80) --
	( 31.37,314.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,341.49) --
	( 31.37,341.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,163.18) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,189.87) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,216.57) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,243.27) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,165.93) --
	( 31.37,165.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,192.63) --
	( 31.37,192.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,219.32) --
	( 31.37,219.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,246.02) --
	( 31.37,246.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 67.70) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 94.40) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,121.10) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,147.79) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 70.46) --
	( 31.37, 70.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 97.16) --
	( 31.37, 97.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,123.85) --
	( 31.37,123.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,150.55) --
	( 31.37,150.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Time since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,300.60) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-12-10 scripts/00-hello.R

@@ -1,0 +1,32 @@
+# 00-hello.R
+# Loading data and other preliminaries
+# Kevin Chen
+# November 2, 2021
+
+library(here)
+library(boxr); box_auth()
+library(lubridate)
+library(data.table)
+
+# Load helper functions, themes, etc
+source("~/headRs/00-my-theme.R")
+
+exposure.lag <- 15
+
+# Load full data
+if (!"cohort_analytic" %in% ls()) {
+	cohort_analytic <- box_read(880479268725)
+	cohort_analytic[,(c("straight", "soluble", "synthetic")) := lapply(
+		list(straight, soluble, synthetic), function(x) {
+			return(shift(x, get("exposure.lag", envir = .GlobalEnv), 0))
+		}),
+		studyno]
+	cohort_analytic[,(paste0("cum_", c("straight", "soluble", "synthetic"))) := lapply(
+		list(straight, soluble, synthetic), function(x) {
+			return(cumsum(x))
+		}),
+		studyno]
+}
+
+cohort_analytic <- cohort_analytic[wh == 1 & nohist == 0 & yin.gm >= 1938]
+

### 2021-12-10 scripts/01-simulation.R

@@ -1,0 +1,182 @@
+# 01-simulation.R
+# Simulating data
+# Kevin Chen
+# November 3, 2021
+
+library(here)
+library(lubridate)
+library(data.table)
+
+# Parameters
+sim_param <- readRDS(here::here("resources", "sim_param.rds"))
+rownames(sim_param) <- sim_param[,1]
+sim_param <- sim_param[,-1]
+
+sim_data <- function(
+	scenario = 1,
+	n = 50000,
+	full = T,
+	K = 20,
+	d = NULL,
+	a = NULL,
+	long = T,
+	param = sim_param) {
+	
+	env.current <- environment()
+	
+	param <- as.data.frame(t(param))[scenario,]
+	
+	U <- as.data.frame(
+		sapply(paste(
+			rep(c("U_H", "U_N", "U_A", "U_D", "U_Y"), each = K),
+			1:K, sep = "."), function(x) {
+				runif(n)
+			}))
+	
+	R <- runif(n, 0, 20)
+	W <- rbinom(n, 1, param$p_W)
+	S <- rbinom(n, 1, param$p_S)
+	H.k <- H.1 <- rbinom(n, 1, param$p_H)
+	N.k <- N.1 <- rbinom(n, 1, plogis(
+		param$beta_0N +
+			param$beta_WN * W +
+			param$beta_HN * H.k +
+			U[,paste0("U_N.", 1)]
+	))
+	if (is.null(d)) {
+		D.k <- D.1 <- rbinom(n, 1, plogis(
+			param$beta_0D +
+				param$beta_WD * W +
+				U[, paste0("U_D.", 1)]
+		))
+	} else {
+		D.k <- D.1 <- rep(d, n)
+	}
+	if (is.null(a)) {
+		A.1 <- rbinom(n, 1, plogis(
+			param$beta_0A + param$beta_WA * W + U$U_A.1
+		))
+	} else {
+		A.1 <- rep(a, n)
+	}
+	A.1[N.k == 0] <- 0
+	A.k <- A.1
+	Y.k <- Y.1 <- rbinom(n, 1, plogis(
+		param$beta_0Y +
+			param$beta_WY * W +
+			param$beta_AY * A.1 +
+			param$beta_SY * S * A.1 +
+			param$beta_HY * H.k +
+			U$U_Y.1
+	))
+	
+	# k <- 2
+	# k <- k + 1
+	for (k in 2:K) {
+		H.k[H.k != 1] <- rbinom(sum(H.k != 1), 1, param$p_H)
[…]

### 2021-12-10 scripts/02-analysis.R

@@ -1,0 +1,115 @@
+# 02-analysis.R
+# Analyzing simulated data
+# Kevin Chen
+# December 6, 2021
+
+library(here)
+library(lubridate)
+library(tidyverse)
+library(magrittr)
+library(data.table)
+library(survival)
+
+# Get code for simulation
+source(here("scripts", "01-simulation.R"))
+
+# Get package for running estimators
+# devtools::install_github('osofr/stremr')
+library(stremr)
+
+get_estimates <- function(
+	scenario = 1,
+	a = 0,
+	g_a = "A ~ W + barA",
+	g_d = "D ~ W + barA",
+	stratify = list(D = paste0("t == ", 1:20),
+									A = paste0("t == ", 1:20))
+) {
+	
+	# message("Simulating...")
+	sim.dt <- sim_data(scenario, a = a)
+	sim.dt[,`:=`(barA = shift(as.integer(cumsum(A) > 0), 1, 0)), id]
+	
+	# Get rules
+	sim.dt[,`:=`(A_0 = 0, A_1 = N)]
+	
+	sim.dt <- sim.dt[t <= last_t_obs]
+	
+	# Make stremr object
+	sim.stremr <- importData(
+		sim.dt,
+		ID = "id",
+		t_name = "t",
+		covars = c("R", "W", "S", "H", "N", "barA"),
+		CENS = "D",
+		TRT = "A",
+		OUTCOME = "Y_obs")
+	
+	# Fit PS
+	# message("Fitting PS")
+	sim.stremr <- fitPropensity(
+		sim.stremr,
+		gform_TRT = g_a,
+		gform_CENS = g_d,
+		stratify_TRT = stratify,
+		stratify_CENS = stratify,
+	)
+	
+	w <- getIPWeights(
+		sim.stremr,
+		intervened_TRT = paste0("A_", a))
+	
+	wkm <- w %>% survNPMSM(sim.stremr) %$% estimates
+	
+	# nrow(w)
+	# nrow(sim.dt)
+	# Get rid of rows according to `obs` for Aalen filter
+	awkm <- w[sim.dt$obs == 1,] %>%
+		survNPMSM(sim.stremr) %$%
+		estimates
+	
+	return(
+		data.table(
+			t = 1:20,
+			# KM = wkm$St.KM,
+			WKM = wkm$St.NPMSM,
+			AWKM = awkm$St.NPMSM)
+	)
+}
+
+
+# km %>% melt(
+# 	measure.vars = names(.)[-1],
[…]

### 2021-12-10 scripts/03-results.R

@@ -1,0 +1,92 @@
+# 02-analysis.R
+# Analyzing simulated data
+# Kevin Chen
+# December 6, 2021
+
+library(here)
+library(lubridate)
+library(tidyverse)
+library(magrittr)
+library(data.table)
+library(survival)
+
+# Get code for simulation
+source(here("scripts", "01-simulation.R"))
+
+# Get script from github
+library(RCurl)
+eval(parse(text = getURL(
+	"https://raw.githubusercontent.com/kvntchn/HeadRs/master/00-my-theme.R",
+	ssl.verifypeer = F
+)))
+
+# Get package for running estimators
+# devtools::install_github('osofr/stremr')
+library(stremr)
+
+truth_a0 <- readRDS(here("resources", "truth_a0.rds"))
+truth_a1 <- readRDS(here("resources", "truth_a1.rds"))
+
+data.frame(truth_a0[[5]][,2],
+					 truth_a1[[5]][,2])
+
+a0 <- rbindlist(
+	lapply(1:5, function(scenario = 1) {
+		melt(rbindlist(readRDS(here("resources", paste0("a0_scenario", scenario, ".rds")))
+		)[,.(WKM = mean(WKM), AWKM = mean(AWKM)), t],
+		measure.vars = c("WKM", "AWKM"),
+		variable.name = "Estimator",
+		value.name = "Survival")
+	}),
+	idcol = "scenario"
+)
+a1 <- rbindlist(
+	lapply(1:5, function(scenario) {
+		melt(rbindlist(readRDS(here("resources", paste0("a1_scenario", scenario, ".rds")))
+		)[,.(WKM = mean(WKM), AWKM = mean(AWKM)), t],
+		measure.vars = c("WKM", "AWKM"),
+		variable.name = "Estimator",
+		value.name = "Survival")
+	}),
+	idcol = "scenario"
+)
+
+
+sim_results <- rbindlist(list(
+	rbindlist(lapply(list(rbindlist(truth_a0, idcol = "scenario"),
+												rbindlist(truth_a1, idcol = "scenario")),
+									 melt,
+									 measure.vars = "Truth",
+									 variable.name = "Estimator",
+									 value.name = "Survival"),
+						idcol = "rule"),
+	rbindlist(list(a0, a1),
+						idcol = "rule")
+))
+
+sim_results[,`:=`(
+	scenario = paste0("Scenario ", scenario),
[…]

### 2021-12-10 scripts/04-application.R

@@ -1,0 +1,191 @@
+# 04-application.R
+# Analyzing simulated data
+# Kevin Chen
+# December 6, 2021
+
+library(here)
+library(lubridate)
+library(tidyverse)
+library(magrittr)
+library(data.table)
+library(survival)
+
+library(boxr); box_auth()
+if (!"cohort_analytic" %in% ls()) {
+	source(here::here("scripts", "00-hello.R"))
+}
+
+# Get package for running estimators
+# devtools::install_github('osofr/stremr')
+library(stremr)
+
+years_fu <- 40
+cohort_analytic <- cohort_analytic[
+	year < year(yin) + years_fu &
+		nohist == 0 &
+		wh == 1]
+
+# Covariate engineering
+cohort_analytic[,`:=`(
+	Straight = as.integer(straight > 0),
+	Soluble = as.integer(soluble > 0),
+	Synthetic = as.integer(synthetic > 0),
+	R = as.integer(year >= 1985),
+	Plant = factor(plant),
+	Race = factor(race),
+	Sex = factor(sex),
+	Age = cut(age.year2/365, c(
+		min(age.year2/365),
+		quantile(age.year2[canc_co == 1]/365, seq(0.2, 0.8, 0.2)),
+		max(age.year2/365)),
+		include.lowest = T, dig.lab = 4),
+	Hire = cut(yin.gm, c(
+		min(yin.gm),
+		quantile(yin.gm[canc_co == 1], seq(0.2, 0.8, 0.2)),
+		max(yin.gm)),
+		include.lowest = T, dig.lab = 4),
+	N = as.integer(year <= year(yout)),
+	off = {
+		off <- off.gan + off.han + off.san
+		off[year > year(yout)] <- 0
+		off[year >= 1995] <- 0
+		off[is.na(off)] <- 0},
+	duration = time_length(difftime(year2, yin), 'year')
+)]
+# Lag some covariates
+cohort_analytic[,`:=`(
+	off = shift(cumsum(off), 15, 1),
+	duration = shift(duration, 15, 1)
+), studyno]
+# Cut by distribution of cases after lag
+cohort_analytic[, `:=`(
+	Off = cut(off, unique(c(
+		-Inf,
+		0,
[…]

### 2021-12-11 paper.tex
Interim results; running on GM data now

@@
 \hypersetup{
-  pdftitle={Estimating survival in left filtered data: simulation and application},
+  pdftitle={Estimating survival in left filtered data},
   pdfauthor={Kevin Chen},
@@
 
-\title{Estimating survival in left filtered data: simulation and
-application}
+\title{Estimating survival in left filtered data}
 \author{Kevin Chen}
@@
 hazards modeling (Naimi et al. 2013; Garcia et al. 2017). However, these
-measures of associations are themselves subject to the confounding they
-seek to quantify.
-
-If sequential ignorability of exposure status at each point in follow-up
-and positivity can be attained conditional on covariates, then causal
-methods can be applied to account for the HWSE. Past studies have
-applied causal methods capable of accounting for time-varying
-confounding affected by past exposure to the study of MWF exposures and
-cancer mortality outcomes in the UAW-GM Cohort Study (Garcia et al.
-2018; Izano et al. 2019), but the study of cancer incidence outcomes is
-further problematized by incomplete observation of cancer incidence
-outcomes over the study period. We wish to make inferences about the
+measures of associations were themselves subject to the confounding
+structures they sought to characterize.
+
+If conditional sequential ignorability of exposure and censoring status
+at each point in follow-up and positivity can be attained given
+covariate history, then causal methods can be applied to account for the
+HWSE. Past studies have applied causal methods capable of accounting for
+time-varying confounding affected by past exposure to the study of MWF
+exposures and cancer mortality outcomes in the UAW-GM Cohort Study
+(Garcia et al. 2018; Izano et al. 2019), but the study of cancer
+incidence outcomes is further problematized by the incomplete
+observation of cancer incidence outcomes at every point of follow-up
+over the study period. Nonetheless, we wish to make inferences about the
 carcinogenicity of MWF exposure over an individual's lifetime starting
-three years after they enter the workforce. The UAW-GM cohort includes
-those hired roughly between 1938 and 1982. However, cancer incidence
-reporting at the Michigan Cancer Registry did not begin until 1985. In
-particular, we have the presence of \emph{left filtering} in the UAW-GM
-Cohort Study when cancer incidence is the outcome of interest: before
-1985, both cancer incidence status and time of cancer incidence are
-unknown. Observation of the complete cancer incidence outcome vector
-over the study period is conditional on an individual surviving to 1985
-cancer-free.
+upon entry into the workforce. The UAW-GM Cohort included those hired
+roughly between 1938 and 1985. However, cancer incidence reporting at
+the Michigan Cancer Registry did not begin until 1985. Hence, our
+observed cohort data is subject to \emph{left filtering}: cancer
+incidence is the outcome of interest, but before 1985, both cancer
+incidence status and time of cancer incidence are unknown. Observation
+of the complete cancer incidence outcome vector over the study period
+was conditional on an individual surviving to 1985 cancer-free.
 
@@
 her dissertation research, Izano (2017) conducted a quantitative bias
-analysis for the estimation of survival curves in the presence of left
-filtering and the HWSE. She simulated data compatible with the HWSE and
+analysis for the estimation of survival curves using left filtered data
+in the presence of HWSE. She simulated data compatible with the HWSE and
 estimated cancer-free survival curves using an inverse probability of
@@
 1993; Xie and Liu 2005). Data were simulated under five different
-scenarios. The causal estimands of interest were the survival curves
-under interventions: (1) always exposed at work with no censoring due to
-death and (2) never exposed at work with no censoring due to death. For
-each intervention, three survival curves were produced: (1) the true
-survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
-The bias in mean survival difference calculated by AWKM was negligible
-when the true 20-year risk of cancer was under 0.25.
-
-Here, we replicate the simulation and bias analysis presented in Chapter
-3 of Izano (2017), embed the problem in the non-parametric structural
-causal approach of Pearl (1995), comment on the results, and apply the
-WKM and AWKM estimators to the UAW-GM Cohort.
+scenarios. The survival curves under the following interventions were
+computed or estimated in 250 replicates: (1) always exposed at work with
+no censoring due to death and (2) never exposed at work with no
+censoring due to death. For each intervention, three survival curves
+were produced: (1) the true survival curve, (2) the WKM survival curve,
+and (3) AWKM survival curve. Estimator bias was evaluated by comparing
+the average of 250 estimates of to the average difference in cancer-free
+survival under the two rules to the true average survival difference
+when exposure and censoring were controlled deterministically.
+
+The present project replicates the simulation and bias analyses
+presented in Chapter 3 of Izano (2017), embeds the problem in the
+non-parametric structural causal approach of Pearl (1995), and applies
+the WKM and AWKM estimators to the estimation of colon cancer survival
+under exposure/censoring rules in the UAW-GM Cohort.
 
@@
 
-The UAW-GM Cohort data includes person-year level exposure, outcome, and
-covariate data starting three years after hire. To emulate the shape of
-the data for this longitudinal cohort, we consider 20 years of data over
-time indexed by years since hire. Notation representing the variables of
-interest are presented in Table \ref{tab:variables}.
+The UAW-GM Cohort data included person-year level exposure, outcome, and
+covariate data starting at hire. To emulate the shape of the data for
+this longitudinal cohort, we considered 20 years of data over time
+indexed by years since hire. Notation representing the variables of
+interest are presented in Table \ref{tab:variables}. The causal model
+represents hypothetical relationships between variables over time
+compatible with the theory underlying the HWSE in longitudinal
+occupational cohort studies. At each time point, the effect of
+cumulative exposure \(\bar A(t)\) on cancer incidence \(Y^(t)\) is
+confounded by a path through employment status \(N(t)\) and underlying
+health \(H(t)\) as well as the path through past exposure
+\(\bar A(t - 1)\) and vital status \(D(t)\). These paths follow
+straightforward logic: occupational exposure depends upon employment
+status and past exposure; mortality status is affected by past exposure
+and cancer history. Confounding by baseline covariates \(W\) is assumed
+throughout.
 
@@
 \(X\) the full data, where we have \(R = 0\) for all. In the observed
-data \(X^\text{obs}\), we cannot assume \(R = 0\) for all, and
-susceptibility \(S\) is not known:
+data \(X^\text{obs}\), we cannot assume \(R = 0\) for all;
+susceptibility \(S\) and underlying health status \(H\) are not known:
 \[X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).\]
@@
 %
+\path[->] (H0) edge (N0);
+\path[->] (N0) edge (A0);
+\path[->] (A0) edge [bend right=20] (Y0);
 \path[->] (H0) edge (H);
@@
 
+Figure \ref{fig:dag} clarifies our conceptualization of the HWSE. At
+each time point \(t\), the cumulative effect of exposure \(\bar A(t)\)
+on cancer incidence \(Y^*(t)\) is confounded by employment status
+\(N(t)\) through the backdoor path
+\(\bar A(t) \leftarrow N(t) \leftarrow H(t) \rightarrow Y^*(t)\). In the
+absence of observed data on health status \(H(t)\), an analyst may be
+tempted to condition on employment status \(N(t)\), but doing so would
+introduce collider bias while blocking the causal path between past
+exposure \(\bar A(t - 1)\) and cancer \(Y^*(t)\). Furthermore, an
+analysis starting at an arbitrary time point after the time origin
+(hire) would be tantamount to conditioning on those still alive at that
+time, which would also result in both collider bias and the conditioning
+on nodes on the causal path between the exposure and outcome of
+interest.
+
 \hypertarget{simulation}{%
@@
 
-Parametric relationships between the variables were imposed in
-simulations. For the \(n = 50\,000\) units over \(T = 20\) years, we
-have:
+To generate data compatible with our structural causal model, we imposed
+parametric relationships between the variables. For the \(n = 50\,000\)
+units over \(T = 20\) years, we have:
 
@@
 
-\begin{table}
+\begin{table}[h]
 \caption{Simulation parameters.}
@@
 
-The substantive question of interest is the causal effect of
+The substantive question of interest was the causal effect of
 occupational exposure to MWF on cancer incidence risk. Since
 occupational MWF exposure occurs only when individuals are at work, we
-define dynamic exposure regimes that depend on employment status. Under
+defined dynamic exposure regimes that depend on employment status. Under
 rule \(a_0\), set \(D(t) = 0\), and set \(A(t) = 0\) while \(N(t) = 1\).
 Under rule \(a_1\), set \(D(t) = 0\), and set \(A(t) = 1\) while
-\(N(t) = 1\). Under both rules, we prevent censoring by death as if it
-were intervenable. The causal effect is defined by contrasting the
+\(N(t) = 1\). Under both rules, we prevented censoring by death as if it
+were intervenable. The causal effect was defined by contrasting the
 survival function \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule \(a_1\)
 to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\). Note
-that this causal estimand is defined over \emph{a priori
+that this causal estimand was defined over \emph{a priori
 counterfactuals} not observable in the real world (Frangakis and Rubin
@@
 time until cancer under rule \(a\) is
-\(\mu_{a} = \sum_0^K S_{a}(t) \, dt\). Our causal estimand is summary
-measure \(\psi = \mu_{a_1} - \mu_{a_0}\), the difference in expected
-time until event under two different interventions over 20 years of
-follow-up under five different data generating scenarios. Bias will be
-evaluated by comparing estimates of \(\psi\) to its true value in 250
-simulations per scenario (the original analysis performed 500). The true
-value will be calculated by simulating the full data for five hundred
-thousand individuals (the original analysis used one million) with rules
-\(a_0\) and \(a_1\) applied deterministically. Estimates of \(\psi\)
-will be obtained by first estimating the survival curves \(S_a(t)\)
-using two estimators: the inverse probability weighted Kaplan-Meier
-estimator (WKM) and the Aalen-filtered WKM (AWKM). These survival
-estimators are detailed in the following section.
+\(\mu_{a} = \sum_0^K S_{a}(t) \, dt\). The parameter used in the
+estimation of bias was the summary measure
+\(\psi = \mu_{a_1} - \mu_{a_0}\), the difference in expected time until
+event under two different interventions over 20 years of follow-up under
+five different data generating scenarios. Bias was evaluated by
+comparing estimates of \(\psi\) to its true value in 250 simulations per
+scenario (the original analysis performed 500). The true value was
+calculated by simulating the full data for five hundred thousand
+individuals (the original analysis used one million) with rules \(a_0\)
+and \(a_1\) applied deterministically. Estimates of \(\psi\) were
+obtained by first estimating the survival curves \(S_a(t)\) using two
+estimators: the inverse probability weighted Kaplan-Meier estimator
+(WKM) and the Aalen-filtered WKM (AWKM). These survival estimators are
+detailed in the following section.
 
@@
 %
+\path[->] (H0) edge (N0);
+\path[->] (N0) edge (A0);
 \path[->] (H0) edge (H);
@@
     }\right)
-& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
+& = \alpha_0 + W \alpha_1 + A(t - 1) \alpha_2 \\
 \text{logit} \left(\Prob{
@@
     & = \beta_0 + W \beta_1 + \bar A(t - 1) \beta_2
-\end{aligned}\] The first will be fitted on data for those alive and at
-work at time \(t\). The second will be among those alive and (observed
-to be) cancer-free. For each unit at time \(t\), the weight will be
-calculated by taking the inverse of the cumulative probability of
-following the exposure rule and remaining uncensored: \[\hat w_{a} (t) =
+\end{aligned}\] The first was fit on data for those alive and at work at
+time \(t\). The second was among those alive and (observed to be)
+cancer-free. For each unit at time \(t\), the weight was calculated by
+taking the inverse of the cumulative probability of following the
+exposure rule and remaining uncensored: \[\hat w_{a} (t) =
     \left[
@@
 intervention rule and scenario. Qualitatively, the WKM estimator
-consistently over-estimates survival whereas the the AWKM survival curve
-is much closer to the truth. The bias of the AWKM survival estimate
-appears to be larger earlier in follow-up and smaller as follow-up
-extends forward. The bias of both the the WKM and the AWKM survival
-curves appears largest in Scenario 5.
+consistently over-estimated survival whereas the the AWKM survival curve
+was much closer to the truth. The bias of the AWKM survival estimator
+appeared to be larger in earlier follow-up and smaller for later
+follow-up time points. The bias of both the the WKM and the AWKM
+estimators appeared largest in Scenario 5.
 
@@
 average cancer-free survival time over 20 years of follow-up. These
-numeric results are consistent with the qualitative interpretations of
-Figure \ref{fig:survival}. The WKM estimator over-estimates the
+numeric results were consistent with the qualitative interpretations of
+Figure \ref{fig:survival}. The WKM estimator over-estimated the
 difference in cancer-free survival time, resulting in bias toward the
@@
 survival, resulting in bias away from the null. In every scenario, the
-bias of the WKM-derived contrast is several times larger in magnitude
-than that of the AWKM-derived contrast. The bias of both estimators is
+bias of the WKM-derived contrast was several times larger in magnitude
+than that of the AWKM-derived contrast. The bias of both estimators was
 greatest for Scenario 5.
 
-The qualitative results here are consistent with those of Izano (2017).
-However, true and estimated survival in the present analysis is larger
+The qualitative results here were consistent with those of Izano (2017).
+However, true and estimated survival in the present analysis was larger
 than those found previously. Furthermore, the true and estimator average
-mean differences in survival are smaller in magnitude in the present
-case. The magnitudes of the bias estimates are also smaller.
+mean differences in survival were smaller in magnitude in the present
+case. The magnitudes of the bias estimates were also smaller.
 
@@
 $a_0$ & Truth & 19.08 & 19.10 & 19.10 & 18.02 & 17.83 \\ 
-   & WKM & 19.52 & 19.51 & 19.53 & 18.92 & 18.90 \\ 
-   & AWKM & 19.02 & 19.00 & 19.02 & 17.79 & 17.72 \\ 
+   & WKM & 19.52 & 19.51 & 19.52 & 18.91 & 18.90 \\ 
+   & AWKM & 19.01 & 19.00 & 19.01 & 17.80 & 17.71 \\ 
    \midrule
 $a_1$ & Truth & 18.80 & 18.79 & 18.76 & 17.54 & 17.29 \\ 
-   & WKM & 19.39 & 19.37 & 19.37 & 18.68 & 18.62 \\ 
-   & AWKM & 18.70 & 18.67 & 18.67 & 17.30 & 17.07 \\ 
+   & WKM & 19.41 & 19.39 & 19.39 & 18.68 & 18.67 \\ 
+   & AWKM & 18.76 & 18.76 & 18.74 & 17.30 & 17.22 \\ 
    \bottomrule
@@
 Truth & -0.28 & -0.31 & -0.34 & -0.48 & -0.54 \\ 
-  WKM & -0.14 & -0.15 & -0.15 & -0.23 & -0.28 \\ 
-  AWKM & -0.31 & -0.33 & -0.35 & -0.50 & -0.64 \\ 
+  WKM & -0.11 & -0.12 & -0.13 & -0.23 & -0.23 \\ 
+  AWKM & -0.25 & -0.24 & -0.27 & -0.50 & -0.50 \\ 
    \bottomrule
@@
   \midrule
-WKM & 0.14 & 0.16 & 0.19 & 0.25 & 0.26 \\ 
-  AWKM & -0.03 & -0.02 & -0.01 & -0.02 & -0.10 \\ 
+WKM & 0.17 & 0.19 & 0.21 & 0.25 & 0.31 \\ 
+  AWKM & 0.03 & 0.07 & 0.07 & -0.02 & 0.04 \\ 
    \bottomrule
@@
 \end{table}
+
+\hypertarget{application-to-the-uaw-gm-cohort}{%
+\section{Application to the UAW-GM
+Cohort}\label{application-to-the-uaw-gm-cohort}}
+
+In the simulation study, we showed that under several scenarios
+compatible with our hypothetical causal structure, the AWKM survival
+estimator had small bias compared to the WKM estimator. The bias was
+smaller when the cumulative incidence of the outcome was low and at
+later follow-up time points. Next, we estimated cancer-free survival in
+a real-world context. Using data from the UAW-GM Cohort study, we
+followed \(38\,553\) individuals starting from hire to 40 years after
+hire for incidence of colon cancer. This duration of follow-up spans the
+vast majority of individuals' working lifetimes. As in the simulation,
+the UAW-GM data were longitudinal data with baseline covariates,
+time-varying covariates, and a survival outcome.
+
+The exposures of interest were MWF of three types: straight, soluble,
+and synthetic (Byers 2006; F. Mirer 2003; F. E. Mirer 2010). Straight
+MWFs are hydrocarbon-based fluids whose use became widespread by the
+1920s. They continue to be widely used because of their simple
+formulation. In straight MWFs, hydrocarbons of different lengths are
+mixed together with other additives to attain different properties.
+Straight MWFs contain polycyclic aromatic hydrocarbons, long known to be
+carcinogenic (IARC 1973). Soluble oils are water-based oil emulsions
+first introduced in response to rising oil prices. They now make up the
+largest market share of MWFs (Childers 2006). Soluble oils are
+vulnerable to microbial contamination, so the addition of biocides is
+needed. However, their high lubricity makes soluble MWFs the most
+popular fluid type. Synthetic MWFs have the best toxicological profile,
+have no oil, and have a higher resistance to microbial growth. They were
+introduced into the MWF market in the second half of the 20th C., but
+fail to out-perform soluble MWFs in metalworking applications. Soluble
+and synthetic MWFs contain biocides, corrosion inhibitors, and
+chlorinated compounds, some classified as carcinogenic by the IARC (IARC
+1987).
+
+The outcome of interest was colon cancer incidence. There is little past
+research linking colon cancer to MWF exposures, but there is some
+evidence suggesting that straight MWFs cause colon cancer (Izano et al.
+2019). We obtained cancer incidence data via linkage to the Michigan
+Cancer Registry, which recorded cancer incidence cases starting on
+January 1, 1985. The cohort is comprised of individuals hired between
+1938 and 1985. Cancer-free survival to the start of the registry was a
+left-filtering process possibly in the presence of the HWSE as
+investigated in the simulations. Over the 40 year follow-up period,
+vital status was obtained through the Social Security Administration,
+the National Death Index, as well as records provided by the UAW.
+Baseline confounders included race, sex, plant, and year of hire.
+Time-varying confounders included age, cumulative time off, and exposure
+to the metalworking fluids not under study. These terms were included in
+the estimation of both the treatment and censoring mechanisms, which
+were estimated with stratification on every year of follow-up. The
+exposure rules of interest were identical to those in the simulation
+study: \(a_0\) never exposed and \(a_1\) always exposed while at work.
+We assumed that the effect of exposure on health status, mortality,
+cancer incidence, etc occurs after a lag of 15 years. Similarly, we
+assumed that the effects of cumulative time off occur after a 15 year
+lag. Counterfactual survival under rules \(a_0\) and \(a_1\) were
+estimated using the WKM and AWKM estimators. Summary statistics for the
+full study population and the colon cancer cases are presented in Table
+\ref{tab:popchar}.
+
+\begin{table}[h]
+\caption{Study population characteristics.}
+\label{tab:popchar}
+\begin{center}\begin{tabular}{lrlrl}
+\toprule
+&       \multicolumn{2}{c}{Full cohort}       & \multicolumn{2}{c}{Colon cancer cases}      \\
+\midrule
+$n$ (person-years) 
+            &     38 553 & (1 402 372)       & 267 & (9 635)        \\
+Race (\%) \\
+\hspace{1.5em} Black   &      7 133 & (18.5)                &  83 & (31.1)          \\
+\hspace{1.5em} White   &     31 420 & (81.5)                & 184 & (68.9)          \\
+Sex (\%) \\
+\hspace{1.5em} Female  &      4 757 & (12.3)                &  49 & (18.4)      \\
+\hspace{1.5em} Male    &     33 796 & (87.7)                & 218 & (81.6)      \\
+Plant (\%) \\
+\hspace{1.5em} Plant 1 &      9 092 & (23.6)                &  66 & (24.7)      \\
+\hspace{1.5em} Plant 2 &     17 090 & (44.3)                & 107 & (40.1)      \\
+\hspace{1.5em} Plant 3 &     12 371 & (32.1)                &  94 & (35.2)          \\
+\midrule
+Ever exposed to MWF (\%)
+                        &     22193 & (57.6)                & 104 & (39.0)          \\
+Year of hire (mean (\textsc{sd}))
+                        &     1963 & (11.62)            & 1968 & (8.79)         \\
+Age (mean (\textsc{sd}))
+                        &     63.38 & (9.08)                & 67.78 & (9.27)        \\
+Cumulative time off (mean (\textsc{sd}))
+                        &     0.04 & (0.14)               & 0.05 & (0.15)       \\
+\bottomrule
+\end{tabular}\end{center}
+\end{table}
+
+\hypertarget{assumptions}{%
+\subsection{Assumptions}\label{assumptions}}
+
+Since we are working with observational data, the evaluation of the
+no-interference, causal consistency, ignorability, and positivity
+assumptions are critical for causal inference. The stability of our
+estimation depends on positivity, which we assessed qualitatively by
+examining the distribution of the weights. The no-interference
+assumption may be problematized by the fact that there were a finite
+number of job types in the factory setting. If one worker operates a
+particular metalworking machine, then the the other workers are not able
+to operate that machine at that time. Instead, they may be assigned to
+assembly tasks, which have lower MWF exposure opportunities. That said,
+since these factories were quite large, there may be approximate
+independence. The consistency assumption is also problematic. The MWFs
+of interest are complex chemical mixtures whose composition changes by
+design and by nature. Over the last several decades, the formulation of
+MWFs has changed significantly in reaction to performance needs and
+toxicity concerns (F. Mirer 2003; Byers 2006). The composition of MWFs
+also undergoes unintentional changes because of the nature of their use:
+MWFs are often applied in contexts where contamination by other
+substances and microbes is possible and chemical changes due to heat and
+pressure are likely. Indeed, there are substantial concerns over the
+carcinogenicity of the chemical species formed in the MWF mixtures that
+were not originally added (Hidajat et al. 2020). Concerns regarding the
+consistency assumption may be abrogated in part by adequate adjustment
+for secular and factory-level characteristics.
+
+Another key assumption meriting discussion is that of conditional
+ignorability. In order to achieve identification, even in the absence of
+left filtering, we need to have conditionally ignorable future exposure
+status and ignorable future censoring status at each time point given
+past data. In occupational cohorts, employment status and health history
+are strong predictors of future death (Häfner 1987; Halliday 2014;
+Laliotis and Stavropoulou 2018). Logically, major causes of death first
+act through employment status before they precipitate death. This
+dynamic is actually a key component in the setup for HWSE. We are
+therefore relatively confident that conditional ignorability of
+censoring due to death is attained given covariate, exposure, and cancer
+history. Our confidence in the conditional ignorability of exposure
+given history was not as strong. In particular, workers may be assigned
+to certain tasks based on their specific skills and knowledge, which may
+be associated with structural privileges that confer a lower risk of
+deleterious health outcomes. The potential magnitude of this
+uncontrolled confounding is likely to be limited, however. The education
+level of the workers in the cohort was homogeneous, and all cohort
+members were members of the UAW union, which had uniform procedures in
+place for equitable access to training, wages, and career advancement
+(Harbison 1950; Barnard 2005). The presence of UAW policies support the
+assertion that given time since hire, job types (and therefore
+exposures) were randomly allocated.
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  Foo
+\end{itemize}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\begin{itemize}
+\tightlist
+\item
+  FU in GM is much longer than 20 years
+\item
+  Exclusion restriction on \(H\) so that its parents do not include
+  \(A\) is not necessary for identification in full data
+\item
+  Exclusion restriction on \(D\) so that its parents do not include
+  \(H\) not needed if \(H\) is observed and conditioned upon
+\item
+  Not clear if these were for convenience or what
+\item
+  What if we increase FU? Lags?
+\item
+  Greater fineness in exposure definition? Different interventions?
+\item
+  No way to verify to what extent the simulation informs the real data
+  generating system
+\item
+  Model specification, double robustness
+\end{itemize}
 
@@
 
+\leavevmode\hypertarget{ref-Barnard_2005}{}%
+Barnard, John. 2005. \emph{American Vanguard: The United Auto Workers
+During the Reuther Years, 1935-1970}. Wayne State University Press.
+
 \leavevmode\hypertarget{ref-Byers_2006}{}%
 Byers, Jerry P. 2006. \emph{Metalworking Fluids}. CRC Press.
+
+\leavevmode\hypertarget{ref-Childers_2006}{}%
+Childers, Jean. 2006. {``The Chemistry of Metalworking Fluids.''} In
+\emph{Metalworking Fluids}. CRC Press.
 
@@
 
+\leavevmode\hypertarget{ref-Halliday_2014}{}%
+Halliday, Timothy J. 2014. {``Unemployment and Mortality: Evidence from
+the PSID.''} \emph{Soc Sci Med} 113 (July): 15--22.
+\url{https://doi.org/10.1016/j.socscimed.2014.04.038}.
+
+\leavevmode\hypertarget{ref-Harbison_1950}{}%
+Harbison, Frederick H. 1950. {``The General Motors-United Auto Workers
+Agreement of 1950.''} \emph{Journal of Political Economy} 58 (5):
+397--411.
+
+\leavevmode\hypertarget{ref-Hafner_1987}{}%
+Häfner, H. 1987. {``Unemployment and Health.''} \emph{Dtsch Med
+Wochenschr} 112 (37): 1428--32.
+\url{https://doi.org/10.1055/s-2008-1068265}.
+
+\leavevmode\hypertarget{ref-Hidajat_2020}{}%
+Hidajat, Mira, Damien Martin McElvenny, Peter Ritchie, Andrew Darnton,
+William Mueller, Raymond M Agius, John W Cherrie, and Frank de Vocht.
+2020. {``Lifetime Cumulative Exposure to Rubber Dust, Fumes and
+n-Nitrosamines and Non-Cancer Mortality: A 49-Year Follow-up of UK
+Rubber Factory Workers.''} \emph{Occup Environ Med} 77 (5): 316--23.
+\url{https://doi.org/10.1136/oemed-2019-106269}.
+
+\leavevmode\hypertarget{ref-IARC_1973}{}%
+IARC. 1973. \emph{IARC Monographs on the Evaluation of Carcinogenic Risk
+of the Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons and
+Heterocyclic Compounds}. Vol. 3. World Health Organization International
+Agency for Research on Cancer.
+
+\leavevmode\hypertarget{ref-IARC_1987}{}%
+---------. 1987. \emph{IARC Monographs on the Evaluation of the
+Carcinogenic Risk of Chemicals to Humans. Overall Evaluations of
+Carcinogenicity: An Updating of IARC Monographs, Volumes 1 to 42}.
+\emph{World Health Organization}. Vol. 7. World Health Organization
+International Agency for Research on Cancer.
+
 \leavevmode\hypertarget{ref-Izano_2017_thesis}{}%
@@
 
+\leavevmode\hypertarget{ref-Laliotis_2018}{}%
+Laliotis, Ioannis, and Charitini Stavropoulou. 2018. {``Crises and
+Mortality: Does the Level of Unemployment Matter?''} \emph{Soc Sci Med}
+214 (October): 99--109.
+\url{https://doi.org/10.1016/j.socscimed.2018.08.016}.
+
+\leavevmode\hypertarget{ref-Mirer_2003}{}%
+Mirer, Franklin. 2003. {``Updated Epidemiology of Workers Exposed to
+Metalworking Fluids Provides Sufficient Evidence for Carcinogenicity.''}
+\emph{Applied Occupational and Environmental Hygiene} 18 (11): 902--12.
+
+\leavevmode\hypertarget{ref-Mirer_2010}{}%
+Mirer, Franklin E. 2010. {``New Evidence on the Health Hazards and
+Control of Metalworking Fluids Since Completion of the OSHA Advisory
+Committee Report.''} \emph{American Journal of Industrial Medicine} 53
+(8): 792--801.
+
 \leavevmode\hypertarget{ref-Naimi_2013}{}%

### 2021-12-11 reports/01-introduction.Rmd
Interim results; running on GM data now

@@
 Previous studies have attempted to assess the presence of the HWSE in observed data by assessing so-called path-specific associations using Cox proportional hazards modeling [@Naimi_2013;@Garcia_2017].
-However, these measures of associations are themselves subject to the confounding they seek to quantify.
+However, these measures of associations were themselves subject to the confounding structures they sought to characterize.
 
-If sequential ignorability of exposure status at each point in follow-up and positivity can be attained conditional on covariates, then causal methods can be applied to account for the HWSE.
-Past studies have applied causal methods capable of accounting for time-varying confounding affected by past exposure to the study of MWF exposures and cancer mortality outcomes in the UAW-GM Cohort Study [@Garcia_2018;@Izano_2019], but the study of cancer incidence outcomes is further problematized by incomplete observation of cancer incidence outcomes over the study period.
-We wish to make inferences about the carcinogenicity of MWF exposure over an individual's lifetime starting three years after they enter the workforce.
-The UAW-GM Cohort includes those hired roughly between 1938 and 1982.
+If conditional sequential ignorability of exposure and censoring status at each point in follow-up and positivity can be attained given covariate history, then causal methods can be applied to account for the HWSE.
+Past studies have applied causal methods capable of accounting for time-varying confounding affected by past exposure to the study of MWF exposures and cancer mortality outcomes in the UAW-GM Cohort Study [@Garcia_2018;@Izano_2019], but the study of cancer incidence outcomes is further problematized by the incomplete observation of cancer incidence outcomes at every point of follow-up over the study period.
+Nonetheless, we wish to make inferences about the carcinogenicity of MWF exposure over an individual's lifetime starting upon entry into the workforce.
+The UAW-GM Cohort included those hired roughly between 1938 and 1985.
 However, cancer incidence reporting at the Michigan Cancer Registry did not begin until 1985.
-In particular, we have the presence of _left filtering_ in the UAW-GM Cohort Study when cancer incidence is the outcome of interest: before 1985, both cancer incidence status and time of cancer incidence are unknown.
-Observation of the complete cancer incidence outcome vector over the study period is conditional on an individual surviving to 1985 cancer-free.
+Hence, our observed cohort data is subject to _left filtering_: cancer incidence is the outcome of interest, but before 1985, both cancer incidence status and time of cancer incidence are unknown.
+Observation of the complete cancer incidence outcome vector over the study period was conditional on an individual surviving to 1985 cancer-free.
 
 In the presence of the HWSE, left filtering implies outcome misclassification that is informative of true cancer status.
-As part of her dissertation research, @Izano_2017_thesis conducted a quantitative bias analysis for the estimation of survival curves in the presence of left filtering and the HWSE.
+As part of her dissertation research, @Izano_2017_thesis conducted a quantitative bias analysis for the estimation of survival curves using left filtered data in the presence of HWSE.
 She simulated data compatible with the HWSE and estimated cancer-free survival curves using an inverse probability of treatment and censoring weighted Kaplan-Meier (WKM) estimator and the WKM with an Aalen filter for left-filtering (AWKM) [@Andersen_1993;@Xie_2005].
 Data were simulated under five different scenarios.
-The causal estimands of interest were the survival curves under interventions: (1) always exposed at work with no censoring due to death and (2) never exposed at work with no censoring due to death.
+The survival curves under the following interventions were computed or estimated in 250 replicates: (1) always exposed at work with no censoring due to death and (2) never exposed at work with no censoring due to death.
 For each intervention, three survival curves were produced: (1) the true survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
-The bias in mean survival difference calculated by AWKM was negligible when the true 20-year risk of cancer was under 0.25.
+Estimator bias was evaluated by comparing the average of 250 estimates of to the average difference in cancer-free survival under the two rules to the true average survival difference when exposure and censoring were controlled deterministically.
 
-Here, we replicate the simulation and bias analysis presented in Chapter 3 of @Izano_2017_thesis, embed the problem in the non-parametric structural causal approach of @Pearl_1995, comment on the results, and apply the WKM and AWKM estimators to the UAW-GM Cohort.
+The present project replicates the simulation and bias analyses presented in Chapter 3 of @Izano_2017_thesis, embeds the problem in the non-parametric structural causal approach of @Pearl_1995, and applies the WKM and AWKM estimators to the estimation of colon cancer survival under exposure/censoring rules in the UAW-GM Cohort.

### 2021-12-11 reports/02-methods.Rmd
Interim results; running on GM data now

@@
 
-The UAW-GM Cohort data includes person-year level exposure, outcome, and covariate data starting three years after hire.
-To emulate the shape of the data for this longitudinal cohort, we consider 20 years of data over time indexed by years since hire.
+The UAW-GM Cohort data included person-year level exposure, outcome, and covariate data starting at hire.
+To emulate the shape of the data for this longitudinal cohort, we considered 20 years of data over time indexed by years since hire.
 Notation representing the variables of interest are presented in Table \ref{tab:variables}.
+The causal model represents hypothetical relationships between variables over time compatible with the theory underlying the HWSE in longitudinal occupational cohort studies.
+At each time point, the effect of cumulative exposure $\bar A(t)$ on cancer incidence $Y^(t)$ is confounded by a path through employment status $N(t)$ and underlying health $H(t)$ as well as the path through past exposure $\bar A(t - 1)$ and vital status $D(t)$.
+These paths follow straightforward logic: occupational exposure depends upon employment status and past exposure; mortality status is affected by past exposure and cancer history.
+Confounding by baseline covariates $W$ is assumed throughout.
 
@@
 Call $X$ the full data, where we have $R = 0$ for all.
-In the observed data $X^\text{obs}$, we cannot assume $R = 0$ for all, and susceptibility $S$ is not known:
+In the observed data $X^\text{obs}$, we cannot assume $R = 0$ for all; susceptibility $S$ and underlying health status $H$ are not known:
 $$X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).$$
@@
 
+Figure \ref{fig:dag} clarifies our conceptualization of the HWSE.
+At each time point $t$, the cumulative effect of exposure $\bar A(t)$ on cancer incidence $Y^*(t)$ is confounded by employment status $N(t)$ through the backdoor path $\bar A(t) \leftarrow N(t) \leftarrow H(t) \rightarrow Y^*(t)$.
+In the absence of observed data on health status $H(t)$, an analyst may be tempted to condition on employment status $N(t)$, but doing so would introduce collider bias while blocking the causal path between past exposure $\bar A(t - 1)$ and cancer $Y^*(t)$.
+Furthermore, an analysis starting at an arbitrary time point after the time origin (hire) would be tantamount to conditioning on those still alive at that time, which would also result in both collider bias and the conditioning on nodes on the causal path between the exposure and outcome of interest.
+
 ## Simulation
 
-Parametric relationships between the variables were imposed in simulations. For the $n = 50\,000$ units over $T = 20$ years, we have:
+To generate data compatible with our structural causal model, we imposed parametric relationships between the variables. For the $n = 50\,000$ units over $T = 20$ years, we have:
 
@@
 
-The substantive question of interest is the causal effect of occupational exposure to MWF on cancer incidence risk.
-Since occupational MWF exposure occurs only when individuals are at work, we define dynamic exposure regimes that depend on employment status.
+The substantive question of interest was the causal effect of occupational exposure to MWF on cancer incidence risk.
+Since occupational MWF exposure occurs only when individuals are at work, we defined dynamic exposure regimes that depend on employment status.
 Under rule $a_0$, set $D(t) = 0$, and set $A(t) = 0$ while $N(t) = 1$.
 Under rule $a_1$, set $D(t) = 0$, and set $A(t) = 1$ while $N(t) = 1$.
-Under both rules, we prevent censoring by death as if it were intervenable.
-The causal effect is defined by contrasting the survival function $S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}$ under rule $a_1$ to $S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}$ that under rule $a_0$.
-Note that this causal estimand is defined over _a priori counterfactuals_ not observable in the real world [@Frangakis_2002].
+Under both rules, we prevented censoring by death as if it were intervenable.
+The causal effect was defined by contrasting the survival function $S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}$ under rule $a_1$ to $S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}$ that under rule $a_0$.
+Note that this causal estimand was defined over _a priori counterfactuals_ not observable in the real world [@Frangakis_2002].
 This approach is standard in epidemiologic studies, however.
@@
 The expected time until cancer under rule $a$ is $\mu_{a} = \sum_0^K S_{a}(t) \, dt$.
-Our causal estimand is summary measure $\psi = \mu_{a_1} - \mu_{a_0}$, the difference in expected time until event under two different interventions over 20 years of follow-up under five different data generating scenarios.
-Bias will be evaluated by comparing estimates of $\psi$ to its true value in 250 simulations per scenario (the original analysis performed 500).
-The true value will be calculated by simulating the full data for five hundred thousand individuals (the original analysis used one million) with rules $a_0$ and $a_1$ applied deterministically.
-Estimates of $\psi$ will be obtained by first estimating the survival curves $S_a(t)$ using two estimators: the inverse probability weighted Kaplan-Meier estimator (WKM) and the Aalen-filtered WKM (AWKM).
+The parameter used in the estimation of bias was the summary measure $\psi = \mu_{a_1} - \mu_{a_0}$, the difference in expected time until event under two different interventions over 20 years of follow-up under five different data generating scenarios.
+Bias was evaluated by comparing estimates of $\psi$ to its true value in 250 simulations per scenario (the original analysis performed 500).
+The true value was calculated by simulating the full data for five hundred thousand individuals (the original analysis used one million) with rules $a_0$ and $a_1$ applied deterministically.
+Estimates of $\psi$ were obtained by first estimating the survival curves $S_a(t)$ using two estimators: the inverse probability weighted Kaplan-Meier estimator (WKM) and the Aalen-filtered WKM (AWKM).
 These survival estimators are detailed in the following section.
@@
 	}\right)
-& = \alpha_0 + W \alpha_1 + \bar A(t - 1) \alpha_2 \\
+& = \alpha_0 + W \alpha_1 + A(t - 1) \alpha_2 \\
 \text{logit} \left(\Prob{
@@
 \end{aligned}$$
-The first will be fitted on data for those alive and at work at time $t$.
-The second will be among those alive and (observed to be) cancer-free.
-For each unit at time $t$, the weight will be calculated by taking the inverse of the cumulative probability of following the exposure rule and remaining uncensored:
+The first was fit on data for those alive and at work at time $t$.
+The second was among those alive and (observed to be) cancer-free.
+For each unit at time $t$, the weight was calculated by taking the inverse of the cumulative probability of following the exposure rule and remaining uncensored:
 $$\hat w_{a} (t) =

### 2021-12-11 reports/03-results.Rmd
Interim results; running on GM data now

@@
 Figure \ref{fig:survival} presents the true survival curves as well as the WKM and AWKM survival curves averaged over 250 replications for each intervention rule and scenario.
-Qualitatively, the WKM estimator consistently over-estimates survival whereas the the AWKM survival curve is much closer to the truth.
-The bias of the AWKM survival estimate appears to be larger earlier in follow-up and smaller as follow-up extends forward.
-The bias of both the the WKM and the AWKM survival curves appears largest in Scenario 5.
+Qualitatively, the WKM estimator consistently over-estimated survival whereas the the AWKM survival curve was much closer to the truth.
+The bias of the AWKM survival estimator appeared to be larger in  earlier follow-up and smaller for later follow-up time points.
+The bias of both the the WKM and the AWKM estimators appeared largest in Scenario 5.
 
@@
 Table \ref{tab:bias} presents estimates of the bias of the WKM and AWKM estimators for $\psi$, the difference in average cancer-free survival time over 20 years of follow-up.
-These numeric results are consistent with the qualitative interpretations of Figure \ref{fig:survival}.
-The WKM estimator over-estimates the difference in cancer-free survival time, resulting in bias toward the null, whereas the AWKM estimator under-estimates the cancer-free survival, resulting in bias away from the null.
-In every scenario, the bias of the WKM-derived contrast is several times larger in magnitude than that of the AWKM-derived contrast.
-The bias of both estimators is greatest for Scenario 5.
+These numeric results were consistent with the qualitative interpretations of Figure \ref{fig:survival}.
+The WKM estimator over-estimated the difference in cancer-free survival time, resulting in bias toward the null, whereas the AWKM estimator under-estimates the cancer-free survival, resulting in bias away from the null.
+In every scenario, the bias of the WKM-derived contrast was several times larger in magnitude than that of the AWKM-derived contrast.
+The bias of both estimators was greatest for Scenario 5.
 
-The qualitative results here are consistent with those of @Izano_2017_thesis.
-However, true and estimated survival in the present analysis is larger than those found previously.
-Furthermore, the true and estimator average mean differences in survival are smaller in magnitude in the present case.
-The magnitudes of the bias estimates are also smaller.
+The qualitative results here were consistent with those of @Izano_2017_thesis.
+However, true and estimated survival in the present analysis was larger than those found previously.
+Furthermore, the true and estimator average mean differences in survival were smaller in magnitude in the present case.
+The magnitudes of the bias estimates were also smaller.
 

### 2021-12-11 reports/04-gm.Rmd
Interim results; running on GM data now

@@
 
+```{r, include=F}
+knitr::opts_chunk$set(echo = F, results = "asis", fig.align = "center")
+if (!"mytheme" %in% ls()) {
+  source("~/headRs/00-my-theme.R")
+  library(data.table)
+  options(tikzDefaultEngine = 'pdftex')
+}
+library(tidyverse); library(data.table)
+library(here)
+library(tableone)
+```
+
 # Application to the UAW-GM Cohort
@@
 The bias was smaller when the cumulative incidence of the outcome was low and at later follow-up time points.
-Now, we estimate cancer-free survival in a real-world context.
-Using data from the UAW-GM Cohort study, we follow individuals starting from hire to 40 years after hire for incidence of colon cancer.
+Next, we estimated cancer-free survival in a real-world context.
+Using data from the UAW-GM Cohort study, we followed $38\,553$ individuals starting from hire to 40 years after hire for incidence of colon cancer.
 This duration of follow-up spans the vast majority of individuals' working lifetimes.
+As in the simulation, the UAW-GM data were longitudinal data with baseline covariates, time-varying covariates, and a survival outcome.
 
-Colon cancer incidence was obtained via linkage to the Michigan Cancer Registry, which recorded cancer incidence cases starting on January 1, 1985.
+The exposures of interest were MWF of three types: straight, soluble, and synthetic [@Byers_2006; @Mirer_2003; @Mirer_2010].
+Straight MWFs are hydrocarbon-based fluids whose use became widespread by the 1920s.
+They continue to be widely used because of their simple formulation.
+In straight MWFs, hydrocarbons of different lengths are mixed together with other additives to attain different properties.
+Straight MWFs contain polycyclic aromatic hydrocarbons, long known to be carcinogenic [@IARC_1973].
+Soluble oils are water-based oil emulsions first introduced in response to rising oil prices.
+They now make up the largest market share of MWFs [@Childers_2006].
+Soluble oils are vulnerable to microbial contamination, so the addition of biocides is needed.
+However, their high lubricity makes soluble MWFs the most popular fluid type.
+Synthetic MWFs have the best toxicological profile, have no oil, and have a higher resistance to microbial growth.
+They were introduced into the MWF market in the second half of the 20th C., but fail to out-perform soluble MWFs in metalworking applications.
+Soluble and synthetic MWFs contain biocides, corrosion inhibitors, and chlorinated compounds, some classified as carcinogenic by the IARC [@IARC_1987].
+
+The outcome of interest was colon cancer incidence.
+There is little past research linking colon cancer to MWF exposures, but there is some evidence suggesting that straight MWFs cause colon cancer [@Izano_2019].
+We obtained cancer incidence data via linkage to the Michigan Cancer Registry, which recorded cancer incidence cases starting on January 1, 1985.
 <!-- and linkage to Surveillance, Epidemiology, and End Results (SEER), which recorded cancer incidence cases starting on January 1, 1973. -->
 The cohort is comprised of individuals hired between 1938 and 1985.
-Cancer-free survival to the start of the registry is a left-filtering process possibly in the presence of the HWSE as investigated in the simulations.
+Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE as investigated in the simulations.
 Over the 40 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
@@
 Time-varying confounders included age, cumulative time off, and exposure to the metalworking fluids not under study.
-Representations of these terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every year of follow-up.
+These terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every year of follow-up.
 The exposure rules of interest were identical to those in the simulation study: $a_0$ never exposed and $a_1$ always exposed while at work.
-We assume that the effect of exposure on health status, mortality, cancer incidence, etc occurs after a lag of 15 years.
-Similarly, we assume that the effects of cumulative time off occur after a 15 year lag.
+We assumed that the effect of exposure on health status, mortality, cancer incidence, etc occurs after a lag of 15 years.
+Similarly, we assumed that the effects of cumulative time off occur after a 15 year lag.
 Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.
+Summary statistics for the full study population and the colon cancer cases are presented in Table \ref{tab:popchar}.
 
@@
 mwf <- NULL
-source(here("scripts", "04-application.R"))
+if (!"cohort_analytic" %in% ls()) {source(here("scripts", "04-application.R"))}
+full.tab <- cohort_analytic[,.(
+	studyno,
+	Race,
+	Sex,
+	Plant,
+	yin = yin.gm,
+	age = age.year2/365,
+	off = off.gan + off.san + off.han,
+	straight = as.integer(straight > 0),
+	soluble = as.integer(straight > 0),
+	synthetic = as.integer(straight > 0),
+	death = `All causes`,
+	canc_co
+)]
+
+nrow(full.tab)
+print(
+	CreateTableOne(data = full.tab[,.(
+		Race = Race[1],
+		Sex = Sex[1],
+		Plant = c("Plant 1", "Plant 2", "Plant 3")[which.max(table(Plant))],
+		Dead = factor(max(death))
+	), studyno]),
+	showAllLevels = T)
+
+print(
+	CreateTableOne(data = full.tab[,.(
+		Straight = factor(as.integer(sum(shift(straight, 15, 0)) <= 0)),
+		Soluble = factor(as.integer(sum(shift(soluble, 15, 0)) <= 0)),
+		Synthetic = factor(as.integer(sum(shift(synthetic, 15, 0)) <= 0)),
+		`Year of hire` = yin[1],
+		Age = age[min(.N, .I[canc_co == 1], na.rm = T)],
+		`Cumulative time off` = shift(
+			off, 15, 0)[min(.N, .I[canc_co == 1], na.rm = T)]
+	), studyno])
+	)
+
+nrow(full.tab[studyno %in% full.tab[canc_co == 1, studyno]])
+print(
+	CreateTableOne(data = full.tab[studyno %in% full.tab[canc_co == 1, studyno],.(
+		Race = Race[1],
+		Sex = Sex[1],
+		Plant = c("Plant 1", "Plant 2", "Plant 3")[which.max(table(Plant))]
+	), studyno]),
+	showAllLevels = T)
+
+print(
+	CreateTableOne(data = full.tab[studyno %in% full.tab[canc_co == 1, studyno],.(
+		Straight = factor(as.integer(sum(shift(straight, 15, 0)) <= 0)),
+		Soluble = factor(as.integer(sum(shift(soluble, 15, 0)) <= 0)),
+		Synthetic = factor(as.integer(sum(shift(synthetic, 15, 0)) <= 0)),
+		`Year of hire` = yin[1],
+		Age = age[min(.N, .I[canc_co == 1], na.rm = T)],
+		`Cumulative time off` = shift(
+			off, 15, 0)[min(.N, .I[canc_co == 1], na.rm = T)]
+	), studyno])
+	)
+
+xtable(head(cars))
 ```
+
+\begin{table}[h]
+\caption{Study population characteristics.}
+\label{tab:popchar}
+\begin{center}\begin{tabular}{lrlrl}
+\toprule
+&		\multicolumn{2}{c}{Full cohort} 	  & \multicolumn{2}{c}{Colon cancer cases}		\\
+\midrule
+$n$ (person-years) 
+            &     38 553 & (1 402 372)       & 267 & (9 635)		\\
+Race (\%) \\
+\hspace{1.5em} Black   &      7 133 & (18.5)    			&  83 & (31.1)  		\\
+\hspace{1.5em} White   &     31 420 & (81.5)    			& 184 & (68.9)  		\\
+Sex (\%) \\
+\hspace{1.5em} Female  &      4 757 & (12.3)    			&  49 & (18.4)		\\
+\hspace{1.5em} Male    &     33 796 & (87.7)    			& 218 & (81.6)		\\
+Plant (\%) \\
+\hspace{1.5em} Plant 1 &      9 092 & (23.6)    			&  66 & (24.7)		\\
+\hspace{1.5em} Plant 2 &     17 090 & (44.3)    			& 107 & (40.1) 		\\
+\hspace{1.5em} Plant 3 &     12 371 & (32.1)    			&  94 & (35.2)    		\\
+\midrule
+Ever exposed to MWF (\%)
+						&     22193 & (57.6)    			& 104 & (39.0)  		\\
+Year of hire (mean (\textsc{sd}))
+						&     1963 & (11.62)    		& 1968 & (8.79) 		\\
+Age (mean (\textsc{sd}))
+						&     63.38 & (9.08)    			& 67.78 & (9.27) 		\\
+Cumulative time off (mean (\textsc{sd}))
+						&     0.04 & (0.14)    			  & 0.05 & (0.15) 		\\
+\bottomrule
+\end{tabular}\end{center}
+\end{table}
+
+## Assumptions
+
+Since we are working with observational data, the evaluation of the no-interference, causal consistency, ignorability, and positivity assumptions are critical for causal inference.
+The stability of our estimation depends on positivity, which we assessed qualitatively by examining the distribution of the weights.
+The no-interference assumption may be problematized by the fact that there were a finite number of job types in the factory setting.
+If one worker operates a particular metalworking machine, then the the other workers are not able to operate that machine at that time.
+Instead, they may be assigned to assembly tasks, which have lower MWF exposure opportunities.
+That said, since these factories were quite large, there may be approximate independence.
+The consistency assumption is also problematic.
+The MWFs of interest are complex chemical mixtures whose composition changes by design and by nature.
+Over the last several decades, the formulation of MWFs has changed significantly in reaction to performance needs and toxicity concerns [@Mirer_2003; @Byers_2006].
+The composition of MWFs also undergoes unintentional changes because of the nature of their use: MWFs are often applied in contexts where contamination by other substances and microbes is possible and chemical changes due to heat and pressure are likely.
+Indeed, there are substantial concerns over the carcinogenicity of the chemical species formed in the MWF mixtures that were not originally added [@Hidajat_2020].
+Concerns regarding the consistency assumption may be abrogated in part by adequate adjustment for secular and factory-level characteristics.
+
+Another key assumption meriting discussion is that of conditional ignorability.
+In order to achieve identification, even in the absence of left filtering, we need to have conditionally ignorable future exposure status and ignorable future censoring status at each time point given past data.
+In occupational cohorts, employment status and health history are strong predictors of future death [@Hafner_1987;@Halliday_2014;@Laliotis_2018].
+Logically, major causes of death first act through employment status before they precipitate death.
+This dynamic is actually a key component in the setup for HWSE.
+We are therefore relatively confident that conditional ignorability of censoring due to death is attained given covariate, exposure, and cancer history.
+Our confidence in the conditional ignorability of exposure given history was not as strong.
+In particular, workers may be assigned to certain tasks based on their specific skills and knowledge, which may be associated with structural privileges that confer a lower risk of deleterious health outcomes.
+The potential magnitude of this uncontrolled confounding is likely to be limited, however.
+The education level of the workers in the cohort was homogeneous, and all cohort members were members of the UAW union, which had uniform procedures in place for equitable access to training, wages, and career advancement [@Harbison_1950;@Barnard_2005].
+The presence of UAW policies support the assertion that given time since hire, job types (and therefore exposures) were randomly allocated.
+
+## Results
+
+- Foo

### 2021-12-11 reports/resources/results.tex
Interim results; running on GM data now

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-12-09 11:35:50
+% Created by tikzDevice version 0.12.3.1 on 2021-12-10 17:23:19
 % !TEX encoding = UTF-8 Unicode
@@
 	( 57.06,532.44) --
-	( 57.06,532.29) --
-	( 70.24,532.29) --
+	( 57.06,532.30) --
+	( 70.24,532.30) --
 	( 70.24,532.07) --
 	( 83.42,532.07) --
-	( 83.42,531.75) --
-	( 96.59,531.75) --
-	( 96.59,531.34) --
-	(109.77,531.34) --
-	(109.77,530.83) --
-	(122.95,530.83) --
-	(122.95,530.24) --
-	(136.12,530.24) --
-	(136.12,529.56) --
-	(149.30,529.56) --
-	(149.30,528.80) --
-	(162.48,528.80) --
-	(162.48,527.94) --
-	(175.66,527.94) --
-	(175.66,526.99) --
-	(188.83,526.99) --
-	(188.83,525.97) --
-	(202.01,525.97) --
-	(202.01,524.86) --
-	(215.19,524.86) --
-	(215.19,523.67) --
-	(228.36,523.67) --
-	(228.36,522.42) --
-	(241.54,522.42) --
-	(241.54,521.08) --
-	(254.72,521.08) --
-	(254.72,519.67) --
-	(267.89,519.67) --
-	(267.89,518.18) --
-	(281.07,518.18) --
-	(281.07,516.64) --
-	(294.25,516.64) --
-	(294.25,515.02);
+	( 83.42,531.73) --
+	( 96.59,531.73) --
+	( 96.59,531.32) --
+	(109.77,531.32) --
+	(109.77,530.81) --
+	(122.95,530.81) --
+	(122.95,530.21) --
+	(136.12,530.21) --
+	(136.12,529.54) --
+	(149.30,529.54) --
+	(149.30,528.76) --
+	(162.48,528.76) --
+	(162.48,527.90) --
+	(175.66,527.90) --
+	(175.66,526.95) --
+	(188.83,526.95) --
+	(188.83,525.91) --
+	(202.01,525.91) --
+	(202.01,524.81) --
+	(215.19,524.81) --
+	(215.19,523.61) --
+	(228.36,523.61) --
+	(228.36,522.37) --
+	(241.54,522.37) --
+	(241.54,521.03) --
+	(254.72,521.03) --
+	(254.72,519.61) --
+	(267.89,519.61) --
+	(267.89,518.13) --
+	(281.07,518.13) --
+	(281.07,516.58) --
+	(294.25,516.58) --
+	(294.25,514.97);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,532.44) --
-	( 57.06,532.22) --
-	( 70.24,532.22) --
-	( 70.24,531.89) --
-	( 83.42,531.89) --
-	( 83.42,531.43) --
-	( 96.59,531.43) --
-	( 96.59,530.86) --
-	(109.77,530.86) --
-	(109.77,530.19) --
-	(122.95,530.19) --
-	(122.95,529.41) --
-	(136.12,529.41) --
-	(136.12,528.53) --
-	(149.30,528.53) --
-	(149.30,527.54) --
-	(162.48,527.54) --
-	(162.48,526.46) --
-	(175.66,526.46) --
-	(175.66,525.27) --
-	(188.83,525.27) --
-	(188.83,523.99) --
-	(202.01,523.99) --
-	(202.01,522.62) --
-	(215.19,522.62) --
-	(215.19,521.16) --
-	(228.36,521.16) --
-	(228.36,519.61) --
-	(241.54,519.61) --
-	(241.54,517.96) --
-	(254.72,517.96) --
-	(254.72,516.23) --
-	(267.89,516.23) --
-	(267.89,514.43) --
-	(281.07,514.43) --
-	(281.07,512.53) --
-	(294.25,512.53) --
-	(294.25,510.60);
+	( 57.06,532.24) --
+	( 70.24,532.24) --
+	( 70.24,531.95) --
+	( 83.42,531.95) --
+	( 83.42,531.52) --
+	( 96.59,531.52) --
+	( 96.59,530.99) --
+	(109.77,530.99) --
+	(109.77,530.36) --
+	(122.95,530.36) --
+	(122.95,529.62) --
+	(136.12,529.62) --
+	(136.12,528.78) --
+	(149.30,528.78) --
+	(149.30,527.83) --
+	(162.48,527.83) --
+	(162.48,526.76) --
+	(175.66,526.76) --
+	(175.66,525.59) --
+	(188.83,525.59) --
+	(188.83,524.34) --
+	(202.01,524.34) --
+	(202.01,523.00) --
+	(215.19,523.00) --
+	(215.19,521.57) --
+	(228.36,521.57) --
+	(228.36,520.03) --
+	(241.54,520.03) --
+	(241.54,518.38) --
+	(254.72,518.38) --
+	(254.72,516.64) --
+	(267.89,516.64) --
+	(267.89,514.79) --
+	(281.07,514.79) --
+	(281.07,512.92) --
+	(294.25,512.92) --
+	(294.25,511.00);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 	( 57.06,532.44) --
-	( 57.06,531.49) --
-	( 70.24,531.49) --
-	( 70.24,530.36) --
-	( 83.42,530.36) --
-	( 83.42,529.08) --
-	( 96.59,529.08) --
-	( 96.59,527.72) --
-	(109.77,527.72) --
-	(109.77,526.29) --
-	(122.95,526.29) --
-	(122.95,524.82) --
-	(136.12,524.82) --
-	(136.12,523.34) --
-	(149.30,523.34) --
-	(149.30,521.83) --
-	(162.48,521.83) --
-	(162.48,520.30) --
-	(175.66,520.30) --
-	(175.66,518.75) --
-	(188.83,518.75) --
-	(188.83,517.21) --
-	(202.01,517.21) --
-	(202.01,515.66) --
-	(215.19,515.66) --
-	(215.19,514.12) --
-	(228.36,514.12) --
-	(228.36,512.61) --
-	(241.54,512.61) --
-	(241.54,511.09) --
-	(254.72,511.09) --
-	(254.72,509.58) --
-	(267.89,509.58) --
-	(267.89,508.07) --
-	(281.07,508.07) --
-	(281.07,506.59) --
-	(294.25,506.59) --
-	(294.25,505.04);
+	( 57.06,531.51) --
+	( 70.24,531.51) --
+	( 70.24,530.38) --
+	( 83.42,530.38) --
+	( 83.42,529.04) --
+	( 96.59,529.04) --
+	( 96.59,527.67) --
+	(109.77,527.67) --
+	(109.77,526.22) --
+	(122.95,526.22) --
+	(122.95,524.74) --
+	(136.12,524.74) --
+	(136.12,523.26) --
+	(149.30,523.26) --
+	(149.30,521.73) --
+	(162.48,521.73) --
+	(162.48,520.19) --
+	(175.66,520.19) --
+	(175.66,518.63) --
+	(188.83,518.63) --
+	(188.83,517.08) --
+	(202.01,517.08) --
+	(202.01,515.54) --
+	(215.19,515.54) --
+	(215.19,514.00) --
+	(228.36,514.00) --
+	(228.36,512.49) --
+	(241.54,512.49) --
+	(241.54,510.97) --
+	(254.72,510.97) --
+	(254.72,509.45) --
+	(267.89,509.45) --
+	(267.89,507.96) --
+	(281.07,507.96) --
+	(281.07,506.46) --
+	(294.25,506.46) --
+	(294.25,504.92);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,532.44) --
-	( 57.06,530.98) --
-	( 70.24,530.98) --
-	( 70.24,529.33) --
-	( 83.42,529.33) --
-	( 83.42,527.51) --
-	( 96.59,527.51) --
-	( 96.59,525.64) --
-	(109.77,525.64) --
-	(109.77,523.73) --
-	(122.95,523.73) --
-	(122.95,521.81) --
-	(136.12,521.81) --
-	(136.12,519.88) --
-	(149.30,519.88) --
-	(149.30,517.95) --
-	(162.48,517.95) --
-	(162.48,516.03) --
-	(175.66,516.03) --
-	(175.66,514.10) --
-	(188.83,514.10) --
-	(188.83,512.19) --
-	(202.01,512.19) --
-	(202.01,510.32) --
-	(215.19,510.32) --
-	(215.19,508.45) --
-	(228.36,508.45) --
-	(228.36,506.59) --
-	(241.54,506.59) --
-	(241.54,504.74) --
-	(254.72,504.74) --
-	(254.72,502.91) --
-	(267.89,502.91) --
-	(267.89,501.12) --
-	(281.07,501.12) --
-	(281.07,499.32) --
-	(294.25,499.32) --
-	(294.25,497.50);
+	( 57.06,531.12) --
+	( 70.24,531.12) --
+	( 70.24,529.67) --
+	( 83.42,529.67) --
+	( 83.42,527.97) --
+	( 96.59,527.97) --
+	( 96.59,526.22) --
+	(109.77,526.22) --
+	(109.77,524.43) --
+	(122.95,524.43) --
+	(122.95,522.60) --
+	(136.12,522.60) --
+	(136.12,520.76) --
+	(149.30,520.76) --
+	(149.30,518.89) --
+	(162.48,518.89) --
+	(162.48,517.00) --
+	(175.66,517.00) --
+	(175.66,515.09) --
+	(188.83,515.09) --
+	(188.83,513.22) --
+	(202.01,513.22) --
+	(202.01,511.38) --
+	(215.19,511.38) --
+	(215.19,509.55) --
+	(228.36,509.55) --
+	(228.36,507.70) --
+	(241.54,507.70) --
+	(241.54,505.84) --
+	(254.72,505.84) --
+	(254.72,504.00) --
+	(267.89,504.00) --
+	(267.89,502.15) --
+	(281.07,502.15) --
+	(281.07,500.38) --
+	(294.25,500.38) --
+	(294.25,498.55);
 \definecolor{drawColor}{gray}{0.20}
@@
 	(162.48,433.22) --
-	(162.48,432.34) --
-	(175.66,432.34) --
+	(162.48,432.33) --
+	(175.66,432.33) --
 	(175.66,431.35) --
@@
 	(215.19,429.17) --
-	(215.19,427.94) --
-	(228.36,427.94) --
-	(228.36,426.65) --
-	(241.54,426.65) --
-	(241.54,425.29) --
-	(254.72,425.29) --
-	(254.72,423.84) --
-	(267.89,423.84) --
-	(267.89,422.32) --
-	(281.07,422.32) --
-	(281.07,420.74) --
-	(294.25,420.74) --
-	(294.25,419.11);
+	(215.19,427.95) --
+	(228.36,427.95) --
+	(228.36,426.66) --
+	(241.54,426.66) --
+	(241.54,425.30) --
+	(254.72,425.30) --
+	(254.72,423.86) --
+	(267.89,423.86) --
+	(267.89,422.34) --
+	(281.07,422.34) --
+	(281.07,420.76) --
+	(294.25,420.76) --
+	(294.25,419.13);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,436.96) --
-	( 57.06,436.75) --
-	( 70.24,436.75) --
-	( 70.24,436.42) --
-	( 83.42,436.42) --
-	( 83.42,435.95) --
-	( 96.59,435.95) --
-	( 96.59,435.37) --
-	(109.77,435.37) --
-	(109.77,434.66) --
-	(122.95,434.66) --
-	(122.95,433.84) --
-	(136.12,433.84) --
-	(136.12,432.91) --
-	(149.30,432.91) --
-	(149.30,431.87) --
-	(162.48,431.87) --
-	(162.48,430.71) --
-	(175.66,430.71) --
-	(175.66,429.46) --
-	(188.83,429.46) --
-	(188.83,428.14) --
-	(202.01,428.14) --
-	(202.01,426.71) --
-	(215.19,426.71) --
-	(215.19,425.22) --
-	(228.36,425.22) --
-	(228.36,423.62) --
-	(241.54,423.62) --
-	(241.54,421.93) --
-	(254.72,421.93) --
-	(254.72,420.17) --
-	(267.89,420.17) --
-	(267.89,418.34) --
-	(281.07,418.34) --
-	(281.07,416.45) --
-	(294.25,416.45) --
-	(294.25,414.50);
+	( 57.06,436.79) --
+	( 70.24,436.79) --
+	( 70.24,436.50) --
+	( 83.42,436.50) --
+	( 83.42,436.07) --
+	( 96.59,436.07) --
+	( 96.59,435.53) --
+	(109.77,435.53) --
+	(109.77,434.89) --
+	(122.95,434.89) --
+	(122.95,434.16) --
+	(136.12,434.16) --
+	(136.12,433.29) --
+	(149.30,433.29) --
+	(149.30,432.32) --
+	(162.48,432.32) --
+	(162.48,431.20) --
+	(175.66,431.20) --
+	(175.66,429.97) --
+	(188.83,429.97) --
+	(188.83,428.71) --
+	(202.01,428.71) --
+	(202.01,427.33) --
+	(215.19,427.33) --
+	(215.19,425.87) --
+	(228.36,425.87) --
+	(228.36,424.24) --
+	(241.54,424.24) --
+	(241.54,422.48) --
+	(254.72,422.48) --
+	(254.72,420.67) --
+	(267.89,420.67) --
+	(267.89,418.79) --
+	(281.07,418.79) --
+	(281.07,416.82) --
+	(294.25,416.82) --
+	(294.25,414.88);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 	( 70.24,436.03) --
-	( 70.24,434.87) --
-	( 83.42,434.87) --
+	( 70.24,434.88) --
+	( 83.42,434.88) --
 	( 83.42,433.58) --
@@
 	(122.95,430.73) --
-	(122.95,429.20) --
-	(136.12,429.20) --
+	(122.95,429.19) --
+	(136.12,429.19) --
 	(136.12,427.66) --
@@
 	(162.48,426.11) --
-	(162.48,424.55) --
-	(175.66,424.55) --
+	(162.48,424.54) --
+	(175.66,424.54) --
 	(175.66,422.95) --
@@
 	(215.19,419.81) --
-	(215.19,418.23) --
-	(228.36,418.23) --
-	(228.36,416.67) --
-	(241.54,416.67) --
-	(241.54,415.13) --
-	(254.72,415.13) --
-	(254.72,413.59) --
-	(267.89,413.59) --
-	(267.89,412.05) --
-	(281.07,412.05) --
-	(281.07,410.53) --
-	(294.25,410.53) --
-	(294.25,408.97);
+	(215.19,418.25) --
+	(228.36,418.25) --
+	(228.36,416.70) --
+	(241.54,416.70) --
+	(241.54,415.15) --
+	(254.72,415.15) --
+	(254.72,413.61) --
+	(267.89,413.61) --
+	(267.89,412.08) --
+	(281.07,412.08) --
+	(281.07,410.56) --
+	(294.25,410.56) --
+	(294.25,409.00);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,436.96) --
-	( 57.06,435.55) --
-	( 70.24,435.55) --
-	( 70.24,433.88) --
-	( 83.42,433.88) --
-	( 83.42,432.04) --
-	( 96.59,432.04) --
-	( 96.59,430.10) --
-	(109.77,430.10) --
-	(109.77,428.11) --
-	(122.95,428.11) --
-	(122.95,426.11) --
-	(136.12,426.11) --
-	(136.12,424.08) --
-	(149.30,424.08) --
-	(149.30,422.06) --
-	(162.48,422.06) --
-	(162.48,420.03) --
-	(175.66,420.03) --
-	(175.66,418.03) --
-	(188.83,418.03) --
-	(188.83,416.08) --
-	(202.01,416.08) --
-	(202.01,414.13) --
-	(215.19,414.13) --
-	(215.19,412.24) --
-	(228.36,412.24) --
-	(228.36,410.33) --
-	(241.54,410.33) --
-	(241.54,408.44) --
-	(254.72,408.44) --
-	(254.72,406.60) --
-	(267.89,406.60) --
-	(267.89,404.77) --
-	(281.07,404.77) --
-	(281.07,402.99) --
-	(294.25,402.99) --
-	(294.25,401.13);
+	( 57.06,435.82) --
+	( 70.24,435.82) --
+	( 70.24,434.36) --
+	( 83.42,434.36) --
+	( 83.42,432.67) --
+	( 96.59,432.67) --
+	( 96.59,430.87) --
+	(109.77,430.87) --
+	(109.77,429.08) --
+	(122.95,429.08) --
+	(122.95,427.28) --
+	(136.12,427.28) --
+	(136.12,425.38) --
+	(149.30,425.38) --
+	(149.30,423.49) --
+	(162.48,423.49) --
+	(162.48,421.50) --
+	(175.66,421.50) --
+	(175.66,419.53) --
+	(188.83,419.53) --
+	(188.83,417.65) --
+	(202.01,417.65) --
+	(202.01,415.76) --
+	(215.19,415.76) --
+	(215.19,413.91) --
+	(228.36,413.91) --
+	(228.36,411.95) --
+	(241.54,411.95) --
+	(241.54,409.99) --
+	(254.72,409.99) --
+	(254.72,408.06) --
+	(267.89,408.06) --
+	(267.89,406.19) --
+	(281.07,406.19) --
+	(281.07,404.32) --
+	(294.25,404.32) --
+	(294.25,402.48);
 \definecolor{drawColor}{gray}{0.20}
@@
 	( 83.42,341.12) --
-	( 83.42,340.81) --
-	( 96.59,340.81) --
-	( 96.59,340.40) --
-	(109.77,340.40) --
-	(109.77,339.90) --
-	(122.95,339.90) --
-	(122.95,339.31) --
-	(136.12,339.31) --
-	(136.12,338.63) --
-	(149.30,338.63) --
-	(149.30,337.87) --
-	(162.48,337.87) --
-	(162.48,337.01) --
-	(175.66,337.01) --
-	(175.66,336.06) --
-	(188.83,336.06) --
-	(188.83,335.04) --
-	(202.01,335.04) --
-	(202.01,333.93) --
-	(215.19,333.93) --
-	(215.19,332.74) --
-	(228.36,332.74) --
-	(228.36,331.49) --
-	(241.54,331.49) --
-	(241.54,330.15) --
-	(254.72,330.15) --
-	(254.72,328.74) --
-	(267.89,328.74) --
-	(267.89,327.25) --
-	(281.07,327.25) --
-	(281.07,325.71) --
-	(294.25,325.71) --
-	(294.25,324.10);
+	( 83.42,340.80) --
+	( 96.59,340.80) --
+	( 96.59,340.38) --
+	(109.77,340.38) --
+	(109.77,339.87) --
+	(122.95,339.87) --
+	(122.95,339.28) --
+	(136.12,339.28) --
+	(136.12,338.61) --
+	(149.30,338.61) --
+	(149.30,337.84) --
+	(162.48,337.84) --
+	(162.48,336.98) --
+	(175.66,336.98) --
+	(175.66,336.03) --
+	(188.83,336.03) --
+	(188.83,335.00) --
+	(202.01,335.00) --
+	(202.01,333.89) --
+	(215.19,333.89) --
+	(215.19,332.70) --
+	(228.36,332.70) --
+	(228.36,331.45) --
+	(241.54,331.45) --
+	(241.54,330.12) --
+	(254.72,330.12) --
+	(254.72,328.70) --
+	(267.89,328.70) --
+	(267.89,327.22) --
+	(281.07,327.22) --
+	(281.07,325.67) --
+	(294.25,325.67) --
+	(294.25,324.06);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,341.49) --
-	( 57.06,341.27) --
-	( 70.24,341.27) --
-	( 70.24,340.93) --
-	( 83.42,340.93) --
-	( 83.42,340.46) --
-	( 96.59,340.46) --
-	( 96.59,339.87) --
-	(109.77,339.87) --
-	(109.77,339.17) --
-	(122.95,339.17) --
-	(122.95,338.37) --
-	(136.12,338.37) --
-	(136.12,337.47) --
-	(149.30,337.47) --
-	(149.30,336.45) --
-	(162.48,336.45) --
-	(162.48,335.35) --
-	(175.66,335.35) --
-	(175.66,334.13) --
-	(188.83,334.13) --
-	(188.83,332.82) --
-	(202.01,332.82) --
-	(202.01,331.40) --
-	(215.19,331.40) --
-	(215.19,329.89) --
-	(228.36,329.89) --
-	(228.36,328.30) --
-	(241.54,328.30) --
-	(241.54,326.62) --
-	(254.72,326.62) --
-	(254.72,324.85) --
-	(267.89,324.85) --
-	(267.89,323.00) --
-	(281.07,323.00) --
-	(281.07,321.08) --
-	(294.25,321.08) --
-	(294.25,319.07);
+	( 57.06,341.30) --
+	( 70.24,341.30) --
+	( 70.24,341.00) --
+	( 83.42,341.00) --
+	( 83.42,340.57) --
+	( 96.59,340.57) --
+	( 96.59,340.03) --
+	(109.77,340.03) --
+	(109.77,339.38) --
+	(122.95,339.38) --
+	(122.95,338.61) --
+	(136.12,338.61) --
+	(136.12,337.76) --
+	(149.30,337.76) --
+	(149.30,336.78) --
+	(162.48,336.78) --
+	(162.48,335.71) --
+	(175.66,335.71) --
+	(175.66,334.51) --
+	(188.83,334.51) --
+	(188.83,333.23) --
+	(202.01,333.23) --
+	(202.01,331.82) --
+	(215.19,331.82) --
+	(215.19,330.32) --
+	(228.36,330.32) --
+	(228.36,328.73) --
+	(241.54,328.73) --
+	(241.54,327.07) --
+	(254.72,327.07) --
+	(254.72,325.34) --
+	(267.89,325.34) --
+	(267.89,323.47) --
+	(281.07,323.47) --
+	(281.07,321.56) --
+	(294.25,321.56) --
+	(294.25,319.55);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 	( 70.24,340.55) --
-	( 70.24,339.41) --
-	( 83.42,339.41) --
-	( 83.42,338.15) --
-	( 96.59,338.15) --
-	( 96.59,336.79) --
-	(109.77,336.79) --
-	(109.77,335.37) --
-	(122.95,335.37) --
-	(122.95,333.90) --
-	(136.12,333.90) --
-	(136.12,332.42) --
-	(149.30,332.42) --
-	(149.30,330.91) --
-	(162.48,330.91) --
-	(162.48,329.38) --
-	(175.66,329.38) --
-	(175.66,327.83) --
-	(188.83,327.83) --
-	(188.83,326.29) --
-	(202.01,326.29) --
-	(202.01,324.76) --
-	(215.19,324.76) --
-	(215.19,323.21) --
-	(228.36,323.21) --
-	(228.36,321.70) --
-	(241.54,321.70) --
-	(241.54,320.17) --
-	(254.72,320.17) --
-	(254.72,318.66) --
-	(267.89,318.66) --
-	(267.89,317.16) --
-	(281.07,317.16) --
-	(281.07,315.68) --
-	(294.25,315.68) --
-	(294.25,314.13);
+	( 70.24,339.42) --
+	( 83.42,339.42) --
+	( 83.42,338.11) --
+	( 96.59,338.11) --
+	( 96.59,336.75) --
+	(109.77,336.75) --
+	(109.77,335.30) --
+	(122.95,335.30) --
+	(122.95,333.82) --
+	(136.12,333.82) --
+	(136.12,332.35) --
+	(149.30,332.35) --
+	(149.30,330.83) --
+	(162.48,330.83) --
+	(162.48,329.30) --
+	(175.66,329.30) --
+	(175.66,327.75) --
+	(188.83,327.75) --
+	(188.83,326.20) --
+	(202.01,326.20) --
+	(202.01,324.66) --
+	(215.19,324.66) --
+	(215.19,323.12) --
+	(228.36,323.12) --
+	(228.36,321.61) --
+	(241.54,321.61) --
+	(241.54,320.09) --
+	(254.72,320.09) --
+	(254.72,318.58) --
+	(267.89,318.58) --
+	(267.89,317.08) --
+	(281.07,317.08) --
+	(281.07,315.59) --
+	(294.25,315.59) --
+	(294.25,314.04);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,341.49) --
-	( 57.06,340.03) --
-	( 70.24,340.03) --
-	( 70.24,338.32) --
-	( 83.42,338.32) --
-	( 83.42,336.45) --
-	( 96.59,336.45) --
-	( 96.59,334.51) --
-	(109.77,334.51) --
-	(109.77,332.52) --
-	(122.95,332.52) --
-	(122.95,330.54) --
-	(136.12,330.54) --
-	(136.12,328.59) --
-	(149.30,328.59) --
-	(149.30,326.59) --
-	(162.48,326.59) --
-	(162.48,324.64) --
-	(175.66,324.64) --
-	(175.66,322.66) --
-	(188.83,322.66) --
-	(188.83,320.72) --
-	(202.01,320.72) --
-	(202.01,318.76) --
-	(215.19,318.76) --
-	(215.19,316.84) --
-	(228.36,316.84) --
-	(228.36,314.94) --
-	(241.54,314.94) --
-	(241.54,313.05) --
-	(254.72,313.05) --
-	(254.72,311.18) --
-	(267.89,311.18) --
-	(267.89,309.34) --
-	(281.07,309.34) --
-	(281.07,307.52) --
-	(294.25,307.52) --
-	(294.25,305.63);
+	( 57.06,340.23) --
+	( 70.24,340.23) --
+	( 70.24,338.73) --
+	( 83.42,338.73) --
+	( 83.42,337.01) --
+	( 96.59,337.01) --
+	( 96.59,335.22) --
+	(109.77,335.22) --
+	(109.77,333.37) --
+	(122.95,333.37) --
+	(122.95,331.48) --
+	(136.12,331.48) --
+	(136.12,329.61) --
+	(149.30,329.61) --
+	(149.30,327.68) --
+	(162.48,327.68) --
+	(162.48,325.78) --
+	(175.66,325.78) --
+	(175.66,323.83) --
+	(188.83,323.83) --
+	(188.83,321.93) --
+	(202.01,321.93) --
+	(202.01,319.98) --
+	(215.19,319.98) --
+	(215.19,318.06) --
+	(228.36,318.06) --
+	(228.36,316.16) --
+	(241.54,316.16) --
+	(241.54,314.28) --
+	(254.72,314.28) --
+	(254.72,312.45) --
+	(267.89,312.45) --
+	(267.89,310.59) --
+	(281.07,310.59) --
+	(281.07,308.77) --
+	(294.25,308.77) --
+	(294.25,306.87);
 \definecolor{drawColor}{gray}{0.20}
@@
 	( 70.24,245.72) --
-	( 70.24,245.20) --
-	( 83.42,245.20) --
-	( 83.42,244.44) --
-	( 96.59,244.44) --
-	( 96.59,243.50) --
-	(109.77,243.50) --
-	(109.77,242.30) --
-	(122.95,242.30) --
-	(122.95,240.95) --
-	(136.12,240.95) --
-	(136.12,239.38) --
-	(149.30,239.38) --
-	(149.30,237.62) --
-	(162.48,237.62) --
-	(162.48,235.68) --
-	(175.66,235.68) --
-	(175.66,233.51) --
-	(188.83,233.51) --
-	(188.83,231.15) --
-	(202.01,231.15) --
-	(202.01,228.63) --
-	(215.19,228.63) --
-	(215.19,225.94) --
-	(228.36,225.94) --
-	(228.36,223.15) --
-	(241.54,223.15) --
-	(241.54,220.21) --
-	(254.72,220.21) --
-	(254.72,217.04) --
-	(267.89,217.04) --
-	(267.89,213.83) --
-	(281.07,213.83) --
-	(281.07,210.42) --
-	(294.25,210.42) --
-	(294.25,206.83);
+	( 70.24,245.22) --
+	( 83.42,245.22) --
+	( 83.42,244.49) --
+	( 96.59,244.49) --
+	( 96.59,243.55) --
+	(109.77,243.55) --
+	(109.77,242.36) --
+	(122.95,242.36) --
+	(122.95,240.98) --
+	(136.12,240.98) --
+	(136.12,239.40) --
+	(149.30,239.40) --
+	(149.30,237.63) --
+	(162.48,237.63) --
+	(162.48,235.66) --
+	(175.66,235.66) --
+	(175.66,233.45) --
+	(188.83,233.45) --
+	(188.83,231.09) --
+	(202.01,231.09) --
+	(202.01,228.56) --
+	(215.19,228.56) --
+	(215.19,225.87) --
+	(228.36,225.87) --
+	(228.36,223.01) --
+	(241.54,223.01) --
+	(241.54,219.97) --
+	(254.72,219.97) --
+	(254.72,216.86) --
+	(267.89,216.86) --
+	(267.89,213.57) --
+	(281.07,213.57) --
+	(281.07,210.22) --
+	(294.25,210.22) --
+	(294.25,206.69);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,246.02) --
-	( 57.06,245.60) --
-	( 70.24,245.60) --
+	( 57.06,245.59) --
+	( 70.24,245.59) --
 	( 70.24,244.91) --
 	( 83.42,244.91) --
-	( 83.42,243.96) --
-	( 96.59,243.96) --
-	( 96.59,242.75) --
-	(109.77,242.75) --
-	(109.77,241.30) --
-	(122.95,241.30) --
-	(122.95,239.59) --
-	(136.12,239.59) --
-	(136.12,237.68) --
-	(149.30,237.68) --
-	(149.30,235.54) --
-	(162.48,235.54) --
-	(162.48,233.19) --
-	(175.66,233.19) --
-	(175.66,230.59) --
-	(188.83,230.59) --
-	(188.83,227.77) --
-	(202.01,227.77) --
-	(202.01,224.78) --
-	(215.19,224.78) --
-	(215.19,221.62) --
-	(228.36,221.62) --
-	(228.36,218.26) --
-	(241.54,218.26) --
-	(241.54,214.74) --
-	(254.72,214.74) --
-	(254.72,211.07) --
-	(267.89,211.07) --
-	(267.89,207.27) --
-	(281.07,207.27) --
-	(281.07,203.34) --
-	(294.25,203.34) --
-	(294.25,199.32);
+	( 83.42,243.97) --
+	( 96.59,243.97) --
+	( 96.59,242.78) --
+	(109.77,242.78) --
+	(109.77,241.36) --
+	(122.95,241.36) --
+	(122.95,239.66) --
+	(136.12,239.66) --
+	(136.12,237.77) --
+	(149.30,237.77) --
+	(149.30,235.63) --
+	(162.48,235.63) --
+	(162.48,233.29) --
+	(175.66,233.29) --
+	(175.66,230.69) --
+	(188.83,230.69) --
+	(188.83,227.85) --
+	(202.01,227.85) --
+	(202.01,224.84) --
+	(215.19,224.84) --
+	(215.19,221.67) --
+	(228.36,221.67) --
+	(228.36,218.22) --
+	(241.54,218.22) --
+	(241.54,214.58) --
+	(254.72,214.58) --
+	(254.72,210.76) --
+	(267.89,210.76) --
+	(267.89,206.94) --
+	(281.07,206.94) --
+	(281.07,202.93) --
+	(294.25,202.93) --
+	(294.25,199.00);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 	( 57.06,246.02) --
-	( 57.06,244.02) --
-	( 70.24,244.02) --
-	( 70.24,241.42) --
-	( 83.42,241.42) --
-	( 83.42,238.39) --
-	( 96.59,238.39) --
-	( 96.59,235.27) --
-	(109.77,235.27) --
-	(109.77,231.91) --
-	(122.95,231.91) --
-	(122.95,228.58) --
-	(136.12,228.58) --
-	(136.12,225.17) --
-	(149.30,225.17) --
-	(149.30,221.77) --
-	(162.48,221.77) --
-	(162.48,218.37) --
-	(175.66,218.37) --
-	(175.66,214.93) --
-	(188.83,214.93) --
-	(188.83,211.48) --
-	(202.01,211.48) --
-	(202.01,208.09) --
-	(215.19,208.09) --
-	(215.19,204.75) --
-	(228.36,204.75) --
-	(228.36,201.51) --
-	(241.54,201.51) --
-	(241.54,198.32) --
-	(254.72,198.32) --
-	(254.72,195.10) --
-	(267.89,195.10) --
-	(267.89,192.02) --
-	(281.07,192.02) --
-	(281.07,188.93) --
-	(294.25,188.93) --
-	(294.25,185.68);
+	( 57.06,244.05) --
+	( 70.24,244.05) --
+	( 70.24,241.55) --
+	( 83.42,241.55) --
+	( 83.42,238.62) --
+	( 96.59,238.62) --
+	( 96.59,235.52) --
+	(109.77,235.52) --
+	(109.77,232.18) --
+	(122.95,232.18) --
+	(122.95,228.78) --
+	(136.12,228.78) --
+	(136.12,225.36) --
+	(149.30,225.36) --
+	(149.30,221.94) --
+	(162.48,221.94) --
+	(162.48,218.49) --
+	(175.66,218.49) --
+	(175.66,214.98) --
+	(188.83,214.98) --
+	(188.83,211.54) --
+	(202.01,211.54) --
+	(202.01,208.13) --
+	(215.19,208.13) --
+	(215.19,204.78) --
+	(228.36,204.78) --
+	(228.36,201.47) --
+	(241.54,201.47) --
+	(241.54,198.16) --
+	(254.72,198.16) --
+	(254.72,194.99) --
+	(267.89,194.99) --
+	(267.89,191.84) --
+	(281.07,191.84) --
+	(281.07,188.80) --
+	(294.25,188.80) --
+	(294.25,185.60);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,246.02) --
-	( 57.06,243.21) --
-	( 70.24,243.21) --
-	( 70.24,239.79) --
-	( 83.42,239.79) --
-	( 83.42,236.00) --
-	( 96.59,236.00) --
-	( 96.59,232.02) --
-	(109.77,232.02) --
-	(109.77,227.97) --
-	(122.95,227.97) --
-	(122.95,223.83) --
-	(136.12,223.83) --
-	(136.12,219.72) --
-	(149.30,219.72) --
-	(149.30,215.62) --
-	(162.48,215.62) --
-	(162.48,211.58) --
-	(175.66,211.58) --
-	(175.66,207.50) --
-	(188.83,207.50) --
-	(188.83,203.47) --
-	(202.01,203.47) --
-	(202.01,199.53) --
-	(215.19,199.53) --
-	(215.19,195.67) --
-	(228.36,195.67) --
-	(228.36,191.86) --
-	(241.54,191.86) --
-	(241.54,188.13) --
-	(254.72,188.13) --
-	(254.72,184.48) --
-	(267.89,184.48) --
-	(267.89,180.92) --
-	(281.07,180.92) --
-	(281.07,177.44) --
-	(294.25,177.44) --
-	(294.25,173.89);
+	( 57.06,243.15) --
+	( 70.24,243.15) --
+	( 70.24,239.77) --
+	( 83.42,239.77) --
+	( 83.42,236.02) --
+	( 96.59,236.02) --
+	( 96.59,232.11) --
+	(109.77,232.11) --
+	(109.77,228.13) --
+	(122.95,228.13) --
+	(122.95,224.01) --
+	(136.12,224.01) --
+	(136.12,219.94) --
+	(149.30,219.94) --
+	(149.30,215.85) --
+	(162.48,215.85) --
+	(162.48,211.80) --
+	(175.66,211.80) --
+	(175.66,207.73) --
+	(188.83,207.73) --
+	(188.83,203.66) --
+	(202.01,203.66) --
+	(202.01,199.70) --
+	(215.19,199.70) --
+	(215.19,195.82) --
+	(228.36,195.82) --
+	(228.36,191.90) --
+	(241.54,191.90) --
+	(241.54,188.04) --
+	(254.72,188.04) --
+	(254.72,184.24) --
+	(267.89,184.24) --
+	(267.89,180.67) --
+	(281.07,180.67) --
+	(281.07,177.12) --
+	(294.25,177.12) --
+	(294.25,173.64);
 \definecolor{drawColor}{gray}{0.20}
@@
 	( 83.42,149.60) --
-	( 83.42,148.80) --
-	( 96.59,148.80) --
+	( 83.42,148.79) --
+	( 96.59,148.79) --
 	( 96.59,147.79) --
@@
 	(136.12,145.20) --
-	(136.12,143.60) --
-	(149.30,143.60) --
+	(136.12,143.61) --
+	(149.30,143.61) --
 	(149.30,141.83) --
 	(162.48,141.83) --
-	(162.48,139.87) --
-	(175.66,139.87) --
+	(162.48,139.86) --
+	(175.66,139.86) --
 	(175.66,137.70) --
 	(188.83,137.70) --
-	(188.83,135.38) --
-	(202.01,135.38) --
-	(202.01,132.85) --
-	(215.19,132.85) --
-	(215.19,130.17) --
-	(228.36,130.17) --
-	(228.36,127.33) --
-	(241.54,127.33) --
-	(241.54,124.36) --
-	(254.72,124.36) --
-	(254.72,121.23) --
-	(267.89,121.23) --
-	(267.89,117.97) --
-	(281.07,117.97) --
-	(281.07,114.60) --
-	(294.25,114.60) --
-	(294.25,111.13);
+	(188.83,135.37) --
+	(202.01,135.37) --
+	(202.01,132.84) --
+	(215.19,132.84) --
+	(215.19,130.16) --
+	(228.36,130.16) --
+	(228.36,127.31) --
+	(241.54,127.31) --
+	(241.54,124.33) --
+	(254.72,124.33) --
+	(254.72,121.21) --
+	(267.89,121.21) --
+	(267.89,117.94) --
+	(281.07,117.94) --
+	(281.07,114.58) --
+	(294.25,114.58) --
+	(294.25,111.11);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,150.55) --
-	( 57.06,149.98) --
-	( 70.24,149.98) --
-	( 70.24,149.15) --
-	( 83.42,149.15) --
-	( 83.42,148.07) --
-	( 96.59,148.07) --
-	( 96.59,146.72) --
-	(109.77,146.72) --
-	(109.77,145.12) --
-	(122.95,145.12) --
-	(122.95,143.34) --
-	(136.12,143.34) --
-	(136.12,141.33) --
-	(149.30,141.33) --
-	(149.30,139.13) --
-	(162.48,139.13) --
-	(162.48,136.72) --
-	(175.66,136.72) --
-	(175.66,134.08) --
-	(188.83,134.08) --
-	(188.83,131.21) --
-	(202.01,131.21) --
-	(202.01,128.21) --
-	(215.19,128.21) --
-	(215.19,124.95) --
-	(228.36,124.95) --
-	(228.36,121.55) --
-	(241.54,121.55) --
-	(241.54,118.03) --
-	(254.72,118.03) --
-	(254.72,114.36) --
-	(267.89,114.36) --
-	(267.89,110.52) --
-	(281.07,110.52) --
-	(281.07,106.54) --
-	(294.25,106.54) --
-	(294.25,102.60);
+	( 57.06,150.07) --
+	( 70.24,150.07) --
+	( 70.24,149.32) --
+	( 83.42,149.32) --
+	( 83.42,148.30) --
+	( 96.59,148.30) --
+	( 96.59,147.04) --
+	(109.77,147.04) --
+	(109.77,145.50) --
+	(122.95,145.50) --
+	(122.95,143.83) --
+	(136.12,143.83) --
+	(136.12,141.94) --
+	(149.30,141.94) --
+	(149.30,139.74) --
+	(162.48,139.74) --
+	(162.48,137.40) --
+	(175.66,137.40) --
+	(175.66,134.81) --
+	(188.83,134.81) --
+	(188.83,132.03) --
+	(202.01,132.03) --
+	(202.01,129.02) --
+	(215.19,129.02) --
+	(215.19,125.87) --
+	(228.36,125.87) --
+	(228.36,122.58) --
+	(241.54,122.58) --
+	(241.54,119.15) --
+	(254.72,119.15) --
+	(254.72,115.52) --
+	(267.89,115.52) --
+	(267.89,111.71) --
+	(281.07,111.71) --
+	(281.07,107.78) --
+	(294.25,107.78) --
+	(294.25,103.68);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 	( 57.06,150.55) --
-	( 57.06,148.10) --
-	( 70.24,148.10) --
-	( 70.24,145.20) --
-	( 83.42,145.20) --
-	( 83.42,142.03) --
-	( 96.59,142.03) --
-	( 96.59,138.69) --
-	(109.77,138.69) --
-	(109.77,135.34) --
-	(122.95,135.34) --
-	(122.95,131.92) --
-	(136.12,131.92) --
+	( 57.06,148.08) --
+	( 70.24,148.08) --
+	( 70.24,145.17) --
+	( 83.42,145.17) --
+	( 83.42,141.98) --
+	( 96.59,141.98) --
+	( 96.59,138.67) --
+	(109.77,138.67) --
+	(109.77,135.32) --
+	(122.95,135.32) --
+	(122.95,131.90) --
+	(136.12,131.90) --
 	(136.12,128.47) --
 	(149.30,128.47) --
-	(149.30,125.06) --
-	(162.48,125.06) --
-	(162.48,121.64) --
-	(175.66,121.64) --
-	(175.66,118.21) --
-	(188.83,118.21) --
-	(188.83,114.83) --
-	(202.01,114.83) --
-	(202.01,111.45) --
-	(215.19,111.45) --
-	(215.19,108.12) --
-	(228.36,108.12) --
-	(228.36,104.84) --
-	(241.54,104.84) --
-	(241.54,101.63) --
-	(254.72,101.63) --
-	(254.72, 98.46) --
-	(267.89, 98.46) --
-	(267.89, 95.35) --
-	(281.07, 95.35) --
-	(281.07, 92.30) --
-	(294.25, 92.30) --
-	(294.25, 89.17);
+	(149.30,125.04) --
+	(162.48,125.04) --
+	(162.48,121.61) --
+	(175.66,121.61) --
+	(175.66,118.18) --
+	(188.83,118.18) --
+	(188.83,114.80) --
+	(202.01,114.80) --
+	(202.01,111.42) --
+	(215.19,111.42) --
+	(215.19,108.10) --
+	(228.36,108.10) --
+	(228.36,104.80) --
+	(241.54,104.80) --
+	(241.54,101.58) --
+	(254.72,101.58) --
+	(254.72, 98.42) --
+	(267.89, 98.42) --
+	(267.89, 95.30) --
+	(281.07, 95.30) --
+	(281.07, 92.26) --
+	(294.25, 92.26) --
+	(294.25, 89.13);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 57.06,150.55) --
-	( 57.06,146.77) --
-	( 70.24,146.77) --
-	( 70.24,142.62) --
-	( 83.42,142.62) --
-	( 83.42,138.34) --
-	( 96.59,138.34) --
-	( 96.59,133.93) --
-	(109.77,133.93) --
-	(109.77,129.46) --
-	(122.95,129.46) --
-	(122.95,125.14) --
-	(136.12,125.14) --
-	(136.12,120.87) --
-	(149.30,120.87) --
-	(149.30,116.70) --
-	(162.48,116.70) --
-	(162.48,112.57) --
-	(175.66,112.57) --
-	(175.66,108.48) --
-	(188.83,108.48) --
-	(188.83,104.39) --
-	(202.01,104.39) --
-	(202.01,100.49) --
-	(215.19,100.49) --
-	(215.19, 96.56) --
-	(228.36, 96.56) --
-	(228.36, 92.75) --
-	(241.54, 92.75) --
-	(241.54, 89.06) --
-	(254.72, 89.06) --
-	(254.72, 85.46) --
-	(267.89, 85.46) --
-	(267.89, 81.90) --
-	(281.07, 81.90) --
-	(281.07, 78.43) --
-	(294.25, 78.43) --
-	(294.25, 74.99);
+	( 57.06,147.32) --
+	( 70.24,147.32) --
+	( 70.24,143.59) --
+	( 83.42,143.59) --
+	( 83.42,139.53) --
+	( 96.59,139.53) --
+	( 96.59,135.42) --
+	(109.77,135.42) --
+	(109.77,131.09) --
+	(122.95,131.09) --
+	(122.95,127.04) --
+	(136.12,127.04) --
+	(136.12,122.99) --
+	(149.30,122.99) --
+	(149.30,118.80) --
+	(162.48,118.80) --
+	(162.48,114.77) --
+	(175.66,114.77) --
+	(175.66,110.73) --
+	(188.83,110.73) --
+	(188.83,106.75) --
+	(202.01,106.75) --
+	(202.01,102.80) --
+	(215.19,102.80) --
+	(215.19, 98.97) --
+	(228.36, 98.97) --
+	(228.36, 95.25) --
+	(241.54, 95.25) --
+	(241.54, 91.63) --
+	(254.72, 91.63) --
+	(254.72, 88.04) --
+	(267.89, 88.04) --
+	(267.89, 84.49) --
+	(281.07, 84.49) --
+	(281.07, 81.02) --
+	(294.25, 81.02) --
+	(294.25, 77.41);
 \definecolor{drawColor}{gray}{0.20}

### 2021-12-11 scripts/02-analysis.R

@@ -20,7 +20,7 @@ library(stremr)
 get_estimates <- function(
 	scenario = 1,
 	a = 0,
-	g_a = "A ~ W + barA",
+	g_a = "A ~ W + shiftA",
 	g_d = "D ~ W + barA",
 	stratify = list(D = paste0("t == ", 1:20),
 									A = paste0("t == ", 1:20))
@@ -28,7 +28,10 @@ get_estimates <- function(
 	
 	# message("Simulating...")
 	sim.dt <- sim_data(scenario, a = a)
-	sim.dt[,`:=`(barA = shift(as.integer(cumsum(A) > 0), 1, 0)), id]
+	sim.dt[,`:=`(
+		shiftA = shift(A, 1, 0),
+		barA = shift(as.integer(cumsum(A) > 0), 1, 0)
+		), id]
 	
 	# Get rules
 	sim.dt[,`:=`(A_0 = 0, A_1 = N)]

### 2021-12-11 scripts/04-application.R

@@ -82,9 +82,9 @@ cohort_analytic[,`:=`(
 ), studyno]
 # Get exposure history
 cohort_analytic[,`:=`(
-	barStraight = shift(as.integer(cumsum(straight) > 0), 16, 0),
-	barSoluble = shift(as.integer(cumsum(Soluble) > 0), 16, 0),
-	barSynthetic = shift(as.integer(cumsum(Synthetic) > 0), 16, 0),
+	barStraight = shift(Straight, 16, 0),
+	barSoluble = shift(Soluble, 16, 0),
+	barSynthetic = shift(Synthetic, 16, 0),
 	N = shift(N, 15, 0)
 ), studyno]
 

### 2021-12-12 paper.tex
Draft ready

@@
 non-parametric structural causal approach of Pearl (1995), and applies
-the WKM and AWKM estimators to the estimation of colon cancer survival
-under exposure/censoring rules in the UAW-GM Cohort.
+the WKM and AWKM estimators to the estimation of digestive-system
+cancer-free survival under exposure/censoring rules in the UAW-GM
+Cohort. The \texttt{stremr} package was used to estimate the WKM and
+AWKM survival curves in both the simulation and the applied analyses
+(Sofrygin, van der Laan, and Neugebauer 2021).
 
@@
 appeared to be larger in earlier follow-up and smaller for later
-follow-up time points. The bias of both the the WKM and the AWKM
-estimators appeared largest in Scenario 5.
+follow-up time points. The bias of the WKM estimator appeared largest in
+Scenario 5. The bias of the AWKM estimator was similar across the five
+scenarios
 
@@
 survival, resulting in bias away from the null. In every scenario, the
-bias of the WKM-derived contrast was several times larger in magnitude
-than that of the AWKM-derived contrast. The bias of both estimators was
-greatest for Scenario 5.
+bias of the WKM-derived contrast was two to several times larger in
+magnitude than that of the AWKM-derived contrast.
 
@@
 later follow-up time points. Next, we estimated cancer-free survival in
-a real-world context. Using data from the UAW-GM Cohort study, we
-followed \(38\,553\) individuals starting from hire to 40 years after
-hire for incidence of colon cancer. This duration of follow-up spans the
-vast majority of individuals' working lifetimes. As in the simulation,
-the UAW-GM data were longitudinal data with baseline covariates,
-time-varying covariates, and a survival outcome.
+a real-world context. Using data from two plants participating in the
+UAW-GM Cohort study, we followed \(38\,553\) individuals starting from
+hire to 40 years after hire for incidence of digestive system cancers
+(colon, rectal, esophageal, or stomach). This duration of follow-up
+spans the vast majority of individuals' working lifetimes. As in the
+simulation, the UAW-GM data were longitudinal data with baseline
+covariates, time-varying covariates, and a survival outcome.
 
@@
 
-The outcome of interest was colon cancer incidence. There is little past
-research linking colon cancer to MWF exposures, but there is some
-evidence suggesting that straight MWFs cause colon cancer (Izano et al.
-2019). We obtained cancer incidence data via linkage to the Michigan
-Cancer Registry, which recorded cancer incidence cases starting on
-January 1, 1985. The cohort is comprised of individuals hired between
-1938 and 1985. Cancer-free survival to the start of the registry was a
-left-filtering process possibly in the presence of the HWSE as
-investigated in the simulations. Over the 40 year follow-up period,
-vital status was obtained through the Social Security Administration,
-the National Death Index, as well as records provided by the UAW.
-Baseline confounders included race, sex, plant, and year of hire.
-Time-varying confounders included age, cumulative time off, and exposure
-to the metalworking fluids not under study. These terms were included in
-the estimation of both the treatment and censoring mechanisms, which
-were estimated with stratification on every year of follow-up. The
-exposure rules of interest were identical to those in the simulation
-study: \(a_0\) never exposed and \(a_1\) always exposed while at work.
-We assumed that the effect of exposure on health status, mortality,
-cancer incidence, etc occurs after a lag of 15 years. Similarly, we
-assumed that the effects of cumulative time off occur after a 15 year
-lag. Counterfactual survival under rules \(a_0\) and \(a_1\) were
-estimated using the WKM and AWKM estimators. Summary statistics for the
-full study population and the colon cancer cases are presented in Table
+The outcome of interest was digestive system cancer incidence. There is
+little past research linking digestive system cancers to MWF exposures,
+but there is some evidence suggesting that straight MWFs cause digestive
+system cancers (Izano et al. 2019). Cancer incidence was obtained by
+linkage to Surveillance, Epidemiology, and End Results (SEER), which
+recorded cancer incidence cases starting on January 1, 1973. The cohort
+is comprised of individuals hired between 1938 and 1975. Cancer-free
+survival to the start of the registry was a left-filtering process
+possibly in the presence of the HWSE as investigated in the simulations.
+Over the 40 year follow-up period, vital status was obtained through the
+Social Security Administration, the National Death Index, as well as
+records provided by the UAW. The exposure rules of interest in the
+applied analysis were different than those in the simulation study:
+\(a_0\) being exposed with 75\% chance in the years exposure was
+observed and \(a_1\) being exposed in the years exposure was observed.
+Weights were truncated at 1000. Binary exposure is defined to be
+exposure above the median level of exposure to straight, soluble, and
+synthetic MWFs or not. Counterfactual survival under rules \(a_0\) and
+\(a_1\) were estimated using the WKM and AWKM estimators. Baseline
+confounders included race, sex, plant, and year of hire. Time-varying
+confounders included age, cumulative time off, employment status, and
+exposure to the metalworking fluids exposure from the past year. These
+terms were included in the estimation of both the treatment and
+censoring mechanisms, which were estimated with stratification on every
+two years of follow-up. Summary statistics for the full study population
+and the digestive system cancer cases are presented in Table
 \ref{tab:popchar}.
@@
 \toprule
-&       \multicolumn{2}{c}{Full cohort}       & \multicolumn{2}{c}{Colon cancer cases}      \\
+&       \multicolumn{2}{c}{Full cohort}       & \multicolumn{2}{c}{Digestive cancer cases}      \\
 \midrule
 $n$ (person-years) 
-            &     38 553 & (1 402 372)       & 267 & (9 635)        \\
+                       &     26 182 & (695 475) & 213 & (6000) \\ 
 Race (\%) \\
-\hspace{1.5em} Black   &      7 133 & (18.5)                &  83 & (31.1)          \\
-\hspace{1.5em} White   &     31 420 & (81.5)                & 184 & (68.9)          \\
+\hspace{1.5em} Black   &      6 017 & (23.0)  &  66 & (31.0)  \\ 
+\hspace{1.5em} White   &     20 165 & (77.0)  & 147 & (69.0)  \\ 
 Sex (\%) \\
-\hspace{1.5em} Female  &      4 757 & (12.3)                &  49 & (18.4)      \\
-\hspace{1.5em} Male    &     33 796 & (87.7)                & 218 & (81.6)      \\
+\hspace{1.5em} Female  &      3 328 & (12.7)  &  15 & (7.0)  \\ 
+\hspace{1.5em} Male    &     22 854 & (87.3)  & 198 & (93.0)  \\ 
 Plant (\%) \\
-\hspace{1.5em} Plant 1 &      9 092 & (23.6)                &  66 & (24.7)      \\
-\hspace{1.5em} Plant 2 &     17 090 & (44.3)                & 107 & (40.1)      \\
-\hspace{1.5em} Plant 3 &     12 371 & (32.1)                &  94 & (35.2)          \\
+\hspace{1.5em} Plant 1 &      9 092 & (34.7)  & 103 & (48.4)  \\ 
+\hspace{1.5em} Plant 2 &     17 090 & (65.3)  & 110 & (51.6)  \\ 
 \midrule
 Ever exposed to MWF (\%)
-                        &     22193 & (57.6)                & 104 & (39.0)          \\
+                                            &      13 240 & (50.6)  &  95 & (44.6)  \\ 
 Year of hire (mean (\textsc{sd}))
-                        &     1963 & (11.62)            & 1968 & (8.79)         \\
-Age (mean (\textsc{sd}))
-                        &     63.38 & (9.08)                & 67.78 & (9.27)        \\
-Cumulative time off (mean (\textsc{sd}))
-                        &     0.04 & (0.14)               & 0.05 & (0.15)       \\
+                                            &            1963 & (12.26) & 1960 & (9.55) \\ 
+Age at end of follow-up (mean (\textsc{sd}))
+                                            &         55.09 & (12.02) & 63.58 & (9.40) \\ 
+Cumulative years off (mean (\textsc{sd}))
+                                            &          0.06 & (0.15)  & 0.12 & (0.24)   \\
 \bottomrule
@@
 Since we are working with observational data, the evaluation of the
-no-interference, causal consistency, ignorability, and positivity
-assumptions are critical for causal inference. The stability of our
-estimation depends on positivity, which we assessed qualitatively by
-examining the distribution of the weights. The no-interference
-assumption may be problematized by the fact that there were a finite
-number of job types in the factory setting. If one worker operates a
-particular metalworking machine, then the the other workers are not able
-to operate that machine at that time. Instead, they may be assigned to
-assembly tasks, which have lower MWF exposure opportunities. That said,
-since these factories were quite large, there may be approximate
-independence. The consistency assumption is also problematic. The MWFs
-of interest are complex chemical mixtures whose composition changes by
-design and by nature. Over the last several decades, the formulation of
-MWFs has changed significantly in reaction to performance needs and
-toxicity concerns (F. Mirer 2003; Byers 2006). The composition of MWFs
-also undergoes unintentional changes because of the nature of their use:
-MWFs are often applied in contexts where contamination by other
-substances and microbes is possible and chemical changes due to heat and
-pressure are likely. Indeed, there are substantial concerns over the
-carcinogenicity of the chemical species formed in the MWF mixtures that
-were not originally added (Hidajat et al. 2020). Concerns regarding the
-consistency assumption may be abrogated in part by adequate adjustment
-for secular and factory-level characteristics.
+no-interference, causal consistency, ignorability, and overlap
+(positivity) assumptions are critical for causal inference. The
+stability of our estimation depends on positivity, which we assessed
+qualitatively by examining the distribution of the weights. The
+no-interference assumption may be problematized by the fact that there
+were a finite number of job types in the factory setting. If one worker
+operates a particular metalworking machine, then the the other workers
+are not able to operate that machine at that time. Instead, they may be
+assigned to assembly tasks, which have lower MWF exposure opportunities.
+That said, since these factories were quite large, there may be
+approximate independence. The consistency assumption is also
+problematic. The MWFs of interest are complex chemical mixtures whose
+composition changes by design and by nature. Over the last several
+decades, the formulation of MWFs has changed significantly in reaction
+to performance needs and toxicity concerns (F. Mirer 2003; Byers 2006).
+The composition of MWFs also undergoes unintentional changes because of
+the nature of their use: MWFs are often applied in contexts where
+contamination by other substances and microbes is possible and chemical
+changes due to heat and pressure are likely. Indeed, there are
+substantial concerns over the carcinogenicity of the chemical species
+formed in the MWF mixtures that were not originally added (Hidajat et
+al. 2020). Concerns regarding the consistency assumption may be
+abrogated in part by adequate adjustment for secular and factory-level
+characteristics.
 
@@
 deleterious health outcomes. The potential magnitude of this
-uncontrolled confounding is likely to be limited, however. The education
+uncontrolled confounding may have been bounded, however. The education
 level of the workers in the cohort was homogeneous, and all cohort
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Foo
-\end{itemize}
+Estimated digestive system cancer-free curves under rules \(a_0\) and
+\(a_1\) applied to the three MWF types are presented in Figure
+\ref{fig:gm_survival}. The survival curves are more or less overlapping
+under the two exposure rules. Numeric values for the cancer-free
+survival and difference in cancer-free survival are presented in Tables
+\ref{tab:gm_survival} and \ref{tab:gm_differences}. The numeric
+summaries are consistent with the qualitative interpretation of the
+estimated survival curves; for all MWF types, expected survival time
+does not differ substantially across rules \(a_0\) and \(a_1\).
+Nonetheless, reducing exposure to straight and soluble MWFs does result
+in a longer survival time, though the difference is less than a month in
+time.
+
+\begin{figure}[h]
+\caption{Cancer-free survival over time since hire under interventions for exposure to straight, soluble, and synthetic metalworking fluids.
+The estimated inverse probability weighted Kaplan-Meier (WKM) survival curve is represented by the solid.
+The estimated Aalen-filtered inverse probability weighted Kaplan-Meier (AWKM) survival curve is represented by the dashed-line.
+Salmon color indicates survival and survival estimates under rule $a_0$; cyan color indicates those under rule $a_1$.}
+\label{fig:gm_survival}
+\begin{center}
+\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/gm_results.pdf}
+\end{center}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Estimated cancer-free survival time over 35-year follow-up.} 
+\label{tab:gm_survival}
+\begin{tabular}{llrrr}
+  \toprule
+Rule & Estimator & Straight & Soluble & Synthetic \\ 
+  \midrule
+$a_0$ & WKM & 29.9606 & 29.9605 & 29.9626 \\ 
+  $a_0$ & AWKM & 29.9337 & 29.9398 & 29.9443 \\ 
+   \midrule
+$a_1$ & WKM & 29.9600 & 29.9584 & 29.9648 \\ 
+  $a_1$ & AWKM & 29.9325 & 29.9360 & 29.9479 \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
+\begin{table}[H]
+\centering
+\caption{Estimated difference in average cancer-free survival time over 35-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\% to $a_0$ never exposed.} 
+\label{tab:gm_differences}
+\begin{tabular}{lrrr}
+  \toprule
+Estimator & Straight & Soluble & Synthetic \\ 
+  \midrule
+WKM & -0.0006 & -0.0021 & 0.0022 \\ 
+  AWKM & -0.0012 & -0.0039 & 0.0037 \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
+
+Figure \ref{fig:gm_weights} presents the median cumulative weight
+applied years since hire with ribbons showing the minimum and maximum
+weight. The overlap in the distribution of weights under the two rules
+for synthetic MWF exposure suggests that the model for the treatment and
+censoring mechanisms were inadequate in distinguishing the units of
+analysis by their probability of following a certain exposure rule or of
+remaining alive. The distribution of the weights was very skewed.
+Without truncation, they would have been in the order of magnitude of
+\(10^{20}\) or higher. Distributional summaries of the cumulative
+weights without truncation are presented in Table \ref{tab:gm_w}. The
+presence of extremely large weights suggests that our observed data were
+inadequate for answering the causal question of interest due to
+practical violations in overlap (Petersen et al. 2012).
+
+\begin{table}[H]
+\centering
+\caption{Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 35$ years since hire for each metalworking fluid type and exposure rule.} 
+\label{tab:gm_w}
+\begin{tabular}{llrrrrrrr}
+  \toprule
+MWF type & Rule & $t$ & Minimum & Q1 & Median & Mean & Q3 & Maximum \\ 
+  \midrule
+Straight & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+  Soluble & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+  Synthetic & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
+  Straight & $a_0$ &  35 & 0.00 & 2.25 & 4.71 & $9.7 \times 10^{16}$ & 4622.00 & $7.3 \times 10^{20}$ \\ 
+   & $a_1$ &  35 & 0.00 & 2.70 & 13.40 & $1.3 \times 10^{18}$ & 22142.45 & $9.8 \times 10^{21}$ \\ 
+  Soluble & $a_0$ &  35 & 0.00 & 4.04 & 858.96 & $5.2 \times 10^{15}$ & 74610.19 & $2.3 \times 10^{19}$ \\ 
+   & $a_1$ &  35 & 0.00 & 158.56 & 6685.12 & $2.3 \times 10^{17}$ & 1227858.13 & $1.7 \times 10^{21}$ \\ 
+  Synthetic & $a_0$ &  35 & 0.00 & 1.02 & 1.25 & $3.7 \times 10^{19}$ & 8.85 & $3.2 \times 10^{23}$ \\ 
+   & $a_1$ &  35 & 0.00 & 1.02 & 1.36 & $2.1 \times 10^{21}$ & 22.63 & $1.8 \times 10^{25}$ \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\caption{Median of the cumulative weights for each year since hire with ribbons delimiting the range of values calculated.
+Salmon color corresponds to the weights used in the estimation of the survival curve under rule $a_0$; cyan corresponds to those for rule $a_1$.}
+\label{fig:gm_weights}
+\begin{center}
+\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/gm_weights.pdf}
+\end{center}
+\end{figure}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  FU in GM is much longer than 20 years
-\item
-  Exclusion restriction on \(H\) so that its parents do not include
-  \(A\) is not necessary for identification in full data
-\item
-  Exclusion restriction on \(D\) so that its parents do not include
-  \(H\) not needed if \(H\) is observed and conditioned upon
-\item
-  Not clear if these were for convenience or what
-\item
-  What if we increase FU? Lags?
-\item
-  Greater fineness in exposure definition? Different interventions?
-\item
-  No way to verify to what extent the simulation informs the real data
-  generating system
-\item
-  Model specification, double robustness
-\end{itemize}
+In the simulation study, we showed that the inverse probability of
+exposure/censoring weighted Kaplan-Meier estimator resulted in lower
+bias in the estimation of average survival time than did the weighted
+Kaplan-Meier estimator without the Aalen filter. While the Aalen filter
+corrects for non-informative left-filtering in the estimation of the
+discrete hazard by excluding person-years not observed under the cancer
+registry. These person-years contribute to estimation during the
+estimation of exposure and censoring weights. Speculatively, the
+combination of the two extensions to the Kaplan-Meier estimator may
+result in the partial control of informative left censoring without
+adjusting for informative left truncation.
+
+The simulation permitted the evaluation of the estimators in clean,
+well-behaved scenarios, but the same luxury was not possible when using
+observed data. Several assumptions used in the simulation study were
+incompatible with what is known about cancer epidemiology. Firstly,
+cumulative incidence in the simulations was close to 15\% (or higher)
+over a 20-year follow-up. This is an extraordinarily high risk of
+cancer, especially because most workers in the automotive manufacturing
+industry start their careers at a fairly young age. Digestive system
+cancers are among the most common forms of cancer in the Unite states,
+and in 35 years of follow-up, we were still only able to observe a
+cumulative incidence of less than 1\%. The simulation scenarios suggest
+that the bias of the WKM and AWKM estimators is higher when cumulative
+incidence is higher, but when cumulative incidence is low, we rely on
+very few observations to index the risk sets.
+
+There are multiple opportunities for future work. The simulation study
+can be expanded to investigate subtler exposure-outcome effects. In the
+present work, the discrete hazard ratio of cancer incidence given
+exposure was rather high at about 1.28. Furthermore, we assumed the
+luxury of knowing the true treatment and censoring mechanisms' model
+forms, but this is quite unrealistic. In future simulations, the effect
+of model mis-specification should be investigated. Alternatively, we
+could estimate survival using a doubly robust method. There can also be
+several improvements made from the subject-matter expertise
+point-of-view. The exposure rules investigated in the applied analysis
+were chosen naively. Other dynamic or stochastic exposure interventions
+may have been of greater interest to occupational health policy, and
+they may have led to improved numeric performance as well. The present
+analysis did not lag exposure status, which is standard practice in
+cancer epidemiology -- the biological responses to carcinogens do not
+occur until several years or decades after exposure. The true causal
+effects of MWF exposure may not yet be observable after 35 years of
+follow-up.
 
@@
 
+\leavevmode\hypertarget{ref-Petersen_2012}{}%
+Petersen, Maya L, Kristin E Porter, Susan Gruber, Yue Wang, and Mark J
+van der Laan. 2012. {``Diagnosing and Responding to Violations in the
+Positivity Assumption.''} \emph{Statistical Methods in Medical Research}
+21 (1): 31--54. \url{https://doi.org/10.1177/0962280210386207}.
+
+\leavevmode\hypertarget{ref-Sofrygin_2021}{}%
+Sofrygin, Oleg, Mark J. van der Laan, and Romain Neugebauer. 2021.
+\emph{Stremr: Streamlined Estimation for Static, Dynamic and Stochastic
+Treatment Regimes in Longitudinal Data}.
+\url{https://github.com/osofr/stremr}.
+
 \leavevmode\hypertarget{ref-Xie_2005}{}%

### 2021-12-12 reports/01-introduction.Rmd
Draft ready

@@
 
-The present project replicates the simulation and bias analyses presented in Chapter 3 of @Izano_2017_thesis, embeds the problem in the non-parametric structural causal approach of @Pearl_1995, and applies the WKM and AWKM estimators to the estimation of colon cancer survival under exposure/censoring rules in the UAW-GM Cohort.
+The present project replicates the simulation and bias analyses presented in Chapter 3 of @Izano_2017_thesis, embeds the problem in the non-parametric structural causal approach of @Pearl_1995, and applies the WKM and AWKM estimators to the estimation of digestive-system cancer-free survival under exposure/censoring rules in the UAW-GM Cohort.
+The `stremr` package was used to estimate the WKM and AWKM survival curves in both the simulation and the applied analyses [@Sofrygin_2021].

### 2021-12-12 reports/03-results.Rmd
Draft ready

@@
 The bias of the AWKM survival estimator appeared to be larger in  earlier follow-up and smaller for later follow-up time points.
-The bias of both the the WKM and the AWKM estimators appeared largest in Scenario 5.
+The bias of the WKM estimator appeared largest in Scenario 5.
+The bias of the AWKM estimator was similar across the five scenarios
 
@@
 The WKM estimator over-estimated the difference in cancer-free survival time, resulting in bias toward the null, whereas the AWKM estimator under-estimates the cancer-free survival, resulting in bias away from the null.
-In every scenario, the bias of the WKM-derived contrast was several times larger in magnitude than that of the AWKM-derived contrast.
-The bias of both estimators was greatest for Scenario 5.
+In every scenario, the bias of the WKM-derived contrast was two to several times larger in magnitude than that of the AWKM-derived contrast.
 

### 2021-12-12 reports/04-gm.Rmd
Draft ready

@@
 library(here)
-library(tableone)
 ```
@@
 Next, we estimated cancer-free survival in a real-world context.
-Using data from the UAW-GM Cohort study, we followed $38\,553$ individuals starting from hire to 40 years after hire for incidence of colon cancer.
+Using data from two plants participating in the UAW-GM Cohort study, we followed $38\,553$ individuals starting from hire to 40 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
 This duration of follow-up spans the vast majority of individuals' working lifetimes.
@@
 
-The outcome of interest was colon cancer incidence.
-There is little past research linking colon cancer to MWF exposures, but there is some evidence suggesting that straight MWFs cause colon cancer [@Izano_2019].
-We obtained cancer incidence data via linkage to the Michigan Cancer Registry, which recorded cancer incidence cases starting on January 1, 1985.
-<!-- and linkage to Surveillance, Epidemiology, and End Results (SEER), which recorded cancer incidence cases starting on January 1, 1973. -->
-The cohort is comprised of individuals hired between 1938 and 1985.
+The outcome of interest was digestive system cancer incidence.
+There is little past research linking digestive system cancers to MWF exposures, but there is some evidence suggesting that straight MWFs cause digestive system cancers [@Izano_2019].
+<!-- We obtained cancer incidence data for those at Plant 3 via linkage to the Michigan Cancer Registry, which recorded cancer incidence cases starting on January 1, 1985. -->
+Cancer incidence was obtained by linkage to Surveillance, Epidemiology, and End Results (SEER), which recorded cancer incidence cases starting on January 1, 1973.
+The cohort is comprised of individuals hired between 1938 and 1975.
 Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE as investigated in the simulations.
 Over the 40 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
+The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ being exposed with 75\% chance in the years exposure was observed and $a_1$ being exposed in the years exposure was observed.
+Weights were truncated at 1000.
+Binary exposure is defined to be exposure above the median level of exposure to straight, soluble, and synthetic MWFs or not.
+Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.
 Baseline confounders included race, sex, plant, and year of hire.
-Time-varying confounders included age, cumulative time off, and exposure to the metalworking fluids not under study.
-These terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every year of follow-up.
-The exposure rules of interest were identical to those in the simulation study: $a_0$ never exposed and $a_1$ always exposed while at work.
-We assumed that the effect of exposure on health status, mortality, cancer incidence, etc occurs after a lag of 15 years.
-Similarly, we assumed that the effects of cumulative time off occur after a 15 year lag.
-Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.
-Summary statistics for the full study population and the colon cancer cases are presented in Table \ref{tab:popchar}.
+Time-varying confounders included age, cumulative time off, employment status, and exposure to the metalworking fluids exposure from the past year.
+These terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every two years of follow-up.
+Summary statistics for the full study population and the digestive system cancer cases are presented in Table \ref{tab:popchar}.
 
 ```{r, eval=F}
+library(tableone)
 mwf <- NULL
-if (!"cohort_analytic" %in% ls()) {source(here("scripts", "04-application.R"))}
-full.tab <- cohort_analytic[,.(
+if (!"gm.dt" %in% ls()) {source(here("scripts", "04-application.R"))}
+full.tab <- gm.dt[,.(
 	studyno,
@@
 	Sex,
-	Plant,
+	Plant = paste("Plant", plant),
 	yin = yin.gm,
@@
 	death = `All causes`,
-	canc_co
+	Y = canc
 )]
 
-nrow(full.tab)
-print(
+full.tab_cat <- print(
 	CreateTableOne(data = full.tab[,.(
@@
 		Sex = Sex[1],
-		Plant = c("Plant 1", "Plant 2", "Plant 3")[which.max(table(Plant))],
-		Dead = factor(max(death))
-	), studyno]),
+		Plant = Plant[1],
+		# Dead = factor(max(death)),
+		`Ever exposed` = factor(c("Yes", "No")[as.integer(sum(straight + soluble + synthetic) > 0) + 1])
+	), studyno][,-1]),
 	showAllLevels = T)
 
-print(
+full.tab_cont <- print(
 	CreateTableOne(data = full.tab[,.(
-		Straight = factor(as.integer(sum(shift(straight, 15, 0)) <= 0)),
-		Soluble = factor(as.integer(sum(shift(soluble, 15, 0)) <= 0)),
-		Synthetic = factor(as.integer(sum(shift(synthetic, 15, 0)) <= 0)),
 		`Year of hire` = yin[1],
-		Age = age[min(.N, .I[canc_co == 1], na.rm = T)],
-		`Cumulative time off` = shift(
-			off, 15, 0)[min(.N, .I[canc_co == 1], na.rm = T)]
-	), studyno])
+		Age = age[min(.N, .I[Y == 1], na.rm = T)],
+		`Cumulative time off` = off[min(.N, .I[Y == 1], na.rm = T)]
+	), studyno][,-1])
 	)
 
-nrow(full.tab[studyno %in% full.tab[canc_co == 1, studyno]])
-print(
-	CreateTableOne(data = full.tab[studyno %in% full.tab[canc_co == 1, studyno],.(
+rownames(full.tab_cat) <- paste(rownames(full.tab_cat), "\n", full.tab_cat[,1])
+full.tab_cat <- as.matrix(full.tab_cat[,2])
+full.tab_cat[1,] <- paste0(full.tab_cat[1,], " (", nrow(full.tab), ")")
+full.tab1 <- rbind(full.tab_cat, as.matrix(full.tab_cont[-1,]))
+
+case.tab_cat <- print(
+	CreateTableOne(data = full.tab[studyno %in% full.tab[Y == 1, studyno],.(
 		Race = Race[1],
 		Sex = Sex[1],
-		Plant = c("Plant 1", "Plant 2", "Plant 3")[which.max(table(Plant))]
-	), studyno]),
+		Plant = Plant[1],
+		`Ever exposed` = factor(c("Yes", "No")[as.integer(sum(straight + soluble + synthetic) > 0) + 1])
+	), studyno][,-1]),
 	showAllLevels = T)
 
-print(
-	CreateTableOne(data = full.tab[studyno %in% full.tab[canc_co == 1, studyno],.(
-		Straight = factor(as.integer(sum(shift(straight, 15, 0)) <= 0)),
-		Soluble = factor(as.integer(sum(shift(soluble, 15, 0)) <= 0)),
-		Synthetic = factor(as.integer(sum(shift(synthetic, 15, 0)) <= 0)),
+case.tab_cont <- print(
+	CreateTableOne(data = full.tab[studyno %in% full.tab[Y == 1, studyno],.(
 		`Year of hire` = yin[1],
-		Age = age[min(.N, .I[canc_co == 1], na.rm = T)],
-		`Cumulative time off` = shift(
-			off, 15, 0)[min(.N, .I[canc_co == 1], na.rm = T)]
-	), studyno])
+		Age = age[min(.N, .I[Y == 1], na.rm = T)],
+		`Cumulative time off` = off[min(.N, .I[Y == 1], na.rm = T)]
+	), studyno][,-1])
 	)
 
-xtable(head(cars))
+rownames(case.tab_cat) <- paste(rownames(case.tab_cat), "\n", case.tab_cat[,1])
+case.tab_cat <- as.matrix(case.tab_cat[,2])
+case.tab_cat[1,] <- paste0(case.tab_cat[1,], " (", nrow(full.tab[studyno %in% full.tab[Y == 1, studyno]]), ")")
+case.tab1 <- rbind(case.tab_cat, as.matrix(case.tab_cont[-1,]))
+
+tab1 <- cbind(full.tab1, case.tab1)
+tab1 <- gsub(" \\(", " \\& \\(", tab1)
+
+print(xtable(tab1), include.rownames = T)
 ```
@@
 \toprule
-&		\multicolumn{2}{c}{Full cohort} 	  & \multicolumn{2}{c}{Colon cancer cases}		\\
+&		\multicolumn{2}{c}{Full cohort} 	  & \multicolumn{2}{c}{Digestive cancer cases}		\\
 \midrule
 $n$ (person-years) 
-            &     38 553 & (1 402 372)       & 267 & (9 635)		\\
+                       &     26 182 & (695 475) & 213 & (6000) \\ 
 Race (\%) \\
-\hspace{1.5em} Black   &      7 133 & (18.5)    			&  83 & (31.1)  		\\
-\hspace{1.5em} White   &     31 420 & (81.5)    			& 184 & (68.9)  		\\
+\hspace{1.5em} Black   &      6 017 & (23.0)  &  66 & (31.0)  \\ 
+\hspace{1.5em} White   &     20 165 & (77.0)  & 147 & (69.0)  \\ 
 Sex (\%) \\
-\hspace{1.5em} Female  &      4 757 & (12.3)    			&  49 & (18.4)		\\
-\hspace{1.5em} Male    &     33 796 & (87.7)    			& 218 & (81.6)		\\
+\hspace{1.5em} Female  &      3 328 & (12.7)  &  15 & (7.0)  \\ 
+\hspace{1.5em} Male    &     22 854 & (87.3)  & 198 & (93.0)  \\ 
 Plant (\%) \\
-\hspace{1.5em} Plant 1 &      9 092 & (23.6)    			&  66 & (24.7)		\\
-\hspace{1.5em} Plant 2 &     17 090 & (44.3)    			& 107 & (40.1) 		\\
-\hspace{1.5em} Plant 3 &     12 371 & (32.1)    			&  94 & (35.2)    		\\
+\hspace{1.5em} Plant 1 &      9 092 & (34.7)  & 103 & (48.4)  \\ 
+\hspace{1.5em} Plant 2 &     17 090 & (65.3)  & 110 & (51.6)  \\ 
 \midrule
 Ever exposed to MWF (\%)
-						&     22193 & (57.6)    			& 104 & (39.0)  		\\
+											&      13 240 & (50.6)  &  95 & (44.6)  \\ 
 Year of hire (mean (\textsc{sd}))
-						&     1963 & (11.62)    		& 1968 & (8.79) 		\\
-Age (mean (\textsc{sd}))
-						&     63.38 & (9.08)    			& 67.78 & (9.27) 		\\
-Cumulative time off (mean (\textsc{sd}))
-						&     0.04 & (0.14)    			  & 0.05 & (0.15) 		\\
+											&        	 1963 & (12.26) & 1960 & (9.55) \\ 
+Age at end of follow-up (mean (\textsc{sd}))
+											&         55.09 & (12.02) & 63.58 & (9.40) \\ 
+Cumulative years off (mean (\textsc{sd}))
+											&          0.06 & (0.15)  & 0.12 & (0.24) 	\\
 \bottomrule
@@
 
-Since we are working with observational data, the evaluation of the no-interference, causal consistency, ignorability, and positivity assumptions are critical for causal inference.
+Since we are working with observational data, the evaluation of the no-interference, causal consistency, ignorability, and overlap (positivity) assumptions are critical for causal inference.
 The stability of our estimation depends on positivity, which we assessed qualitatively by examining the distribution of the weights.
@@
 In particular, workers may be assigned to certain tasks based on their specific skills and knowledge, which may be associated with structural privileges that confer a lower risk of deleterious health outcomes.
-The potential magnitude of this uncontrolled confounding is likely to be limited, however.
+The potential magnitude of this uncontrolled confounding may have been bounded, however.
 The education level of the workers in the cohort was homogeneous, and all cohort members were members of the UAW union, which had uniform procedures in place for equitable access to training, wages, and career advancement [@Harbison_1950;@Barnard_2005].
@@
 
-- Foo
+```{r, include = F}
+source(here("scripts", "05-application-results.R"))
+
+gm_survival.tab <- dcast(
+	melt(gm.surv[t <= 30],
+			 measure.vars = c("WKM", "AWKM"),
+			 variable.name = "Estimator",
+			 value.name = "Survival")[,.(
+		Survival = sum(Survival)
+	), .(MWF = mwf, Rule = rule, Estimator)],
+	... ~ MWF,
+	value.var = "Survival"
+)
+
+setorder(gm_survival.tab, Rule, Estimator)
+
+gm_differences.tab <- gm_survival.tab[,.(
+		Straight  = Straight[2] - Straight[1],
+		Soluble   = Soluble[2] - Soluble[1],
+		Synthetic = Synthetic[2] - Synthetic[1]
+	), .(Estimator)]
+
+```
+
+Estimated digestive system cancer-free curves under rules $a_0$ and $a_1$ applied to the three MWF types are presented in Figure \ref{fig:gm_survival}.
+The survival curves are more or less overlapping under the two exposure rules.
+Numeric values for the cancer-free survival and difference in cancer-free survival are presented in Tables \ref{tab:gm_survival} and \ref{tab:gm_differences}.
+The numeric summaries are consistent with the qualitative interpretation of the estimated survival curves; for all MWF types, expected survival time does not differ substantially across rules $a_0$ and $a_1$.
+Nonetheless, reducing exposure to straight and soluble MWFs does result in a longer survival time, though the difference is less than a month in time.
+
+\begin{figure}[h]
+\caption{Cancer-free survival over time since hire under interventions for exposure to straight, soluble, and synthetic metalworking fluids.
+The estimated inverse probability weighted Kaplan-Meier (WKM) survival curve is represented by the solid.
+The estimated Aalen-filtered inverse probability weighted Kaplan-Meier (AWKM) survival curve is represented by the dashed-line.
+Salmon color indicates survival and survival estimates under rule $a_0$; cyan color indicates those under rule $a_1$.}
+\label{fig:gm_survival}
+\begin{center}
+\includegraphics{`r here::here("reports/resources", "gm_results.pdf")`}
+\end{center}
+\end{figure}
+
+```{r}
+print(xtable(gm_survival.tab,
+			 caption = "Estimated cancer-free survival time over 35-year follow-up.",
+			 label = "tab:gm_survival", digits = 4),
+			hline.after = c(-1,0,2, nrow(gm_survival.tab)),
+			floating = T)
+
+print(xtable(gm_differences.tab,
+			 caption = "Estimated difference in average cancer-free survival time over 35-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\\% to $a_0$ never exposed.",
+			 label = "tab:gm_differences", digits = 4),
+			floating = T)
+
+```
+
+Figure \ref{fig:gm_weights} presents the median cumulative weight applied years since hire with ribbons showing the minimum and maximum weight.
+The overlap in the distribution of weights under the two rules for synthetic MWF exposure suggests that the model for the treatment and censoring mechanisms were inadequate in distinguishing the units of analysis by their probability of following a certain exposure rule or of remaining alive.
+The distribution of the weights was very skewed.
+Without truncation, they would have been in the order of magnitude of $10^{20}$ or higher.
+Distributional summaries of the cumulative weights without truncation are presented in Table \ref{tab:gm_w}.
+The presence of extremely large weights suggests that our observed data were inadequate for answering the causal question of interest due to practical violations in overlap [@Petersen_2012].
+
+```{r}
+gm_w.small_tab <- rbindlist(list(
+	gm_w.tab[t == 1,],
+	gm_w.tab[t == 35,]))
+
+gm_w.small_tab <- gm_w.small_tab[estimator == "WKM", -1]
+setorder(gm_w.small_tab, t, mwf, rule)
+
+gm_w.small_tab$mwf <- rep(as.vector(sapply(
+	c("Straight", "Soluble", "Synthetic"), function(x) {
+	c(x, "")})), 2)
+
+names(gm_w.small_tab)[1:3] <- c("MWF type", "Rule", "$t$")
+
+print(xtable(
+	gm_w.small_tab,
+	caption = "Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 35$ years since hire for each metalworking fluid type and exposure rule.",
+	label = "tab:gm_w",
+	display = c("s", "s", "s", "d", "f", "f", "f", "g", "f", "g")),
+	math.style.exponents = TRUE,
+	floating = T)
+
+```
+
+\begin{figure}
+\caption{Median of the cumulative weights for each year since hire with ribbons delimiting the range of values calculated.
+Salmon color corresponds to the weights used in the estimation of the survival curve under rule $a_0$; cyan corresponds to those for rule $a_1$.}
+\label{fig:gm_weights}
+\begin{center}
+\includegraphics{`r here::here("reports/resources", "gm_weights.pdf")`}
+\end{center}
+\end{figure}

### 2021-12-12 reports/05-discussion.Rmd
Interim results; running on GM data now
Draft ready

@@
 
-- FU in GM is much longer than 20 years
-- Exclusion restriction on $H$ so that its parents do not include $A$ is not necessary for identification in full data
-- Exclusion restriction on $D$ so that its parents do not include $H$ not needed if $H$ is observed and conditioned upon
-- Not clear if these were for convenience or what
-- What if we increase FU? Lags?
-- No way to verify to what extent the simulation informs the real data generating system
+# Discussion
+
+In the simulation study, we showed that the inverse probability of exposure/censoring weighted Kaplan-Meier estimator resulted in lower bias in the estimation of average survival time than did the weighted Kaplan-Meier estimator without the Aalen filter.
+While the Aalen filter corrects for non-informative left-filtering in the estimation of the discrete hazard by excluding person-years not observed under the cancer registry.
+These person-years contribute to estimation during the estimation of exposure and censoring weights.
+Speculatively, the combination of the two extensions to the Kaplan-Meier estimator may result in the partial control of informative left censoring without adjusting for informative left truncation.
+
+The simulation permitted the evaluation of the estimators in clean, well-behaved scenarios, but the same luxury was not possible when using observed data.
+Several assumptions used in the simulation study were incompatible with what is known about cancer epidemiology.
+Firstly, cumulative incidence in the simulations was close to 15\% (or higher) over a 20-year follow-up.
+This is an extraordinarily high risk of cancer, especially because most workers in the automotive manufacturing industry start their careers at a fairly young age.
+Digestive system cancers are among the most common forms of cancer in the Unite states, and in 35 years of follow-up, we were still only able to observe a cumulative incidence of less than 1\%.
+The simulation scenarios suggest that the bias of the WKM and AWKM estimators is higher when cumulative incidence is higher, but when cumulative incidence is low, we rely on very few observations to index the risk sets.
+
+There are multiple opportunities for future work.
+The simulation study can be expanded to investigate subtler exposure-outcome effects.
+In the present work, the discrete hazard ratio of cancer incidence given exposure was rather high at about 1.28.
+Furthermore, we assumed the luxury of knowing the true treatment and censoring mechanisms' model forms, but this is quite unrealistic.
+In future simulations, the effect of model mis-specification should be investigated.
+Alternatively, we could estimate survival using a doubly robust method.
+There can also be several improvements made from the subject-matter expertise point-of-view.
+The exposure rules investigated in the applied analysis were chosen naively.
+Other dynamic or stochastic exposure interventions may have been of greater interest to occupational health policy, and they may have led to improved numeric performance as well.
+The present analysis did not lag exposure status, which is standard practice in cancer epidemiology -- the biological responses to carcinogens do not occur until several years or decades after exposure.
+The true causal effects of MWF exposure may not yet be observable after 35 years of follow-up.

### 2021-12-12 scripts/00-hello.R

@@ -28,5 +28,11 @@ if (!"cohort_analytic" %in% ls()) {
 		studyno]
 }
 
-cohort_analytic <- cohort_analytic[wh == 1 & nohist == 0 & yin.gm >= 1938]
+cohort_analytic[,`:=`(Plant = factor(plant))]
+cohort_analytic[,`:=`(plant = c(1:3)[which.max(table(Plant))]), studyno]
+cohort_analytic[, plant := as.numeric(plant)]
+			
+cohort_analytic <- cohort_analytic[
+	# plant %in% c(1,2) &
+	wh == 1 & nohist == 0 & yin.gm >= 1938]
 

### 2021-12-12 scripts/03-results.R

@@ -76,7 +76,7 @@ sim_results %>% ggplot(aes(
 	color = rule,
 )) + geom_step() + facet_grid(scenario ~ .) +
 	# coord_cartesian(ylim = c(0.8, 1)) +
-	labs(x = "Time since hire", y = "Cancer-free survival") +
+	labs(x = "Years since hire", y = "Cancer-free survival") +
 	mytheme + theme(
 		legend.title = element_blank(),
 		legend.position = "bottom"

### 2021-12-12 scripts/04-application.R

@@ -19,29 +19,29 @@ if (!"cohort_analytic" %in% ls()) {
 # devtools::install_github('osofr/stremr')
 library(stremr)
 
-years_fu <- 40
-cohort_analytic <- cohort_analytic[
-	year < year(yin) + years_fu &
-		nohist == 0 &
-		wh == 1]
+years_fu <- 35
+gm.dt <- cohort_analytic[year >= year(yin) & year < year(yin) + years_fu & (year(yin) <= 1995 - years_fu | year <= 1994)]
+gm.dt <- gm.dt[plant %in% 1:2]
+gm.dt[, canc := ifelse(canc_corec == 1 | canc_es == 1 | canc_st == 1, 1, 
+										ifelse(canc_corec == 2 | canc_es == 2 | canc_st == 2, 2, 0))]
 
 # Covariate engineering
-cohort_analytic[,`:=`(
-	Straight = as.integer(straight > 0),
-	Soluble = as.integer(soluble > 0),
-	Synthetic = as.integer(synthetic > 0),
-	R = as.integer(year >= 1985),
+gm.dt[,`:=`(
+	Straight = as.integer(straight > median(straight[year <= year(yout)])),
+	Soluble = as.integer(soluble > median(soluble[year <= year(yout)])),
+	Synthetic = as.integer(synthetic > median(synthetic[year <= year(yout)])),
+	R = as.integer(year >= 1985 | (year >= 1973 & plant %in% 1:2)),
 	Plant = factor(plant),
 	Race = factor(race),
 	Sex = factor(sex),
 	Age = cut(age.year2/365, c(
 		min(age.year2/365),
-		quantile(age.year2[canc_co == 1]/365, seq(0.2, 0.8, 0.2)),
+		quantile(age.year2[canc == 1]/365, seq(0.2, 0.8, 0.2)),
 		max(age.year2/365)),
 		include.lowest = T, dig.lab = 4),
 	Hire = cut(yin.gm, c(
 		min(yin.gm),
-		quantile(yin.gm[canc_co == 1], seq(0.2, 0.8, 0.2)),
+		quantile(yin.gm[canc == 1], seq(0.2, 0.8, 0.2)),
 		max(yin.gm)),
 		include.lowest = T, dig.lab = 4),
 	N = as.integer(year <= year(yout)),
@@ -52,54 +52,86 @@ cohort_analytic[,`:=`(
[…]

### 2021-12-12 scripts/05-application-results.R

@@ -1,0 +1,120 @@
+# 04-application.R
+# Analyzing simulated data
+# Kevin Chen
+# December 6, 2021
+
+library(here)
+library(lubridate)
+library(tidyverse)
+library(magrittr)
+library(data.table)
+library(survival)
+
+# Get script from github
+library(RCurl)
+eval(parse(text = getURL(
+	"https://raw.githubusercontent.com/kvntchn/HeadRs/master/00-my-theme.R",
+	ssl.verifypeer = F
+)))
+
+str_a0 <- readRDS(here("resources", paste0("straight0_gm", ".rds")))
+str_a1 <- readRDS(here("resources", paste0("straight1_gm", ".rds")))
+sol_a0 <- readRDS(here("resources", paste0("soluble0_gm", ".rds")))
+sol_a1 <- readRDS(here("resources", paste0("soluble1_gm", ".rds")))
+syn_a0 <- readRDS(here("resources", paste0("synthetic0_gm", ".rds")))
+syn_a1 <- readRDS(here("resources", paste0("synthetic1_gm", ".rds")))
+
+gm.surv <- rbindlist(list(
+	rbindlist(list(str_a0[[2]], str_a1[[2]]), idcol = "rule"),
+	rbindlist(list(sol_a0[[2]], sol_a1[[2]]), idcol = "rule"),
+	rbindlist(list(syn_a0[[2]], syn_a1[[2]]), idcol = "rule")
+), idcol = "mwf")
+
+gm.w <- rbindlist(list(
+	rbindlist(list(str_a0[[1]], str_a1[[1]]), idcol = "rule"),
+	rbindlist(list(sol_a0[[1]], sol_a1[[1]]), idcol = "rule"),
+	rbindlist(list(syn_a0[[1]], syn_a1[[1]]), idcol = "rule")
+), idcol = "mwf")
+
+
+gm.surv[,`:=`(
+	mwf = {
+		mwf.labs <- c("Straight", "Soluble", "Synthetic")
+		factor(mwf.labs[mwf], mwf.labs)
+		},
+	rule = c("$a_0$", "$a_1$")[rule]
+)]
+
+gm.w[,`:=`(
+	mwf = {
+		mwf.labs <- c("Straight", "Soluble", "Synthetic")
+		factor(mwf.labs[mwf], mwf.labs)
+		},
+	rule = c("$a_0$", "$a_1$")[rule]
+)]
+
+gm.w <- rbindlist(list(
[…]

### 2021-12-14 paper.tex
Revised draft

@@
 synthetic metalworking fluids (Byers 2006). Possible routes of human
-exposure include absorption through skin, inhalation or aerosols, and
+exposure include absorption through skin, inhalation of aerosols, and
 ingestion of droplets.
 
-A central concern in the analysis of occupational cohorts is the
-potential for the healthy worker survivor effect (HWSE), the phenomenon
-by which healthy individuals remain at work, while less healthy
-individuals leave work -- possibly in response to exposure-related
-health decline. In the presence of the HWSE, those with the highest
-cumulative occupational exposures are also those who are less at risk of
-disease. Thus, standard measures of association would show an inverse
-relationship between occupational exposure and poor health outcomes
-(Arrighi and Hertz-Picciotto 1994). The HWSE is an example of
-time-varying confounding affected by past exposure. Previous studies
-have attempted to assess the presence of the HWSE in observed data by
-assessing so-called path-specific associations using Cox proportional
-hazards modeling (Naimi et al. 2013; Garcia et al. 2017). However, these
-measures of associations were themselves subject to the confounding
+A central concern in the analysis of longitudinal occupational cohort
+data is the potential for bias due to the healthy worker survivor effect
+(HWSE), the phenomenon by which healthy individuals remain at work,
+while less healthy individuals leave work -- possibly in response to
+exposure-related health decline. In the presence of the HWSE, those with
+the highest cumulative occupational exposures are also those who are
+less at risk of disease (more likely to have potential outcome no
+disease under both exposure and no exposure scenarios). Thus, standard
+measures of association would show an inverse relationship between
+occupational exposure and poor health outcomes (Arrighi and
+Hertz-Picciotto 1994). The HWSE is an example of time-varying
+confounding affected by past exposure. Previous studies have attempted
+to assess the presence of the HWSE in observed data by assessing
+so-called path-specific associations using Cox proportional hazards
+modeling (Naimi et al. 2013; Garcia et al. 2017). However, in those
+studies, the estimates were themselves subject to the confounding
 structures they sought to characterize.
@@
 If conditional sequential ignorability of exposure and censoring status
-at each point in follow-up and positivity can be attained given
-covariate history, then causal methods can be applied to account for the
-HWSE. Past studies have applied causal methods capable of accounting for
-time-varying confounding affected by past exposure to the study of MWF
-exposures and cancer mortality outcomes in the UAW-GM Cohort Study
-(Garcia et al. 2018; Izano et al. 2019), but the study of cancer
-incidence outcomes is further problematized by the incomplete
-observation of cancer incidence outcomes at every point of follow-up
-over the study period. Nonetheless, we wish to make inferences about the
-carcinogenicity of MWF exposure over an individual's lifetime starting
-upon entry into the workforce. The UAW-GM Cohort included those hired
-roughly between 1938 and 1985. However, cancer incidence reporting at
-the Michigan Cancer Registry did not begin until 1985. Hence, our
-observed cohort data is subject to \emph{left filtering}: cancer
-incidence is the outcome of interest, but before 1985, both cancer
-incidence status and time of cancer incidence are unknown. Observation
-of the complete cancer incidence outcome vector over the study period
-was conditional on an individual surviving to 1985 cancer-free.
+at each point in follow-up and positivity (overlap) can be attained
+given covariate history, then longitudinal causal methods can be applied
+to account for the HWSE. Past studies have applied causal methods
+capable of accounting for time-varying confounding affected by past
+exposure to the study of MWF exposures and cancer mortality outcomes in
+the UAW-GM Cohort Study (Garcia et al. 2018; Izano et al. 2019).
+However, the study of cancer incidence outcomes is further problematized
+by the incomplete observation of cancer incidence outcomes at every
+point of follow-up over the study period. Nonetheless, we wish to make
+inferences about the carcinogenicity of MWF exposure over an
+individual's lifetime starting upon entry into the workforce. The UAW-GM
+Cohort included those hired roughly between 1938 and 1985. However,
+cancer incidence reporting did not begin until 1973. Hence, our observed
+cohort data exhibits \emph{left filtering}: cancer incidence is the
+outcome of interest, but before 1985, both cancer incidence status and
+time of cancer incidence are unknown. Observation of the complete cancer
+incidence outcome vector over the study period was conditional on an
+individual surviving to 1985 cancer-free.
 
@@
 the average of 250 estimates of to the average difference in cancer-free
-survival under the two rules to the true average survival difference
+survival under the two rules to the true average difference in survival
 when exposure and censoring were controlled deterministically.
@@
 the WKM and AWKM estimators to the estimation of digestive-system
-cancer-free survival under exposure/censoring rules in the UAW-GM
+cancer-free survival under exposure and no censoring rules in the UAW-GM
 Cohort. The \texttt{stremr} package was used to estimate the WKM and
@@
 occupational cohort studies. At each time point, the effect of
-cumulative exposure \(\bar A(t)\) on cancer incidence \(Y^(t)\) is
-confounded by a path through employment status \(N(t)\) and underlying
+cumulative exposure \(\bar A(t)\) on cancer incidence \(Y^*(t)\) is
+confounded by the path through employment status \(N(t)\) and underlying
 health \(H(t)\) as well as the path through past exposure
@@
 \[X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).\]
-The bar notation to indicates variable history where
-\(\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t\). In the case of
-exposure, \(\bar A_i(t)\) is the indicator of whether unit \(i\) was
-ever exposed through time \(t\). Note that true cancer status \(Y^*(t)\)
-not observed until \(t \ge R\), after the start of the registry. Call
-\(X\) the full data, where we have \(R = 0\) for all. In the observed
-data \(X^\text{obs}\), we cannot assume \(R = 0\) for all;
-susceptibility \(S\) and underlying health status \(H\) are not known:
+In general, we use bar notation to indicate variable history as follows
+\(\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t\). Note that true cancer
+status \(Y^*(t)\) is not observed until \(t \ge R\), after the start of
+the registry. Call \(X\) the full data, where we have \(R = 0\) for all.
+In the observed data \(X^\text{obs}\), we cannot assume \(R = 0\) for
+all. Additionally, susceptibility \(S\) and underlying health status
+\(H\) are not known:
 \[X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).\]
@@
 \(U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}\)
-are mutually independent. Exposure status is a time-varying indicator;
-let exposure history \(\bar A(t)\) be summarized as being ever-exposed
-or not with \(\bar A(t) = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}\). The
-outcome of interest is a survival outcome, so
+are mutually independent. Exposure status is a time-varying indicator,
+and exposure history is summarized as
+\(\bar A(t) = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}\). The outcome of
+interest is a survival outcome, so
 \(Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1\). The observed outcome \(Y(t)\)
-at time \(t\) is a function of true outcome status and the time points
-delimiting left and right censoring. An abbreviated directed acyclic
+at time \(t\) is a function of true outcome status, time of left
+censoring, and time of right censoring. An abbreviated directed acyclic
 graph (DAG) representing the causal relationships encoded in the
@@
 \path[->] (N0) edge (A0);
-\path[->] (A0) edge [bend right=20] (Y0);
+\path[->] (A0) edge [bend right=30] (Y0);
 \path[->] (H0) edge (H);
@@
 absence of observed data on health status \(H(t)\), an analyst may be
-tempted to condition on employment status \(N(t)\), but doing so would
-introduce collider bias while blocking the causal path between past
-exposure \(\bar A(t - 1)\) and cancer \(Y^*(t)\). Furthermore, an
-analysis starting at an arbitrary time point after the time origin
-(hire) would be tantamount to conditioning on those still alive at that
-time, which would also result in both collider bias and the conditioning
-on nodes on the causal path between the exposure and outcome of
-interest.
+tempted to conduct an analysis by simply ``blocking'' or conditioning on
+employment status \(N(t)\), but doing so would introduce collider bias
+while blocking the causal path between past exposure \(\bar A(t - 1)\)
+and cancer \(Y^*(t)\). Furthermore, an analysis starting at an arbitrary
+time point after the time origin (hire) would be tantamount to
+conditioning on those still alive at that time, which would result in
+both collider bias and the conditioning on nodes on the causal path
+between the exposure and the outcome of interest.
 
@@
 
-Five sets of data were generated using these equations to represent five
-scenarios. Scenario 1 represents the base case where 10\% of workers are
-susceptible to exposure-related effects, the odds ratio of mortality
-each additional year following cancer diagnosis is about 1.6, and there
-is moderate time-varying confounding by health status. In scenario 2, we
-have greater cancer-related mortality by increasing
-\(\beta_{\bar Y}^D\). In scenario 3, we increase \(p_S\), the proportion
-of the study population susceptible to the carcinogenic effects of MWF
-exposure. In scenario 4, we consider greater time-varying confounding by
-health status by increasing \(\beta_H^N\) and \(\beta_H^Y\). In the last
-scenario, we have greater background cancer incidence by increasing
-\(\beta_0^Y\). The sets of parameters used in the five scenarios are
-presented in Table \ref{tab:params}.
+Five sets of data were generated using these equations, but with
+different parameters, to represent five scenarios. Scenario 1 represents
+the base case where 10\% of workers are susceptible to exposure-related
+effects, the odds ratio of mortality each additional year following
+cancer diagnosis is about 1.6, and there is moderate time-varying
+confounding by health status. In scenario 2, we have greater
+cancer-related mortality by increasing \(\beta_{\bar Y}^D\). In scenario
+3, we increase \(p_S\), the proportion of the study population
+susceptible to the carcinogenic effects of MWF exposure. In scenario 4,
+we consider greater time-varying confounding by health status by
+increasing \(\beta_H^N\) and \(\beta_H^Y\). In the last scenario, we
+have greater background cancer incidence by increasing \(\beta_0^Y\).
+The sets of parameters used in the five scenarios are presented in Table
+\ref{tab:params}.
 
@@
 were intervenable. The causal effect was defined by contrasting the
-survival function \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule \(a_1\)
-to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\). Note
-that this causal estimand was defined over \emph{a priori
+survival functions \(S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}\) under rule
+\(a_1\) to \(S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}\) that under rule \(a_0\).
+Note that this causal estimand was defined over \emph{a priori
 counterfactuals} not observable in the real world (Frangakis and Rubin
-2002). This approach is standard in epidemiologic studies, however.
+2002). This approach is standard in epidemiologic studies.
 
@@
 scenario (the original analysis performed 500). The true value was
-calculated by simulating the full data for five hundred thousand
-individuals (the original analysis used one million) with rules \(a_0\)
-and \(a_1\) applied deterministically. Estimates of \(\psi\) were
-obtained by first estimating the survival curves \(S_a(t)\) using two
-estimators: the inverse probability weighted Kaplan-Meier estimator
-(WKM) and the Aalen-filtered WKM (AWKM). These survival estimators are
-detailed in the following section.
+calculated by simulating the full data for \(500\,000\) individuals (the
+original analysis used one million) with rules \(a_0\) and \(a_1\)
+applied deterministically. Estimates of \(\psi\) were obtained by
+estimating the survival curves \(S_a(t)\) using two estimators: the
+inverse probability weighted Kaplan-Meier estimator (WKM) and the
+Aalen-filtered WKM (AWKM). These survival estimators are detailed in the
+following section.
 
@@
 cases \(c^0_{a}(t)\) that occurred in interval \((t - 1, t]\) and the
-number of units at risk \(R^0_{a}(t)\) in that interval at all event
+number of units at risk \(r^0_{a}(t)\) in that interval at all event
 times \(t\). Assuming cancer status was assessed at the end of regular
@@
 & = \sum_i^n \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \\
-R^0_{a} (t)
+r^0_{a} (t)
 & = \sum_i^n \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}.
@@
 1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
+\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{r^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
 \end{cases}\] where \(t_1\) is the first event time.
@@
 & = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}\\
-R^w_{a} (t)
+r^w_{a} (t)
 & = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)}
@@
 & = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
-R_{a} (t)
+r_{a} (t)
 & = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
@@
 1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
+\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{r_{a}(j)}\right) & \text{if } t \ge t_1 \\
 \end{cases}\] where \(t_1\) is the first event time.
@@
 In the full data, the WKM and AWKM estimators are equivalent, and
-identification is achieved under overlap (positivity) and sequential
-ignorability (randomization) assumptions: \[\begin{aligned}
+identification is achieved under positivity and sequential ignorability
+assumptions: \[\begin{aligned}
 Y^*_{a, \bar d = 0} (t')   & \indep A(t) \mid W,\ \bar A(t - 1) = \bar a(t - 1),\ D(t - 1) = 0,\ N(t) = 1\\
@@
 \(\big(\bar A(t), D(t)\big)\) at each time \(t\) is identified. Causal
-identification is not attained when true cancer status \(Y^*(t)\) is not
-known.
+identification is not attainable when true cancer status \(Y^*(t)\) is
+not known.
 
@@
 compatible with our hypothetical causal structure, the AWKM survival
-estimator had small bias compared to the WKM estimator. The bias was
+estimator had a smaller bias than the WKM estimator. The bias was
 smaller when the cumulative incidence of the outcome was low and at
@@
 a real-world context. Using data from two plants participating in the
-UAW-GM Cohort study, we followed \(38\,553\) individuals starting from
-hire to 40 years after hire for incidence of digestive system cancers
+UAW-GM Cohort study, we followed \(26\,182\) individuals starting from
+hire to 35 years after hire for incidence of digestive system cancers
 (colon, rectal, esophageal, or stomach). This duration of follow-up
-spans the vast majority of individuals' working lifetimes. As in the
-simulation, the UAW-GM data were longitudinal data with baseline
+spans a sizable proportion of a usual worker's working lifetime. As in
+the simulation, the UAW-GM data were longitudinal data with baseline
 covariates, time-varying covariates, and a survival outcome.
@@
 and synthetic (Byers 2006; F. Mirer 2003; F. E. Mirer 2010). Straight
-MWFs are hydrocarbon-based fluids whose use became widespread by the
-1920s. They continue to be widely used because of their simple
-formulation. In straight MWFs, hydrocarbons of different lengths are
-mixed together with other additives to attain different properties.
+MWFs are hydrocarbon-based fluids that became widely-used by the 1920s.
+They continue to occupy a large portion of the MWF market due to their
+simple formulation. In straight MWFs, hydrocarbons of different lengths
+are mixed together with other additives to attain different properties.
 Straight MWFs contain polycyclic aromatic hydrocarbons, long known to be
@@
 first introduced in response to rising oil prices. They now make up the
-largest market share of MWFs (Childers 2006). Soluble oils are
-vulnerable to microbial contamination, so the addition of biocides is
-needed. However, their high lubricity makes soluble MWFs the most
-popular fluid type. Synthetic MWFs have the best toxicological profile,
-have no oil, and have a higher resistance to microbial growth. They were
-introduced into the MWF market in the second half of the 20th C., but
-fail to out-perform soluble MWFs in metalworking applications. Soluble
-and synthetic MWFs contain biocides, corrosion inhibitors, and
-chlorinated compounds, some classified as carcinogenic by the IARC (IARC
-1987).
+largest market share of MWFs (Childers 2006). Soluble MWFs are
+vulnerable to microbial contamination, so they contain biocides and
+chlorinated chemicals. Soluble MWFs have carcinogenic potential from
+both their oil components and their additives, but their high lubricity
+makes them the most popular fluid type. Synthetic MWFs have the best
+toxicological profile, have no oil, and have a higher resistance to
+microbial growth. They were introduced into the MWF market in the second
+half of the 20th C., but failed to out-perform soluble MWFs in
+industrial metalworking applications. Synthetic MWFs contain biocides,
+corrosion inhibitors, and chlorinated compounds, some classified as
+carcinogenic by the IARC (IARC 1987).
 
@@
 survival to the start of the registry was a left-filtering process
-possibly in the presence of the HWSE as investigated in the simulations.
-Over the 40 year follow-up period, vital status was obtained through the
+possibly in the presence of the HWSE, as was the case in simulations.
+Over the 35 year follow-up period, vital status was obtained through the
 Social Security Administration, the National Death Index, as well as
@@
 observed and \(a_1\) being exposed in the years exposure was observed.
-Weights were truncated at 1000. Binary exposure is defined to be
-exposure above the median level of exposure to straight, soluble, and
-synthetic MWFs or not. Counterfactual survival under rules \(a_0\) and
-\(a_1\) were estimated using the WKM and AWKM estimators. Baseline
-confounders included race, sex, plant, and year of hire. Time-varying
-confounders included age, cumulative time off, employment status, and
-exposure to the metalworking fluids exposure from the past year. These
-terms were included in the estimation of both the treatment and
-censoring mechanisms, which were estimated with stratification on every
-two years of follow-up. Summary statistics for the full study population
-and the digestive system cancer cases are presented in Table
-\ref{tab:popchar}.
+Weights were truncated at 1000. Exposure was binary and defined to be
+whether there was exposure above the median level of exposure to
+straight, soluble, and synthetic MWFs. Counterfactual survival under
+rules \(a_0\) and \(a_1\) were estimated using the WKM and AWKM
+estimators. Treatment and censoring mechanisms were estimated using
+logistic regression conditional on baseline and time-varying
+confounders. These logistic regressions were estimated with
+stratification by every two years of follow-up. Baseline confounders
+included race, sex, plant, and year of hire. Time-varying confounders
+included age, cumulative time off, employment status, and exposure to
+the metalworking fluids exposure from past years (3 years in the case of
+exposure and 6 years in the case of death due to censoring). Summary
+statistics for the full study population and those who experienced
+digestive system cancer are presented in Table \ref{tab:popchar}.
 
@@
 operates a particular metalworking machine, then the the other workers
-are not able to operate that machine at that time. Instead, they may be
-assigned to assembly tasks, which have lower MWF exposure opportunities.
-That said, since these factories were quite large, there may be
-approximate independence. The consistency assumption is also
+would not be able to operate that machine at that time. Instead, they
+may be assigned to assembly tasks, which have lower MWF exposure
+opportunities. That said, since these factories were quite large, there
+may be approximate independence. The consistency assumption is also
 problematic. The MWFs of interest are complex chemical mixtures whose
-composition changes by design and by nature. Over the last several
-decades, the formulation of MWFs has changed significantly in reaction
-to performance needs and toxicity concerns (F. Mirer 2003; Byers 2006).
-The composition of MWFs also undergoes unintentional changes because of
-the nature of their use: MWFs are often applied in contexts where
-contamination by other substances and microbes is possible and chemical
-changes due to heat and pressure are likely. Indeed, there are
-substantial concerns over the carcinogenicity of the chemical species
-formed in the MWF mixtures that were not originally added (Hidajat et
-al. 2020). Concerns regarding the consistency assumption may be
-abrogated in part by adequate adjustment for secular and factory-level
-characteristics.
-
-Another key assumption meriting discussion is that of conditional
+composition underwent changes by design and by nature of their use. Over
+the last several decades, the formulation of MWFs has changed
+significantly in reaction to performance needs and toxicity concerns (F.
+Mirer 2003; Byers 2006). The composition of MWFs also undergoes
+unintentional changes over the course of their use: MWFs are often
+applied in contexts where contamination by other substances and microbes
+is possible and chemical changes due to heat and pressure are likely. In
+fact, concern over the carcinogenicity of MWFs includes concerns over
+chemical species formed in MWF mixtures that were not originally added
+(Hidajat et al. 2020). Concerns regarding the consistency assumption may
+be abrogated in part by adequate adjustment for secular and
+factory-level characteristics.
+
+Another key assumption meriting discussion is that of sequential
 ignorability. In order to achieve identification, even in the absence of
@@
 deleterious health outcomes. The potential magnitude of this
-uncontrolled confounding may have been bounded, however. The education
-level of the workers in the cohort was homogeneous, and all cohort
+uncontrolled confounding may be bounded, however. Education level among
+workers in the cohort was approximately homogeneous, and all cohort
 members were members of the UAW union, which had uniform procedures in
@@
 \(a_1\) applied to the three MWF types are presented in Figure
-\ref{fig:gm_survival}. The survival curves are more or less overlapping
-under the two exposure rules. Numeric values for the cancer-free
-survival and difference in cancer-free survival are presented in Tables
-\ref{tab:gm_survival} and \ref{tab:gm_differences}. The numeric
-summaries are consistent with the qualitative interpretation of the
-estimated survival curves; for all MWF types, expected survival time
-does not differ substantially across rules \(a_0\) and \(a_1\).
-Nonetheless, reducing exposure to straight and soluble MWFs does result
-in a longer survival time, though the difference is less than a month in
-time.
+\ref{fig:gm_survival}. Surprisingly, the survival curves were more or
+less overlapping under the two exposure rules. Numeric values for the
+cancer-free survival and difference in cancer-free survival are
+presented in Tables \ref{tab:gm_survival} and \ref{tab:gm_differences}.
+The numeric summaries were consistent with the qualitative
+interpretation of the estimated survival curves; expected survival time
+does not differ substantially comparing rules \(a_0\) and \(a_1\)
+applied to all MWF types. Nonetheless, reducing exposure to straight and
+soluble MWFs yielded a longer estimated survival time, though the
+difference was less than a month in time.
 
@@
 Without truncation, they would have been in the order of magnitude of
-\(10^{20}\) or higher. Distributional summaries of the cumulative
+\(10^{20}\) or even higher. Distributional summaries of the cumulative
 weights without truncation are presented in Table \ref{tab:gm_w}. The
 presence of extremely large weights suggests that our observed data were
-inadequate for answering the causal question of interest due to
+inadequate for answering the causal questions of interest due to
 practical violations in overlap (Petersen et al. 2012).
@@
 observed data. Several assumptions used in the simulation study were
-incompatible with what is known about cancer epidemiology. Firstly,
+incompatible with what is known about cancer etiology. Firstly,
 cumulative incidence in the simulations was close to 15\% (or higher)
@@
 cancers are among the most common forms of cancer in the Unite states,
-and in 35 years of follow-up, we were still only able to observe a
-cumulative incidence of less than 1\%. The simulation scenarios suggest
+but over 35 years of follow-up, we were only able to observe a
+cumulative incidence of less than 1\%. The simulation results suggested
 that the bias of the WKM and AWKM estimators is higher when cumulative
-incidence is higher, but when cumulative incidence is low, we rely on
-very few observations to index the risk sets.
+incidence is higher, but when cumulative incidence is low, there is a
+different problem: the reliance on few observations to index the risk
+sets.
 
@@
 effects of MWF exposure may not yet be observable after 35 years of
-follow-up.
+follow-up. As follow-up in this cohort study continues, we will have the
+opportunity to investigate the carcinogenic effects of MWF exposure
+further.
 

### 2021-12-14 reports/01-introduction.Rmd
Revised draft

@@
 The three major classes of MWF are straight, soluble, and synthetic metalworking fluids [@Byers_2006].
-Possible routes of human exposure include absorption through skin, inhalation or aerosols, and ingestion of droplets.
+Possible routes of human exposure include absorption through skin, inhalation of aerosols, and ingestion of droplets.
 
-A central concern in the analysis of occupational cohorts is the potential for the healthy worker survivor effect (HWSE), the phenomenon by which healthy individuals remain at work, while less healthy individuals leave work -- possibly in response to exposure-related health decline.
-In the presence of the HWSE, those with the highest cumulative occupational exposures are also those who are less at risk of disease.
+A central concern in the analysis of longitudinal occupational cohort data is the potential for bias due to the healthy worker survivor effect (HWSE), the phenomenon by which healthy individuals remain at work, while less healthy individuals leave work -- possibly in response to exposure-related health decline.
+In the presence of the HWSE, those with the highest cumulative occupational exposures are also those who are less at risk of disease (more likely to have potential outcome no disease under both exposure and no exposure scenarios).
 Thus, standard measures of association would show an inverse relationship between occupational exposure and poor health outcomes [@Arrighi_1994].
@@
 Previous studies have attempted to assess the presence of the HWSE in observed data by assessing so-called path-specific associations using Cox proportional hazards modeling [@Naimi_2013;@Garcia_2017].
-However, these measures of associations were themselves subject to the confounding structures they sought to characterize.
+However, in those studies, the estimates were themselves subject to the confounding structures they sought to characterize.
 
-If conditional sequential ignorability of exposure and censoring status at each point in follow-up and positivity can be attained given covariate history, then causal methods can be applied to account for the HWSE.
-Past studies have applied causal methods capable of accounting for time-varying confounding affected by past exposure to the study of MWF exposures and cancer mortality outcomes in the UAW-GM Cohort Study [@Garcia_2018;@Izano_2019], but the study of cancer incidence outcomes is further problematized by the incomplete observation of cancer incidence outcomes at every point of follow-up over the study period.
+If conditional sequential ignorability of exposure and censoring status at each point in follow-up and positivity (overlap) can be attained given covariate history, then longitudinal causal methods can be applied to account for the HWSE.
+Past studies have applied causal methods capable of accounting for time-varying confounding affected by past exposure to the study of MWF exposures and cancer mortality outcomes in the UAW-GM Cohort Study [@Garcia_2018;@Izano_2019].
+However, the study of cancer incidence outcomes is further problematized by the incomplete observation of cancer incidence outcomes at every point of follow-up over the study period.
 Nonetheless, we wish to make inferences about the carcinogenicity of MWF exposure over an individual's lifetime starting upon entry into the workforce.
 The UAW-GM Cohort included those hired roughly between 1938 and 1985.
-However, cancer incidence reporting at the Michigan Cancer Registry did not begin until 1985.
-Hence, our observed cohort data is subject to _left filtering_: cancer incidence is the outcome of interest, but before 1985, both cancer incidence status and time of cancer incidence are unknown.
+However, cancer incidence reporting did not begin until 1973.
+Hence, our observed cohort data exhibits _left filtering_: cancer incidence is the outcome of interest, but before 1985, both cancer incidence status and time of cancer incidence are unknown.
 Observation of the complete cancer incidence outcome vector over the study period was conditional on an individual surviving to 1985 cancer-free.
@@
 For each intervention, three survival curves were produced: (1) the true survival curve, (2) the WKM survival curve, and (3) AWKM survival curve.
-Estimator bias was evaluated by comparing the average of 250 estimates of to the average difference in cancer-free survival under the two rules to the true average survival difference when exposure and censoring were controlled deterministically.
+Estimator bias was evaluated by comparing the average of 250 estimates of to the average difference in cancer-free survival under the two rules to the true average difference in survival when exposure and censoring were controlled deterministically.
 
-The present project replicates the simulation and bias analyses presented in Chapter 3 of @Izano_2017_thesis, embeds the problem in the non-parametric structural causal approach of @Pearl_1995, and applies the WKM and AWKM estimators to the estimation of digestive-system cancer-free survival under exposure/censoring rules in the UAW-GM Cohort.
+The present project replicates the simulation and bias analyses presented in Chapter 3 of @Izano_2017_thesis, embeds the problem in the non-parametric structural causal approach of @Pearl_1995, and applies the WKM and AWKM estimators to the estimation of digestive-system cancer-free survival under exposure and no censoring rules in the UAW-GM Cohort.
 The `stremr` package was used to estimate the WKM and AWKM survival curves in both the simulation and the applied analyses [@Sofrygin_2021].

### 2021-12-14 reports/02-methods.Rmd
Revised draft

@@
 The causal model represents hypothetical relationships between variables over time compatible with the theory underlying the HWSE in longitudinal occupational cohort studies.
-At each time point, the effect of cumulative exposure $\bar A(t)$ on cancer incidence $Y^(t)$ is confounded by a path through employment status $N(t)$ and underlying health $H(t)$ as well as the path through past exposure $\bar A(t - 1)$ and vital status $D(t)$.
+At each time point, the effect of cumulative exposure $\bar A(t)$ on cancer incidence $Y^*(t)$ is confounded by the path through employment status $N(t)$ and underlying health $H(t)$ as well as the path through past exposure $\bar A(t - 1)$ and vital status $D(t)$.
 These paths follow straightforward logic: occupational exposure depends upon employment status and past exposure; mortality status is affected by past exposure and cancer history.
@@
 $$X_i(t) = \left(R_i = 0, W_i, S_i, \bar H_i(t), \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y^*_i(t) = \bar Y_i(t) \right).$$
-The bar notation to indicates variable history where $\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t$.
-In the case of exposure, $\bar A_i(t)$ is the indicator of whether unit $i$ was ever exposed through time $t$.
-Note that true cancer status $Y^*(t)$ not observed until $t \ge R$, after the start of the registry.
+In general, we use bar notation to indicate variable history as follows $\bar X_i(t) = \left(X_i(k)\right)_{k = 1}^t$.
+Note that true cancer status $Y^*(t)$ is not observed until $t \ge R$, after the start of the registry.
 Call $X$ the full data, where we have $R = 0$ for all.
-In the observed data $X^\text{obs}$, we cannot assume $R = 0$ for all; susceptibility $S$ and underlying health status $H$ are not known:
+In the observed data $X^\text{obs}$, we cannot assume $R = 0$ for all.
+Additionally, susceptibility $S$ and underlying health status $H$ are not known:
 $$X^\text{obs}_i(t) = \left(R_i, W_i, \bar N_i(t), \bar A_i(t), \bar a_i(t), \bar Y_i(t) \right).$$
@@
 The exogenous variables (errors) $U = \left( U_R, U_W, U_S, U_{H(t)}, U_{N(t)}, U_{A(t)}, U_{D(t)}, U_{Y^*(t)} \right)_{t = 1}^{T}$ are mutually independent.
-Exposure status is a time-varying indicator; let exposure history $\bar A(t)$ be summarized as being ever-exposed or not with $\bar A(t)  = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}$.
+Exposure status is a time-varying indicator, and exposure history is summarized as $\bar A(t)  = \Ind{\sum_{k = 1}^t\Ind{A(k) = 1} > 0}$.
 The outcome of interest is a survival outcome, so $Y^*(t - 1) = 1 \Rightarrow Y^*(t) = 1$.
-The observed outcome $Y(t)$ at time $t$ is a function of true outcome status and the time points delimiting left and right censoring.
+The observed outcome $Y(t)$ at time $t$ is a function of true outcome status, time of left censoring, and time of right censoring.
 An abbreviated directed acyclic graph (DAG) representing the causal relationships encoded in the equations above is presented in Figure \ref{fig:dag}.
@@
 At each time point $t$, the cumulative effect of exposure $\bar A(t)$ on cancer incidence $Y^*(t)$ is confounded by employment status $N(t)$ through the backdoor path $\bar A(t) \leftarrow N(t) \leftarrow H(t) \rightarrow Y^*(t)$.
-In the absence of observed data on health status $H(t)$, an analyst may be tempted to condition on employment status $N(t)$, but doing so would introduce collider bias while blocking the causal path between past exposure $\bar A(t - 1)$ and cancer $Y^*(t)$.
-Furthermore, an analysis starting at an arbitrary time point after the time origin (hire) would be tantamount to conditioning on those still alive at that time, which would also result in both collider bias and the conditioning on nodes on the causal path between the exposure and outcome of interest.
+In the absence of observed data on health status $H(t)$, an analyst may be tempted to conduct an analysis by simply "blocking" or conditioning on employment status $N(t)$, but doing so would introduce collider bias while blocking the causal path between past exposure $\bar A(t - 1)$ and cancer $Y^*(t)$.
+Furthermore, an analysis starting at an arbitrary time point after the time origin (hire) would be tantamount to conditioning on those still alive at that time, which would result in both collider bias and the conditioning on nodes on the causal path between the exposure and the outcome of interest.
 
@@
 
-Five sets of data were generated using these equations to represent five scenarios.
+Five sets of data were generated using these equations, but with different parameters, to represent five scenarios.
 Scenario 1 represents the base case where 10% of workers are susceptible to exposure-related effects, the odds ratio of mortality each additional year following cancer diagnosis is about 1.6, and there is moderate time-varying confounding by health status.
@@
 Under both rules, we prevented censoring by death as if it were intervenable.
-The causal effect was defined by contrasting the survival function $S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}$ under rule $a_1$ to $S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}$ that under rule $a_0$.
+The causal effect was defined by contrasting the survival functions $S_{a_1}(t) = 1 - \E{Y_{a_1}(t)}$ under rule $a_1$ to $S_{a_0}(t) = 1 - \E{Y_{a_0}(t)}$ that under rule $a_0$.
 Note that this causal estimand was defined over _a priori counterfactuals_ not observable in the real world [@Frangakis_2002].
-This approach is standard in epidemiologic studies, however.
+This approach is standard in epidemiologic studies.
 
@@
 Bias was evaluated by comparing estimates of $\psi$ to its true value in 250 simulations per scenario (the original analysis performed 500).
-The true value was calculated by simulating the full data for five hundred thousand individuals (the original analysis used one million) with rules $a_0$ and $a_1$ applied deterministically.
-Estimates of $\psi$ were obtained by first estimating the survival curves $S_a(t)$ using two estimators: the inverse probability weighted Kaplan-Meier estimator (WKM) and the Aalen-filtered WKM (AWKM).
+The true value was calculated by simulating the full data for $500\,000$ individuals (the original analysis used one million) with rules $a_0$ and $a_1$ applied deterministically.
+Estimates of $\psi$ were obtained by estimating the survival curves $S_a(t)$ using two estimators: the inverse probability weighted Kaplan-Meier estimator (WKM) and the Aalen-filtered WKM (AWKM).
 These survival estimators are detailed in the following section.
@@
 First, we review the estimator of @Xie_2005, an extension of the KM estimator where units are weighted by the inverse probability of treatment.
-The standard KM estimator requires counting up the number of cases $c^0_{a}(t)$ that occurred in interval $(t - 1, t]$ and the number of units at risk $R^0_{a}(t)$ in that interval at all event times $t$.
+The standard KM estimator requires counting up the number of cases $c^0_{a}(t)$ that occurred in interval $(t - 1, t]$ and the number of units at risk $r^0_{a}(t)$ in that interval at all event times $t$.
 Assuming cancer status was assessed at the end of regular intervals $t = 1, \ldots, K$, we have:
@@
 1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{R^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
+\prod_{j \le t} \left(1 - \frac{c^0_{a}(j)}{r^0_{a}(j)}\right) & \text{if } t \ge t_1 \\
 \end{cases}$$
@@
 1 & \text{if } t < t_1 \\
-\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{R_{a}(j)}\right) & \text{if } t \ge t_1 \\
+\prod_{j \le t} \left(1 - \frac{c_{a}(j)}{r_{a}(j)}\right) & \text{if } t \ge t_1 \\
 \end{cases}$$
@@
 
-In the full data, the WKM and AWKM estimators are equivalent, and identification is achieved under overlap (positivity) and sequential ignorability (randomization) assumptions:
+In the full data, the WKM and AWKM estimators are equivalent, and identification is achieved under positivity and sequential ignorability assumptions:
 $$\begin{aligned}
@@
 Thus, the causal effect of the joint intervention on $\big(\bar A(t), D(t)\big)$ at each time $t$ is identified.
-Causal identification is not attained when true cancer status $Y^*(t)$ is not known.
+Causal identification is not attainable when true cancer status $Y^*(t)$ is not known.
 

### 2021-12-14 reports/04-gm.Rmd
Revised draft

@@
 
-In the simulation study, we showed that under several scenarios compatible with our hypothetical causal structure, the AWKM survival estimator had small bias compared to the WKM estimator.
+In the simulation study, we showed that under several scenarios compatible with our hypothetical causal structure, the AWKM survival estimator had a smaller bias than the WKM estimator.
 The bias was smaller when the cumulative incidence of the outcome was low and at later follow-up time points.
 Next, we estimated cancer-free survival in a real-world context.
-Using data from two plants participating in the UAW-GM Cohort study, we followed $38\,553$ individuals starting from hire to 40 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
-This duration of follow-up spans the vast majority of individuals' working lifetimes.
+Using data from two plants participating in the UAW-GM Cohort study, we followed $26\,182$ individuals starting from hire to 35 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
+This duration of follow-up spans a sizable proportion of a usual worker's working lifetime.
 As in the simulation, the UAW-GM data were longitudinal data with baseline covariates, time-varying covariates, and a survival outcome.
@@
 The exposures of interest were MWF of three types: straight, soluble, and synthetic [@Byers_2006; @Mirer_2003; @Mirer_2010].
-Straight MWFs are hydrocarbon-based fluids whose use became widespread by the 1920s.
-They continue to be widely used because of their simple formulation.
+Straight MWFs are hydrocarbon-based fluids that became widely-used by the 1920s.
+They continue to occupy a large portion of the MWF market due to their simple formulation.
 In straight MWFs, hydrocarbons of different lengths are mixed together with other additives to attain different properties.
@@
 They now make up the largest market share of MWFs [@Childers_2006].
-Soluble oils are vulnerable to microbial contamination, so the addition of biocides is needed.
-However, their high lubricity makes soluble MWFs the most popular fluid type.
+Soluble MWFs are vulnerable to microbial contamination, so they contain biocides and chlorinated chemicals.
+Soluble MWFs have carcinogenic potential from both their oil components and their additives, but their high lubricity makes them the most popular fluid type.
 Synthetic MWFs have the best toxicological profile, have no oil, and have a higher resistance to microbial growth.
-They were introduced into the MWF market in the second half of the 20th C., but fail to out-perform soluble MWFs in metalworking applications.
-Soluble and synthetic MWFs contain biocides, corrosion inhibitors, and chlorinated compounds, some classified as carcinogenic by the IARC [@IARC_1987].
+They were introduced into the MWF market in the second half of the 20th C., but failed to out-perform soluble MWFs in industrial metalworking applications.
+Synthetic MWFs contain biocides, corrosion inhibitors, and chlorinated compounds, some classified as carcinogenic by the IARC [@IARC_1987].
 
@@
 The cohort is comprised of individuals hired between 1938 and 1975.
-Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE as investigated in the simulations.
-Over the 40 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
+Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE, as was the case in simulations.
+Over the 35 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
 The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ being exposed with 75\% chance in the years exposure was observed and $a_1$ being exposed in the years exposure was observed.
 Weights were truncated at 1000.
-Binary exposure is defined to be exposure above the median level of exposure to straight, soluble, and synthetic MWFs or not.
+Exposure was binary and defined to be whether there was exposure above the median level of exposure to straight, soluble, and synthetic MWFs.
 Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.
+Treatment and censoring mechanisms were estimated using logistic regression conditional on baseline and time-varying confounders.
+These logistic regressions were estimated with stratification by every two years of follow-up.
 Baseline confounders included race, sex, plant, and year of hire.
-Time-varying confounders included age, cumulative time off, employment status, and exposure to the metalworking fluids exposure from the past year.
-These terms were included in the estimation of both the treatment and censoring mechanisms, which were estimated with stratification on every two years of follow-up.
-Summary statistics for the full study population and the digestive system cancer cases are presented in Table \ref{tab:popchar}.
+Time-varying confounders included age, cumulative time off, employment status, and exposure to the metalworking fluids exposure from past years (3 years in the case of exposure and 6 years in the case of death due to censoring).
+Summary statistics for the full study population and those who experienced digestive system cancer are presented in Table \ref{tab:popchar}.
 
@@
 The no-interference assumption may be problematized by the fact that there were a finite number of job types in the factory setting.
-If one worker operates a particular metalworking machine, then the the other workers are not able to operate that machine at that time.
+If one worker operates a particular metalworking machine, then the the other workers would not be able to operate that machine at that time.
 Instead, they may be assigned to assembly tasks, which have lower MWF exposure opportunities.
@@
 The consistency assumption is also problematic.
-The MWFs of interest are complex chemical mixtures whose composition changes by design and by nature.
+The MWFs of interest are complex chemical mixtures whose composition underwent changes by design and by nature of their use.
 Over the last several decades, the formulation of MWFs has changed significantly in reaction to performance needs and toxicity concerns [@Mirer_2003; @Byers_2006].
-The composition of MWFs also undergoes unintentional changes because of the nature of their use: MWFs are often applied in contexts where contamination by other substances and microbes is possible and chemical changes due to heat and pressure are likely.
-Indeed, there are substantial concerns over the carcinogenicity of the chemical species formed in the MWF mixtures that were not originally added [@Hidajat_2020].
+The composition of MWFs also undergoes unintentional changes over the course of their use: MWFs are often applied in contexts where contamination by other substances and microbes is possible and chemical changes due to heat and pressure are likely.
+In fact, concern over the carcinogenicity of MWFs includes concerns over chemical species formed in MWF mixtures that were not originally added [@Hidajat_2020].
 Concerns regarding the consistency assumption may be abrogated in part by adequate adjustment for secular and factory-level characteristics.
 
-Another key assumption meriting discussion is that of conditional ignorability.
+Another key assumption meriting discussion is that of sequential ignorability.
 In order to achieve identification, even in the absence of left filtering, we need to have conditionally ignorable future exposure status and ignorable future censoring status at each time point given past data.
@@
 In particular, workers may be assigned to certain tasks based on their specific skills and knowledge, which may be associated with structural privileges that confer a lower risk of deleterious health outcomes.
-The potential magnitude of this uncontrolled confounding may have been bounded, however.
-The education level of the workers in the cohort was homogeneous, and all cohort members were members of the UAW union, which had uniform procedures in place for equitable access to training, wages, and career advancement [@Harbison_1950;@Barnard_2005].
+The potential magnitude of this uncontrolled confounding may be bounded, however.
+Education level among workers in the cohort was approximately homogeneous, and all cohort members were members of the UAW union, which had uniform procedures in place for equitable access to training, wages, and career advancement [@Harbison_1950;@Barnard_2005].
 The presence of UAW policies support the assertion that given time since hire, job types (and therefore exposures) were randomly allocated.
@@
 Estimated digestive system cancer-free curves under rules $a_0$ and $a_1$ applied to the three MWF types are presented in Figure \ref{fig:gm_survival}.
-The survival curves are more or less overlapping under the two exposure rules.
+Surprisingly, the survival curves were more or less overlapping under the two exposure rules.
 Numeric values for the cancer-free survival and difference in cancer-free survival are presented in Tables \ref{tab:gm_survival} and \ref{tab:gm_differences}.
-The numeric summaries are consistent with the qualitative interpretation of the estimated survival curves; for all MWF types, expected survival time does not differ substantially across rules $a_0$ and $a_1$.
-Nonetheless, reducing exposure to straight and soluble MWFs does result in a longer survival time, though the difference is less than a month in time.
+The numeric summaries were consistent with the qualitative interpretation of the estimated survival curves; expected survival time does not differ substantially comparing rules $a_0$ and $a_1$ applied to all MWF types.
+Nonetheless, reducing exposure to straight and soluble MWFs yielded a longer estimated survival time, though the difference was less than a month in time.
 
@@
 The distribution of the weights was very skewed.
-Without truncation, they would have been in the order of magnitude of $10^{20}$ or higher.
+Without truncation, they would have been in the order of magnitude of $10^{20}$ or even higher.
 Distributional summaries of the cumulative weights without truncation are presented in Table \ref{tab:gm_w}.
-The presence of extremely large weights suggests that our observed data were inadequate for answering the causal question of interest due to practical violations in overlap [@Petersen_2012].
+The presence of extremely large weights suggests that our observed data were inadequate for answering the causal questions of interest due to practical violations in overlap [@Petersen_2012].
 

### 2021-12-14 reports/05-discussion.Rmd
Revised draft

@@
 The simulation permitted the evaluation of the estimators in clean, well-behaved scenarios, but the same luxury was not possible when using observed data.
-Several assumptions used in the simulation study were incompatible with what is known about cancer epidemiology.
+Several assumptions used in the simulation study were incompatible with what is known about cancer etiology.
 Firstly, cumulative incidence in the simulations was close to 15\% (or higher) over a 20-year follow-up.
 This is an extraordinarily high risk of cancer, especially because most workers in the automotive manufacturing industry start their careers at a fairly young age.
-Digestive system cancers are among the most common forms of cancer in the Unite states, and in 35 years of follow-up, we were still only able to observe a cumulative incidence of less than 1\%.
-The simulation scenarios suggest that the bias of the WKM and AWKM estimators is higher when cumulative incidence is higher, but when cumulative incidence is low, we rely on very few observations to index the risk sets.
+Digestive system cancers are among the most common forms of cancer in the Unite states, but over 35 years of follow-up, we were only able to observe a cumulative incidence of less than 1\%.
+The simulation results suggested that the bias of the WKM and AWKM estimators is higher when cumulative incidence is higher, but when cumulative incidence is low, there is a different problem: the reliance on few observations to index the risk sets.
 
@@
 The true causal effects of MWF exposure may not yet be observable after 35 years of follow-up.
+As follow-up in this cohort study continues, we will have the opportunity to investigate the carcinogenic effects of MWF exposure further.

### 2022-01-13 paper.tex
Add github repo link
Prepare to run

@@
 presented in Chapter 3 of Izano (2017), embeds the problem in the
-non-parametric structural causal approach of Pearl (1995), and applies
-the WKM and AWKM estimators to the estimation of digestive-system
-cancer-free survival under exposure and no censoring rules in the UAW-GM
-Cohort. The \texttt{stremr} package was used to estimate the WKM and
-AWKM survival curves in both the simulation and the applied analyses
-(Sofrygin, van der Laan, and Neugebauer 2021).
+non-parametric structural causal approach of (\textbf{Pearl\_1995?}),
+and applies the WKM and AWKM estimators to the estimation of
+digestive-system cancer-free survival under exposure and no censoring
+rules in the UAW-GM Cohort. The \texttt{stremr} package was used to
+estimate the WKM and AWKM survival curves in both the simulation and the
+applied analyses (Sofrygin, van der Laan, and Neugebauer 2021). All code
+necessary for replicating the analyses presented here may be found on
+\href{https://github.com/kvntchn/gm-delayed-entry.git}{GitHub/kvntchn/gm-delayed-entry}.
+Note that running the script for the applied analyses will require
+additional permissions.
 
@@
 Note that this causal estimand was defined over \emph{a priori
-counterfactuals} not observable in the real world (Frangakis and Rubin
-2002). This approach is standard in epidemiologic studies.
+counterfactuals} not observable in the real world
+(\textbf{Frangakis\_2002?}). This approach is standard in epidemiologic
+studies.
 
@@
 \begin{center}
-\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/results.pdf}
+\includegraphics{/Users/kevinchen/eisen/gm-delayed-entry/reports/resources/results.pdf}
 \end{center}
@@
 UAW-GM Cohort study, we followed \(26\,182\) individuals starting from
-hire to 35 years after hire for incidence of digestive system cancers
-(colon, rectal, esophageal, or stomach). This duration of follow-up
-spans a sizable proportion of a usual worker's working lifetime. As in
-the simulation, the UAW-GM data were longitudinal data with baseline
-covariates, time-varying covariates, and a survival outcome.
+hire to 65 years after hire for incidence of digestive system cancers
+(colon, rectal, esophageal, or stomach). As in the simulation, the
+UAW-GM data were longitudinal data with baseline covariates,
+time-varying covariates, and a survival outcome.
 
@@
 Straight MWFs contain polycyclic aromatic hydrocarbons, long known to be
-carcinogenic (IARC 1973). Soluble oils are water-based oil emulsions
-first introduced in response to rising oil prices. They now make up the
-largest market share of MWFs (Childers 2006). Soluble MWFs are
-vulnerable to microbial contamination, so they contain biocides and
-chlorinated chemicals. Soluble MWFs have carcinogenic potential from
-both their oil components and their additives, but their high lubricity
-makes them the most popular fluid type. Synthetic MWFs have the best
-toxicological profile, have no oil, and have a higher resistance to
-microbial growth. They were introduced into the MWF market in the second
-half of the 20th C., but failed to out-perform soluble MWFs in
-industrial metalworking applications. Synthetic MWFs contain biocides,
-corrosion inhibitors, and chlorinated compounds, some classified as
-carcinogenic by the IARC (IARC 1987).
+carcinogenic (\emph{IARC Monographs on the Evaluation of Carcinogenic
+Risk of the Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons
+and Heterocyclic Compounds} 1973). Soluble oils are water-based oil
+emulsions first introduced in response to rising oil prices. They now
+make up the largest market share of MWFs (\textbf{Childers\_2006?}).
+Soluble MWFs are vulnerable to microbial contamination, so they contain
+biocides and chlorinated chemicals. Soluble MWFs have carcinogenic
+potential from both their oil components and their additives, but their
+high lubricity makes them the most popular fluid type. Synthetic MWFs
+have the best toxicological profile, have no oil, and have a higher
+resistance to microbial growth. They were introduced into the MWF market
+in the second half of the 20th C., but failed to out-perform soluble
+MWFs in industrial metalworking applications. Synthetic MWFs contain
+biocides, corrosion inhibitors, and chlorinated compounds, some
+classified as carcinogenic by the IARC (\textbf{IARC\_1987?}).
 
@@
 possibly in the presence of the HWSE, as was the case in simulations.
-Over the 35 year follow-up period, vital status was obtained through the
+Over the 65 year follow-up period, vital status was obtained through the
 Social Security Administration, the National Death Index, as well as
@@
 applied analysis were different than those in the simulation study:
-\(a_0\) being exposed with 75\% chance in the years exposure was
-observed and \(a_1\) being exposed in the years exposure was observed.
+\(a_0\) having cumulative exposure of more than 0.05
+mg/m\textsuperscript{3} years and \(a_1\) having no cumulative exposure.
 Weights were truncated at 1000. Exposure was binary and defined to be
@@
 \begin{center}
-\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/gm_results.pdf}
+\includegraphics{/Users/kevinchen/eisen/gm-delayed-entry/reports/resources/gm_results.pdf}
 \end{center}
@@
 \centering
-\caption{Estimated cancer-free survival time over 35-year follow-up.} 
+\caption{Estimated cancer-free survival time over 65-year follow-up.} 
 \label{tab:gm_survival}
-\begin{tabular}{llrrr}
+\begin{tabular}{llrrrr}
   \toprule
-Rule & Estimator & Straight & Soluble & Synthetic \\ 
+Rule & Estimator & Straight & Soluble & Synthetic & Any \\ 
   \midrule
-$a_0$ & WKM & 29.9606 & 29.9605 & 29.9626 \\ 
-  $a_0$ & AWKM & 29.9337 & 29.9398 & 29.9443 \\ 
+$a_0$ & WKM & 55.9808 & 56.0093 & 56.2051 & 55.8072 \\ 
+  $a_0$ & AWKM & 55.8864 & 55.8952 & 56.1300 & 55.6712 \\ 
    \midrule
-$a_1$ & WKM & 29.9600 & 29.9584 & 29.9648 \\ 
-  $a_1$ & AWKM & 29.9325 & 29.9360 & 29.9479 \\ 
+$a_1$ & WKM & 56.2258 & 56.2760 & 56.1323 &  \\ 
+  $a_1$ & AWKM & 56.0953 & 56.1824 & 56.0066 &  \\ 
    \bottomrule
@@
 \centering
-\caption{Estimated difference in average cancer-free survival time over 35-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\% to $a_0$ never exposed.} 
+\caption{Estimated difference in average cancer-free survival time over 65-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\% to $a_0$ never exposed.} 
 \label{tab:gm_differences}
-\begin{tabular}{lrrr}
+\begin{tabular}{lrrrr}
   \toprule
-Estimator & Straight & Soluble & Synthetic \\ 
+Estimator & Straight & Soluble & Synthetic & Any \\ 
   \midrule
-WKM & -0.0006 & -0.0021 & 0.0022 \\ 
-  AWKM & -0.0012 & -0.0039 & 0.0037 \\ 
+WKM & 0.2449 & 0.2667 & -0.0727 &  \\ 
+  AWKM & 0.2089 & 0.2872 & -0.1233 &  \\ 
    \bottomrule
@@
 \centering
-\caption{Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 35$ years since hire for each metalworking fluid type and exposure rule.} 
+\caption{Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 65$ years since hire for each metalworking fluid type and exposure rule.} 
 \label{tab:gm_w}
@@
   \midrule
-Straight & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Soluble & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Synthetic & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Straight & $a_0$ &  35 & 0.00 & 2.25 & 4.71 & $9.7 \times 10^{16}$ & 4622.00 & $7.3 \times 10^{20}$ \\ 
-   & $a_1$ &  35 & 0.00 & 2.70 & 13.40 & $1.3 \times 10^{18}$ & 22142.45 & $9.8 \times 10^{21}$ \\ 
-  Soluble & $a_0$ &  35 & 0.00 & 4.04 & 858.96 & $5.2 \times 10^{15}$ & 74610.19 & $2.3 \times 10^{19}$ \\ 
-   & $a_1$ &  35 & 0.00 & 158.56 & 6685.12 & $2.3 \times 10^{17}$ & 1227858.13 & $1.7 \times 10^{21}$ \\ 
-  Synthetic & $a_0$ &  35 & 0.00 & 1.02 & 1.25 & $3.7 \times 10^{19}$ & 8.85 & $3.2 \times 10^{23}$ \\ 
-   & $a_1$ &  35 & 0.00 & 1.02 & 1.36 & $2.1 \times 10^{21}$ & 22.63 & $1.8 \times 10^{25}$ \\ 
+Straight & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Soluble & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Synthetic & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Any & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Straight & $a_0$ &  57 &   0 & 4.6 & 5.6 &  93 & $2 \times 10^{2}$ & $3.9 \times 10^{2}$ \\ 
+   & $a_1$ &  57 &   0 &   0 &   0 & 2.4 & 5.2 & 5.8 \\ 
+  Soluble & $a_0$ &  57 &   0 & 3.9 & $1.5 \times 10^{2}$ & $1.7 \times 10^{2}$ & $3.1 \times 10^{2}$ & $3.8 \times 10^{2}$ \\ 
+   & $a_1$ &  57 &   0 &   0 &   0 &  41 &   0 & $3.7 \times 10^{2}$ \\ 
+  Synthetic & $a_0$ &  57 &   0 & 2.6 & 3.2 &  97 & 3.4 & $8.5 \times 10^{2}$ \\ 
+   & $a_1$ &  57 &   0 & 2.5 & 2.9 & 2.4 & 3.3 & 3.6 \\ 
+  Any & $a_0$ &  57 &   0 & 3.6 &  15 & $1.4 \times 10^{2}$ & $3 \times 10^{2}$ & $4.1 \times 10^{2}$ \\ 
+   & $a_1$ &  57 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
    \bottomrule
@@
 \begin{center}
-\includegraphics{/Users/kevinchen/Documents/2021 Fall/256 - Causal Inference/256-final/reports/resources/gm_weights.pdf}
+\includegraphics{/Users/kevinchen/eisen/gm-delayed-entry/reports/resources/gm_weights.pdf}
 \end{center}
@@
 
-\leavevmode\hypertarget{ref-Childers_2006}{}%
-Childers, Jean. 2006. {``The Chemistry of Metalworking Fluids.''} In
-\emph{Metalworking Fluids}. CRC Press.
-
 \leavevmode\hypertarget{ref-Eisen_2001}{}%
@@
 Journal of Industrial Medicine} 22 (6): 809--24.
-
-\leavevmode\hypertarget{ref-Frangakis_2002}{}%
-Frangakis, Constantine E, and Donald B Rubin. 2002. {``Principal
-Stratification in Causal Inference.''} \emph{Biometrics} 58 (1): 21--29.
 
@@
 \leavevmode\hypertarget{ref-IARC_1973}{}%
-IARC. 1973. \emph{IARC Monographs on the Evaluation of Carcinogenic Risk
-of the Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons and
-Heterocyclic Compounds}. Vol. 3. World Health Organization International
-Agency for Research on Cancer.
-
-\leavevmode\hypertarget{ref-IARC_1987}{}%
----------. 1987. \emph{IARC Monographs on the Evaluation of the
-Carcinogenic Risk of Chemicals to Humans. Overall Evaluations of
-Carcinogenicity: An Updating of IARC Monographs, Volumes 1 to 42}.
-\emph{World Health Organization}. Vol. 7. World Health Organization
+\emph{IARC Monographs on the Evaluation of Carcinogenic Risk of the
+Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons and
+Heterocyclic Compounds}. 1973. Vol. 3. World Health Organization
 International Agency for Research on Cancer.
@@
 
-\leavevmode\hypertarget{ref-Pearl_1995}{}%
-Pearl, Judea. 1995. {``Causal Diagrams for Empirical Research.''}
-\emph{Biometrika} 82 (4): 669--88.
-
 \leavevmode\hypertarget{ref-Petersen_2012}{}%

### 2022-01-13 reports/04-gm.Rmd
Prepare to run

@@
 Next, we estimated cancer-free survival in a real-world context.
-Using data from two plants participating in the UAW-GM Cohort study, we followed $26\,182$ individuals starting from hire to 35 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
-This duration of follow-up spans a sizable proportion of a usual worker's working lifetime.
+Using data from two plants participating in the UAW-GM Cohort study, we followed $26\,182$ individuals starting from hire to 65 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
 As in the simulation, the UAW-GM data were longitudinal data with baseline covariates, time-varying covariates, and a survival outcome.
@@
 Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE, as was the case in simulations.
-Over the 35 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
-The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ being exposed with 75\% chance in the years exposure was observed and $a_1$ being exposed in the years exposure was observed.
+Over the 65 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
+The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ having cumulative exposure of more than 0.05 mg/m^3^ years and $a_1$ having no cumulative exposure.
 Weights were truncated at 1000.
@@
 gm_survival.tab <- dcast(
-	melt(gm.surv[t <= 30],
+	melt(gm.surv[t <= 65],
 			 measure.vars = c("WKM", "AWKM"),
@@
 			 value.name = "Survival")[,.(
-		Survival = sum(Survival)
+		Survival = sum(Survival, na.rm = T)
 	), .(MWF = mwf, Rule = rule, Estimator)],
@@
 		Soluble   = Soluble[2] - Soluble[1],
-		Synthetic = Synthetic[2] - Synthetic[1]
+		Synthetic = Synthetic[2] - Synthetic[1],
+		Any = Any[2] - Any[1]
 	), .(Estimator)]
 
+gm_ci.tab <- dcast(
+	melt(gm.surv[t == 55],
+			 measure.vars = c("WKM", "AWKM"),
+			 variable.name = "Estimator",
+			 value.name = "Survival")[,.(
+		"Cumulative incidence" = 1 - Survival
+	), .(MWF = mwf, Rule = rule, Estimator)],
+	... ~ MWF,
+	value.var = "Cumulative incidence"
+)
+
+gm_cir.tab <- gm_ci.tab[,.(
+		Straight  = Straight[2]/Straight[1],
+		Soluble   = Soluble[2]/Soluble[1],
+		Synthetic = Synthetic[2]/Synthetic[1],
+		Any = Any[2]/Any[1]
+	), .(Estimator)]
+
+pander(gm_cir.tab)
 ```
@@
 print(xtable(gm_survival.tab,
-			 caption = "Estimated cancer-free survival time over 35-year follow-up.",
+			 caption = "Estimated cancer-free survival time over 65-year follow-up.",
 			 label = "tab:gm_survival", digits = 4),
@@
 print(xtable(gm_differences.tab,
-			 caption = "Estimated difference in average cancer-free survival time over 35-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\\% to $a_0$ never exposed.",
+			 caption = "Estimated difference in average cancer-free survival time over 65-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\\% to $a_0$ never exposed.",
 			 label = "tab:gm_differences", digits = 4),
@@
 	gm_w.tab[t == 1,],
-	gm_w.tab[t == 35,]))
+	gm_w.tab[t == 57,]))
 
@@
 gm_w.small_tab$mwf <- rep(as.vector(sapply(
-	c("Straight", "Soluble", "Synthetic"), function(x) {
+	c("Straight", "Soluble", "Synthetic", "Any"), function(x) {
 	c(x, "")})), 2)
@@
 	gm_w.small_tab,
-	caption = "Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 35$ years since hire for each metalworking fluid type and exposure rule.",
+	caption = "Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 65$ years since hire for each metalworking fluid type and exposure rule.",
 	label = "tab:gm_w",
-	display = c("s", "s", "s", "d", "f", "f", "f", "g", "f", "g")),
+	display = c("s", "s", "s", "d", "g", "g", "g", "g", "g", "g")),
 	math.style.exponents = TRUE,

### 2022-01-13 scripts/00-hello.R

@@ -16,6 +16,7 @@ exposure.lag <- 15
 # Load full data
 if (!"cohort_analytic" %in% ls()) {
 	cohort_analytic <- box_read(880479268725)
+	cohort_analytic <- cohort_analytic[,-"exposure.lag"]
 	cohort_analytic[,(c("straight", "soluble", "synthetic")) := lapply(
 		list(straight, soluble, synthetic), function(x) {
 			return(shift(x, get("exposure.lag", envir = .GlobalEnv), 0))

### 2022-01-13 scripts/04-application.R

@@ -13,93 +13,122 @@ library(survival)
 library(boxr); box_auth()
 if (!"cohort_analytic" %in% ls()) {
 	source(here::here("scripts", "00-hello.R"))
+	message("Note. Exposure lagged ", exposure.lag, " years")
 }
 
 # Get package for running estimators
 # devtools::install_github('osofr/stremr')
 library(stremr)
 
-years_fu <- 35
-gm.dt <- cohort_analytic[year >= year(yin) & year < year(yin) + years_fu & (year(yin) <= 1995 - years_fu | year <= 1994)]
+years_fu <- 55
+gm.dt <- cohort_analytic[year >= year(yin) & year < (year(yin) + years_fu) & (
+	year(yin) <= (1995 + exposure.lag - years_fu) | year <= (1994 + exposure.lag))]
 gm.dt <- gm.dt[plant %in% 1:2]
-gm.dt[, canc := ifelse(canc_corec == 1 | canc_es == 1 | canc_st == 1, 1, 
-										ifelse(canc_corec == 2 | canc_es == 2 | canc_st == 2, 2, 0))]
+# gm.dt <- gm.dt[sex == "M"]
+gm.dt[, `:=`(
+	canc = ifelse(
+		canc_corec == 1 | canc_es == 1 | canc_st == 1, 1,
+		ifelse(canc_corec == 2 | canc_es == 2 | canc_st == 2, 2, 0))
+)]
+# gm.dt[, `:=`(canc = canc_nhl)]
+# gm.dt[, canc := canc_first]
+
+message(nrow(gm.dt[canc == 1]), " cases in ", n_distinct(gm.dt$studyno), " subjects")
+
+gm.dt[, `:=`(
+	other_canc = ifelse(canc_first == 1 | canc_first == 2 & canc == 0, 1, 0)
+)]
+
+# How much are people exposed?
+gm.dt[year >= year(yin) + 15 & year <= year(yout) + 15,.(
+	studyno,
+	straight = straight > 0.05,
+	soluble = soluble > 0.05,
+	synthetic = synthetic > 0.05
+)][,.(straight = mean(straight),
+			soluble = mean(soluble),
+			synthetic = mean(synthetic)), studyno][,-1] %>% sapply(mean)
+
+mwf.quantiles <- gm.dt[canc == 1,.(
[…]

### 2022-01-13 scripts/05-application-results.R

@@ -28,12 +28,14 @@ gm.surv <- rbindlist(list(
 	rbindlist(list(str_a0[[2]], str_a1[[2]]), idcol = "rule"),
 	rbindlist(list(sol_a0[[2]], sol_a1[[2]]), idcol = "rule"),
 	rbindlist(list(syn_a0[[2]], syn_a1[[2]]), idcol = "rule")
+	# rbindlist(list(any_a0[[2]], any_a1[[2]]), idcol = "rule")
 ), idcol = "mwf")
 
 gm.w <- rbindlist(list(
 	rbindlist(list(str_a0[[1]], str_a1[[1]]), idcol = "rule"),
 	rbindlist(list(sol_a0[[1]], sol_a1[[1]]), idcol = "rule"),
 	rbindlist(list(syn_a0[[1]], syn_a1[[1]]), idcol = "rule")
+	# rbindlist(list(any_a0[[1]], any_a1[[1]]), idcol = "rule")
 ), idcol = "mwf")
 
 

### 2022-01-13 scripts/04-application.R
lapply as loop

@@ -261,7 +261,7 @@ get_estimates_gm <- function(
 # 	geom_step() +
 # 	theme_bw()
 
-mwf <- "Synthetic"
+# mwf <- "Synthetic"
 # Point estimate ###
 if (!is.null(mwf)) {
 	message("\n", mwf, ", a = 0")
@@ -293,8 +293,8 @@ if (!is.null(mwf)) {
 	message("BS started at ", start, "\n")
 	# Progress bar
 	pb <- txtProgressBar(min = 0, max = B, style = 3)
-	bs <- lapply(1:B, function(b = 1) {
-		
+	bs <- list()
+	for (b in 1:B) {
 		bs.dt <- merge(
 			who.mcmc[[b]],
 			gm.dt[studyno %in% who.mcmc[[b]]$studyno,
@@ -318,9 +318,8 @@ if (!is.null(mwf)) {
 		# Set progressbar
 		setTxtProgressBar(pb, b)
 		
-		return(list(a0 = a0, a1 = a1))
-	})
-	
-	saveRDS(a0, here("resources", paste0(tolower(mwf), "_bs_gm", ".rds")))
+		bs[[b]] <- list(a0 = a0, a1 = a1)
+	}
+	saveRDS(bs, here("resources", paste0(tolower(mwf), "_bs_gm", ".rds")))
 }
 

### 2022-01-18 scripts/04-application.R
BS for straight and soluble

@@ -10,8 +10,8 @@ library(magrittr)
 library(data.table)
 library(survival)
 
-library(boxr); box_auth()
 if (!"cohort_analytic" %in% ls()) {
+	library(boxr); box_auth()
 	source(here::here("scripts", "00-hello.R"))
 	message("Note. Exposure lagged ", exposure.lag, " years")
 }
@@ -269,7 +269,7 @@ if (!is.null(mwf)) {
 												 dt = copy(gm.dt),
 												 mwf = mwf)
 	saveRDS(a0, here("resources", paste0(tolower(mwf), "0_gm", ".rds")))
-
+	
 	message("\n", mwf, ", a = 1")
 	a1 <- get_estimates_gm(a = 1,
 												 dt = copy(gm.dt),
@@ -303,6 +303,7 @@ if (!is.null(mwf)) {
 							"Straight", "Soluble", "Synthetic",
 							"cum_Straight", "cum_Soluble", "cum_Synthetic", "Any", "N"),
 						with = F],
+			by = "studyno",
 			all.x = T, allow.cartesian = T
 		)
 		bs.dt[,`:=`(studyno = id,

### 2022-01-19 reports/04-gm.Rmd
soluble BS; get ready for sensitivity analysis with different distribution of R

@@
 		Soluble   = Soluble[2] - Soluble[1],
-		Synthetic = Synthetic[2] - Synthetic[1],
-		Any = Any[2] - Any[1]
+		Synthetic = Synthetic[2] - Synthetic[1]
+		# Any = Any[2] - Any[1]
 	), .(Estimator)]
@@
 		Soluble   = Soluble[2]/Soluble[1],
-		Synthetic = Synthetic[2]/Synthetic[1],
-		Any = Any[2]/Any[1]
+		Synthetic = Synthetic[2]/Synthetic[1]
+		# Any = Any[2]/Any[1]
 	), .(Estimator)]
 
-pander(gm_cir.tab)
+# pander(gm_differences.tab); pander(gm_cir.tab)
 ```

### 2022-01-19 scripts/01-simulation.R

@@ -20,7 +20,8 @@ sim_data <- function(
 	d = NULL,
 	a = NULL,
 	long = T,
-	param = sim_param) {
+	param = sim_param,
+	R.rdist = function(x) {runif(x, 0, 20)}) {
 	
 	env.current <- environment()
 	
@@ -33,7 +34,7 @@ sim_data <- function(
 				runif(n)
 			}))
 	
-	R <- runif(n, 0, 20)
+	R <- R.rdist(n)
 	W <- rbinom(n, 1, param$p_W)
 	S <- rbinom(n, 1, param$p_S)
 	H.k <- H.1 <- rbinom(n, 1, param$p_H)
@@ -164,7 +165,7 @@ sim_data <- function(
 		
 		ldt[, obs := as.integer(t + 1 >= R), id]
 		ldt[,Y_obs := {
-			if (sum(Y[1:floor(R[1])]) > 0) {
+			if (sum(Y[1:min(floor(R[1]), K)]) > 0) {
 				Y_obs <- rep(0, .N)
 			} else {
 				Y_obs <- Y

### 2022-01-19 scripts/02-analysis.R

@@ -23,11 +23,12 @@ get_estimates <- function(
 	g_a = "A ~ W + shiftA",
 	g_d = "D ~ W + barA",
 	stratify = list(D = paste0("t == ", 1:20),
-									A = paste0("t == ", 1:20))
+									A = paste0("t == ", 1:20)),
+	R.rdist = function(x) {runif(x, 0, 20)}
 ) {
 	
 	# message("Simulating...")
-	sim.dt <- sim_data(scenario, a = a)
+	sim.dt <- sim_data(scenario, a = a, R.rdist = R.rdist)
 	sim.dt[,`:=`(
 		shiftA = shift(A, 1, 0),
 		barA = shift(as.integer(cumsum(A) > 0), 1, 0)
@@ -89,8 +90,8 @@ get_estimates <- function(
 # 	geom_step() +
 # 	theme_bw()
 
-get_truth <- function(scenario, a, n = 5e5) {
-	dt <- sim_data(scenario, n = n, a = a, d = 0, long = F)
+get_truth <- function(scenario, a, n = 5e5, R.rdist = function(x) {runif(x, 0, 20)}) {
+	dt <- sim_data(scenario, n = n, a = a, d = 0, long = F, R.rdist = R.rdist)
 	km <- survfit(Surv(last_t, status) ~ 1, data = dt[,.(last_t, status)])
 	return(data.table(
 		t = 1:20,
@@ -101,18 +102,18 @@ get_truth <- function(scenario, a, n = 5e5) {
 # saveRDS(truth_a0, here("resources", "truth_a0.rds"))
 # truth_a1 <- lapply(1:5, get_truth, a = 1, n = 5e4)
 # saveRDS(truth_a1, here("resources", "truth_a1.rds"))
-
-M <- 250
-pb <- txtProgressBar(min = 0, max = M, style = 3)
-message("\nScenario ", scenario, ", a = 0")
-a0 <- lapply(1:M, function(i) {
-	setTxtProgressBar(pb, i)
-	return(get_estimates(scenario))})
-saveRDS(a0, here("resources", paste0("a0_scenario", scenario, ".rds")))
-
-pb <- txtProgressBar(min = 0, max = M, style = 3)
-message("\nScenario ", scenario, ", a = 1")
-a1 <- lapply(1:M, function(i) {
-	setTxtProgressBar(pb, i)
-	return(get_estimates(scenario, a = 1))})
[…]

### 2022-01-19 scripts/04-application.R

@@ -261,34 +261,32 @@ get_estimates_gm <- function(
 # 	geom_step() +
 # 	theme_bw()
 
-# mwf <- "Synthetic"
+# mwf <- "Straight"
 # Point estimate ###
-if (!is.null(mwf)) {
+if ("mwf" %in% ls()) {
 	message("\n", mwf, ", a = 0")
 	a0 <- get_estimates_gm(a = 0,
 												 dt = copy(gm.dt),
 												 mwf = mwf)
 	saveRDS(a0, here("resources", paste0(tolower(mwf), "0_gm", ".rds")))
-
+	
 	message("\n", mwf, ", a = 1")
 	a1 <- get_estimates_gm(a = 1,
 												 dt = copy(gm.dt),
 												 mwf = mwf)
 	saveRDS(a1, here("resources", paste0(tolower(mwf), "1_gm", ".rds")))
-}
-
-# Bootstrap ###
-studyno <- unique(gm.dt$studyno)
-B <- 500
-# set.seed(1240)
-# who.mcmc <- lapply(1:B, function(b = 1) {
-# 	who.mcmc <- data.table(studyno = sample(studyno, replace = T))
-# 	who.mcmc$id <- 1:nrow(who.mcmc)
-# 	return(who.mcmc)
-# 	})
-# saveRDS(who.mcmc, here("resources", "who_mcmc.rds"))
-who.mcmc <- readRDS(here("resources", "who_mcmc.rds"))
-if (!is.null(mwf)) {
+	
+	# Bootstrap ###
+	studyno <- unique(gm.dt$studyno)
+	B <- 500
+	# set.seed(1240)
+	# who.mcmc <- lapply(1:B, function(b = 1) {
+	# 	who.mcmc <- data.table(studyno = sample(studyno, replace = T))
+	# 	who.mcmc$id <- 1:nrow(who.mcmc)
+	# 	return(who.mcmc)
+	# 	})
+	# saveRDS(who.mcmc, here("resources", "who_mcmc.rds"))
+	who.mcmc <- readRDS(here("resources", "who_mcmc.rds"))
 	start <- Sys.time()
 	message("BS started at ", start, "\n")
 	# Progress bar

### 2022-01-19 scripts/05-application-results.R

@@ -70,24 +70,35 @@ gm_w.tab <- dcast(gm.w[,.(
 	value.var = "summary"
 )
 
-# gm.surv %>% melt(
-# 	measure.vars = c("WKM", "AWKM"),
-# 	variable.name = "Estimator",
-# 	value.name = "Survival"
-# ) %>% ggplot(aes(
-# 	x = t, y = Survival,
-# 	lty = Estimator,
-# 	color = rule
-# )) + geom_step() + facet_grid(mwf ~ .) +
-# 	labs(
-# 		y = "Cancer-free survival",
-# 		x = "Years since hire") +
-# 	theme_bw() + theme(
-# 		legend.title = element_blank(),
-# 		legend.position = 'bottom'
-# 	) -> gm.surv.ggplot
-# 
-# gm.surv.ggplot
+gm.surv$rule <- factor(
+	gm.surv$rule,
+	unique(gm.surv$rule),
+	c("Observed exposure", "No exposure")
+)
+gm.surv[mwf == "Straight"] %>% melt(
+	measure.vars = c("WKM", "AWKM"),
+	variable.name = "Estimator",
+	value.name = "Survival"
+) %>% ggplot(aes(
+	x = t, y = Survival,
+	lty = Estimator,
+	color = rule
+)) + geom_step() +
+	# facet_grid(mwf ~ .) +
+	labs(
+		lty = "Estimator",
+		color = "Intervention",
+		y = "Digestive cancer-free survival",
+		x = "Years since hire") +
+	theme_bw() + theme(
+		legend.title = element_text(size = 10),
+		legend.position = 'bottom',
+		legend.margin = margin(l = 0, r = 0, b = 0, t = 0, unit='cm'),
+		legend.box.margin = margin(l = 0, r = 0, b = -0.1, t = -0.1, unit='cm'),
+		legend.box = "vertical"
+	) -> gm.surv.ggplot
+
+gm.surv.ggplot
 # 
 # gm_w.tab[estimator == "WKM"] %>% ggplot(
 # 	aes(x = t,
@@ -108,11 +119,11 @@ gm_w.tab <- dcast(gm.w[,.(
 # 
 # gm.w.ggplot
 # 
-# tikz(here("reports/resources", "gm_results.tex"),
-# 		 width = 4.5, height = 5, standAlone = T)
-# gm.surv.ggplot
-# dev.off()
-# lualatex("gm_results\\.tex", here("reports/resources"))
[…]

### 2022-01-19 scripts/06-sensitivity.R

@@ -1,0 +1,40 @@
+# 06-sensitivity.R
+# Sensitivity analyses
+# Kevin Chen
+# December 18, 2021
+
+library(here)
+source(here("scripts", "02-analysis.R"))
+# source(here("scripts", "04-application.R"))
+# time_to_registry <- gm.dt[canc != 2,.(R = c(1973, 1973, 1985)[plant[1]] - yin.gm[1]), studyno]$R
+# saveRDS(time_to_registry, here("resources", "time_to_registry.rds"))
+time_to_registry <- readRDS(here("resources", "time_to_registry.rds"))
+time_to_registry[time_to_registry <= 0] <- 0
+# hist(time_to_registry)
+# summary(gm.dt[,.(yin.gm[1]), studyno]$V1)
+
+# # Get truth ####
+# truth_a0 <- lapply(1:5, get_truth, a = 0, n = 5e4,
+# 									 R.rdist = function(x) {sample(time_to_registry, x, T)})
+# saveRDS(truth_a0, here("resources/sensitivity", "truth_a0.rds"))
+# truth_a1 <- lapply(1:5, get_truth, a = 1, n = 5e4,
+# 									 R.rdist = function(x) {sample(time_to_registry, x, T)})
+# saveRDS(truth_a1, here("resources/sensitivity", "truth_a1.rds"))
+
+# Get simulation results ####
+M <- 250
+pb <- txtProgressBar(min = 0, max = M, style = 3)
+message("\nScenario ", scenario, ", a = 0")
+a0 <- lapply(1:M, function(i) {
+	setTxtProgressBar(pb, i)
+	return(get_estimates(scenario,
+									 R.rdist = function(x) {sample(time_to_registry, x, T)}))})
+saveRDS(a0, here("resources/sensitivity", paste0("a0_scenario", scenario, ".rds")))
+
+pb <- txtProgressBar(min = 0, max = M, style = 3)
+message("\nScenario ", scenario, ", a = 1")
+a1 <- lapply(1:M, function(i) {
+	setTxtProgressBar(pb, i)
+	return(get_estimates(scenario, a = 1,
+									 R.rdist = function(x) {sample(time_to_registry, x, T)}))})
+saveRDS(a1, here("resources/sensitivity", paste0("a1_scenario", scenario, ".rds")))

### 2022-03-04 paper.tex
SER

--- 2021-12-14 paper.tex
@@
 AWKM survival curves in both the simulation and the applied analyses
-(Sofrygin, van der Laan, and Neugebauer 2021).
+(Sofrygin, van der Laan, and Neugebauer 2021). All code necessary for
+replicating the analyses presented here may be found on
+\href{https://github.com/kvntchn/gm-delayed-entry.git}{GitHub/kvntchn/gm-delayed-entry}.
+Note that running the script for the applied analyses will require
+additional permissions.
 
@@
 \end{table}
+\begin{table}[H]
+\centering
+\caption{True cancer-free 20-year risk and estimator averages over 250 replicates.} 
+\label{tab:survival}
+\begin{tabular}{llrrrrr}
+  \toprule
+Rule & Estimator & Scenario 1 & Scenario 2 & Scenario 3 & Scenario 4 & Scenario 5 \\ 
+  \midrule
+Rule $a_0$ & Truth & 0.12 & 0.12 & 0.12 & 0.25 & 0.26 \\ 
+  Rule $a_0$ & WKM & 0.07 & 0.07 & 0.07 & 0.15 & 0.15 \\ 
+  Rule $a_0$ & AWKM & 0.10 & 0.10 & 0.10 & 0.23 & 0.23 \\ 
+   \midrule
+Rule $a_1$ & Truth & 0.15 & 0.15 & 0.15 & 0.29 & 0.31 \\ 
+  Rule $a_1$ & WKM & 0.08 & 0.08 & 0.08 & 0.18 & 0.18 \\ 
+  Rule $a_1$ & AWKM & 0.13 & 0.13 & 0.13 & 0.27 & 0.27 \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
 
@@
 UAW-GM Cohort study, we followed \(26\,182\) individuals starting from
-hire to 35 years after hire for incidence of digestive system cancers
-(colon, rectal, esophageal, or stomach). This duration of follow-up
-spans a sizable proportion of a usual worker's working lifetime. As in
-the simulation, the UAW-GM data were longitudinal data with baseline
-covariates, time-varying covariates, and a survival outcome.
+hire to 55 years after hire for incidence of digestive system cancers
+(colon, rectal, esophageal, or stomach). As in the simulation, the
+UAW-GM data were longitudinal data with baseline covariates,
+time-varying covariates, and a survival outcome.
 
@@
 Straight MWFs contain polycyclic aromatic hydrocarbons, long known to be
-carcinogenic (IARC 1973). Soluble oils are water-based oil emulsions
-first introduced in response to rising oil prices. They now make up the
-largest market share of MWFs (Childers 2006). Soluble MWFs are
-vulnerable to microbial contamination, so they contain biocides and
+carcinogenic (\emph{IARC Monographs on the Evaluation of Carcinogenic
+Risk of the Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons
+and Heterocyclic Compounds} 1973). Soluble oils are water-based oil
+emulsions first introduced in response to rising oil prices. They now
+make up the largest market share of MWFs (Childers 2006). Soluble MWFs
+are vulnerable to microbial contamination, so they contain biocides and
 chlorinated chemicals. Soluble MWFs have carcinogenic potential from
@@
 recorded cancer incidence cases starting on January 1, 1973. The cohort
-is comprised of individuals hired between 1938 and 1975. Cancer-free
+is comprised of individuals hired between 1938 and 1985. Cancer-free
 survival to the start of the registry was a left-filtering process
 possibly in the presence of the HWSE, as was the case in simulations.
-Over the 35 year follow-up period, vital status was obtained through the
+Over the 55-year follow-up period, vital status was obtained through the
 Social Security Administration, the National Death Index, as well as
@@
 applied analysis were different than those in the simulation study:
-\(a_0\) being exposed with 75\% chance in the years exposure was
-observed and \(a_1\) being exposed in the years exposure was observed.
-Weights were truncated at 1000. Exposure was binary and defined to be
-whether there was exposure above the median level of exposure to
-straight, soluble, and synthetic MWFs. Counterfactual survival under
-rules \(a_0\) and \(a_1\) were estimated using the WKM and AWKM
-estimators. Treatment and censoring mechanisms were estimated using
-logistic regression conditional on baseline and time-varying
-confounders. These logistic regressions were estimated with
+\(a_0\) having cumulative exposure greater than the lower threshold as
+observed and \(a_1\) having no exposure. Weights were truncated at 500.
+Counterfactual survival under rules \(a_0\) and \(a_1\) were estimated
+using the WKM and AWKM estimators. Treatment and censoring mechanisms
+were estimated using logistic regression conditional on baseline and
+time-varying confounders. These logistic regressions were estimated with
 stratification by every two years of follow-up. Baseline confounders
 included race, sex, plant, and year of hire. Time-varying confounders
-included age, cumulative time off, employment status, and exposure to
-the metalworking fluids exposure from past years (3 years in the case of
-exposure and 6 years in the case of death due to censoring). Summary
-statistics for the full study population and those who experienced
-digestive system cancer are presented in Table \ref{tab:popchar}.
+included age, cumulative time off, employment status, and cumulative
+exposure to the metalworking fluids exposure up to through previous
+year. Summary statistics for the full study population and those who
+experienced digestive system cancer are presented in Table
+\ref{tab:popchar}.
 
@@
 \(a_1\) applied to the three MWF types are presented in Figure
-\ref{fig:gm_survival}. Surprisingly, the survival curves were more or
-less overlapping under the two exposure rules. Numeric values for the
-cancer-free survival and difference in cancer-free survival are
-presented in Tables \ref{tab:gm_survival} and \ref{tab:gm_differences}.
-The numeric summaries were consistent with the qualitative
-interpretation of the estimated survival curves; expected survival time
-does not differ substantially comparing rules \(a_0\) and \(a_1\)
-applied to all MWF types. Nonetheless, reducing exposure to straight and
-soluble MWFs yielded a longer estimated survival time, though the
-difference was less than a month in time.
+\ref{fig:gm_survival}. Numeric values for the cancer-free survival and
+difference in cancer-free survival are presented in Tables
+\ref{tab:gm_survival} and \ref{tab:gm_differences}. The numeric
+summaries were consistent with the qualitative interpretation of the
+estimated survival curves. Nonetheless, reducing exposure to straight
+and soluble MWFs yielded a longer expected digestive-free survival time.
 
@@
 \centering
-\caption{Estimated cancer-free survival time over 35-year follow-up.} 
+\caption{Estimated cancer-free survival time over 55-year follow-up.} 
 \label{tab:gm_survival}
@@
   \midrule
-$a_0$ & WKM & 29.9606 & 29.9605 & 29.9626 \\ 
-  $a_0$ & AWKM & 29.9337 & 29.9398 & 29.9443 \\ 
+As observed & WKM & 53.8388 & 54.0067 & 54.1434 \\ 
+  As observed & AWKM & 53.7402 & 53.9111 & 54.0855 \\ 
    \midrule
-$a_1$ & WKM & 29.9600 & 29.9584 & 29.9648 \\ 
-  $a_1$ & AWKM & 29.9325 & 29.9360 & 29.9479 \\ 
+No exposure & WKM & 54.1002 & 54.2562 & 53.9552 \\ 
+  No exposure & AWKM & 54.0099 & 54.1731 & 53.8377 \\ 
    \bottomrule
@@
 \centering
-\caption{Estimated difference in average cancer-free survival time over 35-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\% to $a_0$ never exposed.} 
+\caption{Estimated difference in average cancer-free survival time over 55-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\% to $a_0$ never exposed.} 
 \label{tab:gm_differences}
@@
   \midrule
-WKM & -0.0006 & -0.0021 & 0.0022 \\ 
-  AWKM & -0.0012 & -0.0039 & 0.0037 \\ 
+WKM & 0.2615 & 0.2495 & -0.1883 \\ 
+  AWKM & 0.2697 & 0.2620 & -0.2478 \\ 
    \bottomrule
@@
 
-Figure \ref{fig:gm_weights} presents the median cumulative weight
-applied years since hire with ribbons showing the minimum and maximum
-weight. The overlap in the distribution of weights under the two rules
-for synthetic MWF exposure suggests that the model for the treatment and
-censoring mechanisms were inadequate in distinguishing the units of
-analysis by their probability of following a certain exposure rule or of
-remaining alive. The distribution of the weights was very skewed.
-Without truncation, they would have been in the order of magnitude of
-\(10^{20}\) or even higher. Distributional summaries of the cumulative
-weights without truncation are presented in Table \ref{tab:gm_w}. The
-presence of extremely large weights suggests that our observed data were
-inadequate for answering the causal questions of interest due to
-practical violations in overlap (Petersen et al. 2012).
+Distributional summaries of the cumulative weights without truncation
+are presented in Table \ref{tab:gm_w}. The presence of extremely large
+weights suggests that our observed data were inadequate for answering
+the causal questions of interest due to practical violations in overlap
+(Petersen et al. 2012).
 
@@
 \centering
-\caption{Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 35$ years since hire for each metalworking fluid type and exposure rule.} 
+\caption{Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 55$ years since hire for each metalworking fluid type and exposure rule.} 
 \label{tab:gm_w}
@@
   \midrule
-Straight & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Soluble & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Synthetic & $a_0$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-   & $a_1$ &   1 & 1.00 & 1.00 & 1.00 &   1 & 1.00 &   1 \\ 
-  Straight & $a_0$ &  35 & 0.00 & 2.25 & 4.71 & $9.7 \times 10^{16}$ & 4622.00 & $7.3 \times 10^{20}$ \\ 
-   & $a_1$ &  35 & 0.00 & 2.70 & 13.40 & $1.3 \times 10^{18}$ & 22142.45 & $9.8 \times 10^{21}$ \\ 
-  Soluble & $a_0$ &  35 & 0.00 & 4.04 & 858.96 & $5.2 \times 10^{15}$ & 74610.19 & $2.3 \times 10^{19}$ \\ 
-   & $a_1$ &  35 & 0.00 & 158.56 & 6685.12 & $2.3 \times 10^{17}$ & 1227858.13 & $1.7 \times 10^{21}$ \\ 
-  Synthetic & $a_0$ &  35 & 0.00 & 1.02 & 1.25 & $3.7 \times 10^{19}$ & 8.85 & $3.2 \times 10^{23}$ \\ 
-   & $a_1$ &  35 & 0.00 & 1.02 & 1.36 & $2.1 \times 10^{21}$ & 22.63 & $1.8 \times 10^{25}$ \\ 
+Straight & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Soluble & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Synthetic & $a_0$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+   & $a_1$ &   1 &   1 &   1 &   1 &   1 &   1 &   1 \\ 
+  Straight & $a_0$ &  55 &   0 & 5.5 & 9.9 &  51 &  36 & $2.4 \times 10^{3}$ \\ 
+   & $a_1$ &  55 &   0 &   0 &   0 & 3.6 & 5.1 & $1.4 \times 10^{2}$ \\ 
+  Soluble & $a_0$ &  55 &   0 & 4.2 & 5.9 &  52 &  22 & $6 \times 10^{3}$ \\ 
+   & $a_1$ &  55 &   0 &   0 &   0 & 5.5 &   0 & $1.7 \times 10^{3}$ \\ 
+  Synthetic & $a_0$ &  55 &   0 & 3.2 & 5.6 &  34 &  18 & $2.8 \times 10^{3}$ \\ 
+   & $a_1$ &  55 &   0 &   0 & 2.9 & 3.5 & 4.3 & $1 \times 10^{2}$ \\ 
    \bottomrule
@@
 
+\leavevmode\hypertarget{ref-IARC_1987}{}%
+IARC. 1987. \emph{IARC Monographs on the Evaluation of the Carcinogenic
+Risk of Chemicals to Humans. Overall Evaluations of Carcinogenicity: An
+Updating of IARC Monographs, Volumes 1 to 42}. \emph{World Health
+Organization}. Vol. 7. World Health Organization International Agency
+for Research on Cancer.
+
 \leavevmode\hypertarget{ref-IARC_1973}{}%
-IARC. 1973. \emph{IARC Monographs on the Evaluation of Carcinogenic Risk
-of the Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons and
-Heterocyclic Compounds}. Vol. 3. World Health Organization International
-Agency for Research on Cancer.
-
-\leavevmode\hypertarget{ref-IARC_1987}{}%
----------. 1987. \emph{IARC Monographs on the Evaluation of the
-Carcinogenic Risk of Chemicals to Humans. Overall Evaluations of
-Carcinogenicity: An Updating of IARC Monographs, Volumes 1 to 42}.
-\emph{World Health Organization}. Vol. 7. World Health Organization
+\emph{IARC Monographs on the Evaluation of Carcinogenic Risk of the
+Chemical to Man: Certain Polycyclic Aromatic Hydrocarbons and
+Heterocyclic Compounds}. 1973. Vol. 3. World Health Organization
 International Agency for Research on Cancer.

### 2022-03-04 reports/03-results.Rmd
SER

@@
 sim_results <- readRDS(here("reports/resources", "sim_results.rds"))
+risk.tab <- dcast(
+	sim_results[t == max(t),.(
+		Risk = 1 - Survival
+	), .(Rule = rule, scenario, Estimator)],
+	... ~ scenario,
+	value.var = "Risk"
+)
+
+setorder(risk.tab, Rule, Estimator)
+
 survival.tab <- dcast(
@@
 	floating = T)
+
+print(xtable(risk.tab,
+			 caption = "True cancer-free 20-year risk and estimator averages over 250 replicates.",
+			 label = "tab:survival"),
+			hline.after = c(-1,0,3, nrow(survival.tab)),
+			floating = T)
 ```

### 2022-03-04 reports/04-gm.Rmd
SER

@@
 Next, we estimated cancer-free survival in a real-world context.
-Using data from two plants participating in the UAW-GM Cohort study, we followed $26\,182$ individuals starting from hire to 65 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
+Using data from two plants participating in the UAW-GM Cohort study, we followed $26\,182$ individuals starting from hire to 55 years after hire for incidence of digestive system cancers (colon, rectal, esophageal, or stomach).
 As in the simulation, the UAW-GM data were longitudinal data with baseline covariates, time-varying covariates, and a survival outcome.
@@
 Cancer incidence was obtained by linkage to Surveillance, Epidemiology, and End Results (SEER), which recorded cancer incidence cases starting on January 1, 1973.
-The cohort is comprised of individuals hired between 1938 and 1975.
+The cohort is comprised of individuals hired between 1938 and 1985.
 Cancer-free survival to the start of the registry was a left-filtering process possibly in the presence of the HWSE, as was the case in simulations.
-Over the 65 year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
-The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ having cumulative exposure of more than 0.05 mg/m^3^ years and $a_1$ having no cumulative exposure.
-Weights were truncated at 1000.
-Exposure was binary and defined to be whether there was exposure above the median level of exposure to straight, soluble, and synthetic MWFs.
+Over the 55-year follow-up period, vital status was obtained through the Social Security Administration, the National Death Index, as well as records provided by the UAW.
+The exposure rules of interest in the applied analysis were different than those in the simulation study: $a_0$ having cumulative exposure greater than the lower threshold as observed and $a_1$ having no exposure.
+Weights were truncated at 500.
 Counterfactual survival under rules $a_0$ and $a_1$ were estimated using the WKM and AWKM estimators.
@@
 Baseline confounders included race, sex, plant, and year of hire.
-Time-varying confounders included age, cumulative time off, employment status, and exposure to the metalworking fluids exposure from past years (3 years in the case of exposure and 6 years in the case of death due to censoring).
+Time-varying confounders included age, cumulative time off, employment status, and cumulative exposure to the metalworking fluids exposure up to through previous year.
 Summary statistics for the full study population and those who experienced digestive system cancer are presented in Table \ref{tab:popchar}.
@@
 gm_survival.tab <- dcast(
-	melt(gm.surv[t <= 65],
+	melt(gm.surv[t <= 55],
 			 measure.vars = c("WKM", "AWKM"),
@@
 Estimated digestive system cancer-free curves under rules $a_0$ and $a_1$ applied to the three MWF types are presented in Figure \ref{fig:gm_survival}.
-Surprisingly, the survival curves were more or less overlapping under the two exposure rules.
 Numeric values for the cancer-free survival and difference in cancer-free survival are presented in Tables \ref{tab:gm_survival} and \ref{tab:gm_differences}.
-The numeric summaries were consistent with the qualitative interpretation of the estimated survival curves; expected survival time does not differ substantially comparing rules $a_0$ and $a_1$ applied to all MWF types.
-Nonetheless, reducing exposure to straight and soluble MWFs yielded a longer estimated survival time, though the difference was less than a month in time.
+The numeric summaries were consistent with the qualitative interpretation of the estimated survival curves.
+Nonetheless, reducing exposure to straight and soluble MWFs yielded a longer expected digestive-free survival time.
 
@@
 print(xtable(gm_survival.tab,
-			 caption = "Estimated cancer-free survival time over 65-year follow-up.",
+			 caption = "Estimated cancer-free survival time over 55-year follow-up.",
 			 label = "tab:gm_survival", digits = 4),
@@
 print(xtable(gm_differences.tab,
-			 caption = "Estimated difference in average cancer-free survival time over 65-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\\% to $a_0$ never exposed.",
+			 caption = "Estimated difference in average cancer-free survival time over 55-year follow-up comparing rule $a_1$ exposed above the median level of exposure with probability 1\\% to $a_0$ never exposed.",
 			 label = "tab:gm_differences", digits = 4),
@@
 
-Figure \ref{fig:gm_weights} presents the median cumulative weight applied years since hire with ribbons showing the minimum and maximum weight.
-The overlap in the distribution of weights under the two rules for synthetic MWF exposure suggests that the model for the treatment and censoring mechanisms were inadequate in distinguishing the units of analysis by their probability of following a certain exposure rule or of remaining alive.
+<!-- Figure \ref{fig:gm_weights} presents the median cumulative weight applied years since hire with ribbons showing the minimum and maximum weight.
 The distribution of the weights was very skewed.
 Without truncation, they would have been in the order of magnitude of $10^{20}$ or even higher.
+-->
 Distributional summaries of the cumulative weights without truncation are presented in Table \ref{tab:gm_w}.
@@
 	gm_w.tab[t == 1,],
-	gm_w.tab[t == 57,]))
+	gm_w.tab[t == 55,]))
 
@@
 gm_w.small_tab$mwf <- rep(as.vector(sapply(
-	c("Straight", "Soluble", "Synthetic", "Any"), function(x) {
+	c("Straight", "Soluble", "Synthetic"), function(x) {
 	c(x, "")})), 2)
@@
 	gm_w.small_tab,
-	caption = "Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 65$ years since hire for each metalworking fluid type and exposure rule.",
+	caption = "Summary statistics for the cumulative weights used for the WKM estimator at $t = 1$ and $t = 55$ years since hire for each metalworking fluid type and exposure rule.",
 	label = "tab:gm_w",

### 2022-03-04 reports/resources/gm_results_1-2.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:30:07
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,186.91);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,186.91);
\end{scope}
\begin{scope}
\path[clip] ( 35.37,125.79) rectangle (306.77,181.41);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 35.37,125.79) rectangle (306.77,181.41);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,136.24) --
	(306.77,136.24);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,153.30) --
	(306.77,153.30);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,170.35) --
	(306.77,170.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.18,125.79) --
	( 67.18,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (132.11,125.79) --
	(132.11,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.04,125.79) --
	(197.04,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.97,125.79) --
	(261.97,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,127.71) --
	(306.77,127.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,144.77) --
	(306.77,144.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,161.82) --
	(306.77,161.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,178.88) --
	(306.77,178.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.65,125.79) --
	( 99.65,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (164.57,125.79) --
	(164.57,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50,125.79) --
	(229.50,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.43,125.79) --
	(294.43,181.41);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,178.88) --
	( 73.67,178.88) --
	( 73.67,178.88) --
	( 86.66,178.88) --
	( 86.66,177.42) --
	( 99.65,177.42) --
	( 99.65,175.66) --
	(112.63,175.66) --
	(112.63,173.73) --
	(125.62,173.73) --
	(125.62,171.48) --
	(138.60,171.48) --
	(138.60,169.54) --
	(151.59,169.54) --
	(151.59,167.29) --
	(164.57,167.29) --
	(164.57,164.91) --
	(177.56,164.91) --
	(177.56,162.59) --
	(190.55,162.59) --
	(190.55,160.59) --
	(203.53,160.59) --
	(203.53,158.58) --
	(216.52,158.58) --
	(216.52,156.31) --
	(229.50,156.31) --
	(229.50,154.16) --
	(242.49,154.16) --
	(242.49,152.19) --
	(255.47,152.19) --
	(255.47,150.14) --
	(268.46,150.14) --
	(268.46,148.15) --
	(281.44,148.15) --
	(281.44,146.17) --
	(294.43,146.17) --
	(294.43,139.11);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,178.88) --
	( 73.67,178.88) --
	( 73.67,178.88) --
	( 86.66,178.88) --
	( 86.66,176.64) --
	( 99.65,176.64) --
	( 99.65,174.04) --
	(112.63,174.04) --
	(112.63,171.22) --
	(125.62,171.22) --
	(125.62,168.60) --
	(138.60,168.60) --
	(138.60,165.71) --
	(151.59,165.71) --
	(151.59,162.66) --
	(164.57,162.66) --
	(164.57,159.97) --
	(177.56,159.97) --
	(177.56,157.30) --
	(190.55,157.30) --
	(190.55,154.58) --
	(203.53,154.58) --
	(203.53,151.87) --
	(216.52,151.87) --
	(216.52,149.49) --
	(229.50,149.49) --
	(229.50,147.01) --
	(242.49,147.01) --
	(242.49,144.69) --
	(255.47,144.69) --
	(255.47,142.13) --
	(268.46,142.13) --
	(268.46,139.83) --
	(281.44,139.83) --
	(281.44,137.60) --
	(294.43,137.60) --
	(294.43,129.17);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,178.70) --
	( 73.67,178.70) --
	( 73.67,178.41) --
	( 86.66,178.41) --
	( 86.66,177.98) --
	( 99.65,177.98) --
	( 99.65,177.45) --
	(112.63,177.45) --
	(112.63,176.80) --
	(125.62,176.80) --
	(125.62,176.04) --
	(138.60,176.04) --
	(138.60,175.17) --
	(151.59,175.17) --
	(151.59,174.19) --
	(164.57,174.19) --
	(164.57,173.08) --
	(177.56,173.08) --
	(177.56,171.86) --
	(190.55,171.86) --
	(190.55,170.54) --
	(203.53,170.54) --
	(203.53,169.13) --
	(216.52,169.13) --
	(216.52,167.61) --
	(229.50,167.61) --
	(229.50,166.02) --
	(242.49,166.02) --
	(242.49,164.31) --
	(255.47,164.31) --
	(255.47,162.50) --
	(268.46,162.50) --
	(268.46,160.61) --
	(281.44,160.61) --
	(281.44,158.62) --
	(294.43,158.62) --
	(294.43,156.56);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,178.63) --
	( 73.67,178.63) --
	( 73.67,178.25) --
	( 86.66,178.25) --
	( 86.66,177.71) --
	( 99.65,177.71) --
	( 99.65,177.04) --
	(112.63,177.04) --
	(112.63,176.23) --
	(125.62,176.23) --
	(125.62,175.28) --
	(138.60,175.28) --
	(138.60,174.20) --
	(151.59,174.20) --
	(151.59,172.99) --
	(164.57,172.99) --
	(164.57,171.63) --
	(177.56,171.63) --
	(177.56,170.13) --
	(190.55,170.13) --
	(190.55,168.53) --
	(203.53,168.53) --
	(203.53,166.82) --
	(216.52,166.82) --
	(216.52,165.00) --
	(229.50,165.00) --
	(229.50,163.02) --
	(242.49,163.02) --
	(242.49,160.91) --
	(255.47,160.91) --
	(255.47,158.70) --
	(268.46,158.70) --
	(268.46,156.33) --
	(281.44,156.33) --
	(281.44,153.95) --
	(294.43,153.95) --
	(294.43,151.48);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,177.69) --
	( 73.67,177.69) --
	( 73.67,176.25) --
	( 86.66,176.25) --
	( 86.66,174.54) --
	( 99.65,174.54) --
	( 99.65,172.79) --
	(112.63,172.79) --
	(112.63,170.93) --
	(125.62,170.93) --
	(125.62,169.05) --
	(138.60,169.05) --
	(138.60,167.15) --
	(151.59,167.15) --
	(151.59,165.20) --
	(164.57,165.20) --
	(164.57,163.23) --
	(177.56,163.23) --
	(177.56,161.24) --
	(190.55,161.24) --
	(190.55,159.26) --
	(203.53,159.26) --
	(203.53,157.29) --
	(216.52,157.29) --
	(216.52,155.32) --
	(229.50,155.32) --
	(229.50,153.40) --
	(242.49,153.40) --
	(242.49,151.46) --
	(255.47,151.46) --
	(255.47,149.52) --
	(268.46,149.52) --
	(268.46,147.60) --
	(281.44,147.60) --
	(281.44,145.70) --
	(294.43,145.70) --
	(294.43,143.72);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,178.88) --
	( 60.69,178.88) --
	( 60.69,177.20) --
	( 73.67,177.20) --
	( 73.67,175.34) --
	( 86.66,175.34) --
	( 86.66,173.17) --
	( 99.65,173.17) --
	( 99.65,170.94) --
	(112.63,170.94) --
	(112.63,168.65) --
	(125.62,168.65) --
	(125.62,166.31) --
	(138.60,166.31) --
	(138.60,163.95) --
	(151.59,163.95) --
	(151.59,161.57) --
	(164.57,161.57) --
	(164.57,159.16) --
	(177.56,159.16) --
	(177.56,156.72) --
	(190.55,156.72) --
	(190.55,154.33) --
	(203.53,154.33) --
	(203.53,151.98) --
	(216.52,151.98) --
	(216.52,149.64) --
	(229.50,149.64) --
	(229.50,147.27) --
	(242.49,147.27) --
	(242.49,144.90) --
	(255.47,144.90) --
	(255.47,142.55) --
	(268.46,142.55) --
	(268.46,140.18) --
	(281.44,140.18) --
	(281.44,137.92) --
	(294.43,137.92) --
	(294.43,135.58);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37,125.79) rectangle (306.77,181.41);
\end{scope}
\begin{scope}
\path[clip] ( 35.37, 64.67) rectangle (306.77,120.29);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 35.37, 64.67) rectangle (306.77,120.29);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 75.12) --
	(306.77, 75.12);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 92.18) --
	(306.77, 92.18);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,109.23) --
	(306.77,109.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.18, 64.67) --
	( 67.18,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (132.11, 64.67) --
	(132.11,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.04, 64.67) --
	(197.04,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.97, 64.67) --
	(261.97,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.59) --
	(306.77, 66.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 83.65) --
	(306.77, 83.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,100.70) --
	(306.77,100.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,117.76) --
	(306.77,117.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.65, 64.67) --
	( 99.65,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (164.57, 64.67) --
	(164.57,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50, 64.67) --
	(229.50,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.43, 64.67) --
	(294.43,120.29);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,117.76) --
	( 73.67,117.76) --
	( 73.67,117.76) --
	( 86.66,117.76) --
	( 86.66,116.20) --
	( 99.65,116.20) --
	( 99.65,114.52) --
	(112.63,114.52) --
	(112.63,112.66) --
	(125.62,112.66) --
	(125.62,110.66) --
	(138.60,110.66) --
	(138.60,108.53) --
	(151.59,108.53) --
	(151.59,106.28) --
	(164.57,106.28) --
	(164.57,104.13) --
	(177.56,104.13) --
	(177.56,101.96) --
	(190.55,101.96) --
	(190.55, 99.89) --
	(203.53, 99.89) --
	(203.53, 97.67) --
	(216.52, 97.67) --
	(216.52, 95.77) --
	(229.50, 95.77) --
	(229.50, 93.71) --
	(242.49, 93.71) --
	(242.49, 91.68) --
	(255.47, 91.68) --
	(255.47, 89.56) --
	(268.46, 89.56) --
	(268.46, 87.59) --
	(281.44, 87.59) --
	(281.44, 85.63) --
	(294.43, 85.63) --
	(294.43, 78.25);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,117.76) --
	( 73.67,117.76) --
	( 73.67,117.76) --
	( 86.66,117.76) --
	( 86.66,115.63) --
	( 99.65,115.63) --
	( 99.65,112.88) --
	(112.63,112.88) --
	(112.63,109.89) --
	(125.62,109.89) --
	(125.62,107.28) --
	(138.60,107.28) --
	(138.60,104.24) --
	(151.59,104.24) --
	(151.59,101.45) --
	(164.57,101.45) --
	(164.57, 98.80) --
	(177.56, 98.80) --
	(177.56, 96.10) --
	(190.55, 96.10) --
	(190.55, 93.39) --
	(203.53, 93.39) --
	(203.53, 90.63) --
	(216.52, 90.63) --
	(216.52, 88.25) --
	(229.50, 88.25) --
	(229.50, 85.89) --
	(242.49, 85.89) --
	(242.49, 83.44) --
	(255.47, 83.44) --
	(255.47, 80.87) --
	(268.46, 80.87) --
	(268.46, 78.53) --
	(281.44, 78.53) --
	(281.44, 76.10) --
	(294.43, 76.10) --
	(294.43, 67.20);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,117.58) --
	( 73.67,117.58) --
	( 73.67,117.28) --
	( 86.66,117.28) --
	( 86.66,116.87) --
	( 99.65,116.87) --
	( 99.65,116.33) --
	(112.63,116.33) --
	(112.63,115.67) --
	(125.62,115.67) --
	(125.62,114.88) --
	(138.60,114.88) --
	(138.60,113.98) --
	(151.59,113.98) --
	(151.59,112.97) --
	(164.57,112.97) --
	(164.57,111.84) --
	(177.56,111.84) --
	(177.56,110.59) --
	(190.55,110.59) --
	(190.55,109.24) --
	(203.53,109.24) --
	(203.53,107.80) --
	(216.52,107.80) --
	(216.52,106.25) --
	(229.50,106.25) --
	(229.50,104.60) --
	(242.49,104.60) --
	(242.49,102.86) --
	(255.47,102.86) --
	(255.47,101.02) --
	(268.46,101.02) --
	(268.46, 99.07) --
	(281.44, 99.07) --
	(281.44, 97.06) --
	(294.43, 97.06) --
	(294.43, 94.98);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,117.54) --
	( 73.67,117.54) --
	( 73.67,117.16) --
	( 86.66,117.16) --
	( 86.66,116.62) --
	( 99.65,116.62) --
	( 99.65,115.92) --
	(112.63,115.92) --
	(112.63,115.11) --
	(125.62,115.11) --
	(125.62,114.17) --
	(138.60,114.17) --
	(138.60,113.06) --
	(151.59,113.06) --
	(151.59,111.82) --
	(164.57,111.82) --
	(164.57,110.39) --
	(177.56,110.39) --
	(177.56,108.82) --
	(190.55,108.82) --
	(190.55,107.21) --
	(203.53,107.21) --
	(203.53,105.45) --
	(216.52,105.45) --
	(216.52,103.59) --
	(229.50,103.59) --
	(229.50,101.50) --
	(242.49,101.50) --
	(242.49, 99.26) --
	(255.47, 99.26) --
	(255.47, 96.93) --
	(268.46, 96.93) --
	(268.46, 94.54) --
	(281.44, 94.54) --
	(281.44, 92.02) --
	(294.43, 92.02) --
	(294.43, 89.54);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,116.56) --
	( 73.67,116.56) --
	( 73.67,115.09) --
	( 86.66,115.09) --
	( 86.66,113.43) --
	( 99.65,113.43) --
	( 99.65,111.65) --
	(112.63,111.65) --
	(112.63,109.79) --
	(125.62,109.79) --
	(125.62,107.83) --
	(138.60,107.83) --
	(138.60,105.87) --
	(151.59,105.87) --
	(151.59,103.89) --
	(164.57,103.89) --
	(164.57,101.88) --
	(177.56,101.88) --
	(177.56, 99.85) --
	(190.55, 99.85) --
	(190.55, 97.85) --
	(203.53, 97.85) --
	(203.53, 95.84) --
	(216.52, 95.84) --
	(216.52, 93.85) --
	(229.50, 93.85) --
	(229.50, 91.86) --
	(242.49, 91.86) --
	(242.49, 89.89) --
	(255.47, 89.89) --
	(255.47, 87.93) --
	(268.46, 87.93) --
	(268.46, 85.96) --
	(281.44, 85.96) --
	(281.44, 84.03) --
	(294.43, 84.03) --
	(294.43, 82.03);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,117.76) --
	( 60.69,117.76) --
	( 60.69,116.30) --
	( 73.67,116.30) --
	( 73.67,114.43) --
	( 86.66,114.43) --
	( 86.66,112.27) --
	( 99.65,112.27) --
	( 99.65,109.97) --
	(112.63,109.97) --
	(112.63,107.69) --
	(125.62,107.69) --
	(125.62,105.38) --
	(138.60,105.38) --
	(138.60,102.96) --
	(151.59,102.96) --
	(151.59,100.54) --
	(164.57,100.54) --
	(164.57, 98.00) --
	(177.56, 98.00) --
	(177.56, 95.48) --
	(190.55, 95.48) --
	(190.55, 93.09) --
	(203.53, 93.09) --
	(203.53, 90.67) --
	(216.52, 90.67) --
	(216.52, 88.30) --
	(229.50, 88.30) --
	(229.50, 85.80) --
	(242.49, 85.80) --
	(242.49, 83.29) --
	(255.47, 83.29) --
	(255.47, 80.83) --
	(268.46, 80.83) --
	(268.46, 78.44) --
	(281.44, 78.44) --
	(281.44, 76.05) --
	(294.43, 76.05) --
	(294.43, 73.69);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 64.67) rectangle (306.77,120.29);
\end{scope}
\begin{scope}
\path[clip] (306.77,125.79) rectangle (319.71,181.41);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,125.79) rectangle (319.71,181.41);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,153.60) {Scenario 1};
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,120.29);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,120.29);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14, 92.48) {Scenario 2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.65, 61.92) --
	( 99.65, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (164.57, 61.92) --
	(164.57, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50, 61.92) --
	(229.50, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.43, 61.92) --
	(294.43, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 99.65, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.57, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (229.50, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.43, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,124.96) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,142.01) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,159.07) {0.95};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,176.12) {1.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,127.71) --
	( 35.37,127.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,144.77) --
	( 35.37,144.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,161.82) --
	( 35.37,161.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,178.88) --
	( 35.37,178.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.84) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 80.89) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 97.95) {0.95};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,115.00) {1.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.59) --
	( 35.37, 66.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 83.65) --
	( 35.37, 83.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,100.70) --
	( 35.37,100.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,117.76) --
	( 35.37,117.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (171.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,123.04) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 21.60,  5.50) rectangle (144.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 32.60, 11.00) rectangle ( 47.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.05, 18.23) -- ( 45.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 88.63, 11.00) rectangle (103.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.08, 18.23) -- (101.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 52.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (108.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.67,  5.50) rectangle (320.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (166.67, 11.00) rectangle (181.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.11, 18.23) -- (179.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (214.89, 11.00) rectangle (229.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (216.34, 18.23) -- (227.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (264.84, 11.00) rectangle (279.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (266.28, 18.23) -- (277.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (186.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (234.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (284.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/gm_results_3-4.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:30:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,186.91);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,186.91);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,125.79) rectangle (306.77,181.41);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,125.79) rectangle (306.77,181.41);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,135.73) --
	(306.77,135.73);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,152.99) --
	(306.77,152.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,170.25) --
	(306.77,170.25);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,125.79) --
	( 63.65,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,125.79) --
	(129.54,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,125.79) --
	(195.42,181.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,125.79) --
	(261.31,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,127.10) --
	(306.77,127.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,144.36) --
	(306.77,144.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,161.62) --
	(306.77,161.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,178.88) --
	(306.77,178.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,125.79) --
	( 96.59,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,125.79) --
	(162.48,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,125.79) --
	(228.36,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,125.79) --
	(294.25,181.41);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.88) --
	( 70.24,178.88) --
	( 70.24,178.88) --
	( 83.42,178.88) --
	( 83.42,178.20) --
	( 96.59,178.20) --
	( 96.59,177.27) --
	(109.77,177.27) --
	(109.77,176.28) --
	(122.95,176.28) --
	(122.95,175.28) --
	(136.12,175.28) --
	(136.12,174.14) --
	(149.30,174.14) --
	(149.30,173.02) --
	(162.48,173.02) --
	(162.48,172.01) --
	(175.66,172.01) --
	(175.66,170.88) --
	(188.83,170.88) --
	(188.83,169.86) --
	(202.01,169.86) --
	(202.01,168.78) --
	(215.19,168.78) --
	(215.19,167.74) --
	(228.36,167.74) --
	(228.36,166.69) --
	(241.54,166.69) --
	(241.54,165.71) --
	(254.72,165.71) --
	(254.72,164.68) --
	(267.89,164.68) --
	(267.89,163.58) --
	(281.07,163.58) --
	(281.07,162.52) --
	(294.25,162.52) --
	(294.25,158.92);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.88) --
	( 70.24,178.88) --
	( 70.24,178.88) --
	( 83.42,178.88) --
	( 83.42,177.76) --
	( 96.59,177.76) --
	( 96.59,176.36) --
	(109.77,176.36) --
	(109.77,174.82) --
	(122.95,174.82) --
	(122.95,173.48) --
	(136.12,173.48) --
	(136.12,171.94) --
	(149.30,171.94) --
	(149.30,170.53) --
	(162.48,170.53) --
	(162.48,169.10) --
	(175.66,169.10) --
	(175.66,167.63) --
	(188.83,167.63) --
	(188.83,166.19) --
	(202.01,166.19) --
	(202.01,164.67) --
	(215.19,164.67) --
	(215.19,163.39) --
	(228.36,163.39) --
	(228.36,162.12) --
	(241.54,162.12) --
	(241.54,160.87) --
	(254.72,160.87) --
	(254.72,159.70) --
	(267.89,159.70) --
	(267.89,158.46) --
	(281.07,158.46) --
	(281.07,157.23) --
	(294.25,157.23) --
	(294.25,152.51);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.79) --
	( 70.24,178.79) --
	( 70.24,178.64) --
	( 83.42,178.64) --
	( 83.42,178.43) --
	( 96.59,178.43) --
	( 96.59,178.16) --
	(109.77,178.16) --
	(109.77,177.83) --
	(122.95,177.83) --
	(122.95,177.45) --
	(136.12,177.45) --
	(136.12,177.01) --
	(149.30,177.01) --
	(149.30,176.51) --
	(162.48,176.51) --
	(162.48,175.96) --
	(175.66,175.96) --
	(175.66,175.35) --
	(188.83,175.35) --
	(188.83,174.68) --
	(202.01,174.68) --
	(202.01,173.96) --
	(215.19,173.96) --
	(215.19,173.19) --
	(228.36,173.19) --
	(228.36,172.39) --
	(241.54,172.39) --
	(241.54,171.52) --
	(254.72,171.52) --
	(254.72,170.61) --
	(267.89,170.61) --
	(267.89,169.65) --
	(281.07,169.65) --
	(281.07,168.65) --
	(294.25,168.65) --
	(294.25,167.61);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.75) --
	( 70.24,178.75) --
	( 70.24,178.56) --
	( 83.42,178.56) --
	( 83.42,178.28) --
	( 96.59,178.28) --
	( 96.59,177.93) --
	(109.77,177.93) --
	(109.77,177.51) --
	(122.95,177.51) --
	(122.95,177.02) --
	(136.12,177.02) --
	(136.12,176.46) --
	(149.30,176.46) --
	(149.30,175.83) --
	(162.48,175.83) --
	(162.48,175.14) --
	(175.66,175.14) --
	(175.66,174.36) --
	(188.83,174.36) --
	(188.83,173.54) --
	(202.01,173.54) --
	(202.01,172.62) --
	(215.19,172.62) --
	(215.19,171.66) --
	(228.36,171.66) --
	(228.36,170.63) --
	(241.54,170.63) --
	(241.54,169.55) --
	(254.72,169.55) --
	(254.72,168.43) --
	(267.89,168.43) --
	(267.89,167.23) --
	(281.07,167.23) --
	(281.07,165.99) --
	(294.25,165.99) --
	(294.25,164.69);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.27) --
	( 70.24,178.27) --
	( 70.24,177.54) --
	( 83.42,177.54) --
	( 83.42,176.69) --
	( 96.59,176.69) --
	( 96.59,175.81) --
	(109.77,175.81) --
	(109.77,174.87) --
	(122.95,174.87) --
	(122.95,173.92) --
	(136.12,173.92) --
	(136.12,172.97) --
	(149.30,172.97) --
	(149.30,171.98) --
	(162.48,171.98) --
	(162.48,170.99) --
	(175.66,170.99) --
	(175.66,169.99) --
	(188.83,169.99) --
	(188.83,168.99) --
	(202.01,168.99) --
	(202.01,168.00) --
	(215.19,168.00) --
	(215.19,167.00) --
	(228.36,167.00) --
	(228.36,166.02) --
	(241.54,166.02) --
	(241.54,165.04) --
	(254.72,165.04) --
	(254.72,164.06) --
	(267.89,164.06) --
	(267.89,163.09) --
	(281.07,163.09) --
	(281.07,162.13) --
	(294.25,162.13) --
	(294.25,161.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,178.88) --
	( 57.06,178.88) --
	( 57.06,178.06) --
	( 70.24,178.06) --
	( 70.24,177.09) --
	( 83.42,177.09) --
	( 83.42,175.98) --
	( 96.59,175.98) --
	( 96.59,174.82) --
	(109.77,174.82) --
	(109.77,173.63) --
	(122.95,173.63) --
	(122.95,172.40) --
	(136.12,172.40) --
	(136.12,171.20) --
	(149.30,171.20) --
	(149.30,169.95) --
	(162.48,169.95) --
	(162.48,168.72) --
	(175.66,168.72) --
	(175.66,167.46) --
	(188.83,167.46) --
	(188.83,166.23) --
	(202.01,166.23) --
	(202.01,164.97) --
	(215.19,164.97) --
	(215.19,163.73) --
	(228.36,163.73) --
	(228.36,162.50) --
	(241.54,162.50) --
	(241.54,161.29) --
	(254.72,161.29) --
	(254.72,160.10) --
	(267.89,160.10) --
	(267.89,158.90) --
	(281.07,158.90) --
	(281.07,157.72) --
	(294.25,157.72) --
	(294.25,156.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,125.79) rectangle (306.77,181.41);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 64.67) rectangle (306.77,120.29);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,120.29);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 74.61) --
	(306.77, 74.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 91.87) --
	(306.77, 91.87);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,109.13) --
	(306.77,109.13);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
	( 63.65,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
	(129.54,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
	(195.42,120.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
	(261.31,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 65.98) --
	(306.77, 65.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 83.24) --
	(306.77, 83.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,100.50) --
	(306.77,100.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,117.76) --
	(306.77,117.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
	( 96.59,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
	(162.48,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
	(228.36,120.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
	(294.25,120.29);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,117.76) --
	( 70.24,117.76) --
	( 70.24,117.76) --
	( 83.42,117.76) --
	( 83.42,116.34) --
	( 96.59,116.34) --
	( 96.59,114.46) --
	(109.77,114.46) --
	(109.77,112.33) --
	(122.95,112.33) --
	(122.95,109.82) --
	(136.12,109.82) --
	(136.12,107.36) --
	(149.30,107.36) --
	(149.30,104.92) --
	(162.48,104.92) --
	(162.48,102.44) --
	(175.66,102.44) --
	(175.66,100.04) --
	(188.83,100.04) --
	(188.83, 97.63) --
	(202.01, 97.63) --
	(202.01, 95.21) --
	(215.19, 95.21) --
	(215.19, 92.93) --
	(228.36, 92.93) --
	(228.36, 90.77) --
	(241.54, 90.77) --
	(241.54, 88.50) --
	(254.72, 88.50) --
	(254.72, 86.37) --
	(267.89, 86.37) --
	(267.89, 84.35) --
	(281.07, 84.35) --
	(281.07, 82.26) --
	(294.25, 82.26) --
	(294.25, 75.17);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,117.76) --
	( 70.24,117.76) --
	( 70.24,117.76) --
	( 83.42,117.76) --
	( 83.42,115.96) --
	( 96.59,115.96) --
	( 96.59,113.38) --
	(109.77,113.38) --
	(109.77,110.41) --
	(122.95,110.41) --
	(122.95,107.23) --
	(136.12,107.23) --
	(136.12,104.13) --
	(149.30,104.13) --
	(149.30,101.03) --
	(162.48,101.03) --
	(162.48, 97.99) --
	(175.66, 97.99) --
	(175.66, 94.91) --
	(188.83, 94.91) --
	(188.83, 92.06) --
	(202.01, 92.06) --
	(202.01, 89.37) --
	(215.19, 89.37) --
	(215.19, 86.81) --
	(228.36, 86.81) --
	(228.36, 84.24) --
	(241.54, 84.24) --
	(241.54, 81.76) --
	(254.72, 81.76) --
	(254.72, 79.43) --
	(267.89, 79.43) --
	(267.89, 77.13) --
	(281.07, 77.13) --
	(281.07, 74.99) --
	(294.25, 74.99) --
	(294.25, 67.20);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,117.57) --
	( 70.24,117.57) --
	( 70.24,117.24) --
	( 83.42,117.24) --
	( 83.42,116.77) --
	( 96.59,116.77) --
	( 96.59,116.16) --
	(109.77,116.16) --
	(109.77,115.39) --
	(122.95,115.39) --
	(122.95,114.50) --
	(136.12,114.50) --
	(136.12,113.48) --
	(149.30,113.48) --
	(149.30,112.33) --
	(162.48,112.33) --
	(162.48,111.06) --
	(175.66,111.06) --
	(175.66,109.63) --
	(188.83,109.63) --
	(188.83,108.11) --
	(202.01,108.11) --
	(202.01,106.47) --
	(215.19,106.47) --
	(215.19,104.73) --
	(228.36,104.73) --
	(228.36,102.88) --
	(241.54,102.88) --
	(241.54,100.92) --
	(254.72,100.92) --
	(254.72, 98.90) --
	(267.89, 98.90) --
	(267.89, 96.78) --
	(281.07, 96.78) --
	(281.07, 94.61) --
	(294.25, 94.61) --
	(294.25, 92.33);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,117.48) --
	( 70.24,117.48) --
	( 70.24,117.04) --
	( 83.42,117.04) --
	( 83.42,116.43) --
	( 96.59,116.43) --
	( 96.59,115.66) --
	(109.77,115.66) --
	(109.77,114.74) --
	(122.95,114.74) --
	(122.95,113.65) --
	(136.12,113.65) --
	(136.12,112.42) --
	(149.30,112.42) --
	(149.30,111.04) --
	(162.48,111.04) --
	(162.48,109.53) --
	(175.66,109.53) --
	(175.66,107.85) --
	(188.83,107.85) --
	(188.83,106.01) --
	(202.01,106.01) --
	(202.01,104.07) --
	(215.19,104.07) --
	(215.19,102.02) --
	(228.36,102.02) --
	(228.36, 99.79) --
	(241.54, 99.79) --
	(241.54, 97.43) --
	(254.72, 97.43) --
	(254.72, 94.96) --
	(267.89, 94.96) --
	(267.89, 92.49) --
	(281.07, 92.49) --
	(281.07, 89.90) --
	(294.25, 89.90) --
	(294.25, 87.36);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,116.48) --
	( 70.24,116.48) --
	( 70.24,114.87) --
	( 83.42,114.87) --
	( 83.42,112.98) --
	( 96.59,112.98) --
	( 96.59,110.97) --
	(109.77,110.97) --
	(109.77,108.81) --
	(122.95,108.81) --
	(122.95,106.61) --
	(136.12,106.61) --
	(136.12,104.40) --
	(149.30,104.40) --
	(149.30,102.19) --
	(162.48,102.19) --
	(162.48, 99.96) --
	(175.66, 99.96) --
	(175.66, 97.69) --
	(188.83, 97.69) --
	(188.83, 95.46) --
	(202.01, 95.46) --
	(202.01, 93.26) --
	(215.19, 93.26) --
	(215.19, 91.09) --
	(228.36, 91.09) --
	(228.36, 88.95) --
	(241.54, 88.95) --
	(241.54, 86.82) --
	(254.72, 86.82) --
	(254.72, 84.77) --
	(267.89, 84.77) --
	(267.89, 82.73) --
	(281.07, 82.73) --
	(281.07, 80.77) --
	(294.25, 80.77) --
	(294.25, 78.69);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,117.76) --
	( 57.06,117.76) --
	( 57.06,115.90) --
	( 70.24,115.90) --
	( 70.24,113.71) --
	( 83.42,113.71) --
	( 83.42,111.29) --
	( 96.59,111.29) --
	( 96.59,108.77) --
	(109.77,108.77) --
	(109.77,106.19) --
	(122.95,106.19) --
	(122.95,103.53) --
	(136.12,103.53) --
	(136.12,100.90) --
	(149.30,100.90) --
	(149.30, 98.25) --
	(162.48, 98.25) --
	(162.48, 95.64) --
	(175.66, 95.64) --
	(175.66, 93.00) --
	(188.83, 93.00) --
	(188.83, 90.37) --
	(202.01, 90.37) --
	(202.01, 87.81) --
	(215.19, 87.81) --
	(215.19, 85.31) --
	(228.36, 85.31) --
	(228.36, 82.77) --
	(241.54, 82.77) --
	(241.54, 80.27) --
	(254.72, 80.27) --
	(254.72, 77.82) --
	(267.89, 77.82) --
	(267.89, 75.51) --
	(281.07, 75.51) --
	(281.07, 73.21) --
	(294.25, 73.21) --
	(294.25, 70.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,120.29);
\end{scope}
\begin{scope}
\path[clip] (306.77,125.79) rectangle (319.71,181.41);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,125.79) rectangle (319.71,181.41);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,153.60) {Scenario 3};
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,120.29);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,120.29);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14, 92.48) {Scenario 4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
	( 96.59, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
	(162.48, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
	(228.36, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
	(294.25, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,124.34) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,141.60) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,158.86) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,176.12) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,127.10) --
	( 31.37,127.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,144.36) --
	( 31.37,144.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,161.62) --
	( 31.37,161.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,178.88) --
	( 31.37,178.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 63.23) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 80.48) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 97.74) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,115.00) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 65.98) --
	( 31.37, 65.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 83.24) --
	( 31.37, 83.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,100.50) --
	( 31.37,100.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,117.76) --
	( 31.37,117.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,123.04) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,186.91);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/gm_results_5.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:32:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,135.51);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,135.51);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 64.67) rectangle (306.77,130.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,130.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 78.57) --
	(306.77, 78.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 97.96) --
	(306.77, 97.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,117.34) --
	(306.77,117.34);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
	( 63.65,130.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
	(129.54,130.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
	(195.42,130.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
	(261.31,130.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 68.87) --
	(306.77, 68.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 88.26) --
	(306.77, 88.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,107.65) --
	(306.77,107.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,127.04) --
	(306.77,127.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
	( 96.59,130.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
	(162.48,130.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
	(228.36,130.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
	(294.25,130.01);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,127.04) --
	( 70.24,127.04) --
	( 70.24,127.04) --
	( 83.42,127.04) --
	( 83.42,124.66) --
	( 96.59,124.66) --
	( 96.59,122.06) --
	(109.77,122.06) --
	(109.77,119.04) --
	(122.95,119.04) --
	(122.95,116.10) --
	(136.12,116.10) --
	(136.12,113.15) --
	(149.30,113.15) --
	(149.30,110.13) --
	(162.48,110.13) --
	(162.48,107.32) --
	(175.66,107.32) --
	(175.66,104.56) --
	(188.83,104.56) --
	(188.83,101.93) --
	(202.01,101.93) --
	(202.01, 99.23) --
	(215.19, 99.23) --
	(215.19, 96.51) --
	(228.36, 96.51) --
	(228.36, 94.06) --
	(241.54, 94.06) --
	(241.54, 91.66) --
	(254.72, 91.66) --
	(254.72, 89.32) --
	(267.89, 89.32) --
	(267.89, 87.14) --
	(281.07, 87.14) --
	(281.07, 85.07) --
	(294.25, 85.07) --
	(294.25, 76.99);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,127.04) --
	( 70.24,127.04) --
	( 70.24,127.04) --
	( 83.42,127.04) --
	( 83.42,124.02) --
	( 96.59,124.02) --
	( 96.59,120.04) --
	(109.77,120.04) --
	(109.77,115.99) --
	(122.95,115.99) --
	(122.95,112.23) --
	(136.12,112.23) --
	(136.12,108.44) --
	(149.30,108.44) --
	(149.30,105.00) --
	(162.48,105.00) --
	(162.48,101.60) --
	(175.66,101.60) --
	(175.66, 98.02) --
	(188.83, 98.02) --
	(188.83, 94.76) --
	(202.01, 94.76) --
	(202.01, 91.83) --
	(215.19, 91.83) --
	(215.19, 88.97) --
	(228.36, 88.97) --
	(228.36, 86.33) --
	(241.54, 86.33) --
	(241.54, 83.71) --
	(254.72, 83.71) --
	(254.72, 81.09) --
	(267.89, 81.09) --
	(267.89, 78.47) --
	(281.07, 78.47) --
	(281.07, 76.21) --
	(294.25, 76.21) --
	(294.25, 67.64);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,126.77) --
	( 70.24,126.77) --
	( 70.24,126.34) --
	( 83.42,126.34) --
	( 83.42,125.76) --
	( 96.59,125.76) --
	( 96.59,125.03) --
	(109.77,125.03) --
	(109.77,124.17) --
	(122.95,124.17) --
	(122.95,123.15) --
	(136.12,123.15) --
	(136.12,122.00) --
	(149.30,122.00) --
	(149.30,120.71) --
	(162.48,120.71) --
	(162.48,119.27) --
	(175.66,119.27) --
	(175.66,117.70) --
	(188.83,117.70) --
	(188.83,116.01) --
	(202.01,116.01) --
	(202.01,114.18) --
	(215.19,114.18) --
	(215.19,112.23) --
	(228.36,112.23) --
	(228.36,110.16) --
	(241.54,110.16) --
	(241.54,108.00) --
	(254.72,108.00) --
	(254.72,105.73) --
	(267.89,105.73) --
	(267.89,103.36) --
	(281.07,103.36) --
	(281.07,100.91) --
	(294.25,100.91) --
	(294.25, 98.40);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,126.69) --
	( 70.24,126.69) --
	( 70.24,126.14) --
	( 83.42,126.14) --
	( 83.42,125.40) --
	( 96.59,125.40) --
	( 96.59,124.49) --
	(109.77,124.49) --
	(109.77,123.37) --
	(122.95,123.37) --
	(122.95,122.15) --
	(136.12,122.15) --
	(136.12,120.78) --
	(149.30,120.78) --
	(149.30,119.19) --
	(162.48,119.19) --
	(162.48,117.49) --
	(175.66,117.49) --
	(175.66,115.61) --
	(188.83,115.61) --
	(188.83,113.58) --
	(202.01,113.58) --
	(202.01,111.40) --
	(215.19,111.40) --
	(215.19,109.11) --
	(228.36,109.11) --
	(228.36,106.72) --
	(241.54,106.72) --
	(241.54,104.23) --
	(254.72,104.23) --
	(254.72,101.60) --
	(267.89,101.60) --
	(267.89, 98.83) --
	(281.07, 98.83) --
	(281.07, 95.98) --
	(294.25, 95.98) --
	(294.25, 93.00);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,125.25) --
	( 70.24,125.25) --
	( 70.24,123.13) --
	( 83.42,123.13) --
	( 83.42,120.82) --
	( 96.59,120.82) --
	( 96.59,118.41) --
	(109.77,118.41) --
	(109.77,115.98) --
	(122.95,115.98) --
	(122.95,113.50) --
	(136.12,113.50) --
	(136.12,111.00) --
	(149.30,111.00) --
	(149.30,108.51) --
	(162.48,108.51) --
	(162.48,106.02) --
	(175.66,106.02) --
	(175.66,103.53) --
	(188.83,103.53) --
	(188.83,101.08) --
	(202.01,101.08) --
	(202.01, 98.62) --
	(215.19, 98.62) --
	(215.19, 96.21) --
	(228.36, 96.21) --
	(228.36, 93.81) --
	(241.54, 93.81) --
	(241.54, 91.48) --
	(254.72, 91.48) --
	(254.72, 89.18) --
	(267.89, 89.18) --
	(267.89, 86.91) --
	(281.07, 86.91) --
	(281.07, 84.70) --
	(294.25, 84.70) --
	(294.25, 82.43);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,127.04) --
	( 57.06,127.04) --
	( 57.06,124.69) --
	( 70.24,124.69) --
	( 70.24,121.98) --
	( 83.42,121.98) --
	( 83.42,119.04) --
	( 96.59,119.04) --
	( 96.59,116.05) --
	(109.77,116.05) --
	(109.77,112.90) --
	(122.95,112.90) --
	(122.95,109.96) --
	(136.12,109.96) --
	(136.12,107.02) --
	(149.30,107.02) --
	(149.30,103.98) --
	(162.48,103.98) --
	(162.48,101.05) --
	(175.66,101.05) --
	(175.66, 98.12) --
	(188.83, 98.12) --
	(188.83, 95.23) --
	(202.01, 95.23) --
	(202.01, 92.36) --
	(215.19, 92.36) --
	(215.19, 89.58) --
	(228.36, 89.58) --
	(228.36, 86.88) --
	(241.54, 86.88) --
	(241.54, 84.25) --
	(254.72, 84.25) --
	(254.72, 81.64) --
	(267.89, 81.64) --
	(267.89, 79.06) --
	(281.07, 79.06) --
	(281.07, 76.54) --
	(294.25, 76.54) --
	(294.25, 73.92);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,130.01);
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,130.01);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,130.01);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14, 97.34) {Scenario 5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
	( 96.59, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
	(162.48, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
	(228.36, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
	(294.25, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 66.12) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 85.51) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,104.89) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,124.28) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 68.87) --
	( 31.37, 68.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 88.26) --
	( 31.37, 88.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,107.65) --
	( 31.37,107.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,127.04) --
	( 31.37,127.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70, 97.34) {Survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,135.51);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/results.tex
Draft ready
SER

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-12-10 17:23:19
+% Created by tikzDevice version 0.12.3.1 on 2022-03-04 00:12:39
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,542.02);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,560.09);
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,542.02);
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.37,446.55) rectangle (306.77,536.52);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,560.09);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.37,463.90) rectangle (306.77,554.59);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.37,446.55) rectangle (306.77,536.52);
+\path[fill=fillColor] ( 31.37,463.90) rectangle (306.77,554.59);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,465.69) --
-	(306.77,465.69);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,492.39) --
-	(306.77,492.39);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,519.09) --
-	(306.77,519.09);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,446.55) --
-	( 63.65,536.52);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,446.55) --
-	(129.54,536.52);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,446.55) --
-	(195.42,536.52);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,446.55) --
-	(261.31,536.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,452.35) --
-	(306.77,452.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,479.04) --
-	(306.77,479.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,505.74) --
-	(306.77,505.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,532.44) --
-	(306.77,532.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,446.55) --
-	( 96.59,536.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,446.55) --
-	(162.48,536.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,446.55) --
-	(228.36,536.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,446.55) --
-	(294.25,536.52);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,483.19) --
+	(306.77,483.19);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,510.10) --
+	(306.77,510.10);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,537.01) --
+	(306.77,537.01);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,463.90) --
+	( 63.65,554.59);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,463.90) --
+	(129.54,554.59);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,463.90) --
+	(195.42,554.59);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,463.90) --
+	(261.31,554.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,469.74) --
+	(306.77,469.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,496.65) --
+	(306.77,496.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,523.56) --
+	(306.77,523.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,550.47) --
+	(306.77,550.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,463.90) --
+	( 96.59,554.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,463.90) --
+	(162.48,554.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,463.90) --
+	(228.36,554.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,463.90) --
+	(294.25,554.59);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,532.44) --
-	( 70.24,532.44) --
-	( 70.24,532.44) --
-	( 83.42,532.44) --
-	( 83.42,531.30) --
-	( 96.59,531.30) --
-	( 96.59,529.92) --
-	(109.77,529.92) --
-	(109.77,528.40) --
-	(122.95,528.40) --
-	(122.95,526.64) --
-	(136.12,526.64) --
-	(136.12,525.13) --
-	(149.30,525.13) --
-	(149.30,523.36) --
-	(162.48,523.36) --
-	(162.48,521.51) --
-	(175.66,521.51) --
-	(175.66,519.69) --
-	(188.83,519.69) --
-	(188.83,518.12) --
-	(202.01,518.12) --
-	(202.01,516.55) --
-	(215.19,516.55) --
-	(215.19,514.77) --
-	(228.36,514.77) --
-	(228.36,513.09) --
-	(241.54,513.09) --
-	(241.54,511.55) --
-	(254.72,511.55) --
-	(254.72,509.95) --
-	(267.89,509.95) --
-	(267.89,508.39) --
-	(281.07,508.39) --
-	(281.07,506.83) --
-	(294.25,506.83) --
-	(294.25,501.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,550.47) --
+	( 70.24,550.47) --
+	( 70.24,550.47) --
+	( 83.42,550.47) --
+	( 83.42,548.70) --
+	( 96.59,548.70) --
+	( 96.59,546.65) --
+	(109.77,546.65) --
+	(109.77,544.43) --
+	(122.95,544.43) --
+	(122.95,542.36) --
+	(136.12,542.36) --
+	(136.12,540.08) --
+	(149.30,540.08) --
+	(149.30,537.68) --
+	(162.48,537.68) --
+	(162.48,535.56) --
+	(175.66,535.56) --
+	(175.66,533.45) --
+	(188.83,533.45) --
+	(188.83,531.30) --
+	(202.01,531.30) --
+	(202.01,529.16) --
+	(215.19,529.16) --
+	(215.19,527.28) --
+	(228.36,527.28) --
+	(228.36,525.33) --
+	(241.54,525.33) --
+	(241.54,523.49) --
+	(254.72,523.49) --
+	(254.72,521.48) --
+	(267.89,521.48) --
+	(267.89,519.66) --
+	(281.07,519.66) --
+	(281.07,517.90) --
+	(294.25,517.90) --
+	(294.25,511.26);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,532.44) --
-	( 70.24,532.44) --
-	( 70.24,532.44) --
-	( 83.42,532.44) --
-	( 83.42,530.68) --
-	( 96.59,530.68) --
-	( 96.59,528.65) --
-	(109.77,528.65) --
-	(109.77,526.44) --
-	(122.95,526.44) --
-	(122.95,524.39) --
-	(136.12,524.39) --
-	(136.12,522.13) --
-	(149.30,522.13) --
-	(149.30,519.74) --
-	(162.48,519.74) --
-	(162.48,517.64) --
-	(175.66,517.64) --
-	(175.66,515.55) --
-	(188.83,515.55) --
-	(188.83,513.42) --
-	(202.01,513.42) --
-	(202.01,511.30) --
-	(215.19,511.30) --
-	(215.19,509.43) --
-	(228.36,509.43) --
-	(228.36,507.50) --
-	(241.54,507.50) --
-	(241.54,505.67) --
-	(254.72,505.67) --
-	(254.72,503.67) --
-	(267.89,503.67) --
-	(267.89,501.87) --
-	(281.07,501.87) --
-	(281.07,500.13) --
-	(294.25,500.13) --
-	(294.25,493.53);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,550.47) --
+	( 70.24,550.47) --
+	( 70.24,550.47) --
+	( 83.42,550.47) --
+	( 83.42,549.32) --
+	( 96.59,549.32) --
+	( 96.59,547.94) --
+	(109.77,547.94) --
+	(109.77,546.41) --
+	(122.95,546.41) --
+	(122.95,544.63) --
+	(136.12,544.63) --
+	(136.12,543.11) --
+	(149.30,543.11) --
+	(149.30,541.33) --
+	(162.48,541.33) --
+	(162.48,539.45) --
+	(175.66,539.45) --
+	(175.66,537.62) --
+	(188.83,537.62) --
+	(188.83,536.04) --
+	(202.01,536.04) --
+	(202.01,534.45) --
+	(215.19,534.45) --
+	(215.19,532.67) --
+	(228.36,532.67) --
+	(228.36,530.97) --
+	(241.54,530.97) --
+	(241.54,529.42) --
+	(254.72,529.42) --
+	(254.72,527.80) --
+	(267.89,527.80) --
+	(267.89,526.23) --
+	(281.07,526.23) --
+	(281.07,524.66) --
+	(294.25,524.66) --
+	(294.25,519.09);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,532.30) --
-	( 70.24,532.30) --
-	( 70.24,532.07) --
-	( 83.42,532.07) --
-	( 83.42,531.73) --
-	( 96.59,531.73) --
-	( 96.59,531.32) --
-	(109.77,531.32) --
-	(109.77,530.81) --
-	(122.95,530.81) --
-	(122.95,530.21) --
-	(136.12,530.21) --
-	(136.12,529.54) --
-	(149.30,529.54) --
-	(149.30,528.76) --
-	(162.48,528.76) --
-	(162.48,527.90) --
-	(175.66,527.90) --
-	(175.66,526.95) --
-	(188.83,526.95) --
-	(188.83,525.91) --
-	(202.01,525.91) --
-	(202.01,524.81) --
-	(215.19,524.81) --
-	(215.19,523.61) --
-	(228.36,523.61) --
-	(228.36,522.37) --
-	(241.54,522.37) --
-	(241.54,521.03) --
-	(254.72,521.03) --
-	(254.72,519.61) --
-	(267.89,519.61) --
-	(267.89,518.13) --
-	(281.07,518.13) --
-	(281.07,516.58) --
-	(294.25,516.58) --
-	(294.25,514.97);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,550.37) --
+	( 70.24,550.37) --
+	( 70.24,550.22) --
+	( 83.42,550.22) --
+	( 83.42,550.01) --
+	( 96.59,550.01) --
+	( 96.59,549.74) --
+	(109.77,549.74) --
+	(109.77,549.42) --
+	(122.95,549.42) --
+	(122.95,549.05) --
+	(136.12,549.05) --
+	(136.12,548.63) --
+	(149.30,548.63) --
+	(149.30,548.14) --
+	(162.48,548.14) --
+	(162.48,547.61) --
+	(175.66,547.61) --
+	(175.66,547.02) --
+	(188.83,547.02) --
+	(188.83,546.38) --
+	(202.01,546.38) --
+	(202.01,545.71) --
+	(215.19,545.71) --
+	(215.19,544.99) --
+	(228.36,544.99) --
+	(228.36,544.21) --
+	(241.54,544.21) --
+	(241.54,543.38) --
+	(254.72,543.38) --
+	(254.72,542.50) --
+	(267.89,542.50) --
+	(267.89,541.57) --
+	(281.07,541.57) --
+	(281.07,540.63) --
+	(294.25,540.63) --
+	(294.25,539.65);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,532.24) --
-	( 70.24,532.24) --
-	( 70.24,531.95) --
-	( 83.42,531.95) --
-	( 83.42,531.52) --
-	( 96.59,531.52) --
-	( 96.59,530.99) --
-	(109.77,530.99) --
-	(109.77,530.36) --
-	(122.95,530.36) --
-	(122.95,529.62) --
-	(136.12,529.62) --
-	(136.12,528.78) --
-	(149.30,528.78) --
-	(149.30,527.83) --
-	(162.48,527.83) --
-	(162.48,526.76) --
-	(175.66,526.76) --
-	(175.66,525.59) --
-	(188.83,525.59) --
-	(188.83,524.34) --
-	(202.01,524.34) --
-	(202.01,523.00) --
-	(215.19,523.00) --
-	(215.19,521.57) --
-	(228.36,521.57) --
-	(228.36,520.03) --
-	(241.54,520.03) --
-	(241.54,518.38) --
-	(254.72,518.38) --
-	(254.72,516.64) --
-	(267.89,516.64) --
-	(267.89,514.79) --
-	(281.07,514.79) --
-	(281.07,512.92) --
-	(294.25,512.92) --
-	(294.25,511.00);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,550.40) --
+	( 70.24,550.40) --
+	( 70.24,550.29) --
+	( 83.42,550.29) --
+	( 83.42,550.12) --
+	( 96.59,550.12) --
+	( 96.59,549.91) --
+	(109.77,549.91) --
+	(109.77,549.65) --
+	(122.95,549.65) --
+	(122.95,549.35) --
+	(136.12,549.35) --
+	(136.12,549.01) --
+	(149.30,549.01) --
+	(149.30,548.62) --
+	(162.48,548.62) --
+	(162.48,548.18) --
+	(175.66,548.18) --
+	(175.66,547.70) --
+	(188.83,547.70) --
+	(188.83,547.18) --
+	(202.01,547.18) --
+	(202.01,546.62) --
+	(215.19,546.62) --
+	(215.19,546.02) --
+	(228.36,546.02) --
+	(228.36,545.39) --
+	(241.54,545.39) --
+	(241.54,544.72) --
+	(254.72,544.72) --
+	(254.72,544.00) --
+	(267.89,544.00) --
+	(267.89,543.26) --
+	(281.07,543.26) --
+	(281.07,542.47) --
+	(294.25,542.47) --
+	(294.25,541.66);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,531.51) --
-	( 70.24,531.51) --
-	( 70.24,530.38) --
-	( 83.42,530.38) --
-	( 83.42,529.04) --
-	( 96.59,529.04) --
-	( 96.59,527.67) --
-	(109.77,527.67) --
-	(109.77,526.22) --
-	(122.95,526.22) --
-	(122.95,524.74) --
-	(136.12,524.74) --
-	(136.12,523.26) --
-	(149.30,523.26) --
-	(149.30,521.73) --
-	(162.48,521.73) --
-	(162.48,520.19) --
-	(175.66,520.19) --
-	(175.66,518.63) --
-	(188.83,518.63) --
-	(188.83,517.08) --
-	(202.01,517.08) --
-	(202.01,515.54) --
-	(215.19,515.54) --
-	(215.19,514.00) --
-	(228.36,514.00) --
-	(228.36,512.49) --
-	(241.54,512.49) --
-	(241.54,510.97) --
-	(254.72,510.97) --
-	(254.72,509.45) --
-	(267.89,509.45) --
-	(267.89,507.96) --
-	(281.07,507.96) --
-	(281.07,506.46) --
-	(294.25,506.46) --
-	(294.25,504.92);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,549.81) --
+	( 70.24,549.81) --
+	( 70.24,549.07) --
+	( 83.42,549.07) --
+	( 83.42,548.22) --
+	( 96.59,548.22) --
+	( 96.59,547.34) --
+	(109.77,547.34) --
+	(109.77,546.43) --
+	(122.95,546.43) --
+	(122.95,545.51) --
+	(136.12,545.51) --
+	(136.12,544.58) --
+	(149.30,544.58) --
+	(149.30,543.64) --
+	(162.48,543.64) --
+	(162.48,542.68) --
+	(175.66,542.68) --
+	(175.66,541.72) --
+	(188.83,541.72) --
+	(188.83,540.78) --
+	(202.01,540.78) --
+	(202.01,539.85) --
+	(215.19,539.85) --
+	(215.19,538.93) --
+	(228.36,538.93) --
+	(228.36,537.99) --
+	(241.54,537.99) --
+	(241.54,537.05) --
+	(254.72,537.05) --
+	(254.72,536.13) --
+	(267.89,536.13) --
+	(267.89,535.19) --
+	(281.07,535.19) --
+	(281.07,534.30) --
+	(294.25,534.30) --
+	(294.25,533.37);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
-	( 57.06,532.44) --
-	( 57.06,531.12) --
-	( 70.24,531.12) --
-	( 70.24,529.67) --
-	( 83.42,529.67) --
-	( 83.42,527.97) --
-	( 96.59,527.97) --
-	( 96.59,526.22) --
-	(109.77,526.22) --
-	(109.77,524.43) --
-	(122.95,524.43) --
-	(122.95,522.60) --
-	(136.12,522.60) --
-	(136.12,520.76) --
-	(149.30,520.76) --
-	(149.30,518.89) --
-	(162.48,518.89) --
-	(162.48,517.00) --
-	(175.66,517.00) --
-	(175.66,515.09) --
-	(188.83,515.09) --
-	(188.83,513.22) --
-	(202.01,513.22) --
-	(202.01,511.38) --
-	(215.19,511.38) --
-	(215.19,509.55) --
-	(228.36,509.55) --
-	(228.36,507.70) --
-	(241.54,507.70) --
-	(241.54,505.84) --
-	(254.72,505.84) --
-	(254.72,504.00) --
-	(267.89,504.00) --
-	(267.89,502.15) --
-	(281.07,502.15) --
-	(281.07,500.38) --
-	(294.25,500.38) --
-	(294.25,498.55);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,550.47) --
+	( 57.06,550.47) --
+	( 57.06,550.00) --
+	( 70.24,550.00) --
+	( 70.24,549.43) --
+	( 83.42,549.43) --
+	( 83.42,548.76) --
+	( 96.59,548.76) --
+	( 96.59,548.07) --
+	(109.77,548.07) --
+	(109.77,547.34) --
+	(122.95,547.34) --
+	(122.95,546.59) --
+	(136.12,546.59) --
+	(136.12,545.84) --
+	(149.30,545.84) --
+	(149.30,545.07) --
+	(162.48,545.07) --
+	(162.48,544.29) --
+	(175.66,544.29) --
+	(175.66,543.51) --
+	(188.83,543.51) --
+	(188.83,542.72) --
+	(202.01,542.72) --
+	(202.01,541.95) --
+	(215.19,541.95) --
+	(215.19,541.17) --
+	(228.36,541.17) --
+	(228.36,540.41) --
+	(241.54,540.41) --
+	(241.54,539.65) --
+	(254.72,539.65) --
+	(254.72,538.88) --
+	(267.89,538.88) --
+	(267.89,538.12) --
+	(281.07,538.12) --
+	(281.07,537.37) --
+	(294.25,537.37) --
+	(294.25,536.59);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,446.55) rectangle (306.77,536.52);
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.37,351.08) rectangle (306.77,441.05);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,463.90) rectangle (306.77,554.59);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.37,367.70) rectangle (306.77,458.40);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.37,351.08) rectangle (306.77,441.05);
+\path[fill=fillColor] ( 31.37,367.70) rectangle (306.77,458.40);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,370.22) --
-	(306.77,370.22);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,396.92) --
-	(306.77,396.92);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,423.62) --
-	(306.77,423.62);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,351.08) --
-	( 63.65,441.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,351.08) --
-	(129.54,441.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,351.08) --
-	(195.42,441.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,351.08) --
-	(261.31,441.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,356.87) --
-	(306.77,356.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,383.57) --
-	(306.77,383.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,410.27) --
-	(306.77,410.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,436.96) --
-	(306.77,436.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,351.08) --
-	( 96.59,441.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,351.08) --
-	(162.48,441.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,351.08) --
-	(228.36,441.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,351.08) --
-	(294.25,441.05);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,387.00) --
+	(306.77,387.00);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,413.91) --
+	(306.77,413.91);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,440.82) --
+	(306.77,440.82);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,367.70) --
+	( 63.65,458.40);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,367.70) --
+	(129.54,458.40);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,367.70) --
+	(195.42,458.40);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,367.70) --
+	(261.31,458.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,373.54) --
+	(306.77,373.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,400.45) --
+	(306.77,400.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,427.36) --
+	(306.77,427.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,454.28) --
+	(306.77,454.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,367.70) --
+	( 96.59,458.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,367.70) --
+	(162.48,458.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,367.70) --
+	(228.36,458.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,367.70) --
+	(294.25,458.40);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,436.96) --
-	( 70.24,436.96) --
-	( 70.24,436.96) --
-	( 83.42,436.96) --
-	( 83.42,435.74) --
-	( 96.59,435.74) --
-	( 96.59,434.43) --
-	(109.77,434.43) --
-	(109.77,432.98) --
-	(122.95,432.98) --
-	(122.95,431.41) --
-	(136.12,431.41) --
-	(136.12,429.75) --
-	(149.30,429.75) --
-	(149.30,427.98) --
-	(162.48,427.98) --
-	(162.48,426.30) --
-	(175.66,426.30) --
-	(175.66,424.60) --
-	(188.83,424.60) --
-	(188.83,422.98) --
-	(202.01,422.98) --
-	(202.01,421.24) --
-	(215.19,421.24) --
-	(215.19,419.76) --
-	(228.36,419.76) --
-	(228.36,418.14) --
-	(241.54,418.14) --
-	(241.54,416.55) --
-	(254.72,416.55) --
-	(254.72,414.90) --
-	(267.89,414.90) --
-	(267.89,413.35) --
-	(281.07,413.35) --
-	(281.07,411.82) --
-	(294.25,411.82) --
-	(294.25,406.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,454.28) --
+	( 70.24,454.28) --
+	( 70.24,454.28) --
+	( 83.42,454.28) --
+	( 83.42,452.60) --
+	( 96.59,452.60) --
+	( 96.59,450.43) --
+	(109.77,450.43) --
+	(109.77,448.06) --
+	(122.95,448.06) --
+	(122.95,446.01) --
+	(136.12,446.01) --
+	(136.12,443.61) --
+	(149.30,443.61) --
+	(149.30,441.41) --
+	(162.48,441.41) --
+	(162.48,439.32) --
+	(175.66,439.32) --
+	(175.66,437.19) --
+	(188.83,437.19) --
+	(188.83,435.05) --
+	(202.01,435.05) --
+	(202.01,432.88) --
+	(215.19,432.88) --
+	(215.19,431.00) --
+	(228.36,431.00) --
+	(228.36,429.13) --
+	(241.54,429.13) --
+	(241.54,427.20) --
+	(254.72,427.20) --
+	(254.72,425.17) --
+	(267.89,425.17) --
+	(267.89,423.32) --
+	(281.07,423.32) --
+	(281.07,421.41) --
+	(294.25,421.41) --
+	(294.25,414.38);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,436.96) --
-	( 70.24,436.96) --
-	( 70.24,436.96) --
-	( 83.42,436.96) --
-	( 83.42,435.30) --
-	( 96.59,435.30) --
-	( 96.59,433.15) --
-	(109.77,433.15) --
-	(109.77,430.80) --
-	(122.95,430.80) --
-	(122.95,428.76) --
-	(136.12,428.76) --
-	(136.12,426.39) --
-	(149.30,426.39) --
-	(149.30,424.20) --
-	(162.48,424.20) --
-	(162.48,422.13) --
-	(175.66,422.13) --
-	(175.66,420.01) --
-	(188.83,420.01) --
-	(188.83,417.89) --
-	(202.01,417.89) --
-	(202.01,415.73) --
-	(215.19,415.73) --
-	(215.19,413.87) --
-	(228.36,413.87) --
-	(228.36,412.02) --
-	(241.54,412.02) --
-	(241.54,410.11) --
-	(254.72,410.11) --
-	(254.72,408.09) --
-	(267.89,408.09) --
-	(267.89,406.26) --
-	(281.07,406.26) --
-	(281.07,404.36) --
-	(294.25,404.36) --
-	(294.25,397.39);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,454.28) --
+	( 70.24,454.28) --
+	( 70.24,454.28) --
+	( 83.42,454.28) --
+	( 83.42,453.04) --
+	( 96.59,453.04) --
+	( 96.59,451.72) --
+	(109.77,451.72) --
+	(109.77,450.26) --
+	(122.95,450.26) --
+	(122.95,448.67) --
+	(136.12,448.67) --
+	(136.12,447.00) --
+	(149.30,447.00) --
+	(149.30,445.22) --
+	(162.48,445.22) --
+	(162.48,443.53) --
+	(175.66,443.53) --
+	(175.66,441.81) --
+	(188.83,441.81) --
+	(188.83,440.18) --
+	(202.01,440.18) --
+	(202.01,438.43) --
+	(215.19,438.43) --
+	(215.19,436.93) --
+	(228.36,436.93) --
+	(228.36,435.30) --
+	(241.54,435.30) --
+	(241.54,433.70) --
+	(254.72,433.70) --
+	(254.72,432.03) --
+	(267.89,432.03) --
+	(267.89,430.48) --
+	(281.07,430.48) --
+	(281.07,428.93) --
+	(294.25,428.93) --
+	(294.25,423.11);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,436.82) --
-	( 70.24,436.82) --
-	( 70.24,436.59) --
-	( 83.42,436.59) --
-	( 83.42,436.27) --
-	( 96.59,436.27) --
-	( 96.59,435.85) --
-	(109.77,435.85) --
-	(109.77,435.33) --
-	(122.95,435.33) --
-	(122.95,434.71) --
-	(136.12,434.71) --
-	(136.12,434.01) --
-	(149.30,434.01) --
-	(149.30,433.22) --
-	(162.48,433.22) --
-	(162.48,432.33) --
-	(175.66,432.33) --
-	(175.66,431.35) --
-	(188.83,431.35) --
-	(188.83,430.30) --
-	(202.01,430.30) --
-	(202.01,429.17) --
-	(215.19,429.17) --
-	(215.19,427.95) --
-	(228.36,427.95) --
-	(228.36,426.66) --
-	(241.54,426.66) --
-	(241.54,425.30) --
-	(254.72,425.30) --
-	(254.72,423.86) --
-	(267.89,423.86) --
-	(267.89,422.34) --
-	(281.07,422.34) --
-	(281.07,420.76) --
-	(294.25,420.76) --
-	(294.25,419.13);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,454.19) --
+	( 70.24,454.19) --
+	( 70.24,454.04) --
+	( 83.42,454.04) --
+	( 83.42,453.83) --
+	( 96.59,453.83) --
+	( 96.59,453.55) --
+	(109.77,453.55) --
+	(109.77,453.23) --
+	(122.95,453.23) --
+	(122.95,452.86) --
+	(136.12,452.86) --
+	(136.12,452.42) --
+	(149.30,452.42) --
+	(149.30,451.93) --
+	(162.48,451.93) --
+	(162.48,451.37) --
+	(175.66,451.37) --
+	(175.66,450.75) --
+	(188.83,450.75) --
+	(188.83,450.11) --
+	(202.01,450.11) --
+	(202.01,449.41) --
+	(215.19,449.41) --
+	(215.19,448.68) --
+	(228.36,448.68) --
+	(228.36,447.85) --
+	(241.54,447.85) --
+	(241.54,446.97) --
+	(254.72,446.97) --
+	(254.72,446.05) --
+	(267.89,446.05) --
+	(267.89,445.11) --
+	(281.07,445.11) --
+	(281.07,444.11) --
+	(294.25,444.11) --
+	(294.25,443.13);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,436.79) --
-	( 70.24,436.79) --
-	( 70.24,436.50) --
-	( 83.42,436.50) --
-	( 83.42,436.07) --
-	( 96.59,436.07) --
-	( 96.59,435.53) --
-	(109.77,435.53) --
-	(109.77,434.89) --
-	(122.95,434.89) --
-	(122.95,434.16) --
-	(136.12,434.16) --
-	(136.12,433.29) --
-	(149.30,433.29) --
-	(149.30,432.32) --
-	(162.48,432.32) --
-	(162.48,431.20) --
-	(175.66,431.20) --
-	(175.66,429.97) --
-	(188.83,429.97) --
-	(188.83,428.71) --
-	(202.01,428.71) --
-	(202.01,427.33) --
-	(215.19,427.33) --
-	(215.19,425.87) --
-	(228.36,425.87) --
-	(228.36,424.24) --
-	(241.54,424.24) --
-	(241.54,422.48) --
-	(254.72,422.48) --
-	(254.72,420.67) --
-	(267.89,420.67) --
-	(267.89,418.79) --
-	(281.07,418.79) --
-	(281.07,416.82) --
-	(294.25,416.82) --
-	(294.25,414.88);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,454.20) --
+	( 70.24,454.20) --
+	( 70.24,454.09) --
+	( 83.42,454.09) --
+	( 83.42,453.92) --
+	( 96.59,453.92) --
+	( 96.59,453.71) --
+	(109.77,453.71) --
+	(109.77,453.45) --
+	(122.95,453.45) --
+	(122.95,453.14) --
+	(136.12,453.14) --
+	(136.12,452.78) --
+	(149.30,452.78) --
+	(149.30,452.39) --
+	(162.48,452.39) --
+	(162.48,451.94) --
+	(175.66,451.94) --
+	(175.66,451.45) --
+	(188.83,451.45) --
+	(188.83,450.91) --
+	(202.01,450.91) --
+	(202.01,450.34) --
+	(215.19,450.34) --
+	(215.19,449.73) --
+	(228.36,449.73) --
+	(228.36,449.08) --
+	(241.54,449.08) --
+	(241.54,448.39) --
+	(254.72,448.39) --
+	(254.72,447.66) --
+	(267.89,447.66) --
+	(267.89,446.90) --
+	(281.07,446.90) --
+	(281.07,446.10) --
+	(294.25,446.10) --
+	(294.25,445.28);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,436.03) --
-	( 70.24,436.03) --
-	( 70.24,434.88) --
-	( 83.42,434.88) --
-	( 83.42,433.58) --
-	( 96.59,433.58) --
-	( 96.59,432.19) --
-	(109.77,432.19) --
-	(109.77,430.73) --
-	(122.95,430.73) --
-	(122.95,429.19) --
-	(136.12,429.19) --
-	(136.12,427.66) --
-	(149.30,427.66) --
-	(149.30,426.11) --
-	(162.48,426.11) --
-	(162.48,424.54) --
-	(175.66,424.54) --
-	(175.66,422.95) --
-	(188.83,422.95) --
-	(188.83,421.38) --
-	(202.01,421.38) --
-	(202.01,419.81) --
-	(215.19,419.81) --
-	(215.19,418.25) --
-	(228.36,418.25) --
-	(228.36,416.70) --
-	(241.54,416.70) --
-	(241.54,415.15) --
-	(254.72,415.15) --
-	(254.72,413.61) --
-	(267.89,413.61) --
-	(267.89,412.08) --
-	(281.07,412.08) --
-	(281.07,410.56) --
-	(294.25,410.56) --
-	(294.25,409.00);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,453.70) --
+	( 70.24,453.70) --
+	( 70.24,452.96) --
+	( 83.42,452.96) --
+	( 83.42,452.11) --
+	( 96.59,452.11) --
+	( 96.59,451.20) --
+	(109.77,451.20) --
+	(109.77,450.30) --
+	(122.95,450.30) --
+	(122.95,449.39) --
+	(136.12,449.39) --
+	(136.12,448.43) --
+	(149.30,448.43) --
+	(149.30,447.48) --
+	(162.48,447.48) --
+	(162.48,446.47) --
+	(175.66,446.47) --
+	(175.66,445.48) --
+	(188.83,445.48) --
+	(188.83,444.53) --
+	(202.01,444.53) --
+	(202.01,443.58) --
+	(215.19,443.58) --
+	(215.19,442.64) --
+	(228.36,442.64) --
+	(228.36,441.65) --
+	(241.54,441.65) --
+	(241.54,440.66) --
+	(254.72,440.66) --
+	(254.72,439.69) --
+	(267.89,439.69) --
+	(267.89,438.75) --
+	(281.07,438.75) --
+	(281.07,437.80) --
+	(294.25,437.80) --
+	(294.25,436.87);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
-	( 57.06,436.96) --
-	( 57.06,435.82) --
-	( 70.24,435.82) --
-	( 70.24,434.36) --
-	( 83.42,434.36) --
-	( 83.42,432.67) --
-	( 96.59,432.67) --
-	( 96.59,430.87) --
-	(109.77,430.87) --
-	(109.77,429.08) --
-	(122.95,429.08) --
-	(122.95,427.28) --
-	(136.12,427.28) --
-	(136.12,425.38) --
-	(149.30,425.38) --
-	(149.30,423.49) --
-	(162.48,423.49) --
-	(162.48,421.50) --
-	(175.66,421.50) --
-	(175.66,419.53) --
-	(188.83,419.53) --
-	(188.83,417.65) --
-	(202.01,417.65) --
-	(202.01,415.76) --
-	(215.19,415.76) --
-	(215.19,413.91) --
-	(228.36,413.91) --
-	(228.36,411.95) --
-	(241.54,411.95) --
-	(241.54,409.99) --
-	(254.72,409.99) --
-	(254.72,408.06) --
-	(267.89,408.06) --
-	(267.89,406.19) --
-	(281.07,406.19) --
-	(281.07,404.32) --
-	(294.25,404.32) --
-	(294.25,402.48);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,454.28) --
+	( 57.06,454.28) --
+	( 57.06,453.80) --
+	( 70.24,453.80) --
+	( 70.24,453.22) --
+	( 83.42,453.22) --
+	( 83.42,452.57) --
+	( 96.59,452.57) --
+	( 96.59,451.87) --
+	(109.77,451.87) --
+	(109.77,451.13) --
+	(122.95,451.13) --
+	(122.95,450.36) --
+	(136.12,450.36) --
+	(136.12,449.58) --
+	(149.30,449.58) --
+	(149.30,448.80) --
+	(162.48,448.80) --
+	(162.48,448.01) --
+	(175.66,448.01) --
+	(175.66,447.21) --
+	(188.83,447.21) --
+	(188.83,446.41) --
+	(202.01,446.41) --
+	(202.01,445.62) --
+	(215.19,445.62) --
+	(215.19,444.84) --
+	(228.36,444.84) --
+	(228.36,444.05) --
+	(241.54,444.05) --
+	(241.54,443.27) --
+	(254.72,443.27) --
+	(254.72,442.50) --
+	(267.89,442.50) --
+	(267.89,441.72) --
+	(281.07,441.72) --
+	(281.07,440.96) --
+	(294.25,440.96) --
+	(294.25,440.17);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,351.08) rectangle (306.77,441.05);
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.37,255.61) rectangle (306.77,345.58);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,367.70) rectangle (306.77,458.40);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.37,271.51) rectangle (306.77,362.20);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.37,255.61) rectangle (306.77,345.58);
+\path[fill=fillColor] ( 31.37,271.51) rectangle (306.77,362.20);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,274.75) --
-	(306.77,274.75);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,301.45) --
-	(306.77,301.45);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,328.14) --
-	(306.77,328.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,255.61) --
-	( 63.65,345.58);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,255.61) --
-	(129.54,345.58);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,255.61) --
-	(195.42,345.58);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,255.61) --
-	(261.31,345.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,261.40) --
-	(306.77,261.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,288.10) --
-	(306.77,288.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,314.80) --
-	(306.77,314.80);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,341.49) --
-	(306.77,341.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,255.61) --
-	( 96.59,345.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,255.61) --
-	(162.48,345.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,255.61) --
-	(228.36,345.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,255.61) --
-	(294.25,345.58);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,290.80) --
+	(306.77,290.80);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,317.72) --
+	(306.77,317.72);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,344.63) --
+	(306.77,344.63);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,271.51) --
+	( 63.65,362.20);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,271.51) --
+	(129.54,362.20);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,271.51) --
+	(195.42,362.20);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,271.51) --
+	(261.31,362.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,277.35) --
+	(306.77,277.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,304.26) --
+	(306.77,304.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,331.17) --
+	(306.77,331.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,358.08) --
+	(306.77,358.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,271.51) --
+	( 96.59,362.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,271.51) --
+	(162.48,362.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,271.51) --
+	(228.36,362.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,271.51) --
+	(294.25,362.20);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,341.49) --
-	( 70.24,341.49) --
-	( 70.24,341.49) --
-	( 83.42,341.49) --
-	( 83.42,340.45) --
-	( 96.59,340.45) --
-	( 96.59,339.00) --
-	(109.77,339.00) --
-	(109.77,337.47) --
-	(122.95,337.47) --
-	(122.95,335.92) --
-	(136.12,335.92) --
-	(136.12,334.17) --
-	(149.30,334.17) --
-	(149.30,332.43) --
-	(162.48,332.43) --
-	(162.48,330.88) --
-	(175.66,330.88) --
-	(175.66,329.12) --
-	(188.83,329.12) --
-	(188.83,327.55) --
-	(202.01,327.55) --
-	(202.01,325.87) --
-	(215.19,325.87) --
-	(215.19,324.26) --
-	(228.36,324.26) --
-	(228.36,322.63) --
-	(241.54,322.63) --
-	(241.54,321.13) --
-	(254.72,321.13) --
-	(254.72,319.53) --
-	(267.89,319.53) --
-	(267.89,317.83) --
-	(281.07,317.83) --
-	(281.07,316.18) --
-	(294.25,316.18) --
-	(294.25,310.63);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,358.08) --
+	( 70.24,358.08) --
+	( 70.24,358.08) --
+	( 83.42,358.08) --
+	( 83.42,356.34) --
+	( 96.59,356.34) --
+	( 96.59,354.16) --
+	(109.77,354.16) --
+	(109.77,351.76) --
+	(122.95,351.76) --
+	(122.95,349.67) --
+	(136.12,349.67) --
+	(136.12,347.27) --
+	(149.30,347.27) --
+	(149.30,345.06) --
+	(162.48,345.06) --
+	(162.48,342.84) --
+	(175.66,342.84) --
+	(175.66,340.54) --
+	(188.83,340.54) --
+	(188.83,338.31) --
+	(202.01,338.31) --
+	(202.01,335.93) --
+	(215.19,335.93) --
+	(215.19,333.94) --
+	(228.36,333.94) --
+	(228.36,331.95) --
+	(241.54,331.95) --
+	(241.54,330.01) --
+	(254.72,330.01) --
+	(254.72,328.17) --
+	(267.89,328.17) --
+	(267.89,326.25) --
+	(281.07,326.25) --
+	(281.07,324.34) --
+	(294.25,324.34) --
+	(294.25,316.97);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,341.49) --
-	( 70.24,341.49) --
-	( 70.24,341.49) --
-	( 83.42,341.49) --
-	( 83.42,339.77) --
-	( 96.59,339.77) --
-	( 96.59,337.60) --
-	(109.77,337.60) --
-	(109.77,335.22) --
-	(122.95,335.22) --
-	(122.95,333.15) --
-	(136.12,333.15) --
-	(136.12,330.77) --
-	(149.30,330.77) --
-	(149.30,328.58) --
-	(162.48,328.58) --
-	(162.48,326.38) --
-	(175.66,326.38) --
-	(175.66,324.09) --
-	(188.83,324.09) --
-	(188.83,321.88) --
-	(202.01,321.88) --
-	(202.01,319.52) --
-	(215.19,319.52) --
-	(215.19,317.54) --
-	(228.36,317.54) --
-	(228.36,315.57) --
-	(241.54,315.57) --
-	(241.54,313.64) --
-	(254.72,313.64) --
-	(254.72,311.82) --
-	(267.89,311.82) --
-	(267.89,309.92) --
-	(281.07,309.92) --
-	(281.07,308.01) --
-	(294.25,308.01) --
-	(294.25,300.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,358.08) --
+	( 70.24,358.08) --
+	( 70.24,358.08) --
+	( 83.42,358.08) --
+	( 83.42,357.03) --
+	( 96.59,357.03) --
+	( 96.59,355.57) --
+	(109.77,355.57) --
+	(109.77,354.03) --
+	(122.95,354.03) --
+	(122.95,352.47) --
+	(136.12,352.47) --
+	(136.12,350.70) --
+	(149.30,350.70) --
+	(149.30,348.94) --
+	(162.48,348.94) --
+	(162.48,347.38) --
+	(175.66,347.38) --
+	(175.66,345.61) --
+	(188.83,345.61) --
+	(188.83,344.02) --
+	(202.01,344.02) --
+	(202.01,342.34) --
+	(215.19,342.34) --
+	(215.19,340.71) --
+	(228.36,340.71) --
+	(228.36,339.07) --
+	(241.54,339.07) --
+	(241.54,337.55) --
+	(254.72,337.55) --
+	(254.72,335.94) --
+	(267.89,335.94) --
+	(267.89,334.23) --
+	(281.07,334.23) --
+	(281.07,332.57) --
+	(294.25,332.57) --
+	(294.25,326.97);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,341.35) --
-	( 70.24,341.35) --
-	( 70.24,341.12) --
-	( 83.42,341.12) --
-	( 83.42,340.80) --
-	( 96.59,340.80) --
-	( 96.59,340.38) --
-	(109.77,340.38) --
-	(109.77,339.87) --
-	(122.95,339.87) --
-	(122.95,339.28) --
-	(136.12,339.28) --
-	(136.12,338.61) --
-	(149.30,338.61) --
-	(149.30,337.84) --
-	(162.48,337.84) --
-	(162.48,336.98) --
-	(175.66,336.98) --
-	(175.66,336.03) --
-	(188.83,336.03) --
-	(188.83,335.00) --
-	(202.01,335.00) --
-	(202.01,333.89) --
-	(215.19,333.89) --
-	(215.19,332.70) --
-	(228.36,332.70) --
-	(228.36,331.45) --
-	(241.54,331.45) --
-	(241.54,330.12) --
-	(254.72,330.12) --
-	(254.72,328.70) --
-	(267.89,328.70) --
-	(267.89,327.22) --
-	(281.07,327.22) --
-	(281.07,325.67) --
-	(294.25,325.67) --
-	(294.25,324.06);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,357.99) --
+	( 70.24,357.99) --
+	( 70.24,357.83) --
+	( 83.42,357.83) --
+	( 83.42,357.62) --
+	( 96.59,357.62) --
+	( 96.59,357.34) --
+	(109.77,357.34) --
+	(109.77,357.02) --
+	(122.95,357.02) --
+	(122.95,356.63) --
+	(136.12,356.63) --
+	(136.12,356.20) --
+	(149.30,356.20) --
+	(149.30,355.70) --
+	(162.48,355.70) --
+	(162.48,355.16) --
+	(175.66,355.16) --
+	(175.66,354.56) --
+	(188.83,354.56) --
+	(188.83,353.91) --
+	(202.01,353.91) --
+	(202.01,353.20) --
+	(215.19,353.20) --
+	(215.19,352.45) --
+	(228.36,352.45) --
+	(228.36,351.64) --
+	(241.54,351.64) --
+	(241.54,350.80) --
+	(254.72,350.80) --
+	(254.72,349.93) --
+	(267.89,349.93) --
+	(267.89,348.99) --
+	(281.07,348.99) --
+	(281.07,348.03) --
+	(294.25,348.03) --
+	(294.25,347.02);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,341.30) --
-	( 70.24,341.30) --
-	( 70.24,341.00) --
-	( 83.42,341.00) --
-	( 83.42,340.57) --
-	( 96.59,340.57) --
-	( 96.59,340.03) --
-	(109.77,340.03) --
-	(109.77,339.38) --
-	(122.95,339.38) --
-	(122.95,338.61) --
-	(136.12,338.61) --
-	(136.12,337.76) --
-	(149.30,337.76) --
-	(149.30,336.78) --
-	(162.48,336.78) --
-	(162.48,335.71) --
-	(175.66,335.71) --
-	(175.66,334.51) --
-	(188.83,334.51) --
-	(188.83,333.23) --
-	(202.01,333.23) --
-	(202.01,331.82) --
-	(215.19,331.82) --
-	(215.19,330.32) --
-	(228.36,330.32) --
-	(228.36,328.73) --
-	(241.54,328.73) --
-	(241.54,327.07) --
-	(254.72,327.07) --
-	(254.72,325.34) --
-	(267.89,325.34) --
-	(267.89,323.47) --
-	(281.07,323.47) --
-	(281.07,321.56) --
-	(294.25,321.56) --
-	(294.25,319.55);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,358.01) --
+	( 70.24,358.01) --
+	( 70.24,357.90) --
+	( 83.42,357.90) --
+	( 83.42,357.73) --
+	( 96.59,357.73) --
+	( 96.59,357.52) --
+	(109.77,357.52) --
+	(109.77,357.27) --
+	(122.95,357.27) --
+	(122.95,356.96) --
+	(136.12,356.96) --
+	(136.12,356.63) --
+	(149.30,356.63) --
+	(149.30,356.24) --
+	(162.48,356.24) --
+	(162.48,355.81) --
+	(175.66,355.81) --
+	(175.66,355.33) --
+	(188.83,355.33) --
+	(188.83,354.81) --
+	(202.01,354.81) --
+	(202.01,354.25) --
+	(215.19,354.25) --
+	(215.19,353.65) --
+	(228.36,353.65) --
+	(228.36,353.02) --
+	(241.54,353.02) --
+	(241.54,352.34) --
+	(254.72,352.34) --
+	(254.72,351.63) --
+	(267.89,351.63) --
+	(267.89,350.89) --
+	(281.07,350.89) --
+	(281.07,350.10) --
+	(294.25,350.10) --
+	(294.25,349.29);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,340.55) --
-	( 70.24,340.55) --
-	( 70.24,339.42) --
-	( 83.42,339.42) --
-	( 83.42,338.11) --
-	( 96.59,338.11) --
-	( 96.59,336.75) --
-	(109.77,336.75) --
-	(109.77,335.30) --
-	(122.95,335.30) --
-	(122.95,333.82) --
-	(136.12,333.82) --
-	(136.12,332.35) --
-	(149.30,332.35) --
-	(149.30,330.83) --
-	(162.48,330.83) --
-	(162.48,329.30) --
-	(175.66,329.30) --
-	(175.66,327.75) --
-	(188.83,327.75) --
-	(188.83,326.20) --
-	(202.01,326.20) --
-	(202.01,324.66) --
-	(215.19,324.66) --
-	(215.19,323.12) --
-	(228.36,323.12) --
-	(228.36,321.61) --
-	(241.54,321.61) --
-	(241.54,320.09) --
-	(254.72,320.09) --
-	(254.72,318.58) --
-	(267.89,318.58) --
-	(267.89,317.08) --
-	(281.07,317.08) --
-	(281.07,315.59) --
-	(294.25,315.59) --
-	(294.25,314.04);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,357.44) --
+	( 70.24,357.44) --
+	( 70.24,356.69) --
+	( 83.42,356.69) --
+	( 83.42,355.82) --
+	( 96.59,355.82) --
+	( 96.59,354.92) --
+	(109.77,354.92) --
+	(109.77,353.99) --
+	(122.95,353.99) --
+	(122.95,353.03) --
+	(136.12,353.03) --
+	(136.12,352.09) --
+	(149.30,352.09) --
+	(149.30,351.11) --
+	(162.48,351.11) --
+	(162.48,350.15) --
+	(175.66,350.15) --
+	(175.66,349.17) --
+	(188.83,349.17) --
+	(188.83,348.21) --
+	(202.01,348.21) --
+	(202.01,347.23) --
+	(215.19,347.23) --
+	(215.19,346.26) --
+	(228.36,346.26) --
+	(228.36,345.30) --
+	(241.54,345.30) --
+	(241.54,344.36) --
+	(254.72,344.36) --
+	(254.72,343.43) --
+	(267.89,343.43) --
+	(267.89,342.49) --
+	(281.07,342.49) --
+	(281.07,341.58) --
+	(294.25,341.58) --
+	(294.25,340.62);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
-	( 57.06,341.49) --
-	( 57.06,340.23) --
-	( 70.24,340.23) --
-	( 70.24,338.73) --
-	( 83.42,338.73) --
-	( 83.42,337.01) --
-	( 96.59,337.01) --
-	( 96.59,335.22) --
-	(109.77,335.22) --
-	(109.77,333.37) --
-	(122.95,333.37) --
-	(122.95,331.48) --
-	(136.12,331.48) --
-	(136.12,329.61) --
-	(149.30,329.61) --
-	(149.30,327.68) --
-	(162.48,327.68) --
-	(162.48,325.78) --
-	(175.66,325.78) --
-	(175.66,323.83) --
-	(188.83,323.83) --
-	(188.83,321.93) --
-	(202.01,321.93) --
-	(202.01,319.98) --
-	(215.19,319.98) --
-	(215.19,318.06) --
-	(228.36,318.06) --
-	(228.36,316.16) --
-	(241.54,316.16) --
-	(241.54,314.28) --
-	(254.72,314.28) --
-	(254.72,312.45) --
-	(267.89,312.45) --
-	(267.89,310.59) --
-	(281.07,310.59) --
-	(281.07,308.77) --
-	(294.25,308.77) --
-	(294.25,306.87);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,358.08) --
+	( 57.06,358.08) --
+	( 57.06,357.61) --
+	( 70.24,357.61) --
+	( 70.24,357.04) --
+	( 83.42,357.04) --
+	( 83.42,356.38) --
+	( 96.59,356.38) --
+	( 96.59,355.69) --
+	(109.77,355.69) --
+	(109.77,354.96) --
+	(122.95,354.96) --
+	(122.95,354.21) --
+	(136.12,354.21) --
+	(136.12,353.47) --
+	(149.30,353.47) --
+	(149.30,352.71) --
+	(162.48,352.71) --
+	(162.48,351.93) --
+	(175.66,351.93) --
+	(175.66,351.15) --
+	(188.83,351.15) --
+	(188.83,350.37) --
+	(202.01,350.37) --
+	(202.01,349.60) --
+	(215.19,349.60) --
+	(215.19,348.82) --
+	(228.36,348.82) --
+	(228.36,348.05) --
+	(241.54,348.05) --
+	(241.54,347.29) --
+	(254.72,347.29) --
+	(254.72,346.53) --
+	(267.89,346.53) --
+	(267.89,345.77) --
+	(281.07,345.77) --
+	(281.07,345.02) --
+	(294.25,345.02) --
+	(294.25,344.24);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,255.61) rectangle (306.77,345.58);
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.37,160.14) rectangle (306.77,250.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,271.51) rectangle (306.77,362.20);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.37,175.32) rectangle (306.77,266.01);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.37,160.14) rectangle (306.77,250.11);
+\path[fill=fillColor] ( 31.37,175.32) rectangle (306.77,266.01);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,179.28) --
-	(306.77,179.28);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,205.98) --
-	(306.77,205.98);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,232.67) --
-	(306.77,232.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,160.14) --
-	( 63.65,250.11);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,160.14) --
-	(129.54,250.11);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,160.14) --
-	(195.42,250.11);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,160.14) --
-	(261.31,250.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,165.93) --
-	(306.77,165.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,192.63) --
-	(306.77,192.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,219.32) --
-	(306.77,219.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,246.02) --
-	(306.77,246.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,160.14) --
-	( 96.59,250.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,160.14) --
-	(162.48,250.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,160.14) --
-	(228.36,250.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,160.14) --
-	(294.25,250.11);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,194.61) --
+	(306.77,194.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,221.52) --
+	(306.77,221.52);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,248.43) --
+	(306.77,248.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,175.32) --
+	( 63.65,266.01);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,175.32) --
+	(129.54,266.01);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,175.32) --
+	(195.42,266.01);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,175.32) --
+	(261.31,266.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,181.15) --
+	(306.77,181.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,208.07) --
+	(306.77,208.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,234.98) --
+	(306.77,234.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,261.89) --
+	(306.77,261.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,175.32) --
+	( 96.59,266.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,175.32) --
+	(162.48,266.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,175.32) --
+	(228.36,266.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,175.32) --
+	(294.25,266.01);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,246.02) --
-	( 70.24,246.02) --
-	( 70.24,246.02) --
-	( 83.42,246.02) --
-	( 83.42,243.83) --
-	( 96.59,243.83) --
-	( 96.59,240.92) --
-	(109.77,240.92) --
-	(109.77,237.63) --
-	(122.95,237.63) --
-	(122.95,233.74) --
-	(136.12,233.74) --
-	(136.12,229.93) --
-	(149.30,229.93) --
-	(149.30,226.16) --
-	(162.48,226.16) --
-	(162.48,222.32) --
-	(175.66,222.32) --
-	(175.66,218.61) --
-	(188.83,218.61) --
-	(188.83,214.89) --
-	(202.01,214.89) --
-	(202.01,211.14) --
-	(215.19,211.14) --
-	(215.19,207.61) --
-	(228.36,207.61) --
-	(228.36,204.27) --
-	(241.54,204.27) --
-	(241.54,200.76) --
-	(254.72,200.76) --
-	(254.72,197.48) --
-	(267.89,197.48) --
-	(267.89,194.34) --
-	(281.07,194.34) --
-	(281.07,191.11) --
-	(294.25,191.11) --
-	(294.25,180.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,261.89) --
+	( 70.24,261.89) --
+	( 70.24,261.89) --
+	( 83.42,261.89) --
+	( 83.42,259.08) --
+	( 96.59,259.08) --
+	( 96.59,255.06) --
+	(109.77,255.06) --
+	(109.77,250.42) --
+	(122.95,250.42) --
+	(122.95,245.48) --
+	(136.12,245.48) --
+	(136.12,240.64) --
+	(149.30,240.64) --
+	(149.30,235.81) --
+	(162.48,235.81) --
+	(162.48,231.06) --
+	(175.66,231.06) --
+	(175.66,226.27) --
+	(188.83,226.27) --
+	(188.83,221.82) --
+	(202.01,221.82) --
+	(202.01,217.62) --
+	(215.19,217.62) --
+	(215.19,213.63) --
+	(228.36,213.63) --
+	(228.36,209.63) --
+	(241.54,209.63) --
+	(241.54,205.76) --
+	(254.72,205.76) --
+	(254.72,202.12) --
+	(267.89,202.12) --
+	(267.89,198.54) --
+	(281.07,198.54) --
+	(281.07,195.21) --
+	(294.25,195.21) --
+	(294.25,183.05);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,246.02) --
-	( 70.24,246.02) --
-	( 70.24,246.02) --
-	( 83.42,246.02) --
-	( 83.42,243.24) --
-	( 96.59,243.24) --
-	( 96.59,239.25) --
-	(109.77,239.25) --
-	(109.77,234.65) --
-	(122.95,234.65) --
-	(122.95,229.74) --
-	(136.12,229.74) --
-	(136.12,224.94) --
-	(149.30,224.94) --
-	(149.30,220.15) --
-	(162.48,220.15) --
-	(162.48,215.44) --
-	(175.66,215.44) --
-	(175.66,210.69) --
-	(188.83,210.69) --
-	(188.83,206.27) --
-	(202.01,206.27) --
-	(202.01,202.11) --
-	(215.19,202.11) --
-	(215.19,198.14) --
-	(228.36,198.14) --
-	(228.36,194.18) --
-	(241.54,194.18) --
-	(241.54,190.34) --
-	(254.72,190.34) --
-	(254.72,186.73) --
-	(267.89,186.73) --
-	(267.89,183.18) --
-	(281.07,183.18) --
-	(281.07,179.87) --
-	(294.25,179.87) --
-	(294.25,167.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,261.89) --
+	( 70.24,261.89) --
+	( 70.24,261.89) --
+	( 83.42,261.89) --
+	( 83.42,259.68) --
+	( 96.59,259.68) --
+	( 96.59,256.75) --
+	(109.77,256.75) --
+	(109.77,253.43) --
+	(122.95,253.43) --
+	(122.95,249.51) --
+	(136.12,249.51) --
+	(136.12,245.67) --
+	(149.30,245.67) --
+	(149.30,241.87) --
+	(162.48,241.87) --
+	(162.48,238.00) --
+	(175.66,238.00) --
+	(175.66,234.26) --
+	(188.83,234.26) --
+	(188.83,230.51) --
+	(202.01,230.51) --
+	(202.01,226.73) --
+	(215.19,226.73) --
+	(215.19,223.17) --
+	(228.36,223.17) --
+	(228.36,219.80) --
+	(241.54,219.80) --
+	(241.54,216.27) --
+	(254.72,216.27) --
+	(254.72,212.95) --
+	(267.89,212.95) --
+	(267.89,209.79) --
+	(281.07,209.79) --
+	(281.07,206.54) --
+	(294.25,206.54) --
+	(294.25,195.49);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,245.72) --
-	( 70.24,245.72) --
-	( 70.24,245.22) --
-	( 83.42,245.22) --
-	( 83.42,244.49) --
-	( 96.59,244.49) --
-	( 96.59,243.55) --
-	(109.77,243.55) --
-	(109.77,242.36) --
-	(122.95,242.36) --
-	(122.95,240.98) --
-	(136.12,240.98) --
-	(136.12,239.40) --
-	(149.30,239.40) --
-	(149.30,237.63) --
-	(162.48,237.63) --
-	(162.48,235.66) --
-	(175.66,235.66) --
-	(175.66,233.45) --
-	(188.83,233.45) --
-	(188.83,231.09) --
-	(202.01,231.09) --
-	(202.01,228.56) --
-	(215.19,228.56) --
-	(215.19,225.87) --
-	(228.36,225.87) --
-	(228.36,223.01) --
-	(241.54,223.01) --
-	(241.54,219.97) --
-	(254.72,219.97) --
-	(254.72,216.86) --
-	(267.89,216.86) --
-	(267.89,213.57) --
-	(281.07,213.57) --
-	(281.07,210.22) --
-	(294.25,210.22) --
-	(294.25,206.69);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,261.67) --
+	( 70.24,261.67) --
+	( 70.24,261.33) --
+	( 83.42,261.33) --
+	( 83.42,260.85) --
+	( 96.59,260.85) --
+	( 96.59,260.25) --
+	(109.77,260.25) --
+	(109.77,259.53) --
+	(122.95,259.53) --
+	(122.95,258.68) --
+	(136.12,258.68) --
+	(136.12,257.72) --
+	(149.30,257.72) --
+	(149.30,256.64) --
+	(162.48,256.64) --
+	(162.48,255.46) --
+	(175.66,255.46) --
+	(175.66,254.15) --
+	(188.83,254.15) --
+	(188.83,252.72) --
+	(202.01,252.72) --
+	(202.01,251.20) --
+	(215.19,251.20) --
+	(215.19,249.60) --
+	(228.36,249.60) --
+	(228.36,247.86) --
+	(241.54,247.86) --
+	(241.54,246.02) --
+	(254.72,246.02) --
+	(254.72,244.09) --
+	(267.89,244.09) --
+	(267.89,242.17) --
+	(281.07,242.17) --
+	(281.07,240.14) --
+	(294.25,240.14) --
+	(294.25,238.16);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,245.59) --
-	( 70.24,245.59) --
-	( 70.24,244.91) --
-	( 83.42,244.91) --
-	( 83.42,243.97) --
-	( 96.59,243.97) --
-	( 96.59,242.78) --
-	(109.77,242.78) --
-	(109.77,241.36) --
-	(122.95,241.36) --
-	(122.95,239.66) --
-	(136.12,239.66) --
-	(136.12,237.77) --
-	(149.30,237.77) --
-	(149.30,235.63) --
-	(162.48,235.63) --
-	(162.48,233.29) --
-	(175.66,233.29) --
-	(175.66,230.69) --
-	(188.83,230.69) --
-	(188.83,227.85) --
-	(202.01,227.85) --
-	(202.01,224.84) --
-	(215.19,224.84) --
-	(215.19,221.67) --
-	(228.36,221.67) --
-	(228.36,218.22) --
-	(241.54,218.22) --
-	(241.54,214.58) --
-	(254.72,214.58) --
-	(254.72,210.76) --
-	(267.89,210.76) --
-	(267.89,206.94) --
-	(281.07,206.94) --
-	(281.07,202.93) --
-	(294.25,202.93) --
-	(294.25,199.00);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,261.74) --
+	( 70.24,261.74) --
+	( 70.24,261.48) --
+	( 83.42,261.48) --
+	( 83.42,261.11) --
+	( 96.59,261.11) --
+	( 96.59,260.64) --
+	(109.77,260.64) --
+	(109.77,260.04) --
+	(122.95,260.04) --
+	(122.95,259.34) --
+	(136.12,259.34) --
+	(136.12,258.54) --
+	(149.30,258.54) --
+	(149.30,257.65) --
+	(162.48,257.65) --
+	(162.48,256.66) --
+	(175.66,256.66) --
+	(175.66,255.54) --
+	(188.83,255.54) --
+	(188.83,254.35) --
+	(202.01,254.35) --
+	(202.01,253.08) --
+	(215.19,253.08) --
+	(215.19,251.72) --
+	(228.36,251.72) --
+	(228.36,250.28) --
+	(241.54,250.28) --
+	(241.54,248.74) --
+	(254.72,248.74) --
+	(254.72,247.17) --
+	(267.89,247.17) --
+	(267.89,245.51) --
+	(281.07,245.51) --
+	(281.07,243.82) --
+	(294.25,243.82) --
+	(294.25,242.04);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,244.05) --
-	( 70.24,244.05) --
-	( 70.24,241.55) --
-	( 83.42,241.55) --
-	( 83.42,238.62) --
-	( 96.59,238.62) --
-	( 96.59,235.52) --
-	(109.77,235.52) --
-	(109.77,232.18) --
-	(122.95,232.18) --
-	(122.95,228.78) --
-	(136.12,228.78) --
-	(136.12,225.36) --
-	(149.30,225.36) --
-	(149.30,221.94) --
-	(162.48,221.94) --
-	(162.48,218.49) --
-	(175.66,218.49) --
-	(175.66,214.98) --
-	(188.83,214.98) --
-	(188.83,211.54) --
-	(202.01,211.54) --
-	(202.01,208.13) --
-	(215.19,208.13) --
-	(215.19,204.78) --
-	(228.36,204.78) --
-	(228.36,201.47) --
-	(241.54,201.47) --
-	(241.54,198.16) --
-	(254.72,198.16) --
-	(254.72,194.99) --
-	(267.89,194.99) --
-	(267.89,191.84) --
-	(281.07,191.84) --
-	(281.07,188.80) --
-	(294.25,188.80) --
-	(294.25,185.60);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,260.44) --
+	( 70.24,260.44) --
+	( 70.24,258.73) --
+	( 83.42,258.73) --
+	( 83.42,256.84) --
+	( 96.59,256.84) --
+	( 96.59,254.87) --
+	(109.77,254.87) --
+	(109.77,252.86) --
+	(122.95,252.86) --
+	(122.95,250.78) --
+	(136.12,250.78) --
+	(136.12,248.73) --
+	(149.30,248.73) --
+	(149.30,246.66) --
+	(162.48,246.66) --
+	(162.48,244.62) --
+	(175.66,244.62) --
+	(175.66,242.57) --
+	(188.83,242.57) --
+	(188.83,240.51) --
+	(202.01,240.51) --
+	(202.01,238.51) --
+	(215.19,238.51) --
+	(215.19,236.56) --
+	(228.36,236.56) --
+	(228.36,234.58) --
+	(241.54,234.58) --
+	(241.54,232.63) --
+	(254.72,232.63) --
+	(254.72,230.71) --
+	(267.89,230.71) --
+	(267.89,228.91) --
+	(281.07,228.91) --
+	(281.07,227.12) --
+	(294.25,227.12) --
+	(294.25,225.36);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
-	( 57.06,246.02) --
-	( 57.06,243.15) --
-	( 70.24,243.15) --
-	( 70.24,239.77) --
-	( 83.42,239.77) --
-	( 83.42,236.02) --
-	( 96.59,236.02) --
-	( 96.59,232.11) --
-	(109.77,232.11) --
-	(109.77,228.13) --
-	(122.95,228.13) --
-	(122.95,224.01) --
-	(136.12,224.01) --
-	(136.12,219.94) --
-	(149.30,219.94) --
-	(149.30,215.85) --
-	(162.48,215.85) --
-	(162.48,211.80) --
-	(175.66,211.80) --
-	(175.66,207.73) --
-	(188.83,207.73) --
-	(188.83,203.66) --
-	(202.01,203.66) --
-	(202.01,199.70) --
-	(215.19,199.70) --
-	(215.19,195.82) --
-	(228.36,195.82) --
-	(228.36,191.90) --
-	(241.54,191.90) --
-	(241.54,188.04) --
-	(254.72,188.04) --
-	(254.72,184.24) --
-	(267.89,184.24) --
-	(267.89,180.67) --
-	(281.07,180.67) --
-	(281.07,177.12) --
-	(294.25,177.12) --
-	(294.25,173.64);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,261.89) --
+	( 57.06,261.89) --
+	( 57.06,260.89) --
+	( 70.24,260.89) --
+	( 70.24,259.63) --
+	( 83.42,259.63) --
+	( 83.42,258.16) --
+	( 96.59,258.16) --
+	( 96.59,256.59) --
+	(109.77,256.59) --
+	(109.77,254.90) --
+	(122.95,254.90) --
+	(122.95,253.19) --
+	(136.12,253.19) --
+	(136.12,251.46) --
+	(149.30,251.46) --
+	(149.30,249.74) --
+	(162.48,249.74) --
+	(162.48,248.00) --
+	(175.66,248.00) --
+	(175.66,246.22) --
+	(188.83,246.22) --
+	(188.83,244.49) --
+	(202.01,244.49) --
+	(202.01,242.77) --
+	(215.19,242.77) --
+	(215.19,241.08) --
+	(228.36,241.08) --
+	(228.36,239.40) --
+	(241.54,239.40) --
+	(241.54,237.74) --
+	(254.72,237.74) --
+	(254.72,236.14) --
+	(267.89,236.14) --
+	(267.89,234.55) --
+	(281.07,234.55) --
+	(281.07,233.01) --
+	(294.25,233.01) --
+	(294.25,231.39);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,160.14) rectangle (306.77,250.11);
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.37, 64.67) rectangle (306.77,154.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,175.32) rectangle (306.77,266.01);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.37, 79.12) rectangle (306.77,169.82);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,154.64);
+\path[fill=fillColor] ( 31.37, 79.12) rectangle (306.77,169.82);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 83.81) --
-	(306.77, 83.81);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,110.50) --
-	(306.77,110.50);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,137.20) --
-	(306.77,137.20);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
-	( 63.65,154.64);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
-	(129.54,154.64);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
-	(195.42,154.64);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
-	(261.31,154.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 70.46) --
-	(306.77, 70.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 97.16) --
-	(306.77, 97.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,123.85) --
-	(306.77,123.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,150.55) --
-	(306.77,150.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
-	( 96.59,154.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
-	(162.48,154.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
-	(228.36,154.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
-	(294.25,154.64);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 98.42) --
+	(306.77, 98.42);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,125.33) --
+	(306.77,125.33);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,152.24) --
+	(306.77,152.24);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 79.12) --
+	( 63.65,169.82);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 79.12) --
+	(129.54,169.82);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 79.12) --
+	(195.42,169.82);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 79.12) --
+	(261.31,169.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 84.96) --
+	(306.77, 84.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,111.87) --
+	(306.77,111.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,138.78) --
+	(306.77,138.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,165.69) --
+	(306.77,165.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 79.12) --
+	( 96.59,169.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 79.12) --
+	(162.48,169.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 79.12) --
+	(228.36,169.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 79.12) --
+	(294.25,169.82);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,150.55) --
-	( 70.24,150.55) --
-	( 70.24,150.55) --
-	( 83.42,150.55) --
-	( 83.42,147.28) --
-	( 96.59,147.28) --
-	( 96.59,143.70) --
-	(109.77,143.70) --
-	(109.77,139.54) --
-	(122.95,139.54) --
-	(122.95,135.49) --
-	(136.12,135.49) --
-	(136.12,131.43) --
-	(149.30,131.43) --
-	(149.30,127.27) --
-	(162.48,127.27) --
-	(162.48,123.40) --
-	(175.66,123.40) --
-	(175.66,119.60) --
-	(188.83,119.60) --
-	(188.83,115.97) --
-	(202.01,115.97) --
-	(202.01,112.27) --
-	(215.19,112.27) --
-	(215.19,108.52) --
-	(228.36,108.52) --
-	(228.36,105.14) --
-	(241.54,105.14) --
-	(241.54,101.84) --
-	(254.72,101.84) --
-	(254.72, 98.62) --
-	(267.89, 98.62) --
-	(267.89, 95.61) --
-	(281.07, 95.61) --
-	(281.07, 92.76) --
-	(294.25, 92.76) --
-	(294.25, 81.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,165.69) --
+	( 70.24,165.69) --
+	( 70.24,165.69) --
+	( 83.42,165.69) --
+	( 83.42,161.51) --
+	( 96.59,161.51) --
+	( 96.59,155.98) --
+	(109.77,155.98) --
+	(109.77,150.36) --
+	(122.95,150.36) --
+	(122.95,145.14) --
+	(136.12,145.14) --
+	(136.12,139.89) --
+	(149.30,139.89) --
+	(149.30,135.11) --
+	(162.48,135.11) --
+	(162.48,130.39) --
+	(175.66,130.39) --
+	(175.66,125.41) --
+	(188.83,125.41) --
+	(188.83,120.90) --
+	(202.01,120.90) --
+	(202.01,116.83) --
+	(215.19,116.83) --
+	(215.19,112.86) --
+	(228.36,112.86) --
+	(228.36,109.19) --
+	(241.54,109.19) --
+	(241.54,105.56) --
+	(254.72,105.56) --
+	(254.72,101.91) --
+	(267.89,101.91) --
+	(267.89, 98.28) --
+	(281.07, 98.28) --
+	(281.07, 95.14) --
+	(294.25, 95.14) --
+	(294.25, 83.24);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,150.55) --
-	( 70.24,150.55) --
-	( 70.24,150.55) --
-	( 83.42,150.55) --
-	( 83.42,146.40) --
-	( 96.59,146.40) --
-	( 96.59,140.92) --
-	(109.77,140.92) --
-	(109.77,135.34) --
-	(122.95,135.34) --
-	(122.95,130.16) --
-	(136.12,130.16) --
-	(136.12,124.95) --
-	(149.30,124.95) --
-	(149.30,120.21) --
-	(162.48,120.21) --
-	(162.48,115.52) --
-	(175.66,115.52) --
-	(175.66,110.59) --
-	(188.83,110.59) --
-	(188.83,106.11) --
-	(202.01,106.11) --
-	(202.01,102.07) --
-	(215.19,102.07) --
-	(215.19, 98.13) --
-	(228.36, 98.13) --
-	(228.36, 94.49) --
-	(241.54, 94.49) --
-	(241.54, 90.89) --
-	(254.72, 90.89) --
-	(254.72, 87.28) --
-	(267.89, 87.28) --
-	(267.89, 83.67) --
-	(281.07, 83.67) --
-	(281.07, 80.56) --
-	(294.25, 80.56) --
-	(294.25, 68.76);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,165.69) --
+	( 70.24,165.69) --
+	( 70.24,165.69) --
+	( 83.42,165.69) --
+	( 83.42,162.40) --
+	( 96.59,162.40) --
+	( 96.59,158.79) --
+	(109.77,158.79) --
+	(109.77,154.59) --
+	(122.95,154.59) --
+	(122.95,150.52) --
+	(136.12,150.52) --
+	(136.12,146.42) --
+	(149.30,146.42) --
+	(149.30,142.23) --
+	(162.48,142.23) --
+	(162.48,138.32) --
+	(175.66,138.32) --
+	(175.66,134.49) --
+	(188.83,134.49) --
+	(188.83,130.84) --
+	(202.01,130.84) --
+	(202.01,127.10) --
+	(215.19,127.10) --
+	(215.19,123.32) --
+	(228.36,123.32) --
+	(228.36,119.92) --
+	(241.54,119.92) --
+	(241.54,116.59) --
+	(254.72,116.59) --
+	(254.72,113.35) --
+	(267.89,113.35) --
+	(267.89,110.31) --
+	(281.07,110.31) --
+	(281.07,107.44) --
+	(294.25,107.44) --
+	(294.25, 96.23);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,150.18) --
-	( 70.24,150.18) --
-	( 70.24,149.60) --
-	( 83.42,149.60) --
-	( 83.42,148.79) --
-	( 96.59,148.79) --
-	( 96.59,147.79) --
-	(109.77,147.79) --
-	(109.77,146.60) --
-	(122.95,146.60) --
-	(122.95,145.20) --
-	(136.12,145.20) --
-	(136.12,143.61) --
-	(149.30,143.61) --
-	(149.30,141.83) --
-	(162.48,141.83) --
-	(162.48,139.86) --
-	(175.66,139.86) --
-	(175.66,137.70) --
-	(188.83,137.70) --
-	(188.83,135.37) --
-	(202.01,135.37) --
-	(202.01,132.84) --
-	(215.19,132.84) --
-	(215.19,130.16) --
-	(228.36,130.16) --
-	(228.36,127.31) --
-	(241.54,127.31) --
-	(241.54,124.33) --
-	(254.72,124.33) --
-	(254.72,121.21) --
-	(267.89,121.21) --
-	(267.89,117.94) --
-	(281.07,117.94) --
-	(281.07,114.58) --
-	(294.25,114.58) --
-	(294.25,111.11);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,165.35) --
+	( 70.24,165.35) --
+	( 70.24,164.83) --
+	( 83.42,164.83) --
+	( 83.42,164.11) --
+	( 96.59,164.11) --
+	( 96.59,163.21) --
+	(109.77,163.21) --
+	(109.77,162.12) --
+	(122.95,162.12) --
+	(122.95,160.90) --
+	(136.12,160.90) --
+	(136.12,159.52) --
+	(149.30,159.52) --
+	(149.30,157.94) --
+	(162.48,157.94) --
+	(162.48,156.22) --
+	(175.66,156.22) --
+	(175.66,154.34) --
+	(188.83,154.34) --
+	(188.83,152.30) --
+	(202.01,152.30) --
+	(202.01,150.10) --
+	(215.19,150.10) --
+	(215.19,147.78) --
+	(228.36,147.78) --
+	(228.36,145.35) --
+	(241.54,145.35) --
+	(241.54,142.80) --
+	(254.72,142.80) --
+	(254.72,140.11) --
+	(267.89,140.11) --
+	(267.89,137.29) --
+	(281.07,137.29) --
+	(281.07,134.36) --
+	(294.25,134.36) --
+	(294.25,131.32);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,150.07) --
-	( 70.24,150.07) --
-	( 70.24,149.32) --
-	( 83.42,149.32) --
-	( 83.42,148.30) --
-	( 96.59,148.30) --
-	( 96.59,147.04) --
-	(109.77,147.04) --
-	(109.77,145.50) --
-	(122.95,145.50) --
-	(122.95,143.83) --
-	(136.12,143.83) --
-	(136.12,141.94) --
-	(149.30,141.94) --
-	(149.30,139.74) --
-	(162.48,139.74) --
-	(162.48,137.40) --
-	(175.66,137.40) --
-	(175.66,134.81) --
-	(188.83,134.81) --
-	(188.83,132.03) --
-	(202.01,132.03) --
-	(202.01,129.02) --
-	(215.19,129.02) --
-	(215.19,125.87) --
-	(228.36,125.87) --
-	(228.36,122.58) --
-	(241.54,122.58) --
-	(241.54,119.15) --
-	(254.72,119.15) --
-	(254.72,115.52) --
-	(267.89,115.52) --
-	(267.89,111.71) --
-	(281.07,111.71) --
-	(281.07,107.78) --
-	(294.25,107.78) --
-	(294.25,103.68);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,165.44) --
+	( 70.24,165.44) --
+	( 70.24,165.03) --
+	( 83.42,165.03) --
+	( 83.42,164.45) --
+	( 96.59,164.45) --
+	( 96.59,163.74) --
+	(109.77,163.74) --
+	(109.77,162.88) --
+	(122.95,162.88) --
+	(122.95,161.88) --
+	(136.12,161.88) --
+	(136.12,160.73) --
+	(149.30,160.73) --
+	(149.30,159.45) --
+	(162.48,159.45) --
+	(162.48,158.02) --
+	(175.66,158.02) --
+	(175.66,156.45) --
+	(188.83,156.45) --
+	(188.83,154.75) --
+	(202.01,154.75) --
+	(202.01,152.92) --
+	(215.19,152.92) --
+	(215.19,150.98) --
+	(228.36,150.98) --
+	(228.36,148.91) --
+	(241.54,148.91) --
+	(241.54,146.73) --
+	(254.72,146.73) --
+	(254.72,144.45) --
+	(267.89,144.45) --
+	(267.89,142.05) --
+	(281.07,142.05) --
+	(281.07,139.57) --
+	(294.25,139.57) --
+	(294.25,137.02);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,148.08) --
-	( 70.24,148.08) --
-	( 70.24,145.17) --
-	( 83.42,145.17) --
-	( 83.42,141.98) --
-	( 96.59,141.98) --
-	( 96.59,138.67) --
-	(109.77,138.67) --
-	(109.77,135.32) --
-	(122.95,135.32) --
-	(122.95,131.90) --
-	(136.12,131.90) --
-	(136.12,128.47) --
-	(149.30,128.47) --
-	(149.30,125.04) --
-	(162.48,125.04) --
-	(162.48,121.61) --
-	(175.66,121.61) --
-	(175.66,118.18) --
-	(188.83,118.18) --
-	(188.83,114.80) --
-	(202.01,114.80) --
-	(202.01,111.42) --
-	(215.19,111.42) --
-	(215.19,108.10) --
-	(228.36,108.10) --
-	(228.36,104.80) --
-	(241.54,104.80) --
-	(241.54,101.58) --
-	(254.72,101.58) --
-	(254.72, 98.42) --
-	(267.89, 98.42) --
-	(267.89, 95.30) --
-	(281.07, 95.30) --
-	(281.07, 92.26) --
-	(294.25, 92.26) --
-	(294.25, 89.13);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,163.41) --
+	( 70.24,163.41) --
+	( 70.24,160.81) --
+	( 83.42,160.81) --
+	( 83.42,157.93) --
+	( 96.59,157.93) --
+	( 96.59,154.99) --
+	(109.77,154.99) --
+	(109.77,151.91) --
+	(122.95,151.91) --
+	(122.95,148.94) --
+	(136.12,148.94) --
+	(136.12,145.97) --
+	(149.30,145.97) --
+	(149.30,142.91) --
+	(162.48,142.91) --
+	(162.48,139.94) --
+	(175.66,139.94) --
+	(175.66,136.96) --
+	(188.83,136.96) --
+	(188.83,134.01) --
+	(202.01,134.01) --
+	(202.01,131.07) --
+	(215.19,131.07) --
+	(215.19,128.21) --
+	(228.36,128.21) --
+	(228.36,125.40) --
+	(241.54,125.40) --
+	(241.54,122.65) --
+	(254.72,122.65) --
+	(254.72,119.93) --
+	(267.89,119.93) --
+	(267.89,117.23) --
+	(281.07,117.23) --
+	(281.07,114.59) --
+	(294.25,114.59) --
+	(294.25,111.85);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
-	( 57.06,150.55) --
-	( 57.06,147.32) --
-	( 70.24,147.32) --
-	( 70.24,143.59) --
-	( 83.42,143.59) --
-	( 83.42,139.53) --
-	( 96.59,139.53) --
-	( 96.59,135.42) --
-	(109.77,135.42) --
-	(109.77,131.09) --
-	(122.95,131.09) --
-	(122.95,127.04) --
-	(136.12,127.04) --
-	(136.12,122.99) --
-	(149.30,122.99) --
-	(149.30,118.80) --
-	(162.48,118.80) --
-	(162.48,114.77) --
-	(175.66,114.77) --
-	(175.66,110.73) --
-	(188.83,110.73) --
-	(188.83,106.75) --
-	(202.01,106.75) --
-	(202.01,102.80) --
-	(215.19,102.80) --
-	(215.19, 98.97) --
-	(228.36, 98.97) --
-	(228.36, 95.25) --
-	(241.54, 95.25) --
-	(241.54, 91.63) --
-	(254.72, 91.63) --
-	(254.72, 88.04) --
-	(267.89, 88.04) --
-	(267.89, 84.49) --
-	(281.07, 84.49) --
-	(281.07, 81.02) --
-	(294.25, 81.02) --
-	(294.25, 77.41);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,165.69) --
+	( 57.06,165.69) --
+	( 57.06,163.98) --
+	( 70.24,163.98) --
+	( 70.24,161.94) --
+	( 83.42,161.94) --
+	( 83.42,159.66) --
+	( 96.59,159.66) --
+	( 96.59,157.30) --
+	(109.77,157.30) --
+	(109.77,154.88) --
+	(122.95,154.88) --
+	(122.95,152.41) --
+	(136.12,152.41) --
+	(136.12,149.93) --
+	(149.30,149.93) --
+	(149.30,147.44) --
+	(162.48,147.44) --
+	(162.48,144.92) --
+	(175.66,144.92) --
+	(175.66,142.41) --
+	(188.83,142.41) --
+	(188.83,139.93) --
+	(202.01,139.93) --
+	(202.01,137.45) --
+	(215.19,137.45) --
+	(215.19,135.00) --
+	(228.36,135.00) --
+	(228.36,132.58) --
+	(241.54,132.58) --
+	(241.54,130.19) --
+	(254.72,130.19) --
+	(254.72,127.83) --
+	(267.89,127.83) --
+	(267.89,125.50) --
+	(281.07,125.50) --
+	(281.07,123.22) --
+	(294.25,123.22) --
+	(294.25,120.87);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,154.64);
-\end{scope}
-\begin{scope}
-\path[clip] (306.77,446.55) rectangle (319.71,536.52);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 79.12) rectangle (306.77,169.82);
+\end{scope}
+\begin{scope}
+\path[clip] (306.77,463.90) rectangle (319.71,554.59);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,446.55) rectangle (319.71,536.52);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,463.90) rectangle (319.71,554.59);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,491.54) {Scenario 1};
-\end{scope}
-\begin{scope}
-\path[clip] (306.77,351.08) rectangle (319.71,441.05);
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,509.25) {Scenario 1};
+\end{scope}
+\begin{scope}
+\path[clip] (306.77,367.70) rectangle (319.71,458.40);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,351.08) rectangle (319.71,441.05);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,367.70) rectangle (319.71,458.40);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,396.07) {Scenario 2};
-\end{scope}
-\begin{scope}
-\path[clip] (306.77,255.61) rectangle (319.71,345.58);
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,413.05) {Scenario 2};
+\end{scope}
+\begin{scope}
+\path[clip] (306.77,271.51) rectangle (319.71,362.20);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,255.61) rectangle (319.71,345.58);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,271.51) rectangle (319.71,362.20);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,300.60) {Scenario 3};
-\end{scope}
-\begin{scope}
-\path[clip] (306.77,160.14) rectangle (319.71,250.11);
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,316.86) {Scenario 3};
+\end{scope}
+\begin{scope}
+\path[clip] (306.77,175.32) rectangle (319.71,266.01);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,160.14) rectangle (319.71,250.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,175.32) rectangle (319.71,266.01);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,205.12) {Scenario 4};
-\end{scope}
-\begin{scope}
-\path[clip] (306.77, 64.67) rectangle (319.71,154.64);
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,220.66) {Scenario 4};
+\end{scope}
+\begin{scope}
+\path[clip] (306.77, 79.12) rectangle (319.71,169.82);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,154.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 79.12) rectangle (319.71,169.82);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,109.65) {Scenario 5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,124.47) {Scenario 5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
-	( 96.59, 64.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
-	(162.48, 64.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
-	(228.36, 64.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
-	(294.25, 64.67);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 76.37) --
+	( 96.59, 79.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 76.37) --
+	(162.48, 79.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 76.37) --
+	(228.36, 79.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 76.37) --
+	(294.25, 79.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 68.66) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 68.66) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 68.66) {15};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 68.66) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,449.59) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,476.29) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,502.98) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,529.68) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,466.98) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,493.89) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,520.80) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,547.72) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,452.35) --
-	( 31.37,452.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,479.04) --
-	( 31.37,479.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,505.74) --
-	( 31.37,505.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,532.44) --
-	( 31.37,532.44);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,469.74) --
+	( 31.37,469.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,496.65) --
+	( 31.37,496.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,523.56) --
+	( 31.37,523.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,550.47) --
+	( 31.37,550.47);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,354.12) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,380.82) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,407.51) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,434.21) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,370.79) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,397.70) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,424.61) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,451.52) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,356.87) --
-	( 31.37,356.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,383.57) --
-	( 31.37,383.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,410.27) --
-	( 31.37,410.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,436.96) --
-	( 31.37,436.96);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,373.54) --
+	( 31.37,373.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,400.45) --
+	( 31.37,400.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,427.36) --
+	( 31.37,427.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,454.28) --
+	( 31.37,454.28);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,258.65) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,285.34) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,312.04) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,338.74) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,274.59) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,301.50) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,328.42) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,355.33) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,261.40) --
-	( 31.37,261.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,288.10) --
-	( 31.37,288.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,314.80) --
-	( 31.37,314.80);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,341.49) --
-	( 31.37,341.49);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,277.35) --
+	( 31.37,277.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,304.26) --
+	( 31.37,304.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,331.17) --
+	( 31.37,331.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,358.08) --
+	( 31.37,358.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,163.18) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,189.87) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,216.57) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,243.27) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,178.40) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,205.31) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,232.22) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,259.13) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,165.93) --
-	( 31.37,165.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,192.63) --
-	( 31.37,192.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,219.32) --
-	( 31.37,219.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,246.02) --
-	( 31.37,246.02);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,181.15) --
+	( 31.37,181.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,208.07) --
+	( 31.37,208.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,234.98) --
+	( 31.37,234.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,261.89) --
+	( 31.37,261.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 67.70) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 94.40) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,121.10) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,147.79) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 82.21) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,109.12) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,136.03) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,162.94) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 70.46) --
-	( 31.37, 70.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 97.16) --
-	( 31.37, 97.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,123.85) --
-	( 31.37,123.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,150.55) --
-	( 31.37,150.55);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 84.96) --
+	( 31.37, 84.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,111.87) --
+	( 31.37,111.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,138.78) --
+	( 31.37,138.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,165.69) --
+	( 31.37,165.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Time since hire};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 58.16) {Years since hire};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,300.60) {Cancer-free survival};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,316.86) {Cancer-free survival};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] ( 55.91, 30.95) rectangle (282.22, 45.41);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] ( 61.41, 30.95) rectangle ( 75.86, 45.41);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{248,118,109}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.86, 38.18) -- ( 74.42, 38.18);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] (205.46, 30.95) rectangle (219.91, 45.41);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,191,196}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.91, 38.18) -- (218.47, 38.18);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 81.36, 35.08) {Always exposed while at work};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (225.41, 35.08) {Never exposed};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] ( 92.13,  5.50) rectangle (246.00, 19.95);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] ( 97.63,  5.50) rectangle (112.09, 19.95);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.08, 12.73) -- (110.64, 12.73);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] (145.86,  5.50) rectangle (160.31, 19.95);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.30, 12.73) -- (158.87, 12.73);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[fill=fillColor] (195.80,  5.50) rectangle (210.26, 19.95);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.25, 12.73) -- (208.81, 12.73);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (117.59,  9.63) {Truth};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (165.81,  9.63) {WKM};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (215.76,  9.63) {AWKM};
 \end{scope}

### 2022-03-04 reports/resources/sensitivity/results.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 11:19:01
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,542.02);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,542.02);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,466.60) --
	(306.77,466.60);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,492.93) --
	(306.77,492.93);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,519.27) --
	(306.77,519.27);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,446.55) --
	( 63.65,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,446.55) --
	(129.54,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,446.55) --
	(195.42,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,446.55) --
	(261.31,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,453.43) --
	(306.77,453.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,479.77) --
	(306.77,479.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,506.10) --
	(306.77,506.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,532.44) --
	(306.77,532.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,446.55) --
	( 96.59,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,446.55) --
	(162.48,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,446.55) --
	(228.36,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,446.55) --
	(294.25,536.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,531.33) --
	( 96.59,531.33) --
	( 96.59,530.06) --
	(109.77,530.06) --
	(109.77,528.69) --
	(122.95,528.69) --
	(122.95,527.08) --
	(136.12,527.08) --
	(136.12,525.39) --
	(149.30,525.39) --
	(149.30,523.81) --
	(162.48,523.81) --
	(162.48,522.05) --
	(175.66,522.05) --
	(175.66,520.52) --
	(188.83,520.52) --
	(188.83,518.91) --
	(202.01,518.91) --
	(202.01,517.21) --
	(215.19,517.21) --
	(215.19,515.61) --
	(228.36,515.61) --
	(228.36,514.24) --
	(241.54,514.24) --
	(241.54,512.91) --
	(254.72,512.91) --
	(254.72,511.38) --
	(267.89,511.38) --
	(267.89,509.61) --
	(281.07,509.61) --
	(281.07,508.11) --
	(294.25,508.11) --
	(294.25,502.32);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,530.87) --
	( 96.59,530.87) --
	( 96.59,528.70) --
	(109.77,528.70) --
	(109.77,526.39) --
	(122.95,526.39) --
	(122.95,524.01) --
	(136.12,524.01) --
	(136.12,521.83) --
	(149.30,521.83) --
	(149.30,519.56) --
	(162.48,519.56) --
	(162.48,517.37) --
	(175.66,517.37) --
	(175.66,515.30) --
	(188.83,515.30) --
	(188.83,513.21) --
	(202.01,513.21) --
	(202.01,511.26) --
	(215.19,511.26) --
	(215.19,509.28) --
	(228.36,509.28) --
	(228.36,507.48) --
	(241.54,507.48) --
	(241.54,505.65) --
	(254.72,505.65) --
	(254.72,503.82) --
	(267.89,503.82) --
	(267.89,502.08) --
	(281.07,502.08) --
	(281.07,500.50) --
	(294.25,500.50) --
	(294.25,494.02);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.97) --
	( 70.24,531.97) --
	( 70.24,531.46) --
	( 83.42,531.46) --
	( 83.42,530.89) --
	( 96.59,530.89) --
	( 96.59,530.26) --
	(109.77,530.26) --
	(109.77,529.57) --
	(122.95,529.57) --
	(122.95,528.86) --
	(136.12,528.86) --
	(136.12,528.08) --
	(149.30,528.08) --
	(149.30,527.26) --
	(162.48,527.26) --
	(162.48,526.43) --
	(175.66,526.43) --
	(175.66,525.58) --
	(188.83,525.58) --
	(188.83,524.70) --
	(202.01,524.70) --
	(202.01,523.81) --
	(215.19,523.81) --
	(215.19,522.90) --
	(228.36,522.90) --
	(228.36,521.97) --
	(241.54,521.97) --
	(241.54,521.04) --
	(254.72,521.04) --
	(254.72,520.13) --
	(267.89,520.13) --
	(267.89,519.20) --
	(281.07,519.20) --
	(281.07,518.27) --
	(294.25,518.27) --
	(294.25,517.22);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.83) --
	( 70.24,531.83) --
	( 70.24,531.17) --
	( 83.42,531.17) --
	( 83.42,530.44) --
	( 96.59,530.44) --
	( 96.59,529.64) --
	(109.77,529.64) --
	(109.77,528.78) --
	(122.95,528.78) --
	(122.95,527.89) --
	(136.12,527.89) --
	(136.12,526.93) --
	(149.30,526.93) --
	(149.30,525.92) --
	(162.48,525.92) --
	(162.48,524.89) --
	(175.66,524.89) --
	(175.66,523.85) --
	(188.83,523.85) --
	(188.83,522.78) --
	(202.01,522.78) --
	(202.01,521.69) --
	(215.19,521.69) --
	(215.19,520.57) --
	(228.36,520.57) --
	(228.36,519.46) --
	(241.54,519.46) --
	(241.54,518.35) --
	(254.72,518.35) --
	(254.72,517.24) --
	(267.89,517.24) --
	(267.89,516.10) --
	(281.07,516.10) --
	(281.07,515.00) --
	(294.25,515.00) --
	(294.25,513.74);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.06) --
	( 70.24,531.06) --
	( 70.24,529.66) --
	( 83.42,529.66) --
	( 83.42,528.18) --
	( 96.59,528.18) --
	( 96.59,526.67) --
	(109.77,526.67) --
	(109.77,525.07) --
	(122.95,525.07) --
	(122.95,523.54) --
	(136.12,523.54) --
	(136.12,521.93) --
	(149.30,521.93) --
	(149.30,520.31) --
	(162.48,520.31) --
	(162.48,518.72) --
	(175.66,518.72) --
	(175.66,517.11) --
	(188.83,517.11) --
	(188.83,515.48) --
	(202.01,515.48) --
	(202.01,513.92) --
	(215.19,513.92) --
	(215.19,512.32) --
	(228.36,512.32) --
	(228.36,510.72) --
	(241.54,510.72) --
	(241.54,509.14) --
	(254.72,509.14) --
	(254.72,507.62) --
	(267.89,507.62) --
	(267.89,506.09) --
	(281.07,506.09) --
	(281.07,504.74) --
	(294.25,504.74) --
	(294.25,503.36);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,530.66) --
	( 70.24,530.66) --
	( 70.24,528.84) --
	( 83.42,528.84) --
	( 83.42,526.96) --
	( 96.59,526.96) --
	( 96.59,525.04) --
	(109.77,525.04) --
	(109.77,523.05) --
	(122.95,523.05) --
	(122.95,521.14) --
	(136.12,521.14) --
	(136.12,519.17) --
	(149.30,519.17) --
	(149.30,517.17) --
	(162.48,517.17) --
	(162.48,515.19) --
	(175.66,515.19) --
	(175.66,513.24) --
	(188.83,513.24) --
	(188.83,511.28) --
	(202.01,511.28) --
	(202.01,509.36) --
	(215.19,509.36) --
	(215.19,507.43) --
	(228.36,507.43) --
	(228.36,505.52) --
	(241.54,505.52) --
	(241.54,503.65) --
	(254.72,503.65) --
	(254.72,501.82) --
	(267.89,501.82) --
	(267.89,499.96) --
	(281.07,499.96) --
	(281.07,498.38) --
	(294.25,498.38) --
	(294.25,496.75);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,446.55) rectangle (306.77,536.52);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,371.13) --
	(306.77,371.13);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,397.46) --
	(306.77,397.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,423.80) --
	(306.77,423.80);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,351.08) --
	( 63.65,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,351.08) --
	(129.54,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,351.08) --
	(195.42,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,351.08) --
	(261.31,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,357.96) --
	(306.77,357.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,384.30) --
	(306.77,384.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,410.63) --
	(306.77,410.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,436.96) --
	(306.77,436.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,351.08) --
	( 96.59,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,351.08) --
	(162.48,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,351.08) --
	(228.36,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,351.08) --
	(294.25,441.05);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.99) --
	( 96.59,435.99) --
	( 96.59,434.54) --
	(109.77,434.54) --
	(109.77,433.15) --
	(122.95,433.15) --
	(122.95,431.60) --
	(136.12,431.60) --
	(136.12,430.03) --
	(149.30,430.03) --
	(149.30,428.31) --
	(162.48,428.31) --
	(162.48,426.57) --
	(175.66,426.57) --
	(175.66,424.90) --
	(188.83,424.90) --
	(188.83,423.22) --
	(202.01,423.22) --
	(202.01,421.65) --
	(215.19,421.65) --
	(215.19,420.13) --
	(228.36,420.13) --
	(228.36,418.54) --
	(241.54,418.54) --
	(241.54,417.01) --
	(254.72,417.01) --
	(254.72,415.42) --
	(267.89,415.42) --
	(267.89,413.97) --
	(281.07,413.97) --
	(281.07,412.39) --
	(294.25,412.39) --
	(294.25,406.12);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.30) --
	( 96.59,435.30) --
	( 96.59,433.42) --
	(109.77,433.42) --
	(109.77,431.17) --
	(122.95,431.17) --
	(122.95,428.91) --
	(136.12,428.91) --
	(136.12,426.60) --
	(149.30,426.60) --
	(149.30,424.44) --
	(162.48,424.44) --
	(162.48,422.41) --
	(175.66,422.41) --
	(175.66,420.27) --
	(188.83,420.27) --
	(188.83,418.05) --
	(202.01,418.05) --
	(202.01,416.08) --
	(215.19,416.08) --
	(215.19,414.23) --
	(228.36,414.23) --
	(228.36,412.46) --
	(241.54,412.46) --
	(241.54,410.47) --
	(254.72,410.47) --
	(254.72,408.61) --
	(267.89,408.61) --
	(267.89,406.79) --
	(281.07,406.79) --
	(281.07,405.02) --
	(294.25,405.02) --
	(294.25,398.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.49) --
	( 70.24,436.49) --
	( 70.24,435.98) --
	( 83.42,435.98) --
	( 83.42,435.40) --
	( 96.59,435.40) --
	( 96.59,434.74) --
	(109.77,434.74) --
	(109.77,434.03) --
	(122.95,434.03) --
	(122.95,433.29) --
	(136.12,433.29) --
	(136.12,432.49) --
	(149.30,432.49) --
	(149.30,431.67) --
	(162.48,431.67) --
	(162.48,430.81) --
	(175.66,430.81) --
	(175.66,429.93) --
	(188.83,429.93) --
	(188.83,429.01) --
	(202.01,429.01) --
	(202.01,428.11) --
	(215.19,428.11) --
	(215.19,427.14) --
	(228.36,427.14) --
	(228.36,426.18) --
	(241.54,426.18) --
	(241.54,425.20) --
	(254.72,425.20) --
	(254.72,424.22) --
	(267.89,424.22) --
	(267.89,423.26) --
	(281.07,423.26) --
	(281.07,422.29) --
	(294.25,422.29) --
	(294.25,421.27);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.35) --
	( 70.24,436.35) --
	( 70.24,435.69) --
	( 83.42,435.69) --
	( 83.42,434.95) --
	( 96.59,434.95) --
	( 96.59,434.13) --
	(109.77,434.13) --
	(109.77,433.26) --
	(122.95,433.26) --
	(122.95,432.33) --
	(136.12,432.33) --
	(136.12,431.33) --
	(149.30,431.33) --
	(149.30,430.29) --
	(162.48,430.29) --
	(162.48,429.21) --
	(175.66,429.21) --
	(175.66,428.12) --
	(188.83,428.12) --
	(188.83,427.01) --
	(202.01,427.01) --
	(202.01,425.90) --
	(215.19,425.90) --
	(215.19,424.74) --
	(228.36,424.74) --
	(228.36,423.59) --
	(241.54,423.59) --
	(241.54,422.43) --
	(254.72,422.43) --
	(254.72,421.32) --
	(267.89,421.32) --
	(267.89,420.16) --
	(281.07,420.16) --
	(281.07,419.01) --
	(294.25,419.01) --
	(294.25,417.72);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,435.58) --
	( 70.24,435.58) --
	( 70.24,434.16) --
	( 83.42,434.16) --
	( 83.42,432.67) --
	( 96.59,432.67) --
	( 96.59,431.09) --
	(109.77,431.09) --
	(109.77,429.46) --
	(122.95,429.46) --
	(122.95,427.88) --
	(136.12,427.88) --
	(136.12,426.24) --
	(149.30,426.24) --
	(149.30,424.64) --
	(162.48,424.64) --
	(162.48,423.00) --
	(175.66,423.00) --
	(175.66,421.35) --
	(188.83,421.35) --
	(188.83,419.68) --
	(202.01,419.68) --
	(202.01,418.10) --
	(215.19,418.10) --
	(215.19,416.43) --
	(228.36,416.43) --
	(228.36,414.79) --
	(241.54,414.79) --
	(241.54,413.14) --
	(254.72,413.14) --
	(254.72,411.54) --
	(267.89,411.54) --
	(267.89,409.96) --
	(281.07,409.96) --
	(281.07,408.56) --
	(294.25,408.56) --
	(294.25,407.24);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,435.17) --
	( 70.24,435.17) --
	( 70.24,433.34) --
	( 83.42,433.34) --
	( 83.42,431.44) --
	( 96.59,431.44) --
	( 96.59,429.47) --
	(109.77,429.47) --
	(109.77,427.46) --
	(122.95,427.46) --
	(122.95,425.48) --
	(136.12,425.48) --
	(136.12,423.46) --
	(149.30,423.46) --
	(149.30,421.43) --
	(162.48,421.43) --
	(162.48,419.38) --
	(175.66,419.38) --
	(175.66,417.35) --
	(188.83,417.35) --
	(188.83,415.36) --
	(202.01,415.36) --
	(202.01,413.43) --
	(215.19,413.43) --
	(215.19,411.45) --
	(228.36,411.45) --
	(228.36,409.51) --
	(241.54,409.51) --
	(241.54,407.57) --
	(254.72,407.57) --
	(254.72,405.77) --
	(267.89,405.77) --
	(267.89,403.91) --
	(281.07,403.91) --
	(281.07,402.27) --
	(294.25,402.27) --
	(294.25,400.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,351.08) rectangle (306.77,441.05);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,255.61) rectangle (306.77,345.58);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,255.61) rectangle (306.77,345.58);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,275.66) --
	(306.77,275.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,301.99) --
	(306.77,301.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,328.33) --
	(306.77,328.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,255.61) --
	( 63.65,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,255.61) --
	(129.54,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,255.61) --
	(195.42,345.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,255.61) --
	(261.31,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,262.49) --
	(306.77,262.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,288.82) --
	(306.77,288.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,315.16) --
	(306.77,315.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,341.49) --
	(306.77,341.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,255.61) --
	( 96.59,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,255.61) --
	(162.48,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,255.61) --
	(228.36,345.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,255.61) --
	(294.25,345.58);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.49) --
	( 70.24,341.49) --
	( 70.24,341.49) --
	( 83.42,341.49) --
	( 83.42,340.32) --
	( 96.59,340.32) --
	( 96.59,339.14) --
	(109.77,339.14) --
	(109.77,337.75) --
	(122.95,337.75) --
	(122.95,336.29) --
	(136.12,336.29) --
	(136.12,334.60) --
	(149.30,334.60) --
	(149.30,333.00) --
	(162.48,333.00) --
	(162.48,331.43) --
	(175.66,331.43) --
	(175.66,329.77) --
	(188.83,329.77) --
	(188.83,328.09) --
	(202.01,328.09) --
	(202.01,326.46) --
	(215.19,326.46) --
	(215.19,324.88) --
	(228.36,324.88) --
	(228.36,323.40) --
	(241.54,323.40) --
	(241.54,321.86) --
	(254.72,321.86) --
	(254.72,320.41) --
	(267.89,320.41) --
	(267.89,318.82) --
	(281.07,318.82) --
	(281.07,317.38) --
	(294.25,317.38) --
	(294.25,311.45);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.49) --
	( 70.24,341.49) --
	( 70.24,341.49) --
	( 83.42,341.49) --
	( 83.42,339.84) --
	( 96.59,339.84) --
	( 96.59,337.72) --
	(109.77,337.72) --
	(109.77,335.45) --
	(122.95,335.45) --
	(122.95,333.29) --
	(136.12,333.29) --
	(136.12,331.07) --
	(149.30,331.07) --
	(149.30,328.94) --
	(162.48,328.94) --
	(162.48,326.63) --
	(175.66,326.63) --
	(175.66,324.55) --
	(188.83,324.55) --
	(188.83,322.42) --
	(202.01,322.42) --
	(202.01,320.51) --
	(215.19,320.51) --
	(215.19,318.52) --
	(228.36,318.52) --
	(228.36,316.54) --
	(241.54,316.54) --
	(241.54,314.60) --
	(254.72,314.60) --
	(254.72,312.76) --
	(267.89,312.76) --
	(267.89,310.77) --
	(281.07,310.77) --
	(281.07,309.01) --
	(294.25,309.01) --
	(294.25,302.19);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.04) --
	( 70.24,341.04) --
	( 70.24,340.53) --
	( 83.42,340.53) --
	( 83.42,339.96) --
	( 96.59,339.96) --
	( 96.59,339.34) --
	(109.77,339.34) --
	(109.77,338.65) --
	(122.95,338.65) --
	(122.95,337.93) --
	(136.12,337.93) --
	(136.12,337.15) --
	(149.30,337.15) --
	(149.30,336.35) --
	(162.48,336.35) --
	(162.48,335.52) --
	(175.66,335.52) --
	(175.66,334.66) --
	(188.83,334.66) --
	(188.83,333.79) --
	(202.01,333.79) --
	(202.01,332.90) --
	(215.19,332.90) --
	(215.19,332.01) --
	(228.36,332.01) --
	(228.36,331.09) --
	(241.54,331.09) --
	(241.54,330.18) --
	(254.72,330.18) --
	(254.72,329.26) --
	(267.89,329.26) --
	(267.89,328.30) --
	(281.07,328.30) --
	(281.07,327.37) --
	(294.25,327.37) --
	(294.25,326.33);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.87) --
	( 70.24,340.87) --
	( 70.24,340.16) --
	( 83.42,340.16) --
	( 83.42,339.43) --
	( 96.59,339.43) --
	( 96.59,338.62) --
	(109.77,338.62) --
	(109.77,337.75) --
	(122.95,337.75) --
	(122.95,336.84) --
	(136.12,336.84) --
	(136.12,335.86) --
	(149.30,335.86) --
	(149.30,334.83) --
	(162.48,334.83) --
	(162.48,333.81) --
	(175.66,333.81) --
	(175.66,332.76) --
	(188.83,332.76) --
	(188.83,331.67) --
	(202.01,331.67) --
	(202.01,330.55) --
	(215.19,330.55) --
	(215.19,329.40) --
	(228.36,329.40) --
	(228.36,328.22) --
	(241.54,328.22) --
	(241.54,327.10) --
	(254.72,327.10) --
	(254.72,325.95) --
	(267.89,325.95) --
	(267.89,324.77) --
	(281.07,324.77) --
	(281.07,323.67) --
	(294.25,323.67) --
	(294.25,322.38);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.16) --
	( 70.24,340.16) --
	( 70.24,338.75) --
	( 83.42,338.75) --
	( 83.42,337.29) --
	( 96.59,337.29) --
	( 96.59,335.78) --
	(109.77,335.78) --
	(109.77,334.19) --
	(122.95,334.19) --
	(122.95,332.65) --
	(136.12,332.65) --
	(136.12,331.05) --
	(149.30,331.05) --
	(149.30,329.45) --
	(162.48,329.45) --
	(162.48,327.86) --
	(175.66,327.86) --
	(175.66,326.23) --
	(188.83,326.23) --
	(188.83,324.62) --
	(202.01,324.62) --
	(202.01,323.06) --
	(215.19,323.06) --
	(215.19,321.50) --
	(228.36,321.50) --
	(228.36,319.93) --
	(241.54,319.93) --
	(241.54,318.36) --
	(254.72,318.36) --
	(254.72,316.84) --
	(267.89,316.84) --
	(267.89,315.25) --
	(281.07,315.25) --
	(281.07,313.90) --
	(294.25,313.90) --
	(294.25,312.54);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,339.67) --
	( 70.24,339.67) --
	( 70.24,337.70) --
	( 83.42,337.70) --
	( 83.42,335.81) --
	( 96.59,335.81) --
	( 96.59,333.86) --
	(109.77,333.86) --
	(109.77,331.84) --
	(122.95,331.84) --
	(122.95,329.88) --
	(136.12,329.88) --
	(136.12,327.89) --
	(149.30,327.89) --
	(149.30,325.84) --
	(162.48,325.84) --
	(162.48,323.89) --
	(175.66,323.89) --
	(175.66,321.90) --
	(188.83,321.90) --
	(188.83,319.92) --
	(202.01,319.92) --
	(202.01,317.95) --
	(215.19,317.95) --
	(215.19,315.96) --
	(228.36,315.96) --
	(228.36,313.96) --
	(241.54,313.96) --
	(241.54,312.05) --
	(254.72,312.05) --
	(254.72,310.18) --
	(267.89,310.18) --
	(267.89,308.25) --
	(281.07,308.25) --
	(281.07,306.67) --
	(294.25,306.67) --
	(294.25,305.01);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,255.61) rectangle (306.77,345.58);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,160.14) rectangle (306.77,250.11);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,160.14) rectangle (306.77,250.11);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,180.19) --
	(306.77,180.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,206.52) --
	(306.77,206.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,232.85) --
	(306.77,232.85);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,160.14) --
	( 63.65,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,160.14) --
	(129.54,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,160.14) --
	(195.42,250.11);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,160.14) --
	(261.31,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,167.02) --
	(306.77,167.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,193.35) --
	(306.77,193.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,219.69) --
	(306.77,219.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,246.02) --
	(306.77,246.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,160.14) --
	( 96.59,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,160.14) --
	(162.48,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,160.14) --
	(228.36,250.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,160.14) --
	(294.25,250.11);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,246.02) --
	( 70.24,246.02) --
	( 70.24,246.02) --
	( 83.42,246.02) --
	( 83.42,243.99) --
	( 96.59,243.99) --
	( 96.59,241.05) --
	(109.77,241.05) --
	(109.77,237.70) --
	(122.95,237.70) --
	(122.95,233.72) --
	(136.12,233.72) --
	(136.12,229.94) --
	(149.30,229.94) --
	(149.30,225.93) --
	(162.48,225.93) --
	(162.48,221.98) --
	(175.66,221.98) --
	(175.66,218.17) --
	(188.83,218.17) --
	(188.83,214.60) --
	(202.01,214.60) --
	(202.01,211.01) --
	(215.19,211.01) --
	(215.19,207.49) --
	(228.36,207.49) --
	(228.36,204.27) --
	(241.54,204.27) --
	(241.54,201.08) --
	(254.72,201.08) --
	(254.72,197.91) --
	(267.89,197.91) --
	(267.89,194.81) --
	(281.07,194.81) --
	(281.07,191.65) --
	(294.25,191.65) --
	(294.25,180.29);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,246.02) --
	( 70.24,246.02) --
	( 70.24,246.02) --
	( 83.42,246.02) --
	( 83.42,243.12) --
	( 96.59,243.12) --
	( 96.59,238.79) --
	(109.77,238.79) --
	(109.77,234.27) --
	(122.95,234.27) --
	(122.95,229.56) --
	(136.12,229.56) --
	(136.12,224.88) --
	(149.30,224.88) --
	(149.30,220.23) --
	(162.48,220.23) --
	(162.48,215.62) --
	(175.66,215.62) --
	(175.66,211.52) --
	(188.83,211.52) --
	(188.83,206.92) --
	(202.01,206.92) --
	(202.01,202.81) --
	(215.19,202.81) --
	(215.19,198.66) --
	(228.36,198.66) --
	(228.36,194.73) --
	(241.54,194.73) --
	(241.54,190.98) --
	(254.72,190.98) --
	(254.72,187.55) --
	(267.89,187.55) --
	(267.89,184.05) --
	(281.07,184.05) --
	(281.07,180.84) --
	(294.25,180.84) --
	(294.25,168.65);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.06) --
	( 70.24,245.06) --
	( 70.24,243.91) --
	( 83.42,243.91) --
	( 83.42,242.59) --
	( 96.59,242.59) --
	( 96.59,241.11) --
	(109.77,241.11) --
	(109.77,239.52) --
	(122.95,239.52) --
	(122.95,237.84) --
	(136.12,237.84) --
	(136.12,236.04) --
	(149.30,236.04) --
	(149.30,234.18) --
	(162.48,234.18) --
	(162.48,232.27) --
	(175.66,232.27) --
	(175.66,230.33) --
	(188.83,230.33) --
	(188.83,228.36) --
	(202.01,228.36) --
	(202.01,226.37) --
	(215.19,226.37) --
	(215.19,224.33) --
	(228.36,224.33) --
	(228.36,222.29) --
	(241.54,222.29) --
	(241.54,220.26) --
	(254.72,220.26) --
	(254.72,218.27) --
	(267.89,218.27) --
	(267.89,216.24) --
	(281.07,216.24) --
	(281.07,214.24) --
	(294.25,214.24) --
	(294.25,212.02);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,244.62) --
	( 70.24,244.62) --
	( 70.24,243.07) --
	( 83.42,243.07) --
	( 83.42,241.41) --
	( 96.59,241.41) --
	( 96.59,239.56) --
	(109.77,239.56) --
	(109.77,237.62) --
	(122.95,237.62) --
	(122.95,235.60) --
	(136.12,235.60) --
	(136.12,233.47) --
	(149.30,233.47) --
	(149.30,231.24) --
	(162.48,231.24) --
	(162.48,228.97) --
	(175.66,228.97) --
	(175.66,226.62) --
	(188.83,226.62) --
	(188.83,224.30) --
	(202.01,224.30) --
	(202.01,221.92) --
	(215.19,221.92) --
	(215.19,219.51) --
	(228.36,219.51) --
	(228.36,217.09) --
	(241.54,217.09) --
	(241.54,214.63) --
	(254.72,214.63) --
	(254.72,212.15) --
	(267.89,212.15) --
	(267.89,209.73) --
	(281.07,209.73) --
	(281.07,207.33) --
	(294.25,207.33) --
	(294.25,204.79);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,243.20) --
	( 70.24,243.20) --
	( 70.24,240.04) --
	( 83.42,240.04) --
	( 83.42,236.63) --
	( 96.59,236.63) --
	( 96.59,233.06) --
	(109.77,233.06) --
	(109.77,229.39) --
	(122.95,229.39) --
	(122.95,225.81) --
	(136.12,225.81) --
	(136.12,222.15) --
	(149.30,222.15) --
	(149.30,218.49) --
	(162.48,218.49) --
	(162.48,214.87) --
	(175.66,214.87) --
	(175.66,211.28) --
	(188.83,211.28) --
	(188.83,207.72) --
	(202.01,207.72) --
	(202.01,204.32) --
	(215.19,204.32) --
	(215.19,200.86) --
	(228.36,200.86) --
	(228.36,197.47) --
	(241.54,197.47) --
	(241.54,194.12) --
	(254.72,194.12) --
	(254.72,190.96) --
	(267.89,190.96) --
	(267.89,187.78) --
	(281.07,187.78) --
	(281.07,185.03) --
	(294.25,185.03) --
	(294.25,182.31);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,241.91) --
	( 70.24,241.91) --
	( 70.24,237.65) --
	( 83.42,237.65) --
	( 83.42,233.36) --
	( 96.59,233.36) --
	( 96.59,228.90) --
	(109.77,228.90) --
	(109.77,224.45) --
	(122.95,224.45) --
	(122.95,220.18) --
	(136.12,220.18) --
	(136.12,215.86) --
	(149.30,215.86) --
	(149.30,211.53) --
	(162.48,211.53) --
	(162.48,207.29) --
	(175.66,207.29) --
	(175.66,203.01) --
	(188.83,203.01) --
	(188.83,198.88) --
	(202.01,198.88) --
	(202.01,194.88) --
	(215.19,194.88) --
	(215.19,190.88) --
	(228.36,190.88) --
	(228.36,186.95) --
	(241.54,186.95) --
	(241.54,182.99) --
	(254.72,182.99) --
	(254.72,179.15) --
	(267.89,179.15) --
	(267.89,175.46) --
	(281.07,175.46) --
	(281.07,172.26) --
	(294.25,172.26) --
	(294.25,169.25);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,160.14) rectangle (306.77,250.11);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 64.67) rectangle (306.77,154.64);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,154.64);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 84.71) --
	(306.77, 84.71);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,111.05) --
	(306.77,111.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,137.38) --
	(306.77,137.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
	( 63.65,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
	(129.54,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
	(195.42,154.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
	(261.31,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 71.55) --
	(306.77, 71.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 97.88) --
	(306.77, 97.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,124.22) --
	(306.77,124.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,150.55) --
	(306.77,150.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
	( 96.59,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
	(162.48,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
	(228.36,154.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
	(294.25,154.64);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,150.55) --
	( 70.24,150.55) --
	( 70.24,150.55) --
	( 83.42,150.55) --
	( 83.42,147.34) --
	( 96.59,147.34) --
	( 96.59,143.70) --
	(109.77,143.70) --
	(109.77,139.88) --
	(122.95,139.88) --
	(122.95,135.65) --
	(136.12,135.65) --
	(136.12,131.81) --
	(149.30,131.81) --
	(149.30,127.92) --
	(162.48,127.92) --
	(162.48,124.01) --
	(175.66,124.01) --
	(175.66,120.10) --
	(188.83,120.10) --
	(188.83,116.29) --
	(202.01,116.29) --
	(202.01,112.73) --
	(215.19,112.73) --
	(215.19,109.26) --
	(228.36,109.26) --
	(228.36,106.08) --
	(241.54,106.08) --
	(241.54,102.93) --
	(254.72,102.93) --
	(254.72, 99.83) --
	(267.89, 99.83) --
	(267.89, 96.92) --
	(281.07, 96.92) --
	(281.07, 94.25) --
	(294.25, 94.25) --
	(294.25, 83.61);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,150.55) --
	( 70.24,150.55) --
	( 70.24,150.55) --
	( 83.42,150.55) --
	( 83.42,146.65) --
	( 96.59,146.65) --
	( 96.59,141.13) --
	(109.77,141.13) --
	(109.77,135.61) --
	(122.95,135.61) --
	(122.95,130.52) --
	(136.12,130.52) --
	(136.12,125.32) --
	(149.30,125.32) --
	(149.30,120.35) --
	(162.48,120.35) --
	(162.48,115.63) --
	(175.66,115.63) --
	(175.66,111.00) --
	(188.83,111.00) --
	(188.83,106.51) --
	(202.01,106.51) --
	(202.01,102.52) --
	(215.19,102.52) --
	(215.19, 98.47) --
	(228.36, 98.47) --
	(228.36, 94.60) --
	(241.54, 94.60) --
	(241.54, 91.02) --
	(254.72, 91.02) --
	(254.72, 87.48) --
	(267.89, 87.48) --
	(267.89, 83.96) --
	(281.07, 83.96) --
	(281.07, 80.93) --
	(294.25, 80.93) --
	(294.25, 68.76);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,149.34) --
	( 70.24,149.34) --
	( 70.24,148.04) --
	( 83.42,148.04) --
	( 83.42,146.59) --
	( 96.59,146.59) --
	( 96.59,145.04) --
	(109.77,145.04) --
	(109.77,143.41) --
	(122.95,143.41) --
	(122.95,141.71) --
	(136.12,141.71) --
	(136.12,139.90) --
	(149.30,139.90) --
	(149.30,138.03) --
	(162.48,138.03) --
	(162.48,136.10) --
	(175.66,136.10) --
	(175.66,134.16) --
	(188.83,134.16) --
	(188.83,132.18) --
	(202.01,132.18) --
	(202.01,130.20) --
	(215.19,130.20) --
	(215.19,128.16) --
	(228.36,128.16) --
	(228.36,126.14) --
	(241.54,126.14) --
	(241.54,124.12) --
	(254.72,124.12) --
	(254.72,122.14) --
	(267.89,122.14) --
	(267.89,120.11) --
	(281.07,120.11) --
	(281.07,118.12) --
	(294.25,118.12) --
	(294.25,115.91);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,148.97) --
	( 70.24,148.97) --
	( 70.24,147.24) --
	( 83.42,147.24) --
	( 83.42,145.46) --
	( 96.59,145.46) --
	( 96.59,143.56) --
	(109.77,143.56) --
	(109.77,141.56) --
	(122.95,141.56) --
	(122.95,139.50) --
	(136.12,139.50) --
	(136.12,137.33) --
	(149.30,137.33) --
	(149.30,135.09) --
	(162.48,135.09) --
	(162.48,132.82) --
	(175.66,132.82) --
	(175.66,130.50) --
	(188.83,130.50) --
	(188.83,128.20) --
	(202.01,128.20) --
	(202.01,125.90) --
	(215.19,125.90) --
	(215.19,123.50) --
	(228.36,123.50) --
	(228.36,121.13) --
	(241.54,121.13) --
	(241.54,118.80) --
	(254.72,118.80) --
	(254.72,116.52) --
	(267.89,116.52) --
	(267.89,114.21) --
	(281.07,114.21) --
	(281.07,111.97) --
	(294.25,111.97) --
	(294.25,109.50);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,147.00) --
	( 70.24,147.00) --
	( 70.24,143.42) --
	( 83.42,143.42) --
	( 83.42,139.69) --
	( 96.59,139.69) --
	( 96.59,135.94) --
	(109.77,135.94) --
	(109.77,132.19) --
	(122.95,132.19) --
	(122.95,128.56) --
	(136.12,128.56) --
	(136.12,124.88) --
	(149.30,124.88) --
	(149.30,121.23) --
	(162.48,121.23) --
	(162.48,117.58) --
	(175.66,117.58) --
	(175.66,113.99) --
	(188.83,113.99) --
	(188.83,110.43) --
	(202.01,110.43) --
	(202.01,107.04) --
	(215.19,107.04) --
	(215.19,103.62) --
	(228.36,103.62) --
	(228.36,100.27) --
	(241.54,100.27) --
	(241.54, 96.95) --
	(254.72, 96.95) --
	(254.72, 93.82) --
	(267.89, 93.82) --
	(267.89, 90.65) --
	(281.07, 90.65) --
	(281.07, 87.93) --
	(294.25, 87.93) --
	(294.25, 85.24);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,150.55) --
	( 57.06,150.55) --
	( 57.06,145.92) --
	( 70.24,145.92) --
	( 70.24,141.15) --
	( 83.42,141.15) --
	( 83.42,136.56) --
	( 96.59,136.56) --
	( 96.59,131.97) --
	(109.77,131.97) --
	(109.77,127.38) --
	(122.95,127.38) --
	(122.95,123.00) --
	(136.12,123.00) --
	(136.12,118.62) --
	(149.30,118.62) --
	(149.30,114.27) --
	(162.48,114.27) --
	(162.48,110.02) --
	(175.66,110.02) --
	(175.66,105.79) --
	(188.83,105.79) --
	(188.83,101.71) --
	(202.01,101.71) --
	(202.01, 97.83) --
	(215.19, 97.83) --
	(215.19, 93.87) --
	(228.36, 93.87) --
	(228.36, 90.03) --
	(241.54, 90.03) --
	(241.54, 86.28) --
	(254.72, 86.28) --
	(254.72, 82.77) --
	(267.89, 82.77) --
	(267.89, 79.27) --
	(281.07, 79.27) --
	(281.07, 76.29) --
	(294.25, 76.29) --
	(294.25, 73.36);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,154.64);
\end{scope}
\begin{scope}
\path[clip] (306.77,446.55) rectangle (319.71,536.52);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,446.55) rectangle (319.71,536.52);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,491.54) {Scenario 1};
\end{scope}
\begin{scope}
\path[clip] (306.77,351.08) rectangle (319.71,441.05);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,351.08) rectangle (319.71,441.05);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,396.07) {Scenario 2};
\end{scope}
\begin{scope}
\path[clip] (306.77,255.61) rectangle (319.71,345.58);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,255.61) rectangle (319.71,345.58);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,300.60) {Scenario 3};
\end{scope}
\begin{scope}
\path[clip] (306.77,160.14) rectangle (319.71,250.11);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77,160.14) rectangle (319.71,250.11);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,205.12) {Scenario 4};
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,154.64);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,154.64);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,109.65) {Scenario 5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
	( 96.59, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
	(162.48, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
	(228.36, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
	(294.25, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,450.68) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,477.01) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,503.35) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,529.68) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,453.43) --
	( 31.37,453.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,479.77) --
	( 31.37,479.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,506.10) --
	( 31.37,506.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,532.44) --
	( 31.37,532.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,355.21) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,381.54) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,407.88) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,434.21) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,357.96) --
	( 31.37,357.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,384.30) --
	( 31.37,384.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,410.63) --
	( 31.37,410.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,436.96) --
	( 31.37,436.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,259.74) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,286.07) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,312.40) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,338.74) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,262.49) --
	( 31.37,262.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,288.82) --
	( 31.37,288.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,315.16) --
	( 31.37,315.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,341.49) --
	( 31.37,341.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,164.26) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,190.60) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,216.93) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,243.27) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,167.02) --
	( 31.37,167.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,193.35) --
	( 31.37,193.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,219.69) --
	( 31.37,219.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,246.02) --
	( 31.37,246.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 68.79) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 95.13) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,121.46) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,147.79) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 71.55) --
	( 31.37, 71.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 97.88) --
	( 31.37, 97.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,124.22) --
	( 31.37,124.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,150.55) --
	( 31.37,150.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,300.60) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/sensitivity/results_1.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:08
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,154.86);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,154.86);
\end{scope}
\begin{scope}
\path[clip] ( 35.37, 64.67) rectangle (306.77,149.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 35.37, 64.67) rectangle (306.77,149.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.54) --
	(306.77, 79.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.93) --
	(306.77,105.93);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.32) --
	(306.77,132.32);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.18, 64.67) --
	( 67.18,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (132.11, 64.67) --
	(132.11,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.04, 64.67) --
	(197.04,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.97, 64.67) --
	(261.97,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.34) --
	(306.77, 66.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.73) --
	(306.77, 92.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.12) --
	(306.77,119.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,145.51) --
	(306.77,145.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.65, 64.67) --
	( 99.65,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (164.57, 64.67) --
	(164.57,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50, 64.67) --
	(229.50,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.43, 64.67) --
	(294.43,149.36);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,143.30) --
	( 99.65,140.75) --
	(112.63,138.01) --
	(125.62,134.78) --
	(138.60,131.40) --
	(151.59,128.22) --
	(164.57,124.71) --
	(177.56,121.64) --
	(190.55,118.40) --
	(203.53,115.01) --
	(216.52,111.80) --
	(229.50,109.04) --
	(242.49,106.38) --
	(255.47,103.32) --
	(268.46, 99.77) --
	(281.44, 96.75) --
	(294.43, 85.15);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.70,145.51) --
	( 60.69,145.51) --
	( 73.67,145.51) --
	( 86.66,142.38) --
	( 99.65,138.02) --
	(112.63,133.41) --
	(125.62,128.63) --
	(138.60,124.26) --
	(151.59,119.71) --
	(164.57,115.31) --
	(177.56,111.16) --
	(190.55,106.98) --
	(203.53,103.08) --
	(216.52, 99.10) --
	(229.50, 95.50) --
	(242.49, 91.83) --
	(255.47, 88.16) --
	(268.46, 84.67) --
	(281.44, 81.50) --
	(294.43, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.58) --
	( 73.67,143.55) --
	( 86.66,142.41) --
	( 99.65,141.16) --
	(112.63,139.78) --
	(125.62,138.35) --
	(138.60,136.78) --
	(151.59,135.15) --
	(164.57,133.48) --
	(177.56,131.78) --
	(190.55,130.01) --
	(203.53,128.23) --
	(216.52,126.40) --
	(229.50,124.54) --
	(242.49,122.68) --
	(255.47,120.85) --
	(268.46,118.98) --
	(281.44,117.13) --
	(294.43,115.03);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,144.30) --
	( 73.67,142.98) --
	( 86.66,141.51) --
	( 99.65,139.92) --
	(112.63,138.20) --
	(125.62,136.41) --
	(138.60,134.48) --
	(151.59,132.46) --
	(164.57,130.39) --
	(177.56,128.31) --
	(190.55,126.17) --
	(203.53,123.97) --
	(216.52,121.74) --
	(229.50,119.50) --
	(242.49,117.29) --
	(255.47,115.06) --
	(268.46,112.77) --
	(281.44,110.57) --
	(294.43,108.03);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,142.77) --
	( 73.67,139.94) --
	( 86.66,136.99) --
	( 99.65,133.96) --
	(112.63,130.76) --
	(125.62,127.69) --
	(138.60,124.46) --
	(151.59,121.22) --
	(164.57,118.02) --
	(177.56,114.80) --
	(190.55,111.53) --
	(203.53,108.40) --
	(216.52,105.20) --
	(229.50,102.00) --
	(242.49, 98.82) --
	(255.47, 95.78) --
	(268.46, 92.70) --
	(281.44, 90.00) --
	(294.43, 87.25);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
	( 60.69,141.95) --
	( 73.67,138.32) --
	( 86.66,134.53) --
	( 99.65,130.68) --
	(112.63,126.70) --
	(125.62,122.87) --
	(138.60,118.92) --
	(151.59,114.92) --
	(164.57,110.94) --
	(177.56,107.05) --
	(190.55,103.11) --
	(203.53, 99.27) --
	(216.52, 95.40) --
	(229.50, 91.58) --
	(242.49, 87.82) --
	(255.47, 84.15) --
	(268.46, 80.43) --
	(281.44, 77.26) --
	(294.43, 73.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 64.67) rectangle (306.77,149.36);
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,149.36);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,149.36);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.65, 61.92) --
	( 99.65, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (164.57, 61.92) --
	(164.57, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50, 61.92) --
	(229.50, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.43, 61.92) --
	(294.43, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 99.65, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.57, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (229.50, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.43, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.59) {0.85};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 89.98) {0.90};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.37) {0.95};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,142.76) {1.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.34) --
	( 35.37, 66.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.73) --
	( 35.37, 92.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.12) --
	( 35.37,119.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,145.51) --
	( 35.37,145.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (171.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,107.02) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 21.60,  5.50) rectangle (144.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 32.60, 11.00) rectangle ( 47.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.05, 18.23) -- ( 45.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 88.63, 11.00) rectangle (103.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.08, 18.23) -- (101.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 52.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (108.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (155.67,  5.50) rectangle (320.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (166.67, 11.00) rectangle (181.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.11, 18.23) -- (179.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (214.89, 11.00) rectangle (229.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (216.34, 18.23) -- (227.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (264.84, 11.00) rectangle (279.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (266.28, 18.23) -- (277.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (186.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (234.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (284.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/sensitivity/results_2.tex
SER

--- 2022-03-04 reports/resources/sensitivity/results_1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:08
+% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:09
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.54) --
-	(306.77, 79.54);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.59) --
+	(306.77, 79.59);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.93) --
-	(306.77,105.93);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.96) --
+	(306.77,105.96);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.32) --
-	(306.77,132.32);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.33) --
+	(306.77,132.33);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.34) --
-	(306.77, 66.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.41) --
+	(306.77, 66.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.73) --
-	(306.77, 92.73);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.78) --
+	(306.77, 92.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.12) --
-	(306.77,119.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.15) --
+	(306.77,119.15);
 
@@
 	( 73.67,145.51) --
-	( 86.66,143.30) --
-	( 99.65,140.75) --
-	(112.63,138.01) --
+	( 86.66,143.56) --
+	( 99.65,140.66) --
+	(112.63,137.87) --
 	(125.62,134.78) --
-	(138.60,131.40) --
-	(151.59,128.22) --
-	(164.57,124.71) --
-	(177.56,121.64) --
-	(190.55,118.40) --
-	(203.53,115.01) --
-	(216.52,111.80) --
-	(229.50,109.04) --
-	(242.49,106.38) --
-	(255.47,103.32) --
-	(268.46, 99.77) --
-	(281.44, 96.75) --
-	(294.43, 85.15);
+	(138.60,131.62) --
+	(151.59,128.18) --
+	(164.57,124.69) --
+	(177.56,121.35) --
+	(190.55,118.00) --
+	(203.53,114.85) --
+	(216.52,111.79) --
+	(229.50,108.62) --
+	(242.49,105.56) --
+	(255.47,102.37) --
+	(268.46, 99.47) --
+	(281.44, 96.31) --
+	(294.43, 83.75);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 73.67,145.51) --
-	( 86.66,142.38) --
-	( 99.65,138.02) --
-	(112.63,133.41) --
-	(125.62,128.63) --
-	(138.60,124.26) --
-	(151.59,119.71) --
-	(164.57,115.31) --
-	(177.56,111.16) --
-	(190.55,106.98) --
-	(203.53,103.08) --
-	(216.52, 99.10) --
-	(229.50, 95.50) --
-	(242.49, 91.83) --
-	(255.47, 88.16) --
-	(268.46, 84.67) --
-	(281.44, 81.50) --
+	( 86.66,142.18) --
+	( 99.65,138.42) --
+	(112.63,133.91) --
+	(125.62,129.39) --
+	(138.60,124.77) --
+	(151.59,120.43) --
+	(164.57,116.37) --
+	(177.56,112.09) --
+	(190.55,107.64) --
+	(203.53,103.68) --
+	(216.52, 99.99) --
+	(229.50, 96.45) --
+	(242.49, 92.45) --
+	(255.47, 88.73) --
+	(268.46, 85.08) --
+	(281.44, 81.53) --
 	(294.43, 68.52);
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,144.58) --
-	( 73.67,143.55) --
-	( 86.66,142.41) --
-	( 99.65,141.16) --
-	(112.63,139.78) --
-	(125.62,138.35) --
-	(138.60,136.78) --
-	(151.59,135.15) --
-	(164.57,133.48) --
-	(177.56,131.78) --
-	(190.55,130.01) --
-	(203.53,128.23) --
-	(216.52,126.40) --
-	(229.50,124.54) --
-	(242.49,122.68) --
-	(255.47,120.85) --
-	(268.46,118.98) --
-	(281.44,117.13) --
-	(294.43,115.03);
+	( 60.69,144.57) --
+	( 73.67,143.54) --
+	( 86.66,142.38) --
+	( 99.65,141.07) --
+	(112.63,139.64) --
+	(125.62,138.17) --
+	(138.60,136.55) --
+	(151.59,134.92) --
+	(164.57,133.20) --
+	(177.56,131.42) --
+	(190.55,129.59) --
+	(203.53,127.78) --
+	(216.52,125.83) --
+	(229.50,123.91) --
+	(242.49,121.96) --
+	(255.47,120.00) --
+	(268.46,118.06) --
+	(281.44,116.12) --
+	(294.43,114.08);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,144.30) --
-	( 73.67,142.98) --
-	( 86.66,141.51) --
-	( 99.65,139.92) --
-	(112.63,138.20) --
-	(125.62,136.41) --
-	(138.60,134.48) --
-	(151.59,132.46) --
-	(164.57,130.39) --
-	(177.56,128.31) --
-	(190.55,126.17) --
-	(203.53,123.97) --
-	(216.52,121.74) --
-	(229.50,119.50) --
-	(242.49,117.29) --
-	(255.47,115.06) --
-	(268.46,112.77) --
-	(281.44,110.57) --
-	(294.43,108.03);
+	( 60.69,144.29) --
+	( 73.67,142.96) --
+	( 86.66,141.49) --
+	( 99.65,139.85) --
+	(112.63,138.10) --
+	(125.62,136.23) --
+	(138.60,134.24) --
+	(151.59,132.15) --
+	(164.57,129.99) --
+	(177.56,127.79) --
+	(190.55,125.59) --
+	(203.53,123.36) --
+	(216.52,121.03) --
+	(229.50,118.72) --
+	(242.49,116.41) --
+	(255.47,114.18) --
+	(268.46,111.87) --
+	(281.44,109.56) --
+	(294.43,106.98);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,142.77) --
-	( 73.67,139.94) --
-	( 86.66,136.99) --
-	( 99.65,133.96) --
-	(112.63,130.76) --
-	(125.62,127.69) --
-	(138.60,124.46) --
-	(151.59,121.22) --
-	(164.57,118.02) --
-	(177.56,114.80) --
-	(190.55,111.53) --
-	(203.53,108.40) --
-	(216.52,105.20) --
-	(229.50,102.00) --
-	(242.49, 98.82) --
-	(255.47, 95.78) --
-	(268.46, 92.70) --
-	(281.44, 90.00) --
-	(294.43, 87.25);
+	( 60.69,142.74) --
+	( 73.67,139.90) --
+	( 86.66,136.92) --
+	( 99.65,133.75) --
+	(112.63,130.48) --
+	(125.62,127.33) --
+	(138.60,124.04) --
+	(151.59,120.82) --
+	(164.57,117.55) --
+	(177.56,114.24) --
+	(190.55,110.90) --
+	(203.53,107.74) --
+	(216.52,104.39) --
+	(229.50,101.12) --
+	(242.49, 97.80) --
+	(255.47, 94.60) --
+	(268.46, 91.44) --
+	(281.44, 88.64) --
+	(294.43, 85.98);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,141.95) --
-	( 73.67,138.32) --
-	( 86.66,134.53) --
-	( 99.65,130.68) --
-	(112.63,126.70) --
-	(125.62,122.87) --
-	(138.60,118.92) --
-	(151.59,114.92) --
-	(164.57,110.94) --
-	(177.56,107.05) --
-	(190.55,103.11) --
-	(203.53, 99.27) --
-	(216.52, 95.40) --
-	(229.50, 91.58) --
-	(242.49, 87.82) --
-	(255.47, 84.15) --
-	(268.46, 80.43) --
-	(281.44, 77.26) --
-	(294.43, 73.99);
+	( 60.69,141.92) --
+	( 73.67,138.26) --
+	( 86.66,134.46) --
+	( 99.65,130.50) --
+	(112.63,126.48) --
+	(125.62,122.52) --
+	(138.60,118.48) --
+	(151.59,114.40) --
+	(164.57,110.31) --
+	(177.56,106.24) --
+	(190.55,102.24) --
+	(203.53, 98.39) --
+	(216.52, 94.42) --
+	(229.50, 90.53) --
+	(242.49, 86.65) --
+	(255.47, 83.04) --
+	(268.46, 79.32) --
+	(281.44, 76.03) --
+	(294.43, 72.72);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 1};
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 2};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.59) {0.85};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.65) {0.85};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 89.98) {0.90};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 90.02) {0.90};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.37) {0.95};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.39) {0.95};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.34) --
-	( 35.37, 66.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.41) --
+	( 35.37, 66.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.73) --
-	( 35.37, 92.73);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.78) --
+	( 35.37, 92.78);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.12) --
-	( 35.37,119.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.15) --
+	( 35.37,119.15);
 

### 2022-03-04 reports/resources/sensitivity/results_3.tex
SER

--- 2022-03-04 reports/resources/sensitivity/results_2.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:09
+% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:10
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 79.59) --
-	(306.77, 79.59);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 81.03) --
+	(306.77, 81.03);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,105.96) --
-	(306.77,105.96);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,106.82) --
+	(306.77,106.82);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.33) --
-	(306.77,132.33);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,132.62) --
+	(306.77,132.62);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 66.41) --
-	(306.77, 66.41);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 68.14) --
+	(306.77, 68.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 92.78) --
-	(306.77, 92.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 93.93) --
+	(306.77, 93.93);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.15) --
-	(306.77,119.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,119.72) --
+	(306.77,119.72);
 
@@
 	( 73.67,145.51) --
-	( 86.66,143.56) --
-	( 99.65,140.66) --
-	(112.63,137.87) --
-	(125.62,134.78) --
-	(138.60,131.62) --
-	(151.59,128.18) --
-	(164.57,124.69) --
-	(177.56,121.35) --
-	(190.55,118.00) --
-	(203.53,114.85) --
-	(216.52,111.79) --
-	(229.50,108.62) --
-	(242.49,105.56) --
-	(255.47,102.37) --
-	(268.46, 99.47) --
-	(281.44, 96.31) --
-	(294.43, 83.75);
+	( 86.66,143.21) --
+	( 99.65,140.90) --
+	(112.63,138.18) --
+	(125.62,135.32) --
+	(138.60,132.01) --
+	(151.59,128.88) --
+	(164.57,125.81) --
+	(177.56,122.56) --
+	(190.55,119.26) --
+	(203.53,116.07) --
+	(216.52,112.97) --
+	(229.50,110.06) --
+	(242.49,107.05) --
+	(255.47,104.22) --
+	(268.46,101.10) --
+	(281.44, 98.28) --
+	(294.43, 86.66);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 73.67,145.51) --
-	( 86.66,142.18) --
-	( 99.65,138.42) --
-	(112.63,133.91) --
-	(125.62,129.39) --
-	(138.60,124.77) --
-	(151.59,120.43) --
-	(164.57,116.37) --
-	(177.56,112.09) --
-	(190.55,107.64) --
-	(203.53,103.68) --
-	(216.52, 99.99) --
-	(229.50, 96.45) --
-	(242.49, 92.45) --
-	(255.47, 88.73) --
-	(268.46, 85.08) --
-	(281.44, 81.53) --
+	( 86.66,142.29) --
+	( 99.65,138.13) --
+	(112.63,133.67) --
+	(125.62,129.44) --
+	(138.60,125.11) --
+	(151.59,120.93) --
+	(164.57,116.41) --
+	(177.56,112.32) --
+	(190.55,108.15) --
+	(203.53,104.42) --
+	(216.52,100.52) --
+	(229.50, 96.63) --
+	(242.49, 92.83) --
+	(255.47, 89.22) --
+	(268.46, 85.32) --
+	(281.44, 81.88) --
 	(294.43, 68.52);
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,144.57) --
-	( 73.67,143.54) --
-	( 86.66,142.38) --
-	( 99.65,141.07) --
-	(112.63,139.64) --
-	(125.62,138.17) --
-	(138.60,136.55) --
-	(151.59,134.92) --
-	(164.57,133.20) --
-	(177.56,131.42) --
-	(190.55,129.59) --
-	(203.53,127.78) --
-	(216.52,125.83) --
-	(229.50,123.91) --
-	(242.49,121.96) --
-	(255.47,120.00) --
-	(268.46,118.06) --
-	(281.44,116.12) --
-	(294.43,114.08);
+	( 60.69,144.63) --
+	( 73.67,143.62) --
+	( 86.66,142.51) --
+	( 99.65,141.29) --
+	(112.63,139.95) --
+	(125.62,138.54) --
+	(138.60,137.02) --
+	(151.59,135.44) --
+	(164.57,133.82) --
+	(177.56,132.12) --
+	(190.55,130.42) --
+	(203.53,128.69) --
+	(216.52,126.93) --
+	(229.50,125.14) --
+	(242.49,123.36) --
+	(255.47,121.55) --
+	(268.46,119.66) --
+	(281.44,117.85) --
+	(294.43,115.82);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,144.29) --
-	( 73.67,142.96) --
-	( 86.66,141.49) --
-	( 99.65,139.85) --
-	(112.63,138.10) --
-	(125.62,136.23) --
-	(138.60,134.24) --
-	(151.59,132.15) --
-	(164.57,129.99) --
-	(177.56,127.79) --
-	(190.55,125.59) --
-	(203.53,123.36) --
-	(216.52,121.03) --
-	(229.50,118.72) --
-	(242.49,116.41) --
-	(255.47,114.18) --
-	(268.46,111.87) --
-	(281.44,109.56) --
-	(294.43,106.98);
+	( 60.69,144.30) --
+	( 73.67,142.91) --
+	( 86.66,141.47) --
+	( 99.65,139.90) --
+	(112.63,138.18) --
+	(125.62,136.39) --
+	(138.60,134.49) --
+	(151.59,132.46) --
+	(164.57,130.47) --
+	(177.56,128.40) --
+	(190.55,126.28) --
+	(203.53,124.07) --
+	(216.52,121.82) --
+	(229.50,119.52) --
+	(242.49,117.32) --
+	(255.47,115.08) --
+	(268.46,112.76) --
+	(281.44,110.61) --
+	(294.43,108.08);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,142.74) --
-	( 73.67,139.90) --
-	( 86.66,136.92) --
-	( 99.65,133.75) --
-	(112.63,130.48) --
-	(125.62,127.33) --
-	(138.60,124.04) --
-	(151.59,120.82) --
-	(164.57,117.55) --
-	(177.56,114.24) --
-	(190.55,110.90) --
-	(203.53,107.74) --
-	(216.52,104.39) --
-	(229.50,101.12) --
-	(242.49, 97.80) --
-	(255.47, 94.60) --
-	(268.46, 91.44) --
-	(281.44, 88.64) --
-	(294.43, 85.98);
+	( 60.69,142.91) --
+	( 73.67,140.14) --
+	( 86.66,137.29) --
+	( 99.65,134.33) --
+	(112.63,131.21) --
+	(125.62,128.19) --
+	(138.60,125.06) --
+	(151.59,121.93) --
+	(164.57,118.81) --
+	(177.56,115.61) --
+	(190.55,112.47) --
+	(203.53,109.42) --
+	(216.52,106.36) --
+	(229.50,103.27) --
+	(242.49,100.21) --
+	(255.47, 97.22) --
+	(268.46, 94.11) --
+	(281.44, 91.46) --
+	(294.43, 88.80);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 47.70,145.51) --
-	( 60.69,141.92) --
-	( 73.67,138.26) --
-	( 86.66,134.46) --
-	( 99.65,130.50) --
-	(112.63,126.48) --
-	(125.62,122.52) --
-	(138.60,118.48) --
-	(151.59,114.40) --
-	(164.57,110.31) --
-	(177.56,106.24) --
-	(190.55,102.24) --
-	(203.53, 98.39) --
-	(216.52, 94.42) --
-	(229.50, 90.53) --
-	(242.49, 86.65) --
-	(255.47, 83.04) --
-	(268.46, 79.32) --
-	(281.44, 76.03) --
-	(294.43, 72.72);
+	( 60.69,141.95) --
+	( 73.67,138.09) --
+	( 86.66,134.39) --
+	( 99.65,130.57) --
+	(112.63,126.61) --
+	(125.62,122.77) --
+	(138.60,118.86) --
+	(151.59,114.84) --
+	(164.57,111.04) --
+	(177.56,107.14) --
+	(190.55,103.26) --
+	(203.53, 99.39) --
+	(216.52, 95.50) --
+	(229.50, 91.58) --
+	(242.49, 87.85) --
+	(255.47, 84.17) --
+	(268.46, 80.40) --
+	(281.44, 77.31) --
+	(294.43, 74.04);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 2};
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 3};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 63.65) {0.85};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 65.38) {0.85};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 90.02) {0.90};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42, 91.17) {0.90};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.39) {0.95};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 30.42,116.97) {0.95};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 66.41) --
-	( 35.37, 66.41);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 68.14) --
+	( 35.37, 68.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 92.78) --
-	( 35.37, 92.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62, 93.93) --
+	( 35.37, 93.93);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.15) --
-	( 35.37,119.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.62,119.72) --
+	( 35.37,119.72);
 

### 2022-03-04 reports/resources/sensitivity/results_4.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:11
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

\setmainfont{Arial}

\usepackage[italic]{mathastext}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,154.86);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,154.86);
\end{scope}
\begin{scope}
\path[clip] ( 31.37, 64.67) rectangle (306.77,149.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37, 64.67) rectangle (306.77,149.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 80.00) --
	(306.77, 80.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,106.20) --
	(306.77,106.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,132.41) --
	(306.77,132.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65, 64.67) --
	( 63.65,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54, 64.67) --
	(129.54,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42, 64.67) --
	(195.42,149.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31, 64.67) --
	(261.31,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 66.89) --
	(306.77, 66.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 93.10) --
	(306.77, 93.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,119.31) --
	(306.77,119.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,145.51) --
	(306.77,145.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 64.67) --
	( 96.59,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 64.67) --
	(162.48,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 64.67) --
	(228.36,149.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 64.67) --
	(294.25,149.36);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,143.49) --
	( 96.59,140.57) --
	(109.77,137.23) --
	(122.95,133.27) --
	(136.12,129.51) --
	(149.30,125.52) --
	(162.48,121.59) --
	(175.66,117.80) --
	(188.83,114.25) --
	(202.01,110.67) --
	(215.19,107.17) --
	(228.36,103.96) --
	(241.54,100.79) --
	(254.72, 97.64) --
	(267.89, 94.55) --
	(281.07, 91.40) --
	(294.25, 80.10);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,142.63) --
	( 96.59,138.32) --
	(109.77,133.82) --
	(122.95,129.13) --
	(136.12,124.48) --
	(149.30,119.85) --
	(162.48,115.26) --
	(175.66,111.18) --
	(188.83,106.60) --
	(202.01,102.51) --
	(215.19, 98.38) --
	(228.36, 94.47) --
	(241.54, 90.74) --
	(254.72, 87.33) --
	(267.89, 83.84) --
	(281.07, 80.65) --
	(294.25, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.56) --
	( 70.24,143.42) --
	( 83.42,142.10) --
	( 96.59,140.63) --
	(109.77,139.04) --
	(122.95,137.37) --
	(136.12,135.58) --
	(149.30,133.73) --
	(162.48,131.83) --
	(175.66,129.90) --
	(188.83,127.94) --
	(202.01,125.96) --
	(215.19,123.92) --
	(228.36,121.90) --
	(241.54,119.88) --
	(254.72,117.90) --
	(267.89,115.87) --
	(281.07,113.88) --
	(294.25,111.68);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.12) --
	( 70.24,142.58) --
	( 83.42,140.92) --
	( 96.59,139.08) --
	(109.77,137.15) --
	(122.95,135.15) --
	(136.12,133.02) --
	(149.30,130.80) --
	(162.48,128.55) --
	(175.66,126.21) --
	(188.83,123.90) --
	(202.01,121.53) --
	(215.19,119.13) --
	(228.36,116.72) --
	(241.54,114.27) --
	(254.72,111.80) --
	(267.89,109.40) --
	(281.07,107.01) --
	(294.25,104.48);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,142.70) --
	( 70.24,139.57) --
	( 83.42,136.17) --
	( 96.59,132.62) --
	(109.77,128.96) --
	(122.95,125.41) --
	(136.12,121.76) --
	(149.30,118.12) --
	(162.48,114.51) --
	(175.66,110.94) --
	(188.83,107.40) --
	(202.01,104.01) --
	(215.19,100.57) --
	(228.36, 97.20) --
	(241.54, 93.86) --
	(254.72, 90.72) --
	(267.89, 87.55) --
	(281.07, 84.81) --
	(294.25, 82.11);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,141.43) --
	( 70.24,137.18) --
	( 83.42,132.92) --
	( 96.59,128.48) --
	(109.77,124.05) --
	(122.95,119.80) --
	(136.12,115.50) --
	(149.30,111.19) --
	(162.48,106.97) --
	(175.66,102.71) --
	(188.83, 98.60) --
	(202.01, 94.62) --
	(215.19, 90.64) --
	(228.36, 86.73) --
	(241.54, 82.78) --
	(254.72, 78.97) --
	(267.89, 75.29) --
	(281.07, 72.11) --
	(294.25, 69.11);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37, 64.67) rectangle (306.77,149.36);
\end{scope}
\begin{scope}
\path[clip] (306.77, 64.67) rectangle (319.71,149.36);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (306.77, 64.67) rectangle (319.71,149.36);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59, 61.92) --
	( 96.59, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48, 61.92) --
	(162.48, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36, 61.92) --
	(228.36, 64.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25, 61.92) --
	(294.25, 64.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 96.59, 54.21) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (162.48, 54.21) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (228.36, 54.21) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (294.25, 54.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 64.14) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 90.34) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,116.55) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,142.76) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 66.89) --
	( 31.37, 66.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 93.10) --
	( 31.37, 93.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,119.31) --
	( 31.37,119.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,145.51) --
	( 31.37,145.51);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (169.07, 43.70) {Years since hire};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 11.70,107.02) {Cancer-free survival};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 19.60,  5.50) rectangle (142.67, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.60, 11.00) rectangle ( 45.05, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.05, 18.23) -- ( 43.61, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 86.63, 11.00) rectangle (101.09, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.08, 18.23) -- ( 99.64, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 50.55, 15.13) {Rule $a_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (106.59, 15.13) {Rule $a_1$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (153.67,  5.50) rectangle (318.53, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.67, 11.00) rectangle (179.12, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.11, 18.23) -- (177.68, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (212.89, 11.00) rectangle (227.34, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (214.34, 18.23) -- (225.90, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (262.84, 11.00) rectangle (277.29, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (264.28, 18.23) -- (275.85, 18.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (184.62, 15.13) {Truth};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (232.84, 15.13) {WKM};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (282.79, 15.13) {AWKM};
\end{scope}
\end{tikzpicture}

\end{document}

### 2022-03-04 reports/resources/sensitivity/results_5.tex
SER

--- 2022-03-04 reports/resources/sensitivity/results_4.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:11
+% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:12
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 80.00) --
-	(306.77, 80.00);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 83.54) --
+	(306.77, 83.54);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,106.20) --
-	(306.77,106.20);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,108.33) --
+	(306.77,108.33);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,132.41) --
-	(306.77,132.41);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,133.12) --
+	(306.77,133.12);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 66.89) --
-	(306.77, 66.89);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 71.14) --
+	(306.77, 71.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 93.10) --
-	(306.77, 93.10);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 95.93) --
+	(306.77, 95.93);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,119.31) --
-	(306.77,119.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,120.72) --
+	(306.77,120.72);
 
@@
 	( 70.24,145.51) --
-	( 83.42,143.49) --
-	( 96.59,140.57) --
-	(109.77,137.23) --
-	(122.95,133.27) --
-	(136.12,129.51) --
-	(149.30,125.52) --
-	(162.48,121.59) --
-	(175.66,117.80) --
-	(188.83,114.25) --
-	(202.01,110.67) --
-	(215.19,107.17) --
-	(228.36,103.96) --
-	(241.54,100.79) --
-	(254.72, 97.64) --
-	(267.89, 94.55) --
-	(281.07, 91.40) --
-	(294.25, 80.10);
+	( 83.42,142.49) --
+	( 96.59,139.06) --
+	(109.77,135.47) --
+	(122.95,131.49) --
+	(136.12,127.87) --
+	(149.30,124.21) --
+	(162.48,120.53) --
+	(175.66,116.85) --
+	(188.83,113.27) --
+	(202.01,109.91) --
+	(215.19,106.65) --
+	(228.36,103.65) --
+	(241.54,100.68) --
+	(254.72, 97.77) --
+	(267.89, 95.03) --
+	(281.07, 92.51) --
+	(294.25, 82.50);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 	( 70.24,145.51) --
-	( 83.42,142.63) --
-	( 96.59,138.32) --
-	(109.77,133.82) --
-	(122.95,129.13) --
-	(136.12,124.48) --
-	(149.30,119.85) --
-	(162.48,115.26) --
-	(175.66,111.18) --
-	(188.83,106.60) --
-	(202.01,102.51) --
-	(215.19, 98.38) --
-	(228.36, 94.47) --
-	(241.54, 90.74) --
-	(254.72, 87.33) --
-	(267.89, 83.84) --
-	(281.07, 80.65) --
+	( 83.42,141.84) --
+	( 96.59,136.64) --
+	(109.77,131.45) --
+	(122.95,126.66) --
+	(136.12,121.76) --
+	(149.30,117.09) --
+	(162.48,112.64) --
+	(175.66,108.28) --
+	(188.83,104.06) --
+	(202.01,100.30) --
+	(215.19, 96.48) --
+	(228.36, 92.84) --
+	(241.54, 89.48) --
+	(254.72, 86.14) --
+	(267.89, 82.83) --
+	(281.07, 79.97) --
 	(294.25, 68.52);
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
-	( 57.06,144.56) --
-	( 70.24,143.42) --
-	( 83.42,142.10) --
-	( 96.59,140.63) --
-	(109.77,139.04) --
-	(122.95,137.37) --
-	(136.12,135.58) --
+	( 57.06,144.38) --
+	( 70.24,143.15) --
+	( 83.42,141.79) --
+	( 96.59,140.33) --
+	(109.77,138.79) --
+	(122.95,137.19) --
+	(136.12,135.49) --
 	(149.30,133.73) --
-	(162.48,131.83) --
-	(175.66,129.90) --
-	(188.83,127.94) --
-	(202.01,125.96) --
-	(215.19,123.92) --
-	(228.36,121.90) --
-	(241.54,119.88) --
-	(254.72,117.90) --
-	(267.89,115.87) --
-	(281.07,113.88) --
-	(294.25,111.68);
+	(162.48,131.91) --
+	(175.66,130.09) --
+	(188.83,128.22) --
+	(202.01,126.36) --
+	(215.19,124.44) --
+	(228.36,122.53) --
+	(241.54,120.63) --
+	(254.72,118.77) --
+	(267.89,116.86) --
+	(281.07,114.98) --
+	(294.25,112.91);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
-	( 57.06,144.12) --
-	( 70.24,142.58) --
-	( 83.42,140.92) --
-	( 96.59,139.08) --
-	(109.77,137.15) --
-	(122.95,135.15) --
-	(136.12,133.02) --
-	(149.30,130.80) --
-	(162.48,128.55) --
-	(175.66,126.21) --
-	(188.83,123.90) --
-	(202.01,121.53) --
-	(215.19,119.13) --
-	(228.36,116.72) --
-	(241.54,114.27) --
-	(254.72,111.80) --
-	(267.89,109.40) --
-	(281.07,107.01) --
-	(294.25,104.48);
+	( 57.06,144.03) --
+	( 70.24,142.40) --
+	( 83.42,140.72) --
+	( 96.59,138.93) --
+	(109.77,137.05) --
+	(122.95,135.11) --
+	(136.12,133.07) --
+	(149.30,130.97) --
+	(162.48,128.83) --
+	(175.66,126.65) --
+	(188.83,124.48) --
+	(202.01,122.31) --
+	(215.19,120.05) --
+	(228.36,117.82) --
+	(241.54,115.62) --
+	(254.72,113.48) --
+	(267.89,111.31) --
+	(281.07,109.20) --
+	(294.25,106.87);
 \definecolor{drawColor}{RGB}{248,118,109}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
-	( 57.06,142.70) --
-	( 70.24,139.57) --
-	( 83.42,136.17) --
-	( 96.59,132.62) --
-	(109.77,128.96) --
-	(122.95,125.41) --
-	(136.12,121.76) --
-	(149.30,118.12) --
-	(162.48,114.51) --
-	(175.66,110.94) --
-	(188.83,107.40) --
-	(202.01,104.01) --
-	(215.19,100.57) --
-	(228.36, 97.20) --
-	(241.54, 93.86) --
-	(254.72, 90.72) --
-	(267.89, 87.55) --
-	(281.07, 84.81) --
-	(294.25, 82.11);
+	( 57.06,142.18) --
+	( 70.24,138.80) --
+	( 83.42,135.29) --
+	( 96.59,131.77) --
+	(109.77,128.23) --
+	(122.95,124.82) --
+	(136.12,121.35) --
+	(149.30,117.91) --
+	(162.48,114.48) --
+	(175.66,111.10) --
+	(188.83,107.75) --
+	(202.01,104.56) --
+	(215.19,101.34) --
+	(228.36, 98.18) --
+	(241.54, 95.05) --
+	(254.72, 92.12) --
+	(267.89, 89.13) --
+	(281.07, 86.56) --
+	(294.25, 84.04);
 \definecolor{drawColor}{RGB}{0,191,196}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
-	( 57.06,141.43) --
-	( 70.24,137.18) --
-	( 83.42,132.92) --
-	( 96.59,128.48) --
-	(109.77,124.05) --
-	(122.95,119.80) --
-	(136.12,115.50) --
-	(149.30,111.19) --
-	(162.48,106.97) --
-	(175.66,102.71) --
-	(188.83, 98.60) --
-	(202.01, 94.62) --
-	(215.19, 90.64) --
-	(228.36, 86.73) --
-	(241.54, 82.78) --
-	(254.72, 78.97) --
-	(267.89, 75.29) --
-	(281.07, 72.11) --
-	(294.25, 69.11);
+	( 57.06,141.16) --
+	( 70.24,136.67) --
+	( 83.42,132.34) --
+	( 96.59,128.02) --
+	(109.77,123.71) --
+	(122.95,119.58) --
+	(136.12,115.46) --
+	(149.30,111.36) --
+	(162.48,107.36) --
+	(175.66,103.38) --
+	(188.83, 99.53) --
+	(202.01, 95.88) --
+	(215.19, 92.16) --
+	(228.36, 88.54) --
+	(241.54, 85.01) --
+	(254.72, 81.71) --
+	(267.89, 78.41) --
+	(281.07, 75.60) --
+	(294.25, 72.85);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 4};
+\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 5};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 64.14) {0.7};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 68.39) {0.7};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 90.34) {0.8};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 93.18) {0.8};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,116.55) {0.9};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,117.97) {0.9};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 66.89) --
-	( 31.37, 66.89);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 71.14) --
+	( 31.37, 71.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 93.10) --
-	( 31.37, 93.10);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 95.93) --
+	( 31.37, 95.93);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,119.31) --
-	( 31.37,119.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,120.72) --
+	( 31.37,120.72);
 

### 2022-03-04 slides.Rmd
SER

---
title: "Estimating survival in left filtered data"
subtitle: "Replication and application of Izano's estimator"
author: "Kevin Chen"
fontsize: 11pt
# mainfont: arial
output:
  beamer_presentation:
    toc: false
    slide_level: 1
    # latex_engine: lualatex
    includes:
      in_header: "~/HeadRs/BeamerHead.sty"
bibliography: "`r path.expand('~/Box Sync/papers/EnvEpi.bib')`"
---

```{r, include=F}
knitr::opts_chunk$set(echo = F, results = "asis", fig.align = "center")
if (!"mytheme" %in% ls()) {
  source("~/headRs/00-my-theme.R")
  library(data.table)
  options(tikzDefaultEngine = 'pdftex')
}
library(tidyverse); library(data.table)
library(here)
```

# Chapter 3 of Izano (2017)

## Drivers of Biased Effect Estimates in Left Filtered Data

- Specified a SEM for "left filtering" in the presence of HWSE
- Simulated large-sample ($n = 10^6$) data once for each of 5 scenarios
- Simulated finite-sample ($n = 50,000$) data 500 times for each scenario
- Applied two estimators:
  - Adjusted Kaplan-Meier
  - Delayed-entry adjusted Kaplan-Meier

# Description of variables

\begin{table}
\begin{center}
\begin{adjustbox}{width=0.85\linewidth}{
\begin{tabular}{lp{0.65\linewidth}}
\toprule
 Variable  &  Description                                 \\ \midrule
 $R$       & Time until start of registry \\
 $W$       & Baseline covariates \\
 $S$       & Susceptibility to effects of metalworking fluid exposure \\
 $H(t)$    & Adverse health status at time $t$ \\
 $N(t)$    & Employment status at time $t$ \\
 $A(t)$    & Metalworking fluid exposure at time $t$ \\
 $D(t)$    & Mortality status at time $t$ \\
 $Y^*(t)$  & Cancer status at time $t$ \\
 $Y(t)$    & Observed Cancer status at time $t$ \\
 $t = \{1, 2, \ldots, 20\}$ & Time, indexed in years after hire \\
 \bottomrule
\end{tabular}
}\end{adjustbox}
\end{center}
\end{table}

# Abbreviated DAG summarizing the causal structure

\begin{figure}
\begin{center}
\begin{adjustbox}{width=\linewidth}{
\begin{tikzpicture}[>= stealth, auto, node distance = 2.25cm, semithick, fill=white, inner sep=0pt]
\tikzstyle{every state}=[shape = circle, align = center, draw = none]
\node[state] (H0) {$H(t - 1)$};
\node[state] (N0) [below right of=H0] {$N(t - 1)$};
\node[state] (A0) [below right of=N0] {$\bar A(t - 1)$};
\node[state] (D0) [below right of=A0] {$D(t - 1)$};
\node[state] (Y0) [below right of=D0] {$Y^*(t - 1)$};
\node[state] (W) [above right of=H0] {$W$};
\node[state] (H) [right of=H0, node distance = 4cm] {$H(t)$};
\node[state] (N) [below right of=H, node distance = 4cm] {$N(t)$};
\node[state] (A) [below right of=N, node distance = 4cm] {$\bar A(t)$};
\node[state] (D) [above right of=N, node distance = 3cm] {$D(t)$};
\node[state] (Y) [above right of=A, node distance = 3cm] {$Y^*(t)$};
\node[state] (S) [above right of=D, node distance = 3cm] {$S$};
%
\path[->] (H0) edge (N0);
\path[->] (N0) edge (A0);
\path[->] (A0) edge [bend right=30] (Y0);
\path[->] (H0) edge (H);
\path[->] (W) edge [bend right=10] (N);
\path[->] (N0) edge (N);
\path[->] (H) edge (N);
\path[->] (A0) edge (N);
\path[->] (W) edge [bend right=15] (A);
\path[->] (A0) edge (A);
\path[->] (N) edge (A);
\path[->] (W) edge (D);
\path[->] (A0) edge [bend left=15] (D);
\path[->] (D0) edge [bend right=15] (D);
\path[->] (Y0) edge [bend right=10] (D);
\path[->] (W) edge [bend left=5] (Y);
\path[->] (S) edge [bend left=30] (Y);
\path[->] (S) edge [bend left=15] (Y0);
\path[->] (H) edge (Y);
\path[->] (A) edge (Y);
\path[->] (D) edge (Y);
\path[->] (Y0) edge (Y);
\end{tikzpicture}
}\end{adjustbox}
\end{center}
\end{figure}

# Scenarios

- Five scenarios represent 5 sets of parameters used to generate data according to the SEM
- Sets 2, 3, 4, and 5 differ from Set 1 by a single parameter each
  - Scenario 2: Greater cancer-related mortality\
  (increase HR from 1.6 to 7.4)
  - Scenario 3: Greater proportion of susceptibles\
  (increase proportion from 10\% to 20\%)
  - Scenario 4: Greater time-varying confounding by history of adverse health\
  (decrease HR of being at work from 0.6 to 0.2 \
  and increase HR of cancer incidence from 2.0 to 5.5)
  - Scenario 5: Greater background incidence\
  (increase baseline log hazard from -7 to -6)

# Target and estimation

- Goal: estimate cancer-free survival indexed by time since hire
  - Under rule where all are exposed while at work
  - Under rule where all are not exposed (ever)
  - Competing risk of death is accounted for by preventing death
- Adjusted KM ie the inverse probability of treatment weighted KM (WKM)
- Delayed-entry adjusted KM ie the Aalen-filtered WKM (AWKM)

# Review of the Kaplan-Meier Estimator

- Let $c(t)$ be the number of cases in the interval $(t - 1, t]$
- Let $r(t)$ be the number of people at risk in interval $(t - 1, t]$
- The standard survival estimator is
$$\widehat {S}(t) =
\begin{cases}
1 & \text{if } t < t_1 \\
\prod_{j \le t} \left(1 - \frac{c(j)}{r(j)}\right) & \text{if } t \ge t_1 \\
\end{cases}$$
where $t_1$ is the first event time
- Restricting to followers of rule $a$, we have \vspace{-0.5\baselineskip}
$$c_a(t), \hspace{1em} r_a(t), \hspace{1em} \widehat{S}_a(t)$$

# Mathematical expression of $c_a(t)$ and $r_a(t)$

$$\begin{aligned}
c_{a} (t)
& = \sum_i^n \underbrace{\Ind{Y_i(t) = 1}}_{\text{Cancer by time } t}
    \times \underbrace{\Ind{Y_i(t - 1) = 0}}_{\text{At-risk at time } t - 1}
    \times \underbrace{\Ind{\bar A_i (t) = \bar a(t)}}_{\text{Followed rule } a} \\
r_{a} (t)
& = \sum_i^n \underbrace{\Ind{Y_i(t - 1) = 0}}_{\text{At-risk at time } t - 1}
    \times \underbrace{\Ind{\bar A_i (t) = \bar a(t)}}_{\text{Followed rule } a}.
\end{aligned}$$

# Inverse probability of treatment weighted KM (WKM)

The $i$th person at time $t$ is weighted by $w_{i, a}(t)$ the predicted probability of following rule $a$ through time $t$:

\begin{adjustbox}{scale=0.8}\parbox{\linewidth}{
$$\begin{aligned}
c^w_{a} (t)
& = \sum_i^n w_{i, a}(t)
    \times \Ind{Y_i(t) = 1}
    \times \Ind{Y_i(t - 1) = 0}
    \times \Ind{\bar A_i (t) = \bar a(t)} \\
r^w_{a} (t)
& = \sum_i^n  w_{i, a}(t)
    \times \Ind{Y_i(t - 1) = 0}
    \times \Ind{\bar A_i (t) = \bar a(t)}.
\end{aligned}$$}
\end{adjustbox}

The $w_{i, a}$ can be estimated by fitting logistic regressions.

# Aalen-filtered WKM (AWKM)

In addition to weighting, we restrict the computation of the discrete hazard to those under observation:

\begin{adjustbox}{scale=0.8}\parbox{\linewidth}{
$$\begin{aligned}
c_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t) = 1} \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i} \\
r_{a} (t)
& = \sum_i^n w_{i, a}(t) \times \Ind{Y_i(t - 1) = 0} \times \Ind{\bar A_i (t) = \bar a(t)} \times \Ind{t \ge R_i}
\end{aligned}$$
}\end{adjustbox}

# Results from Izano's Dissertation (2017)

\includegraphics[width=\textwidth]{private/izano_2017_result_1}
\includegraphics[width=\textwidth]{private/izano_2017_result_2}

\begin{center}
\begin{tabular}{ll}
Red: Always exposed & Blue: Never exposed
\end{tabular}
\begin{tabular}{lll}
Long dashed: WKM & Dot dashed: AWKM & Solid: True KM curve
\end{tabular}
\end{center}

# Results from Izano's Dissertation (2017)

\includegraphics[width=\textwidth]{private/izano_2017_result_3}
\includegraphics[width=\textwidth]{private/izano_2017_result_4}

\begin{center}
\begin{tabular}{ll}
Red: Always exposed & Blue: Never exposed
\end{tabular}
\begin{tabular}{lll}
Long dashed: WKM & Dot dashed: AWKM & Solid: True KM curve
\end{tabular}
\end{center}

# Results from Izano's Dissertation (2017)

\includegraphics[width=\textwidth]{private/izano_2017_result_5}

\begin{center}
\begin{tabular}{ll}
Red: Always exposed & Blue: Never exposed
\end{tabular}
\begin{tabular}{lll}
Long dashed: WKM & Dot dashed: AWKM & Solid: True KM curve
\end{tabular}
\end{center}

# Replication results

\includegraphics[width=\textwidth]{reports/resources/results_1-2}

# Replication results

\includegraphics[width=\textwidth]{reports/resources/results_3-4}

# Replication results

\includegraphics[width=\textwidth]{reports/resources/results_5}

# Application to UAW-GM

- Study population: Workers from Plants 1 or 2, hired after 1938
- 55-year follow-up starting at hire
- MWF exposure lagged 15 years
- Employment records end in 1994; workers considered administratively censored if they were still at work in 2010 (15 years after1 995)
- Rules of interest
  - Natural course: ever-exposed above reference level (0 mg/m^3^$\cdot$years for straights and synthetics; 0.05 mg/m^3^$\cdot$years for solubles)
  - Never exposed
- Under both rules, no censoring by death

# Application results

\begin{center}
\includegraphics[width=0.95\textwidth]{reports/resources/gm_results}
\end{center}

### 2022-03-04 scripts/01-simulation.R

@@ -12,6 +12,8 @@ sim_param <- readRDS(here::here("resources", "sim_param.rds"))
 rownames(sim_param) <- sim_param[,1]
 sim_param <- sim_param[,-1]
 
+sim_param["beta_0Y",] <- c(rep(-14, 4), -7)
+
 sim_data <- function(
 	scenario = 1,
 	n = 50000,

### 2022-03-04 scripts/02-analysis.R

@@ -98,22 +98,29 @@ get_truth <- function(scenario, a, n = 5e5, R.rdist = function(x) {runif(x, 0, 2
 		Truth = c(rep(1, 20 - length(km$surv)), km$surv)
 		))}
 
-# truth_a0 <- lapply(1:5, get_truth, a = 0, n = 5e4)
-# saveRDS(truth_a0, here("resources", "truth_a0.rds"))
-# truth_a1 <- lapply(1:5, get_truth, a = 1, n = 5e4)
-# saveRDS(truth_a1, here("resources", "truth_a1.rds"))
-# 
-# M <- 250
-# pb <- txtProgressBar(min = 0, max = M, style = 3)
-# message("\nScenario ", scenario, ", a = 0")
-# a0 <- lapply(1:M, function(i) {
-# 	setTxtProgressBar(pb, i)
-# 	return(get_estimates(scenario))})
-# saveRDS(a0, here("resources", paste0("a0_scenario", scenario, ".rds")))
-# 
-# pb <- txtProgressBar(min = 0, max = M, style = 3)
-# message("\nScenario ", scenario, ", a = 1")
-# a1 <- lapply(1:M, function(i) {
-# 	setTxtProgressBar(pb, i)
-# 	return(get_estimates(scenario, a = 1))})
-# saveRDS(a1, here("resources", paste0("a1_scenario", scenario, ".rds")))
+truth_a0 <- lapply(1:5, get_truth, a = 0, n = 5e5)
+saveRDS(truth_a0, here("resources", "truth_a0.rds"))
+truth_a1 <- lapply(1:5, get_truth, a = 1, n = 5e5)
+saveRDS(truth_a1, here("resources", "truth_a1.rds"))
+
+M <- 500
+# scenario <- 1
+# for (scenario in 1:5) {
+	pb <- txtProgressBar(min = 0, max = M, style = 3)
+	message("\nScenario ", scenario, ", a = 0")
+	a0 <- list()
+	for (i in 1:M) {
+		a0[[i]] <- get_estimates(scenario)
+		setTxtProgressBar(pb, i)
+	}
+	saveRDS(a0, here("resources", paste0("a0_scenario", scenario, ".rds")))
+	
+	message("\nScenario ", scenario, ", a = 1")
+	pb <- txtProgressBar(min = 0, max = M, style = 3)
+	a1 <- list()
+	for (i in 1:M) {
[…]

### 2022-03-04 scripts/03-results.R

@@ -24,15 +24,17 @@ eval(parse(text = getURL(
 # devtools::install_github('osofr/stremr')
 library(stremr)
 
-truth_a0 <- readRDS(here("resources", "truth_a0.rds"))
-truth_a1 <- readRDS(here("resources", "truth_a1.rds"))
+results.dir <- "resources"
+
+truth_a0 <- readRDS(here(results.dir, "truth_a0.rds"))
+truth_a1 <- readRDS(here(results.dir, "truth_a1.rds"))
 
 data.frame(truth_a0[[5]][,2],
 					 truth_a1[[5]][,2])
 
 a0 <- rbindlist(
 	lapply(1:5, function(scenario = 1) {
-		melt(rbindlist(readRDS(here("resources", paste0("a0_scenario", scenario, ".rds")))
+		melt(rbindlist(readRDS(here(results.dir, paste0("a0_scenario", scenario, ".rds")))
 		)[,.(WKM = mean(WKM), AWKM = mean(AWKM)), t],
 		measure.vars = c("WKM", "AWKM"),
 		variable.name = "Estimator",
@@ -42,7 +44,7 @@ a0 <- rbindlist(
 )
 a1 <- rbindlist(
 	lapply(1:5, function(scenario) {
-		melt(rbindlist(readRDS(here("resources", paste0("a1_scenario", scenario, ".rds")))
+		melt(rbindlist(readRDS(here(results.dir, paste0("a1_scenario", scenario, ".rds")))
 		)[,.(WKM = mean(WKM), AWKM = mean(AWKM)), t],
 		measure.vars = c("WKM", "AWKM"),
 		variable.name = "Estimator",
@@ -66,10 +68,9 @@ sim_results <- rbindlist(list(
 
 sim_results[,`:=`(
 	scenario = paste0("Scenario ", scenario),
-	rule = paste0("Rule ", c("$a_0$", "$a_1$")[rule])
-	)]
-
-saveRDS(sim_results, here("reports/resources", "sim_results.rds"))
+	rule = paste0(c("Never exposed", "Always exposed while at work")[rule])
+		# paste0("Rule ", c("$a_0$", "$a_1$")[rule])
+)]
 
 sim_results %>% ggplot(aes(
 	x = t, y = Survival, lty = Estimator,
@@ -79,14 +80,20 @@ sim_results %>% ggplot(aes(
 	labs(x = "Years since hire", y = "Cancer-free survival") +
 	mytheme + theme(
 		legend.title = element_blank(),
[…]

### 2022-03-04 scripts/04-application.R

@@ -10,6 +10,10 @@ library(magrittr)
 library(data.table)
 library(survival)
 
+if (!"mwf" %in% ls()) {
+	mwf <- "Straight"
+}
+
 if (!"cohort_analytic" %in% ls()) {
 	library(boxr); box_auth()
 	source(here::here("scripts", "00-hello.R"))
@@ -26,6 +30,7 @@ gm.dt <- cohort_analytic[year >= year(yin) & year < (year(yin) + years_fu) & (
 gm.dt <- gm.dt[plant %in% 1:2]
 # gm.dt <- gm.dt[sex == "M"]
 gm.dt[, `:=`(
+	# canc = canc_lu
 	canc = ifelse(
 		canc_corec == 1 | canc_es == 1 | canc_st == 1, 1,
 		ifelse(canc_corec == 2 | canc_es == 2 | canc_st == 2, 2, 0))
@@ -205,10 +210,25 @@ get_estimates_gm <- function(
 	
 	# Fit PS
 	# message("Fitting PS")
+	
+	require(sl3)
+	lrnr_mean <- Lrnr_mean$new()
+	lrnr_xgb <- Lrnr_xgboost$new(nrounds = 15)
+	lrnr_glm <- Lrnr_glm_fast$new()
+	lrnr_rf <- make_learner(Lrnr_ranger)
+	## Stack the above candidates:
+	lrnr_stack <- Stack$new(lrnr_mean, 
+													lrnr_xgb,
+													lrnr_glm,
+													lrnr_rf)
+	lrnr_sl <- Lrnr_sl$new(learners = lrnr_stack, metalearner = Lrnr_solnp$new())
+	
 	dt.stremr <- fitPropensity(
 		dt.stremr,
 		gform_TRT = g_a,
 		gform_CENS = g_d,
+		models_TRT = lrnr_sl,
+		models_CENS = lrnr_sl,
 		stratify_TRT = stratify,
 		stratify_CENS = stratify,
 	)
@@ -261,7 +281,7 @@ get_estimates_gm <- function(
 # 	geom_step() +
 # 	theme_bw()
 
-# mwf <- "Straight"
+# mwf <- "Synthetic"
 # Point estimate ###
 if ("mwf" %in% ls()) {
 	message("\n", mwf, ", a = 0")
@@ -276,49 +296,49 @@ if ("mwf" %in% ls()) {
 												 mwf = mwf)
 	saveRDS(a1, here("resources", paste0(tolower(mwf), "1_gm", ".rds")))
 	
[…]

### 2022-03-04 scripts/05-application-results.R

@@ -73,9 +73,10 @@ gm_w.tab <- dcast(gm.w[,.(
 gm.surv$rule <- factor(
 	gm.surv$rule,
 	unique(gm.surv$rule),
-	c("Observed exposure", "No exposure")
+	c("As observed", "No exposure")
 )
-gm.surv[mwf == "Straight"] %>% melt(
+
+gm.surv %>% melt(
 	measure.vars = c("WKM", "AWKM"),
 	variable.name = "Estimator",
 	value.name = "Survival"
@@ -84,22 +85,24 @@ gm.surv[mwf == "Straight"] %>% melt(
 	lty = Estimator,
 	color = rule
 )) + geom_step() +
-	# facet_grid(mwf ~ .) +
+	facet_grid(mwf ~ .) +
 	labs(
-		lty = "Estimator",
-		color = "Intervention",
+		lty = element_blank(),
+		color = element_blank(),
+		# lty = "Estimator",
+		# color = "Intervention",
 		y = "Digestive cancer-free survival",
 		x = "Years since hire") +
 	theme_bw() + theme(
 		legend.title = element_text(size = 10),
 		legend.position = 'bottom',
 		legend.margin = margin(l = 0, r = 0, b = 0, t = 0, unit='cm'),
-		legend.box.margin = margin(l = 0, r = 0, b = -0.1, t = -0.1, unit='cm'),
-		legend.box = "vertical"
+		legend.box.margin = margin(l = 0, r = 0, b = -0.1, t = -0.1, unit='cm')
+		# legend.box = "vertical"
 	) -> gm.surv.ggplot
 
 gm.surv.ggplot
-# 
+
 # gm_w.tab[estimator == "WKM"] %>% ggplot(
 # 	aes(x = t,
 # 			y = Median,
@@ -119,11 +122,11 @@ gm.surv.ggplot
 # 
 # gm.w.ggplot
 # 
-tikz(here("reports/resources", "gm_results.tex"),
-		 width = 4, height = 3.5, standAlone = T)
-gm.surv.ggplot
-dev.off()
-lualatex("gm_results\\.tex", here("reports/resources"))
+# tikz(here("reports/resources", "gm_results.tex"),
+# 		 width = 4, height = 3.25, standAlone = T)
+# gm.surv.ggplot
+# dev.off()
+# lualatex("gm_results\\.tex", here("reports/resources"))
 # 
 # 
 # tikz(here("reports/resources", "gm_weights.tex"),

### 2022-03-04 scripts/06-sensitivity.R

@@ -6,35 +6,38 @@
 library(here)
 source(here("scripts", "02-analysis.R"))
 # source(here("scripts", "04-application.R"))
+
+
+# Use observed distribution of time to registry #####
 # time_to_registry <- gm.dt[canc != 2,.(R = c(1973, 1973, 1985)[plant[1]] - yin.gm[1]), studyno]$R
 # saveRDS(time_to_registry, here("resources", "time_to_registry.rds"))
 time_to_registry <- readRDS(here("resources", "time_to_registry.rds"))
 time_to_registry[time_to_registry <= 0] <- 0
-# hist(time_to_registry)
+# hist(time_to_registry, breaks = seq(0, 35, 1))
 # summary(gm.dt[,.(yin.gm[1]), studyno]$V1)
 
-# # Get truth ####
+# # Get truth
 # truth_a0 <- lapply(1:5, get_truth, a = 0, n = 5e4,
 # 									 R.rdist = function(x) {sample(time_to_registry, x, T)})
 # saveRDS(truth_a0, here("resources/sensitivity", "truth_a0.rds"))
 # truth_a1 <- lapply(1:5, get_truth, a = 1, n = 5e4,
 # 									 R.rdist = function(x) {sample(time_to_registry, x, T)})
 # saveRDS(truth_a1, here("resources/sensitivity", "truth_a1.rds"))
-
-# Get simulation results ####
-M <- 250
-pb <- txtProgressBar(min = 0, max = M, style = 3)
-message("\nScenario ", scenario, ", a = 0")
-a0 <- lapply(1:M, function(i) {
-	setTxtProgressBar(pb, i)
-	return(get_estimates(scenario,
-									 R.rdist = function(x) {sample(time_to_registry, x, T)}))})
-saveRDS(a0, here("resources/sensitivity", paste0("a0_scenario", scenario, ".rds")))
-
-pb <- txtProgressBar(min = 0, max = M, style = 3)
-message("\nScenario ", scenario, ", a = 1")
-a1 <- lapply(1:M, function(i) {
-	setTxtProgressBar(pb, i)
-	return(get_estimates(scenario, a = 1,
-									 R.rdist = function(x) {sample(time_to_registry, x, T)}))})
-saveRDS(a1, here("resources/sensitivity", paste0("a1_scenario", scenario, ".rds")))
+# 
+# # Get simulation results
+# M <- 250
[…]
